### 2019-02-10 paper/pyg4ometry.tex
Start of paper

%% This template can be used to write a paper for
%% Computer Physics Communications using LaTeX.
%% For authors who want to write a computer program description,
%% an example Program Summary is included that only has to be
%% completed and which will give the correct layout in the
%% preprint and the journal.
%% The `elsarticle' style is used and more information on this style
%% can be found at 
%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
%%
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

%% This list environment is used for the references in the
%% Program Summary
%%
\newcounter{bla}
\newenvironment{refnummer}{%
\list{[\arabic{bla}]}%
{\usecounter{bla}%
 \setlength{\itemindent}{0pt}%
 \setlength{\topsep}{0pt}%
 \setlength{\itemsep}{0pt}%
 \setlength{\labelsep}{2pt}%
 \setlength{\listparindent}{0pt}%
 \settowidth{\labelwidth}{[9]}%
 \setlength{\leftmargin}{\labelwidth}%
 \addtolength{\leftmargin}{\labelsep}%
 \setlength{\rightmargin}{0pt}}}
 {\endlist}

\journal{Computer Physics Communications}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{{\em pyg4ometry}, a python library for the creation of Monte Carlo particle transport geometries}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[a]{Stewart T. Boogert\corref{author}}
\author[a]{Andrey Abramov}
\author[a]{Laurence Nevay}

\cortext[author] {Corresponding author.\\\textit{E-mail address:} stewart.boogert@rhul.ac.uk}
\address[a]{First Address}
\address[b]{Second Address}

\begin{abstract}
%% Text of abstract

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
keyword1; keyword2; keyword3; etc.

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.

{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
  %Delete as appropriate.

\begin{small}
\noindent
{\em Program Title: pyg4ometry }                                         \\
{\em Licensing provisions(please choose one): CC0 1.0/CC By 4.0/MIT/Apache-2.0/BSD 3-clause/BSD 2-clause/GPLv3/GPLv2/LGPL/CC BY NC 3.0/MPL-2.0 }                                   \\
{\em Programming language: python, C/C++}                                   \\

{\em Supplementary material:}                                 \\
  % Fill in if necessary, otherwise leave out.
{\em Journal reference of previous version:}                  \\
  %Only required for a New Version summary, otherwise leave out.
{\em Does the new version supersede the previous version?:}   \\
  %Only required for a New Version summary, otherwise leave out.
{\em Reasons for the new version:}\\
  %Only required for a New Version summary, otherwise leave out.
{\em Summary of revisions:}*\\
  %Only required for a New Version summary, otherwise leave out.

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo particle transport codes is a time consuming and error prone task.  
{\em Solution method(approx. 50-250 words):}\\
  %Describe the method solution here.
{\em Additional comments including Restrictions and Unusual features (approx. 50-250 words):}\\
  %Provide any additional comments here.
   \\

\begin{thebibliography}{0}
\bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
\bibitem{2}Reference 2         % Program Summary section.   
\bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
                               % This list is different from the bibliography at the end of 
                               % the Long Write-Up.
\end{thebibliography}
* Items marked with an asterisk are only required for new versions
of programs previously published in the CPC Program Library.\\
\end{small}

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
include MCMP, FLUKA, Geant3 and Geant4. Each code either has a particular specialism or target user community.  A fundamental requirement of 
all of the codes is to supply a computer readable description of the physical geometry that the particles are passing through.  The creation of geometry 
files is typically a very time consuming activity, the simulation validity and performance is directly dependent on the quality of the geometry. The requirement of a 
geometry system that allows the conversion between files prepared for different codes will enable cross checks of the physics processes in particle 
transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted design (CAD) files exist for systems which 
need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not amenable for PT programmes.  For 
these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop geometry files, convert between 
common PT programme geometry formats and finally import CAD models. This paper describes such geometry creation and conversion package 
called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry description. The main features of  {\em pyg4ometry} 
are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats 
(STEP and XXX) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK.

\section{Geometric descriptions} \label{sec:geometric}

\subsection{Constructive solid geometry (CSG)}
Constructive solid geometry uses boolean operations to model complex surfaces which represent a solid. Typically simple finite or infinite solids are combined 
with operations, such as union, intersection and difference to model more complex solids. FLUKA uses CSG to model solids.

\subsection{Boundary representation (BREP)}
Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices.

\subsection{Tessellated polygons}
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL.

\subsection{Geant4 geometery}
Geant4 geometry description is a mixture of BREP and CSG concepts. Geant4 includes XX fundamental solids, although it does not store a sense of topology
present in traditional CAD BREP systems. Geant4 also provides the ability to perform boolean operations on these primitive solids.

\section{{\em pyg4ometry} design and layout}
The core of {\em pyg4ometry} consists of python classes that wrap Geant4 solid, logical and physical volume objects.

\section{Rapid geometry modelling in Python}

\section{Conversion to Geant4 from common CAD formats}

\section{Conversion between Geant4 and FLUKA}

\section{Performance in Geant4}

\section{Conclusions}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

\bibliographystyle{elsarticle-num}
\bibliography{<your-bib-database>}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use elsarticle-num.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file

### 2019-02-14 paper/pyg4ometry.tex

@@
 %%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
+%%   compress - compres ses without sorting
 %%
@@
 \section{Geometric descriptions} \label{sec:geometric}
+Central to description of a geometric description of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
+geometry and these are described briefly in the following sections.
 
@@
 \subsection{Boundary representation (BREP)}
-Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices.
+Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current PT applications use native 
+file formats employed by CAD systems. The conversion of CAD BREP formats for loading in PT applications is typically performed via a tessellated format.
 
 \subsection{Tessellated polygons}
-Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL.
+Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and more 
+modern variants being PLY, OBJ, etc.
 
 \subsection{Geant4 geometery}
-Geant4 geometry description is a mixture of BREP and CSG concepts. Geant4 includes XX fundamental solids, although it does not store a sense of topology
-present in traditional CAD BREP systems. Geant4 also provides the ability to perform boolean operations on these primitive solids.
+Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes XX fundamental solids, although it does not store a sense 
+of topology present in traditional CAD BREP systems. One of the fundamental solids is a {\em TessellatedSolid} which can used to represent STL or PLY files. 
+Geant4 also provides the ability to perform boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
+Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\it Logical Volumes} 
+and {\it Physical Volumes}. A Logical Volume is a volume that has an outer solid but also material, magnetic field and zero or more physical {\it daughter} volumes. A Physical 
+Volume is a placement (or instance) of a Logical Volume.
 
@@
 
-\section{Rapid geometry modelling in Python}
+\section{Rapid geometry modelling}
 
-\section{Conversion to Geant4 from common CAD formats}
+\section{CAD to Geant4 conversion }
 
-\section{Conversion between Geant4 and FLUKA}
+\section{Geant4 and FLUKA conversion}
 

### 2019-02-18 paper/pyg4ometry.tex
Removed 1st year tutorial chat
Filled out all sections

@@
 \author[a]{Laurence Nevay}
+\author[a]{William Shields}
 
 \cortext[author] {Corresponding author.\\\textit{E-mail address:} stewart.boogert@rhul.ac.uk}
-\address[a]{First Address}
-\address[b]{Second Address}
+\address[a]{John Adams Institute at Royal Holloway, Department of Physics, Royal Holloway, Egham, TW20 0EX, Surrey, UK}
 
 \begin{abstract}
-%% Text of abstract
-
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-keyword1; keyword2; keyword3; etc.
+Geant; Monte Carlo; Particle; Transport; Geometry;
 
@@
 {\em Program Title: pyg4ometry }                                         \\
-{\em Licensing provisions(please choose one): CC0 1.0/CC By 4.0/MIT/Apache-2.0/BSD 3-clause/BSD 2-clause/GPLv3/GPLv2/LGPL/CC BY NC 3.0/MPL-2.0 }                                   \\
+{\em Licensing provisions(please choose one): GPLv3 }                                   \\
 {\em Programming language: python, C/C++}                                   \\
@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo particle transport codes is a time consuming and error prone task.  
+Creating computer readable geometry descriptions for Monte Carlo particle transport codes is a time consuming and error prone task.  \\
 {\em Solution method(approx. 50-250 words):}\\
@@
 There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
-include MCMP, FLUKA, Geant3 and Geant4. Each code either has a particular specialism or target user community.  A fundamental requirement of 
-all of the codes is to supply a computer readable description of the physical geometry that the particles are passing through.  The creation of geometry 
-files is typically a very time consuming activity, the simulation validity and performance is directly dependent on the quality of the geometry. The requirement of a 
-geometry system that allows the conversion between files prepared for different codes will enable cross checks of the physics processes in particle 
-transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted design (CAD) files exist for systems which 
-need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not amenable for PT programmes.  For 
-these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop geometry files, convert between 
+include MCMP, FLUKA, Geant3 and Geant4. Each code either has a particular specialism or target user community.  PT Monte Carlo simulations have 
+diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy, space radiation environment simulation 
+are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that the particles 
+are passing through.  The creation of geometry files is typically a very time consuming activity, the simulation validity and performance is directly dependent 
+on the quality of the geometry. The requirement of a  geometry system that allows the conversion between files prepared for different codes will enable cross 
+checks of the physics processes in particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted design (CAD) 
+files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not amenable for PT 
+programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop geometry files, convert between 
 common PT programme geometry formats and finally import CAD models. This paper describes such geometry creation and conversion package 
@@
 
+\subsection{Geant Detector Mark-up Language} 
+To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
+used as an exchange format for Geant4 geometries. 
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|} \hline
+GDML tag 		&  Child tags				& pyg4ometry class 			\\ \hline
+Defines 			&						&						\\
+Solids 			&						&						\\
+Materials 			&						&						\\
+Structure			&						&						\\ \hline
+\end{tabular}
+\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
+\end{table}
+
 \section{{\em pyg4ometry} design and layout}
-The core of {\em pyg4ometry} consists of python classes that wrap Geant4 solid, logical and physical volume objects.
+The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters material classes.
+The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
+a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
+should be able to start creating geometry in pyg4ometry immediately.
+
+\subsection{Expression engine}
+In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
+In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR. GDML allows for the definition and assignment of 
+variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc. 
+The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally all classes use GDML expressions and not floating point numbers. 
+Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of solid parameters and placements. This allows a user to update variables whilst
+defining geometry and the expression engine will update all internal values.
+
+\subsection{Tessellation engine}
+For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
+geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
+on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
+TetGEN can be employed to give the meshes more desirable output.
+
+\subsection{Visualisation}
+A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene tree is required as the Geant4 volume hierarchy is sufficient 
+to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
+color, surface or wireframe representation and visibility.
+
+\subsection{Internal data representation} 
+The internal data representation follows closely the structure of GDML. A registry class aggregates python ordered dictionaries that are  used to store the main 
+elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
+
+\subsection{Input and output} 
+For each input format available in {\it pyg4ometry} a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
+and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and
 
 \section{Rapid geometry modelling}
+Given the python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the PT problem, vary 
+the parameters of the geometry and visualise the geometry. Finally when the desired result without geometry overlaps is finalised a GDML file can be output
+from the internal memory representation.
 
 \section{CAD to Geant4 conversion }
+STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
+is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
+collection of part features.
 
 \section{Geant4 and FLUKA conversion}
+FLUKA geometry is based upon a limited set of primitive volumes which can be combined using logical operations. Many FLUKA primitives are infinite in extent, so 
+to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table XXX shows the mapping between FLUKA and Geant4 objects.
 
-\section{Performance in Geant4}
+\section{Performance of converted geometry in Geant4}
+Clearly for Geant4 geometry defined in {\it pyg4ometry} the performance is exactly the same as it the geometry was specified in C++ and linked against the Geant4
+libraries. A comparison of the performance of converted CAD or FLUKA geometry compared with native Geant4 solids is required so a user can optimise the available
+computing resources against the human resources (required to convert geometry).
 
 \section{Conclusions}
+The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in particle transport Monte Carlo programmes will save significant 
+amounts of user effort and ultimately yield more accurate simulations. {\it pyg4ometry} is a relatively complete implementation of a geometry creation tool, whilst heavily 
+internally based on Geant4 and GDML can have utility for users of all PT codes. {\it pyg4ometry} can clearly be extended to other formats or applications. As for applications,
+examples include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble  dark matter detectors and geometries for event visualisation.
 

### 2019-02-18 paper/pyg4ometry.tex
Filling out each section

@@
 are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats 
-(STEP and XXX) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK.
+(STEP and IGES) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK.
 
@@
 used as an exchange format for Geant4 geometries. 
-\begin{table}
+\begin{table}[hbt!]
 \centering
@@
 \section{{\em pyg4ometry} design and layout}
-The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters material classes.
+The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
 The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
 a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in pyg4ometry immediately.
+should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
 
@@
 
-\subsection{Visualisation}
-A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene tree is required as the Geant4 volume hierarchy is sufficient 
-to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
-color, surface or wireframe representation and visibility.
-
 \subsection{Internal data representation} 
@@
 For each input format available in {\it pyg4ometry} a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
-and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and
+and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a registry which can be used or manipulated by the user. 
+Output consists of taking the registry and writing the appropriate GDML.
+
+\subsection{Overlap detection}
+All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when encountering such a 
+situation.  A key feature of {\it pyg4ometry} is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
+and determining if the resulting mesh is empty.
+
+\subsection{Visualisation}
+A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
+to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
+color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove
+the potential overlaps. This is dependent on the accuracy of the mesh generated and is a particular problem with meshes based on curved surfaces.
 
@@
 examples include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble  dark matter detectors and geometries for event visualisation. 
+Although not implemented in the current version, a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 application.
 

### 2019-02-19 paper/pyg4ometry.tex
Example of rapid modelling for paper

@@
 %%
-\documentclass[preprint,12pt]{elsarticle}
+%% \documentclass[preprint,12pt]{elsarticle}
 
@@
 %% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%\documentclass[final,3p,times,twocolumn]{elsarticle}
 %% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[final,5p,times,twocolumn]{elsarticle}
 
@@
 \usepackage{amssymb}
+\usepackage{fancyvrb}
 %% The amsthm package provides extended theorem environments
@@
 
-\title{{\em pyg4ometry}, a python library for the creation of Monte Carlo particle transport geometries}
+\title{pyg4ometry: a python library for the creation of Monte Carlo particle transport geometries}
 
@@
 
+{\small
+\begin{verbatim}
+import pyg4ometry.gdml as gd
+import pyg4ometry.geant4 as g4
+import pyg4ometry.visualisation as vi
+
+# create empty data storage structure
+reg = g4.Registry()
+
+# expressions 
+wx = gd.Constant("wx","100",reg)
+wy = gd.Constant("wy","100",reg)
+wz = gd.Constant("wz","100",reg)
+
+bx = gd.Constant("wx","10",reg)
+by = gd.Constant("wy","10",reg)
+bz = gd.Constant("wz","10",reg)
+
+# materials
+bm = g4.Material("G4_Galactic") 
+wm = g4.Material("G4_Iron")
+
+# solids
+wb = g4.solid.Box("wb",wx,wy,wz,reg)
+b  = g4.solid.Box("b",bx,by,bz)
+
+# structure 
+wl = g4.LogicalVolume(wb, wm, "wl", reg)
+bl = g4.LogicalVolume(b, bm, "b", reg)
+bp1 = g4.PhysicalVolume([0,0,0],[0,0,0], 
+                        bl, "b_pv1", wl) 
+bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
+                        bl, "b_pv2", wl)  
+bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0], 
+                        bl, "b_pv3", wl)
+
+# gdml output
+w = gd.Writer()
+w.write(reg,"output.gdml")
+
+# visualisation 
+v = vi.VtkViewer()
+v.addLogicalVolume(wl)
+v.view()
+\end{verbatim}
+}
+
 \section{CAD to Geant4 conversion }

### 2019-02-19 paper/diagrams/rapidModelling.py

@@ -1,0 +1,41 @@
+import pyg4ometry.gdml as gd
+import pyg4ometry.geant4 as g4
+import pyg4ometry.visualisation as vi
+
+# create empty data storage structure
+reg = g4.Registry()
+
+# expressions
+wx = gd.Constant("wx","100",reg)
+wy = gd.Constant("wy","100",reg)
+wz = gd.Constant("wz","100",reg)
+bx = gd.Constant("bx","10",reg)
+by = gd.Constant("by","10",reg)
+bz = gd.Constant("bz","10",reg)
+
+# materials
+bm = g4.Material.nist("G4_Galactic")
+wm = g4.Material.nist("G4_Fe")
+
+# solids
+wb = g4.solid.Box("wb",wx,wy,wz,reg)
+b  = g4.solid.Box("b",bx,by,bz,reg)
+
+# structure
+wl = g4.LogicalVolume(wb, wm, "wl", reg)
+bl = g4.LogicalVolume(b, bm, "b", reg)
+bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],
+                        bl, "b_pv1", wl, [1,1,1], reg)
+bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0],
+                        bl, "b_pv2", wl, [1,1,1], reg)
+bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0],
+                        bl, "b_pv3", wl, [1,1,1], reg)
+
+# gdml output
+w = gd.Writer()
+w.write(reg,"output.gdml")
+
+# visualisation
+v = vi.VtkViewer()
+v.addLogicalVolume(wl)
+v.view()

### 2019-02-20 paper/pyg4ometry.tex
Added example

@@
 \author[a]{William Shields}
+\author[a]{Stuart Walker}
 
@@
 There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
-include MCMP, FLUKA, Geant3 and Geant4. Each code either has a particular specialism or target user community.  PT Monte Carlo simulations have 
-diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy, space radiation environment simulation 
-are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that the particles 
-are passing through.  The creation of geometry files is typically a very time consuming activity, the simulation validity and performance is directly dependent 
-on the quality of the geometry. The requirement of a  geometry system that allows the conversion between files prepared for different codes will enable cross 
-checks of the physics processes in particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted design (CAD) 
-files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not amenable for PT 
-programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop geometry files, convert between 
-common PT programme geometry formats and finally import CAD models. This paper describes such geometry creation and conversion package 
-called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry description. The main features of  {\em pyg4ometry} 
-are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats 
-(STEP and IGES) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK.
+include MCMP, FLUKA, Geant3 and Geant4. All these codes are based on the Monte Carlo technique but each code either has a particular specialism 
+or target user community.  PT Monte Carlo simulations have diverse uses, shielding calculations for radiological protection, detector performance, medical 
+imaging and therapy, space radiation environment simulation are some examples. A fundamental requirement of all of the codes is to supply a computer 
+readable description of the physical geometry that the particles are passing through.  The creation of geometry files is typically a very time consuming activity, 
+the simulation validity and performance is directly dependent on the quality of the geometry. The requirement of a  geometry system that allows the conversion 
+between files prepared for different codes will enable cross checks of the physics processes in particle transport codes. Parallel to the creation of geometry files 
+for PT programs, usually computer assisted design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric 
+representations in CAD files is typically not amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle 
+transport code users to rapidly develop geometry files, convert between common PT programme geometry formats and finally import CAD models. This paper 
+describes such geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry 
+description. The main features of  {\em pyg4ometry} are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry 
+descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK. 
+The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 called BDSIM. Accelerator physicists 
+like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle beam with the accelerator material.
 
@@
 Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\it Logical Volumes} 
-and {\it Physical Volumes}. A Logical Volume is a volume that has an outer solid but also material, magnetic field and zero or more physical {\it daughter} volumes. A Physical 
-Volume is a placement (or instance) of a Logical Volume.
+and {\it Physical Volumes}. A Logical Volume is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field and zero or 
+more physical {\it daughter} volumes. A Physical Volume is a placement (or instance) of a Logical Volume.
 
@@
 \subsection{Internal data representation} 
-The internal data representation follows closely the structure of GDML. A registry class aggregates python ordered dictionaries that are  used to store the main 
+The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
 elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
@@
 \subsection{Overlap detection}
-All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when encountering such a 
-situation.  A key feature of {\it pyg4ometry} is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
-and determining if the resulting mesh is empty.
+All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+throughsuch a situation.  A key feature of {\it pyg4ometry} is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
+and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
+
+{\small 
+\begin{verbatim}
+Overlap detection
+\end{verbatim}
+}
+
+For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$.
+This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final
+PT simulation.
+This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
+Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered.
 
@@
 
+An example of the VTK output for code listing XXX is shown in Figure~\ref{fig:rapidModellingExample}.
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=10cm]{./diagrams/rapidModelling.pdf}
+\caption{VTK visualisation output from code example XXX.}
+\label{fig:rapidModellingExample}
+\end{center}
+\end{figure}
+Significantly more complex geometries can be developed using a structure similar to that shown in code listing XXX.
+
 \section{CAD to Geant4 conversion }
@@
 is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
-collection of part features.
+collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
+and visualisation attributes.
 
@@
 to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table XXX shows the mapping between FLUKA and Geant4 objects.
+An ANTLR based expression parser is used to load and comprehend the FLUKA input syntax, an example is shown in XXX. Each FLUKA body is matched to a Geant4 
+solid and a FLUKA region is represented by a Geant4 CSG tree is formed using the pyg4ometry classes.
+
+\begin{enumerate} 
+\item infinite planes
+\item disjoint unions 
+\end{enumerate}
 
@@
 libraries. A comparison of the performance of converted CAD or FLUKA geometry compared with native Geant4 solids is required so a user can optimise the available
-computing resources against the human resources (required to convert geometry).
+computing resources against the human resources (required to convert geometry). BDSIM is used to load the pyg4ometry generated files  and run basic simulations where 
+high energy particles are
 

### 2019-02-20 paper/diagrams/rapidModelling.py

@@ -6,9 +6,9 @@ import pyg4ometry.visualisation as vi
 reg = g4.Registry()
 
 # expressions
-wx = gd.Constant("wx","100",reg)
-wy = gd.Constant("wy","100",reg)
-wz = gd.Constant("wz","100",reg)
+wx = gd.Constant("wx","50",reg)
+wy = gd.Constant("wy","50",reg)
+wz = gd.Constant("wz","50",reg)
 bx = gd.Constant("bx","10",reg)
 by = gd.Constant("by","10",reg)
 bz = gd.Constant("bz","10",reg)
@@ -25,11 +25,18 @@ b  = g4.solid.Box("b",bx,by,bz,reg)
 wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, bm, "b", reg)
 bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],
-                        bl, "b_pv1", wl, [1,1,1], reg)
-bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0],
-                        bl, "b_pv2", wl, [1,1,1], reg)
-bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0],
-                        bl, "b_pv3", wl, [1,1,1], reg)
+                        bl, "b_pv1", wl, reg)
+bp2 = g4.PhysicalVolume([0,0,-0.25],[-3*bx,0,0],
+                        bl, "b_pv2", wl, reg)
+bp3 = g4.PhysicalVolume([0,0,0.5],[3*bx,0,0],
+                        bl, "b_pv3", wl, reg)
+
+# physical volume vistualisation attributes
+bp1.visOptions.color = (1,0,0)
+bp1.visOptions.alpha = 0.25
+bp2.visOptions.color = (0,1,0)
+bp2.visOptions.representation = "wireframe"
+bp3.visOptions.color = (0,0,1)
 
 # gdml output
 w = gd.Writer()
@@ -38,4 +45,5 @@ w.write(reg,"output.gdml")
 # visualisation
 v = vi.VtkViewer()
 v.addLogicalVolume(wl)
+v.addAxes()
 v.view()

### 2019-03-07 paper/pyg4ometry.tex
Small edits
Small tweeks

@@
 on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
-TetGEN can be employed to give the meshes more desirable output.
+TetGEN can be employed to give the meshes more desirable features.
+
+\subsection{Replica, parametrised and looped volumes}
+A powerful feature of Geant4 and hence GDML is the ability to either repeat or parametrise geometry. The create mulitple replicas of a volume in a cartesian, cylindrical or 
+spherical grid is known as a ReplicaVolume.
 
@@
 elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
+\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 
@@
 
+\subsection{Volume bounding} 
+If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully encompasses the 
+daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume shape that efficiently holds all of its daughters.
+
 \subsection{Visualisation}
@@
 the potential overlaps. This is dependent on the accuracy of the mesh generated and is a particular problem with meshes based on curved surfaces.
+
+\subsection{Adding properties to volumes}
+A pure geometry description is an insufficient description for a PT simulation. Often other attributes need to be assigned for example material definition, magnetic field or
+
+\subsection{Graphical user interface}
+A basic Qt based graphical user interface is also available with pyg4ometry.
+If a model has a large number of volumes defined in a hierarchical tree structure, it is cumbersome for the user to find the logical or physical volume.
 
@@
 
+\section{Interesting use cases}
+pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
+possible applications.
+
+\subsection{Mixing geometry sources}
+It is possible to mix different geometries from STL, STEP, GDML and FLUKA in single GDML file for use in Geant4 and ROOT.
+
+\subsection{Editing existing CAD models}
+Often existing CAD models have either missing details or too much detail.
+
+\subsection{Overlap checking in geometry}
+Often small errors in geometry cause unexpected PT code behaviour.
+
 \section{Performance of converted geometry in Geant4}

### 2019-05-12 pyg4ometry/test/python/PythonAuthoringTests.py
Generic polyhedra

@@ -11,6 +11,9 @@ import T008_Sphere
 import T009_Orb
 import T010_Torus
 import T011_Polycone
+import T012_GenericPolycone
+import T013_Polyhedra
+import T014_GenericPolyhedra
 
 import logging as _log
 
@@ -51,6 +54,14 @@ class PythonAuthoringTests(_unittest.TestCase) :
     def testPolycone(self) :
         self.assertTrue(T011_Polycone.Test())
 
+    def testGenericPolycone(self) :
+        self.assertTrue(T012_GenericPolycone.Test())
+
+    def testPolyhedra(self) :
+        self.assertTrue(T013_Polyhedra.Test())
+
+    def testGenericPolyhedra(self) : 
+        self.assertTrue(T014_GenericPolyhedra.Test())
 
 
 if __name__ == '__main__':

### 2019-05-12 pyg4ometry/test/python/T013_Polyhedra.py

@@ -16,29 +16,26 @@ def Test(vis = False) :
     pi     = _gd.Constant("pi","3.1415926",reg,True)
     psphi  = _gd.Constant("sphi","1",reg,True)
     pdphi  = _gd.Constant("dphi","4",reg,True)
+    pnsid  = _gd.Constant("pnsid","4",reg,True) 
+    
+    prmin1    = _gd.Constant("prmin1","1",reg,True)
+    prmax1    = _gd.Constant("prmax1","9",reg,True)
+    pz1       = _gd.Constant("z1","-10",reg,True)
 
-    prmin1 = _gd.Constant("prmin1","1",reg,True)
-    prmax1 = _gd.Constant("prmax1","9",reg,True)
-    pz1    = _gd.Constant("z1","-10",reg,True)
+    prmin2    = _gd.Constant("prmin2","3",reg,True)
+    prmax2    = _gd.Constant("prmax2","5",reg,True)
+    pz2       = _gd.Constant("z2","12",reg,True)
 
-    prmin2 = _gd.Constant("prmin2","5",reg,True)
-    prmax2 = _gd.Constant("prmax2","9",reg,True)
-    pz2    = _gd.Constant("z2","0",reg,True)
-
-    prmin3 = _gd.Constant("prmin3","3",reg,True)
-    prmax3 = _gd.Constant("prmax3","5",reg,True)
-    pz3    = _gd.Constant("z3","10",reg,True)
-
-    prmin = [prmin1,prmin2,prmin3]
-    prmax = [prmax1,prmax2,prmax3]
-    pz    = [pz1,pz2,pz3]
+    prmin    = [prmin1,prmin2]
+    prmax    = [prmax1,prmax2]
+    pz       = [pz1,pz2]
     
     wm = _g4.MaterialPredefined("G4_Galactic") 
     pm = _g4.MaterialPredefined("G4_Fe") 
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    ps = _g4.solid.Polycone("ps",psphi,pdphi,pz,prmin,prmax,reg,"mm","rad")
+    ps = _g4.solid.Polyhedra("ps",psphi,pdphi,pnsid,len(pz),pz,prmin,prmax,reg,"mm","rad")
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)
@@ -51,7 +48,7 @@ def Test(vis = False) :
     # gdml output 
[…]

### 2019-05-12 pyg4ometry/test/python/T014_GenericPolyhedra.py

@@ -16,29 +16,26 @@ def Test(vis = False) :
     pi     = _gd.Constant("pi","3.1415926",reg,True)
     psphi  = _gd.Constant("sphi","1",reg,True)
     pdphi  = _gd.Constant("dphi","4",reg,True)
+    pnsid  = _gd.Constant("pnsid","4",reg,True) 
+    
+    pr1    = _gd.Constant("pr1","1",reg,True)
+    pz1    = _gd.Constant("pz1","-10",reg,True)
 
-    prmin1 = _gd.Constant("prmin1","1",reg,True)
-    prmax1 = _gd.Constant("prmax1","9",reg,True)
-    pz1    = _gd.Constant("z1","-10",reg,True)
+    pr2    = _gd.Constant("pr2","2",reg,True)
+    pz2    = _gd.Constant("pz2","0",reg,True)
 
-    prmin2 = _gd.Constant("prmin2","5",reg,True)
-    prmax2 = _gd.Constant("prmax2","9",reg,True)
-    pz2    = _gd.Constant("z2","0",reg,True)
+    pr3    = _gd.Constant("pr3","3",reg,True)
+    pz3    = _gd.Constant("pz3","10",reg,True)
 
-    prmin3 = _gd.Constant("prmin3","3",reg,True)
-    prmax3 = _gd.Constant("prmax3","5",reg,True)
-    pz3    = _gd.Constant("z3","10",reg,True)
-
-    prmin = [prmin1,prmin2,prmin3]
-    prmax = [prmax1,prmax2,prmax3]
-    pz    = [pz1,pz2,pz3]
+    pr     = [pr1,pr2,pr3]
+    pz     = [pz1,pz2,pz3]
     
     wm = _g4.MaterialPredefined("G4_Galactic") 
     pm = _g4.MaterialPredefined("G4_Fe") 
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    ps = _g4.solid.Polycone("ps",psphi,pdphi,pz,prmin,prmax,reg,"mm","rad")
+    ps = _g4.solid.GenericPolyhedra("ps",psphi,pdphi,pnsid,pz,pr,reg,"mm","rad")
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)
@@ -51,7 +48,7 @@ def Test(vis = False) :
     # gdml output 
     w = _gd.Writer()
     w.addDetector(reg)
[…]

### 2019-05-12 public/2019-ipac/WEPTS054.tex
Added IPAC paper

% !TeX spellcheck = en_GB
% !TeX program = lualatex
%
% v 2.3  Feb 2019   Volker RW Schaa
%		# changes in the collaboration therefore updated file "jacow-collaboration.tex"
%		# all References with DOIs have their period/full stop before the DOI (after pp. or year)
%		# in the author/affiliation block all ZIP codes in square brackets removed as it was not %         understood as optional parameter and ZIP codes had bin put in brackets
%       # References to the current IPAC are changed to "IPAC'19, Melbourne, Australia"
%       # font for ‘url’ style changed to ‘newtxtt’ as it is easier to distinguish "O" and "0"
%
\documentclass[a4paper,
               %boxit,        % check whether paper is inside correct margins
               %titlepage,    % separate title page
               %refpage       % separate references
               %biblatex,     % biblatex is used
               keeplastbox,   % flushend option: not to un-indent last line in References
               %nospread,     % flushend option: do not fill with whitespace to balance columns
               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
               %xetex,        % use XeLaTeX to process the file
               %luatex,       % use LuaLaTeX to process the file
               ]{jacow}
%
% ONLY FOR \footnote in table/tabular
%
\usepackage{pdfpages,multirow,ragged2e} %
%
% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
% ----------------------------------------------------
% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
%    might generates errors, therefore PNG and JPG first
%
\makeatletter%
	\ifboolexpr{bool{xetex}}
	 {\renewcommand{\Gin@extensions}{.pdf,%
	                    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
	                    .eps,.ps,%
	                    }}{}
\makeatother

% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
% --------------------------------------------------------
%   utf8  is default for XeTeX/LuaTeX
%   utf8  in LaTeX only realises a small portion of codes
%
\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
 {}                                      % input encoding is utf8 by default
 {\usepackage[utf8]{inputenc}}           % switch to utf8

\usepackage[USenglish]{babel}

%
% if BibLaTeX is used
%
\ifboolexpr{bool{jacowbiblatex}}%
 {%
  \addbibresource{jacow-test.bib}
  \addbibresource{biblatex-examples.bib}
 }{}
\listfiles

%%
%%   Lengths for the spaces in the title
%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em

\begin{document}

\title{Pyg4ometry : A Tool to Create Geometries for Geant4, BDSIM, G4Beamline and FLUKA for Particle Loss and Energy Deposit Studies}

\author{Stewart Boogert\thanks{stewart.boogert@rhul.ac.uk}, Andrey Abramov, Joshua Albrecht, \\ Gian Luigi D'Alessandro, Laurence Nevay, William Shields, Stuart Walker \\
JAI, Egham, Surrey)}

\maketitle

%
\begin{abstract}
Studying the energy deposits in accelerator components, mechanical supports, services, ancillary equipment and shielding requires a detailed computer readable description of the component geometry. The creation of geometries is a significant bottle neck in producing complete simulation models and reducing the effort required will provide the ability of non- experts to simulate the effects of beam losses on realistic accelerators. The paper describes a flexible and easy to use PYTHON package to create geometries usable by either Geant4 (and so BDSIM or G4Beamline) or FLUKA either from scratch or by conversion from common engineering formats, such as STEP or IGES created by industry standard CAD/CAM packages. The conversion requires an intermediate conversion to STL or similar triangular or tetrahedral tessellation description. A key capability of \verb|pyg4ometry| is to mix GDML/STEP/STL geometries and visualisation of the resulting geometry and determine if there are any geometric overlaps. An example conversion of a complex geometry is presented along with performance results for physical particle tracking of electromagnetically and hadronically produced particles using BDSIM.
\end{abstract}

\section{INTRODUCTION}

\subsection{Particle transport codes}

\subsection{Geometry generation}

\section{EXAMPLES}
\subsection{Python}

\subsection{Geometry Description Markup Language (GDML)}

\subsection{Computer aided design (STEP)}

\section{SUMMARY}

\section{ACKNOWLEDGEMENTS}
Any acknowledgement should be in a separate section directly preceding
the \textbf{REFERENCES} or \textbf{APPENDIX} section.

%
% only for "biblatex"
%
\ifboolexpr{bool{jacowbiblatex}}%
	{\printbibliography}%
	{%
	% "biblatex" is not used, go the "manual" way

	%\begin{thebibliography}{99}   % Use for  10-99  references
	\begin{thebibliography}{9} % Use for 1-9 references

	\bibitem{jacow-help}
		JACoW,
		\url{http://www.jacow.org}

	\bibitem{IEEE}
		\textit{IEEE Editorial Style Manual},
		IEEE Periodicals, Piscataway,
		NJ, USA, Oct. 2014, pp. 34--52.

	\bibitem{journal-abbreviations}
	\url{https://woodward.library.ubc.ca/researchhelp/journal-abbreviations/}

	\end{thebibliography}
} % end \ifboolexpr
%
% for use as JACoW template the inclusion of the ANNEX parts have been commented out
% to generate the complete documentation please remove the "%" of the next two commands
% 
%%%\newpage

%%%\include{annexes-A4}

\end{document}

### 2019-05-12 pyg4ometry/test/python/PythonAuthoringTests.py
Add python elliptical tube test

@@ -14,6 +14,7 @@ import T011_Polycone
 import T012_GenericPolycone
 import T013_Polyhedra
 import T014_GenericPolyhedra
+import T015_EllipticalTube
 
 import logging as _log
 
@@ -62,6 +63,9 @@ class PythonAuthoringTests(_unittest.TestCase) :
 
     def testGenericPolyhedra(self) : 
         self.assertTrue(T014_GenericPolyhedra.Test())
+
+    def testGenericPolyhedra(self) : 
+        self.assertTrue(T015_EllipticalTube.Test())
 
 
 if __name__ == '__main__':

### 2019-05-12 pyg4ometry/test/python/T015_EllipticalTube.py

@@ -1,0 +1,48 @@
+import os as _os
+import pyg4ometry.gdml as _gd
+import pyg4ometry.geant4 as _g4
+import pyg4ometry.visualisation as _vi
+
+
+def Test(vis = False) : 
+    reg = _g4.Registry()
+    
+    # defines 
+    wx = _gd.Constant("wx","100",reg,True)
+    wy = _gd.Constant("wy","100",reg,True)
+    wz = _gd.Constant("wz","100",reg,True)
+
+    
+    pi     = _gd.Constant("pi","3.1415926",reg,True)
+    ex     = _gd.Constant("ex","10",reg,True)
+    ey     = _gd.Constant("ey","15",reg,True)
+    ez     = _gd.Constant("ez","20",reg,True)
+
+    
+    wm = _g4.MaterialPredefined("G4_Galactic") 
+    em = _g4.MaterialPredefined("G4_Fe") 
+
+    # solids
+    ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
+    es = _g4.solid.EllipticalTube("es",ex,ey,ez,reg)
+        
+    # structure 
+    wl = _g4.LogicalVolume(ws, wm, "wl", reg)
+    el = _g4.LogicalVolume(es, em, "el", reg)
+    ep = _g4.PhysicalVolume([0,0,0],[0,0,0],  el, "e_pv1", wl, reg) 
+    
+    # set world volume
+    reg.setWorld(wl.name)
+    
+    # gdml output 
+    w = _gd.Writer()
+    w.addDetector(reg)
+    w.write(_os.path.join(_os.path.dirname(__file__), "T015_EllipticalTube.gdml"))
+
+    # visualisation
+    if vis : 
+        v = _vi.VtkViewer()
+        v.addLogicalVolume(reg.getWorldVolume())
+        v.view()
+
+    return True

### 2019-05-14 public/2019-ipac/WEPTS054.tex
Improved examples

@@
 \usepackage{pdfpages,multirow,ragged2e} %
+\usepackage{listings}
+\usepackage{fancyvrb}
+
+\lstset{
+ identifierstyle=\small, 
+ commentstyle=\color{red}, 
+ stringstyle=\ttfamily, 
+ showstringspaces=false
+ }
+
 %
@@
 \subsection{Particle transport codes}
+There are multiple different codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
 
@@
 
+\VerbatimInput[fontsize=\small]{./examples/simple.py}
+
+\begin{figure}[!htb]
+   \centering
+   \includegraphics*[width=.9\columnwidth]{./examples/simple.jpg}
+   \caption{Example of three primitive Geant4 solids rendered in VTK.}
+   \label{fig:simple}
+\end{figure}
+
+Figure \ref{fig:dipole} shows a more complex geometry example. 
+\begin{figure}[!htb]
+   \centering
+   \includegraphics*[width=.9\columnwidth]{./examples/dipole.jpg}
+   \caption{Example of a more complex geometry example, this time a cavity beam position monitor}
+   \label{fig:dipole}
+\end{figure}
+
+%\lstinputlisting[language=Python]{./examples/simple.py}
+
 \subsection{Geometry Description Markup Language (GDML)}
+
+\subsection{Standard tessellation language (STL)}
 
@@
 %
+
 \ifboolexpr{bool{jacowbiblatex}}%
@@
 
-	\bibitem{jacow-help}
-		JACoW,
-		\url{http://www.jacow.org}
-
-	\bibitem{IEEE}
-		\textit{IEEE Editorial Style Manual},
-		IEEE Periodicals, Piscataway,
-		NJ, USA, Oct. 2014, pp. 34--52.
-
-	\bibitem{journal-abbreviations}
-	\url{https://woodward.library.ubc.ca/researchhelp/journal-abbreviations/}
+	\bibitem{geant4} Recent developments in Geant4, NIMA 835, pages 186-225, 2016 
+	\bibitem{fluka} CERN-2005-10 (2005),
 
@@
 } % end \ifboolexpr
-%
+
 % for use as JACoW template the inclusion of the ANNEX parts have been commented out
@@
 
+%@article{ALLISON2016186,
+%title = "Recent developments in Geant4",
+%journal = "Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment",
+%volume = "835",
+%pages = "186 - 225",
+%year = "2016",
+%issn = "0168-9002",
+%doi = "https://doi.org/10.1016/j.nima.2016.06.125",
+%url = "http://www.sciencedirect.com/science/article/pii/S0168900216306957",
+%author = "J.
+Allison and K.
+Amako and J.
+Apostolakis and P.
+Arce and M.
+Asai and T.
+Aso and E.
+Bagli and A.
+Bagulya and S.
+Banerjee and G.
+Barrand and B.R.
+Beck and A.G.
+Bogdanov and D.
+Brandt and J.M.C.
+Brown and H.
+Burkhardt and Ph.
+Canal and D.
+Cano-Ott and S.
+Chauvie and K.
+Cho and G.A.P.
+Cirrone and G.
+Cooperman and M.A.
+Cortés-Giraldo and G.
+Cosmo and G.
+Cuttone and G.
+Depaola and L.
+Desorgher and X.
+Dong and A.
+Dotti and V.D.
+Elvira and G.
+Folger and Z.
+Francis and A.
+Galoyan and L.
+Garnier and M.
+Gayer and K.L.
+Genser and V.M.
+Grichine and S.
+Guatelli and P.
+Guèye and P.
+Gumplinger and A.S.
+Howard and I.
+Hřivnáčová and S.
+Hwang and S.
+Incerti and A.
+Ivanchenko and V.N.
+Ivanchenko and F.W.
+Jones and S.Y.
+Jun and P.
+Kaitaniemi and N.
+Karakatsanis and M.
+Karamitros and M.
+Kelsey and A.
+Kimura and T.
+Koi and H.
+Kurashige and A.
+Lechner and S.B.
+Lee and F.
+Longo and M.
+Maire and D.
+Mancusi and A.
+Mantero and E.
+Mendoza and B.
+Morgan and K.
+Murakami and T.
+Nikitina and L.
+Pandola and P.
+Paprocki and J.
+Perl and I.
+Petrović and M.G.
+Pia and W.
+Pokorski and J.M.
+Quesada and M.
+Raine and M.A.
+Reis and A.
+Ribon and A.
+Ristić Fira and F.
+Romano and G.
+Russo and G.
+Santin and T.
+Sasaki and D.
+Sawkey and J.I.
+Shin and I.I.
+Strakovsky and A.
+Taborda and S.
+Tanaka and B.
+Tomé and T.
+Toshito and H.N.
+Tran and P.R.
+Truscott and L.
+Urban and V.
+Uzhinsky and J.M.
+Verbeke and M.
+Verderi and B.L.
+Wendt and H.
+Wenzel and D.H.
+Wright and D.M.
+Wright and T.
+Yamashita and J.
+Yarba and H.
+Yoshida",
+%keywords = "High energy physics, Nuclear physics, Radiation, Simulation, Computing",
+%abstract = "Geant4 is a software toolkit for the simulation of the passage of particles through matter.
+It is used by a large number of experiments and projects in a variety of application domains, including high energy physics, astrophysics and space science, medical physics and radiation protection.
+Over the past several years, major changes have been made to the toolkit in order to accommodate the needs of these user communities, and to efficiently exploit the growth of computing power made available by advances in technology.
+The adaptation of Geant4 to multithreading, advances in physics, detector modeling and visualization, extensions to the toolkit, including biasing and reverse Monte Carlo, and tools for physics and release validation are discussed here."
+%}
+
+%"FLUKA: a multi-particle transport code"
+%A. Ferrari, P.R. Sala, A. Fasso`, and J. Ranft,
+% CERN-2005-10 (2005), INFN/TC_05/11, SLAC-R-773
+
 %%%\include{annexes-A4}

### 2019-05-14 public/2019-ipac/examples/dipole.py

@@ -1,0 +1,123 @@
+import pyg4ometry as _pyg
+import numpy as _np
+import pyg4ometry.geant4 as _g4
+import pyg4ometry.gdml as _gdml
+import pyg4ometry.visualisation as _vis
+
+def dipole() :
+    
+    reg = _g4.Registry()
+    
+    safety       = _gdml.Defines.Constant("length_safety",1e-8,reg)
+    
+    bp_radius    = _gdml.Defines.Constant("beam_pipe_radius",7.5,reg)
+    bp_thickness = _gdml.Defines.Constant("beam_pipe_thickness",2,reg)
+    bp_length    = _gdml.Defines.Constant("beam_pipe_length",50,reg)
+    
+    wg_innerr    = _gdml.Defines.Constant("wg_innerrb",bp_radius,reg)
+    wg_outerd    = _gdml.Defines.Constant("wg_outerd",91.2,reg)
+    wg_outerr    = _gdml.Defines.Constant("wg_outerr",wg_outerd/2.0,reg)
+    wg_length    = _gdml.Defines.Constant("wg_length",50.0,reg)
+
+    # wg_length    = 50.0
+    wg_width     = 8.0
+    wg_height    = _gdml.Defines.Constant("wg_height",27.5,reg)
+    wg_offset    = _gdml.Defines.Constant("wg_offset",12.0,reg)
+    wg_centre    = _gdml.Defines.Constant("wg_centre",wg_offset+wg_height/2,reg)
+
+    ec_innerr    = _gdml.Defines.Constant("ec_innerr",bp_radius,reg)
+    ec_outerr    = _gdml.Defines.Constant("ec_outerr",wg_outerr,reg)
+    ec_length    = _gdml.Defines.Constant("ec_length",5,reg)
+    ec_centre    = _gdml.Defines.Constant("ec_center",wg_length+ec_length/2,reg)
+
+    ca_length    = _gdml.Defines.Constant("ca_length",13,reg)
+    ca_outerr    = _gdml.Defines.Constant("ca_outerr",wg_outerd/2.0,reg)
+    ca_centre    = _gdml.Defines.Constant("ca_centre",ca_length/2.0,reg)
+    ca_innerr    = _gdml.Defines.Constant("ca_innerr",52.778/2.0,reg)
+
+    ce_outerr    = _gdml.Defines.Constant("ce_outerr",ca_innerr+5,reg)
+    ce_length    = _gdml.Defines.Constant("ce_length",5,reg)
+
[…]

### 2019-05-14 public/2019-ipac/examples/simple.py

@@ -1,0 +1,54 @@
+import pyg4ometry.gdml as gd
+import pyg4ometry.geant4 as g4
+import pyg4ometry.visualisation as vi
+
+import numpy as _np
+
+# create empty data storage structure
+reg = g4.Registry()
+
+# expressions 
+wx = gd.Constant("wx","100",reg)
+wy = gd.Constant("wy","100",reg)
+wz = gd.Constant("wz","100",reg)
+
+bx = gd.Constant("bx","10",reg)
+by = gd.Constant("by","10",reg)
+bz = gd.Constant("bz","10",reg)
+
+# materials
+wm = g4.MaterialPredefined("G4_Galactic",reg) 
+m  = g4.MaterialPredefined("G4_Fe",reg) 
+
+# solids
+wb = g4.solid.Box("wb",wx,wy,wz,reg)
+b  = g4.solid.Box("b",bx,by,bz,reg)
+s  = g4.solid.Orb("o",bx/2,reg)
+t  = g4.solid.Tubs("t",0,bx/2,bz,0,2*_np.pi,reg)
+
+# structure 
+wl = g4.LogicalVolume(wb, wm, "wl", reg)
+bl = g4.LogicalVolume(b, m, "b", reg)
+sl = g4.LogicalVolume(s, m, "s", reg)
+tl = g4.LogicalVolume(t, m, "t", reg)
+
+bp = g4.PhysicalVolume([0,0,0.0],[0,0,0], 
+                        bl, "b_pv", wl,reg) 
+sp = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
+                        sl, "s_pv", wl,reg)  
+tp = g4.PhysicalVolume([0,0.5,0],[2*bx,0,0], 
+                        tl, "t_pv", wl,reg) 
+
+# set world volume
+reg.setWorld("wl")
+                        
+# gdml output
+w = gd.Writer()
+w.addDetector(reg)
+w.write("simple.gdml")
+
+# visualisation 
+v = vi.VtkViewer()
+v.addLogicalVolume(wl)
+v.addAxes(40)
+v.view()

### 2019-05-15 public/2019-ipac/WEPTS054.tex
Two pages of IPAC

@@
 Studying the energy deposits in accelerator components, mechanical supports, services, ancillary equipment and shielding requires a detailed computer readable description of the component geometry.
-The creation of geometries is a significant bottle neck in producing complete simulation models and reducing the effort required will provide the ability of non- experts to simulate the effects of beam losses on realistic accelerators.
+The creation of geometries is a significant bottle neck in producing complete simulation models and reducing the effort required will provide the ability of non-experts to simulate the effects of beam losses on realistic accelerators.
 The paper describes a flexible and easy to use PYTHON package to create geometries usable by either Geant4 (and so BDSIM or G4Beamline) or FLUKA either from scratch or by conversion from common engineering formats, such as STEP or IGES created by industry standard CAD/CAM packages.
@@
 \section{INTRODUCTION}
+\verb|Pyg4ometry| started as an internal tool to generate beam line geometries for BDSIM.
 
@@
 There are multiple different codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
+Generally accelerator codes are interfaced  to a particle transport code to produce a complete simulation of beam losses.
+Two beam line simulation tools have been developed on the basis of Geant4, BDSIM and G4Beamline.
 
-\subsection{Geometry generation}
+\subsection{Geometry generation and GDML}
+The specification in a computer readable format the geometry of the material surrounding an accelerator can be an exceedingly time consuming and error prone task.
+Typically either the detector or accelerator infrastructure is constructed over many years and the simulation geometry can be created over similar time scales.
+This does not allow for rapid simulation of a system as the burden of creating the geometry is too great.
+
+\section{SOFTWARE IMPLEMENTATION}
+\verb|pyg4ometry| is a collection of python classes that mimic closely the C++ interface of Geant4.
+The aim to have all of the ``detector'' description classes implemented in python, these include geometry, materials and optical surfaces.
+The \verb|pyg4ometry| defined geometry can then quickly be written as a GDML file for loading into BDSIM or G4Beamline.
+This is a much quicker interface to a full C++ Geant4 application and any programmed geometry can be viewed quickly using VTK.
+A Python interface to the geometry primitives of Geant4 allows conversion applications to be developed from FLUKA/STEP/STL descriptions to \verb|pyg4ometry|.
+Finally and most importantly \verb|pyg4ometry| provides an interface to GDML, as the python interpreter performs important syntax checking of large and complex geometries.
 
@@
    \includegraphics*[width=.9\columnwidth]{./examples/dipole.jpg}
-   \caption{Example of a more complex geometry example, this time a cavity beam position monitor}
+   \caption{Example of a more complex geometry example, this time a cavity beam position monitor.}
    \label{fig:dipole}
@@
 
-\subsection{Geometry Description Markup Language (GDML)}
-
 \subsection{Standard tessellation language (STL)}
@@
 \subsection{Computer aided design (STEP)}
+Arbitrary conversion of CAD/CAM files to \verb|pyg4ometry| is a very challenging task. Typically users convert the CAD description into
+an intermediate surface triangulation (such as STL described previously) and load the geometry as a G4TessellatedSolid.
+A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
+\begin{figure}[!htb]
+   \centering
+   \includegraphics*[width=.9\columnwidth]{./examples/ea9-10.jpg}
+   \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T9 and T10 test beam lines to GDML Each part is 
+   coloured with a randomly to clearly indicate the structure of the shielding.}
+   \label{fig:ea910}
+\end{figure}
 
-\section{SUMMARY}
+\section{SUMMARY AND FUTURE DEVELOPMENTS}
+There any many potential enhancements that are being considered for \verb|pyg4ometry|. Given the interface matches so closely that of Geant4, 
+an alternative C++ output writer can be quickly written to allow \verb|pyg4ometry| to generate C++ code which can be directly compiled into a 
+Geant4 application.
+Although not described in this publication a FLUKA geometry loader has been written and can load large pre-existing geometries into 
+\verb|pyg4ometry| and subsequently write GDML files. This is currently being refactored and will appear in the next public release of \verb|pyg4ometry|.
+In addition to the FLUKA to GDML conversion, conversion of Geant4/GDML geometry to FLUKA is yet unstarted but a relatively straight forward
+task. The requirement that volumes do not overlap causes a problem for the CAD/CAM (STEP) conversion to Geant4/GDML as there is no requirement 
+that the parts and assemblies are not overlapping.
 
 \section{ACKNOWLEDGEMENTS}
-Any acknowledgement should be in a separate section directly preceding
-the \textbf{REFERENCES} or \textbf{APPENDIX} section.
 

### 2019-05-15 pyg4ometry/test/python/PythonDefineTests.py
Started matrix tests

@@ -310,6 +310,26 @@ class PythonDefineTests(_unittest.TestCase) :
     # #############################
     # Matrix
     # #############################
+    def testMatrixConstructor1x10(self) : 
+        r = pyg4ometry.geant4.Registry()
+        m = pyg4ometry.gdml.Matrix("m",1,[1,2,3,4,5,6,7,8,9,10],r,False)
+        self.assertEqual(m.eval(),[1,2,3,4,5,6,7,8,9,10])
+
+
+    def testMatrixConstructor1x10(self) : 
+        r = pyg4ometry.geant4.Registry()
+        m = pyg4ometry.gdml.Matrix("m",2,[1,2,3,4,5,6,7,8,9,10],r,False)
+
+    def testMatrix1x10Index(self) : 
+        r = pyg4ometry.geant4.Registry()
+        m = pyg4ometry.gdml.Matrix("m",1,[1,2,3,4,5,6,7,8,9,10],r,False)
+        self.assertEqual(m[9].eval(),10)
+
+    def testMatrix2x5Index(self) : 
+        r = pyg4ometry.geant4.Registry()
+        m = pyg4ometry.gdml.Matrix("m",2,[1,2,3,4,5,6,7,8,9,10],r,False)
+        self.assertEqual(m[0][2].eval(),3)
+        
     
 if __name__ == '__main__':
     _unittest.main(verbosity=2)        

### 2019-05-16 public/2019-ipac/WEPTS054.tex
Completed examples

@@
 \section{INTRODUCTION}
-\verb|Pyg4ometry| started as an internal tool to generate beam line geometries for BDSIM.
+\verb|Pyg4ometry| started as an internal python scripting tool to generate beam line geometries for BDSIM.
+BDSIM is a Geant4 application which allows a user to rapidly create a full three dimensional model of an accelerator from an optical description.
+A guiding principle of BDSIM is rapid simulation of optical models, in the MADX input format for example, can be converted for use in BDSIM in minutes.
+Rarely described in accelerator optical descriptions is the geometry of the physical material that comprises the accelerator, so beam-pipe, magnets, supports, tunnel, beam instrumentation etc.
+The aim of \verb|pyg4ometry| is to create a tool  in which complex geometry can be created as quickly as a generic BDSIM model.
+A key requirement is to be able to integrate and composite geometry sources to a single file.
 
@@
 This does not allow for rapid simulation of a system as the burden of creating the geometry is too great.
+An XML based markup language Geometry Description Markup Language (GDML) is used as the file format for geometry export in \verb|pyg4ometry|.
 
@@
 This is a much quicker interface to a full C++ Geant4 application and any programmed geometry can be viewed quickly using VTK.
+\verb|pyg4ometry| naterial can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
+GDML has a simple mathematical expression language so geometries can be parametrised, this is also implemented in \verb|pyg4ometry| using ANTLR.
 A Python interface to the geometry primitives of Geant4 allows conversion applications to be developed from FLUKA/STEP/STL descriptions to \verb|pyg4ometry|.
@@
 \subsection{Python}
-
+A complete code example for creation a simple geometry consisting of three Iron solids is shown below.
+The python interfaces are so similar to Geant4 C++ interface and a user can refer to the Geant4 documentation.
 \VerbatimInput[fontsize=\small]{./examples/simple.py}
-
+The code is divided in 6 blocks of definitions, reusable parameters, materials, solids, structure and placement, GDML IO and finally visualisation.
+A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions which need to stored in the output file.
 \begin{figure}[!htb]
@@
 \subsection{Standard tessellation language (STL)}
+STL file format describes a raw unstructured triangulated surface, the normal is defined by the ordering of the vertices. \verb|pyg4ometry| supports the loading 
+STL files and conversion to G4TessellatedSolid. 
+\VerbatimInput[fontsize=\small]{./examples/stl.py}
+
+\begin{figure}[!htb]
+   \centering
+   \includegraphics*[width=.9\columnwidth]{./examples/utahteapot.jpg}
+   \caption{STL surface mesh rendered in VTK using pyg4ometry.}
+   \label{fig:simple}
+\end{figure}
 
@@
 A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
+\VerbatimInput[fontsize=\small]{./examples/freecad.py}
 \begin{figure}[!htb]
@@
 
+\section{BDSIM}
+
+\begin{figure}[!htb]
+   \centering
+   \includegraphics*[width=.9\columnwidth]{./examples/dipole_bdsim.jpg}
+   \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}
+   \label{fig:dipole}
+\end{figure}
+
 \section{SUMMARY AND FUTURE DEVELOPMENTS}
@@
 an alternative C++ output writer can be quickly written to allow \verb|pyg4ometry| to generate C++ code which can be directly compiled into a 
-Geant4 application.
-Although not described in this publication a FLUKA geometry loader has been written and can load large pre-existing geometries into 
+Geant4 application. Although not described in this publication a FLUKA geometry loader has been written and can load large pre-existing geometries into 
 \verb|pyg4ometry| and subsequently write GDML files. This is currently being refactored and will appear in the next public release of \verb|pyg4ometry|.
@@
 task. The requirement that volumes do not overlap causes a problem for the CAD/CAM (STEP) conversion to Geant4/GDML as there is no requirement 
-that the parts and assemblies are not overlapping.
+that the parts and assemblies are not overlapping. Finally a graphical user interface (GUI) can be developed so allow users without programming 
+experience to generate geometry.
+
+\verb|pyg4ometry| is a powerful package to rapidly develop material geometries for accelerator beam line simulations. Currently existing geometry can
+be loaded from GDML, STEP, STL and FLUKA files. We introduce a new python interface to create geometry and adapt existing geometry. \verb|pyg4ometry| 
+can composite geometry from multiple sources to create a complete model which can be exported directly to GDML and then can be loaded into a Geant4 
+based application. Although based on GDML and Geant4 \verb|pyg4ometry| can be easily extended to other MC simulation geometry formats.
 

### 2019-05-16 public/2019-ipac/examples/simple.py

@@ -1,37 +1,33 @@
 import pyg4ometry.gdml as gd
 import pyg4ometry.geant4 as g4
 import pyg4ometry.visualisation as vi
-
 import numpy as _np
 
 # create empty data storage structure
 reg = g4.Registry()
 
-# expressions 
+# 1) expressions 
 wx = gd.Constant("wx","100",reg)
 wy = gd.Constant("wy","100",reg)
 wz = gd.Constant("wz","100",reg)
-
 bx = gd.Constant("bx","10",reg)
 by = gd.Constant("by","10",reg)
 bz = gd.Constant("bz","10",reg)
 
-# materials
+# 2) materials
 wm = g4.MaterialPredefined("G4_Galactic",reg) 
 m  = g4.MaterialPredefined("G4_Fe",reg) 
-
-# solids
+# 3) solids
 wb = g4.solid.Box("wb",wx,wy,wz,reg)
 b  = g4.solid.Box("b",bx,by,bz,reg)
 s  = g4.solid.Orb("o",bx/2,reg)
 t  = g4.solid.Tubs("t",0,bx/2,bz,0,2*_np.pi,reg)
 
-# structure 
+# 4) structure 
 wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, m, "b", reg)
 sl = g4.LogicalVolume(s, m, "s", reg)
 tl = g4.LogicalVolume(t, m, "t", reg)
-
 bp = g4.PhysicalVolume([0,0,0.0],[0,0,0], 
                         bl, "b_pv", wl,reg) 
 sp = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
@@ -42,12 +38,12 @@ tp = g4.PhysicalVolume([0,0.5,0],[2*bx,0,0],
 # set world volume
 reg.setWorld("wl")
                         
-# gdml output
+# 5) gdml output
 w = gd.Writer()
 w.addDetector(reg)
 w.write("simple.gdml")
 
-# visualisation 
+# 6) visualisation 
 v = vi.VtkViewer()
 v.addLogicalVolume(wl)
 v.addAxes(40)

### 2019-05-16 pyg4ometry/test/python/PythonDefineTests.py

@@ -315,7 +315,6 @@ class PythonDefineTests(_unittest.TestCase) :
         m = pyg4ometry.gdml.Matrix("m",1,[1,2,3,4,5,6,7,8,9,10],r,False)
         self.assertEqual(m.eval(),[1,2,3,4,5,6,7,8,9,10])
 
-
     def testMatrixConstructor1x10(self) : 
         r = pyg4ometry.geant4.Registry()
         m = pyg4ometry.gdml.Matrix("m",2,[1,2,3,4,5,6,7,8,9,10],r,False)

### 2019-05-16 public/2019-ipac/WEPTS054.tex
Paper update

@@
 BDSIM is a Geant4 application which allows a user to rapidly create a full three dimensional model of an accelerator from an optical description.
-A guiding principle of BDSIM is rapid simulation of optical models, in the MADX input format for example, can be converted for use in BDSIM in minutes.
-Rarely described in accelerator optical descriptions is the geometry of the physical material that comprises the accelerator, so beam-pipe, magnets, supports, tunnel, beam instrumentation etc.
+A guiding principle of BDSIM is rapid simulation of accelerator models, the MADX input format for example can be converted for use in BDSIM in minutes.
+Rarely described in accelerator optical descriptions is the geometry of the physical material that comprises the accelerator, beam-pipe, magnets, supports, tunnel, beam instrumentation etc.
 The aim of \verb|pyg4ometry| is to create a tool  in which complex geometry can be created as quickly as a generic BDSIM model.
@@
 There are multiple different codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
-Generally accelerator codes are interfaced  to a particle transport code to produce a complete simulation of beam losses.
+Generally accelerator codes, like MAD8, MADX, Transport etc, are interfaced to a Monte Carlo code to produce a complete simulation of beam losses.
 Two beam line simulation tools have been developed on the basis of Geant4, BDSIM and G4Beamline.
@@
 \section{SOFTWARE IMPLEMENTATION}
-\verb|pyg4ometry| is a collection of python classes that mimic closely the C++ interface of Geant4.
+\verb|Pyg4ometry| is a collection of python classes that mimic closely the C++ interface of Geant4.
 The aim to have all of the ``detector'' description classes implemented in python, these include geometry, materials and optical surfaces.
@@
 This is a much quicker interface to a full C++ Geant4 application and any programmed geometry can be viewed quickly using VTK.
-\verb|pyg4ometry| naterial can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
+\verb|Pyg4ometry| geometry can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
 GDML has a simple mathematical expression language so geometries can be parametrised, this is also implemented in \verb|pyg4ometry| using ANTLR.
@@
 A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions which need to stored in the output file.
+The VTK output from this example is shown in Figure~\ref{fig:simple}, where three solids, a cube, sphere and cylinder, are placed with translations and rotations within a cubical world volume.
 \begin{figure}[!htb]
@@
 
-Figure \ref{fig:dipole} shows a more complex geometry example. 
+Figure \ref{fig:dipole} shows a more complex geometry example of a cavity beam position monitor and short sections of beam pipe.
 \begin{figure}[!htb]
    \centering
-   \includegraphics*[width=.9\columnwidth]{./examples/dipole.jpg}
+   \includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
    \caption{Example of a more complex geometry example, this time a cavity beam position monitor.}
@@
 \end{figure}
-
-%\lstinputlisting[language=Python]{./examples/simple.py}
 
@@
    \centering
-   \includegraphics*[width=.9\columnwidth]{./examples/utahteapot.jpg}
+   \includegraphics*[width=.6\columnwidth]{./examples/utahteapot.jpg}
    \caption{STL surface mesh rendered in VTK using pyg4ometry.}
@@
 Arbitrary conversion of CAD/CAM files to \verb|pyg4ometry| is a very challenging task. Typically users convert the CAD description into
-an intermediate surface triangulation (such as STL described previously) and load the geometry as a G4TessellatedSolid.
+an intermediate surface triangulation (such as STL described previously) and load the geometry as a G4TessellatedSolid. An interface for
+loading STEP/STP files was creating using FreeCAD/OpenCASCADE. A single solid in general corresponds to a {\it part} and multiple placements 
+of a solid to a {\it part assembly}.
 A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
@@
    \centering
-   \includegraphics*[width=.9\columnwidth]{./examples/ea9-10.jpg}
+   \includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
    \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T9 and T10 test beam lines to GDML Each part is 
@@
 
-\begin{figure}[!htb]
+\begin{figure}[h!tb]
    \centering
-   \includegraphics*[width=.9\columnwidth]{./examples/dipole_bdsim.jpg}
+   \includegraphics*[width=1.0\columnwidth]{./examples/dipole_bdsim.jpg}
    \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}
@@
 
-\verb|pyg4ometry| is a powerful package to rapidly develop material geometries for accelerator beam line simulations. Currently existing geometry can
+\verb|Pyg4ometry| is a powerful package to rapidly develop material geometries for accelerator beam line simulations. Currently existing geometry can
 be loaded from GDML, STEP, STL and FLUKA files. We introduce a new python interface to create geometry and adapt existing geometry. \verb|pyg4ometry| 

### 2019-05-16 pyg4ometry/test/pythonCompoundExamples/CF_BeamPipe.py
ConFlat beam pipe generator

@@ -1,0 +1,47 @@
+import os as _os
+import pyg4ometry.gdml as _gd
+import pyg4ometry.geant4 as _g4
+import pyg4ometry.visualisation as _vi
+
+
+def CF_BeamPipe(bpLength = 200, bpId = 10, bpThickness = 5, cf_dn = '16') : 
+    reg = _g4.Registry()
+
+    cf_data = {'16': {'od':34, 'id':16, 'bd':27, 'h':7.5, 'nh':6, 'hd':4.3}}
+
+    print cf_data[cf_dn]
+    
+    # defines 
+    wx = _gd.Constant("wx",2*bpLength,reg,True)
+    wy = _gd.Constant("wy",2*bpLength,reg,True)
+    wz = _gd.Constant("wz",2*bpLength,reg,True)
+
+    bpl  = _gd.Constant("bpl",bpLength,reg,True)
+    bpId = _gd.Constant("bpId",cf_data[cf_dn]['id']/2.,reg,True)
+    bpThickness = 
+    bpOd = bpId+
+
+
+    wm = _g4.MaterialPredefined("G4_Galactic") 
+    bm = _g4.MaterialPredefined("G4_Fe") 
+
+    # solids
+    bps = _g4.solid.Box("bps",bpId,bpOd,bpl,0,2*_np.pi, reg, "mm")
+    bs = _g4.solid.Box("bs",bx,by,bz, reg, "mm")
+        
+    # structure 
+    wl = _g4.LogicalVolume(ws, wm, "wl", reg)
+    bl = _g4.LogicalVolume(bs, bm, "bl", reg)
+    bp = _g4.PhysicalVolume([0,0,0],[0,0,0],  bl, "b_pv1", wl, reg) 
+    
+    # set world volume
+    reg.setWorld(wl.name)
+    
+    # gdml output 
+    w = _gd.Writer()
+    w.addDetector(reg)
+    w.write(_os.path.join(_os.path.dirname(__file__), "CF_BeamPipe.gdml"))
+
+    v = _vi.VtkViewer()
+    v.addLogicalVolume(reg.getWorldVolume())
+    v.view()

### 2019-05-16 public/2019-ipac/examples/freecad.py
Paper update

@@ -1,0 +1,3 @@
+import pyg4ometry
+r = pyg4ometry.freecad.Reader("example.step")
+reg = r.getRegistry()

### 2019-05-16 public/2019-ipac/examples/stl.py

@@ -1,0 +1,3 @@
+import pyg4ometry
+r = pyg4ometry.stl.Reader("example.stl")
+reg = r.getRegistry()

### 2019-05-18 pyg4ometry/test/pythonCompoundExamples/CF_BeamPipe.py
Manaul updates

@@ -10,7 +10,7 @@ def CF_BeamPipe(bpLength = 200, bpId = 10, bpThickness = 5, cf_dn = '16') :
     cf_data = {'16': {'od':34, 'id':16, 'bd':27, 'h':7.5, 'nh':6, 'hd':4.3}}
 
     print cf_data[cf_dn]
-    
+       
     # defines 
     wx = _gd.Constant("wx",2*bpLength,reg,True)
     wy = _gd.Constant("wy",2*bpLength,reg,True)

### 2019-05-18 pyg4ometry/test/runTests.py

@@ -1,5 +1,6 @@
 from python import PythonAuthoringTests, PythonDefineTests
 from gdml import GdmlLoadTests
+from stl import StlLoadingTests
 
 import unittest as _unittest
 import logging as _log

### 2019-05-18 pyg4ometry/test/stl/StlLoadingTests.py

@@ -4,6 +4,7 @@ import pyg4ometry.geant4 as _g4
 import pyg4ometry.stl as _stl
 
 import logging as _log
+import os as _os
 
 logger = _log.getLogger()
 logger.disabled = True
@@ -11,23 +12,30 @@ logger.disabled = True
 def LoadStl(fileName) : 
     reg = _g4.Registry()
     r = _stl.Reader(fileName)    
-    l = r.logicalVolume("test",reg)
-    
-    return True
+    l = r.logicalVolume("test","G4_Cu",reg)
+        
+    return True,l
+
+def _pj(filename):
+    """
+    Append the absolute path to *this* directory to the filename so the tests
+    can be ran from anywhere
+    """
+    return _os.path.join(_os.path.dirname(__file__), filename)
 
 class StlTests(_unittest.TestCase) :
     def testLoadStlDog(self) :
-        self.assertTrue(LoadStl("dog.stl"))
-
+        ret,l = LoadStl(_pj("dog.stl"))
+        self.assertTrue(ret)
+                
     def testLoadStlDragon(self) :
-        self.assertTrue(LoadStl("dragon.stl"))
+        self.assertTrue(LoadStl(_pj("dragon.stl")))
 
     def testLoadStlRobot(self) :
-        self.assertTrue(LoadStl("robot.stl"))
+        self.assertTrue(LoadStl(_pj("robot.stl")))
 
     def testLoadStlTeapot(self) :
-        self.assertTrue(LoadStl("utahteapot.stl"))
-
-    
+        self.assertTrue(LoadStl(_pj("utahteapot.stl")))
+            
 if __name__ == '__main__':
     _unittest.main(verbosity=2)        

### 2019-05-18 pyg4ometry/test/stl/__init__.py
STL test import init

@@ -1,0 +1,1 @@
+from StlLoadingTests import *

### 2019-05-19 public/2019-ipac/WEPTS054.tex
Manaul updates
Update manual and new float,str,obj -> string method

@@
 \author{Stewart Boogert\thanks{stewart.boogert@rhul.ac.uk}, Andrey Abramov, Joshua Albrecht, \\ Gian Luigi D'Alessandro, Laurence Nevay, William Shields, Stuart Walker \\
-JAI, Egham, Surrey)}
+JAI at Royal Holloway, University of London, Egham, TW20 0EX, UK}
 
@@
 Studying the energy deposits in accelerator components, mechanical supports, services, ancillary equipment and shielding requires a detailed computer readable description of the component geometry.
-The creation of geometries is a significant bottle neck in producing complete simulation models and reducing the effort required will provide the ability of non-experts to simulate the effects of beam losses on realistic accelerators.
-The paper describes a flexible and easy to use PYTHON package to create geometries usable by either Geant4 (and so BDSIM or G4Beamline) or FLUKA either from scratch or by conversion from common engineering formats, such as STEP or IGES created by industry standard CAD/CAM packages.
+The creation of geometries is a significant bottleneck in producing complete simulation models and reducing the effort required will provide the ability of non-experts to simulate the effects of beam losses on realistic accelerators.
+The paper describes a flexible and easy to use Python package to create geometries usable by either Geant4 (and so BDSIM or G4Beamline) or FLUKA either from scratch or by conversion from common engineering formats, such as STEP or IGES created by industry standard CAD/CAM packages.
 The conversion requires an intermediate conversion to STL or similar triangular or tetrahedral tessellation description.
 A key capability of \verb|pyg4ometry| is to mix GDML/STEP/STL geometries and visualisation of the resulting geometry and determine if there are any geometric overlaps.
-An example conversion of a complex geometry is presented along with performance results for physical particle tracking of electromagnetically and hadronically produced particles using BDSIM.
+An example conversion of a complex geometry used in Geant4/BDSIM is presented.
 \end{abstract}
@@
 \section{INTRODUCTION}
-\verb|Pyg4ometry| started as an internal python scripting tool to generate beam line geometries for BDSIM.
+\verb|Pyg4ometry| started as an internal python scripting tool to generate beam line geometries for BDSIM \cite{bdsim_arxiv, bdsim_manual, Nevay:IPAC19-WEPTS058}.
 BDSIM is a Geant4 application which allows a user to rapidly create a full three dimensional model of an accelerator from an optical description.
@@
 A key requirement is to be able to integrate and composite geometry sources to a single file.
+%I would begin with introducing the concept of geometry for radiation transport and outline some of the problems and limitations mentioned later:
+%
+%* Models that describe the 3D layout, structure and composition of materials that particles can interact with
+%* Must have non-overlapping geometric entities (volumes) to ensure particles can uniquely be located in one such volume at a time. 
+%* Trade-off between geometry complexity and simulation execution time.
+%* Traditionally prepared by hand, separately to other 3D models like engineering specifications.
 
 \subsection{Particle transport codes}
-There are multiple different codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
-Generally accelerator codes, like MAD8, MADX, Transport etc, are interfaced to a Monte Carlo code to produce a complete simulation of beam losses.
-Two beam line simulation tools have been developed on the basis of Geant4, BDSIM and G4Beamline.
+There are multiple different Monte Carlo (MC) codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
+Generally accelerator codes, like MAD8 \cite{mad8}, MADX \cite{madx}, Transport \cite{transport} etc, are interfaced to a MC code to produce a complete simulation of beam losses.
+Two beam line simulation tools have been developed on the basis of Geant4; BDSIM~\cite{bdsim_arxiv} and G4Beamline~\cite{g4beamline}.
 
 \subsection{Geometry generation and GDML}
-The specification in a computer readable format the geometry of the material surrounding an accelerator can be an exceedingly time consuming and error prone task.
+The specification of the geometry of the material surrounding an accelerator can be an exceedingly time consuming and error prone task.
 Typically either the detector or accelerator infrastructure is constructed over many years and the simulation geometry can be created over similar time scales.
 This does not allow for rapid simulation of a system as the burden of creating the geometry is too great.
-An XML based markup language Geometry Description Markup Language (GDML) is used as the file format for geometry export in \verb|pyg4ometry|.
+An XML-based markup language, Geometry Description Markup Language (GDML) is used as the file format for geometry export in \verb|pyg4ometry|.
 
@@
 This is a much quicker interface to a full C++ Geant4 application and any programmed geometry can be viewed quickly using VTK.
-\verb|Pyg4ometry| geometry can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
+Geometry defined using \verb|Pyg4ometry| can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
 GDML has a simple mathematical expression language so geometries can be parametrised, this is also implemented in \verb|pyg4ometry| using ANTLR.
@@
 \subsection{Python}
-A complete code example for creation a simple geometry consisting of three Iron solids is shown below.
-The python interfaces are so similar to Geant4 C++ interface and a user can refer to the Geant4 documentation.
+A complete code example for creation of a simple geometry consisting of three Iron solids is shown below.
+The python interfaces are so similar to the Geant4 C++ interface and the user can refer to the Geant4 documentation.
 \VerbatimInput[fontsize=\small]{./examples/simple.py}
 The code is divided in 6 blocks of definitions, reusable parameters, materials, solids, structure and placement, GDML IO and finally visualisation.
-A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions which need to stored in the output file.
+A key difference between \verb|pyg4ometry| and Geant4 is a dedicated object known as the \verb|Registry| to store all geometry definitions to be stored in the output file.
 The VTK output from this example is shown in Figure~\ref{fig:simple}, where three solids, a cube, sphere and cylinder, are placed with translations and rotations within a cubical world volume.
@@
    \includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
-   \caption{Example of a more complex geometry example, this time a cavity beam position monitor.}
+   \caption{Example of a more complex geometry example, a cavity beam position monitor.}
    \label{fig:dipole}
@@
 \subsection{Standard tessellation language (STL)}
-STL file format describes a raw unstructured triangulated surface, the normal is defined by the ordering of the vertices. \verb|pyg4ometry| supports the loading 
-STL files and conversion to G4TessellatedSolid. 
+STL file format describes a raw unstructured triangulated surface, where the surface normal is defined by the ordering of the vertices. \verb|Pyg4ometry| supports the loading 
+STL files and conversion to G4TessellatedSolid. A classic STL example loaded in \verb|pg4ometry| and displayed in VTK is shown in Figure~\ref{fig:utahteapot}
 \VerbatimInput[fontsize=\small]{./examples/stl.py}
-
 \begin{figure}[!htb]
@@
    \caption{STL surface mesh rendered in VTK using pyg4ometry.}
-   \label{fig:simple}
+   \label{fig:utahteapot}
 \end{figure}
 
-\subsection{Computer aided design (STEP)}
+\subsection{Computer aided design/manufacturing (CAD/CAM)}
 Arbitrary conversion of CAD/CAM files to \verb|pyg4ometry| is a very challenging task. Typically users convert the CAD description into
-an intermediate surface triangulation (such as STL described previously) and load the geometry as a G4TessellatedSolid. An interface for
+an intermediate surface triangulation format (such as STL described previously) and load the geometry as a G4TessellatedSolid. An interface for
 loading STEP/STP files was creating using FreeCAD/OpenCASCADE. A single solid in general corresponds to a {\it part} and multiple placements 
@@
    \includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
-   \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T9 and T10 test beam lines to GDML Each part is 
-   coloured with a randomly to clearly indicate the structure of the shielding.}
+   \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T8 and T11 test beam lines to GDML. Each part is 
+   given a randomly assigned colour to clearly indicate the structure of the shielding.}
    \label{fig:ea910}
@@
 \section{BDSIM}
-
+Geometry created by \verb|pyg4ometry| can be directly loaded into Geant4 based application directly. Figure \ref{fig:dipole-bdsim} shows the cavity BPM 
+example loaded into BDSIM. 
 \begin{figure}[h!tb]
@@
    \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}
-   \label{fig:dipole}
+   \label{fig:dipole-bdsim}
 \end{figure}
@@
 an alternative C++ output writer can be quickly written to allow \verb|pyg4ometry| to generate C++ code which can be directly compiled into a 
-Geant4 application. Although not described in this publication a FLUKA geometry loader has been written and can load large pre-existing geometries into 
-\verb|pyg4ometry| and subsequently write GDML files. This is currently being refactored and will appear in the next public release of \verb|pyg4ometry|.
+Geant4 application. Although not described in this publication, a FLUKA geometry loader has been written and can load large pre-existing geometries into 
+\verb|Pyg4ometry| and subsequently write GDML files. This is currently being refactored and will appear in the next public release of \verb|pyg4ometry|.
 In addition to the FLUKA to GDML conversion, conversion of Geant4/GDML geometry to FLUKA is yet unstarted but a relatively straight forward
@@
 can composite geometry from multiple sources to create a complete model which can be exported directly to GDML and then can be loaded into a Geant4 
-based application. Although based on GDML and Geant4 \verb|pyg4ometry| can be easily extended to other MC simulation geometry formats.
-
-\section{ACKNOWLEDGEMENTS}
+based application. Although based on GDML and Geant4 \verb|pyg4ometry| can be easily extended to other MC simulation geometry formats. \verb|Pyg4ometry| is 
+available via git and published under a GPL licence \cite{pyg4omtery-git}.
 
@@
 
+	\bibitem{bdsim_arxiv} L.~Nevay, \emph{ et~al.}, ``Bdsim: An accelerator tracking code with particle-matter interactions,'' , {\tt arXiv:1808.10745}, 2018.
+
+	\bibitem{g4beamline} \url{http://www.muonsinternal.com/muons3/G4beamline}
+	\bibitem{bdsim_manual}  BDSIM manual, \url{http://www.pp.rhul.ac.uk/bdsim}
+	\bibitem{Nevay:IPAC19-WEPTS058} L.
+J.
+Nevay \emph{et al.}, \textquotedblleft{BDSIM: Recent Developments and New Features Beyond V1.0}\textquotedblright, presented at the 10th Int.
+Particle Accelerator Conf.
+(IPAC'19), Melbourne, Australia, May 2019, paper WEPTS058, this conference.
+
 	\bibitem{geant4} Recent developments in Geant4, NIMA 835, pages 186-225, 2016 	
-	\bibitem{fluka} CERN-2005-10 (2005),
+	\bibitem{fluka} A.~Ferrari, {\em et~al.}, ``{FLUKA}: a multi-particle transport code,'' {\em   CERN Report CERN-2005-10}, 2005.
+
+	\bibitem{mad8} MAD8 \url{http://mad8.web.cern.ch/mad8/}
+	\bibitem{madx} MAD-X \url{http://madx.web.cern.ch/madx/}
+	\bibitem{transport} PSI Graphic Transport Framework by U. Rohrer, based on a CERN-SLAC-FERMILAB version by K.L. Brown et al.
+
+	\bibitem{pyg4omtery-git} \url{https://bitbucket.org/jairhul/pyg4ometry/src/master/}
 
@@
 
-% for use as JACoW template the inclusion of the ANNEX parts have been commented out
-% to generate the complete documentation please remove the "%" of the next two commands
-% 
-%%%\newpage
-
-%@article{ALLISON2016186,
-%title = "Recent developments in Geant4",
-%journal = "Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment",
-%volume = "835",
-%pages = "186 - 225",
-%year = "2016",
-%issn = "0168-9002",
-%doi = "https://doi.org/10.1016/j.nima.2016.06.125",
-%url = "http://www.sciencedirect.com/science/article/pii/S0168900216306957",
-%author = "J.
-Allison and K.
-Amako and J.
-Apostolakis and P.
-Arce and M.
-Asai and T.
-Aso and E.
-Bagli and A.
-Bagulya and S.
-Banerjee and G.
-Barrand and B.R.
-Beck and A.G.
-Bogdanov and D.
-Brandt and J.M.C.
-Brown and H.
-Burkhardt and Ph.
-Canal and D.
-Cano-Ott and S.
-Chauvie and K.
-Cho and G.A.P.
-Cirrone and G.
-Cooperman and M.A.
-Cortés-Giraldo and G.
-Cosmo and G.
-Cuttone and G.
-Depaola and L.
-Desorgher and X.
-Dong and A.
-Dotti and V.D.
-Elvira and G.
-Folger and Z.
-Francis and A.
-Galoyan and L.
-Garnier and M.
-Gayer and K.L.
-Genser and V.M.
-Grichine and S.
-Guatelli and P.
-Guèye and P.
-Gumplinger and A.S.
-Howard and I.
-Hřivnáčová and S.
-Hwang and S.
-Incerti and A.
-Ivanchenko and V.N.
-Ivanchenko and F.W.
-Jones and S.Y.
-Jun and P.
-Kaitaniemi and N.
-Karakatsanis and M.
-Karamitros and M.
-Kelsey and A.
-Kimura and T.
-Koi and H.
-Kurashige and A.
-Lechner and S.B.
-Lee and F.
-Longo and M.
-Maire and D.
-Mancusi and A.
-Mantero and E.
-Mendoza and B.
-Morgan and K.
-Murakami and T.
-Nikitina and L.
-Pandola and P.
-Paprocki and J.
-Perl and I.
-Petrović and M.G.
-Pia and W.
-Pokorski and J.M.
-Quesada and M.
-Raine and M.A.
-Reis and A.
-Ribon and A.
-Ristić Fira and F.
-Romano and G.
-Russo and G.
-Santin and T.
-Sasaki and D.
-Sawkey and J.I.
-Shin and I.I.
-Strakovsky and A.
-Taborda and S.
-Tanaka and B.
-Tomé and T.
-Toshito and H.N.
-Tran and P.R.
-Truscott and L.
-Urban and V.
-Uzhinsky and J.M.
-Verbeke and M.
-Verderi and B.L.
-Wendt and H.
-Wenzel and D.H.
-Wright and D.M.
-Wright and T.
-Yamashita and J.
-Yarba and H.
-Yoshida",
-%keywords = "High energy physics, Nuclear physics, Radiation, Simulation, Computing",
-%abstract = "Geant4 is a software toolkit for the simulation of the passage of particles through matter.
-It is used by a large number of experiments and projects in a variety of application domains, including high energy physics, astrophysics and space science, medical physics and radiation protection.
-Over the past several years, major changes have been made to the toolkit in order to accommodate the needs of these user communities, and to efficiently exploit the growth of computing power made available by advances in technology.
-The adaptation of Geant4 to multithreading, advances in physics, detector modeling and visualization, extensions to the toolkit, including biasing and reverse Monte Carlo, and tools for physics and release validation are discussed here."
-%}
-
-%"FLUKA: a multi-particle transport code"
-%A. Ferrari, P.R. Sala, A. Fasso`, and J. Ranft,
-% CERN-2005-10 (2005), INFN/TC_05/11, SLAC-R-773
-
-%%%\include{annexes-A4}
-
 \end{document}

### 2019-05-19 public/2019-ipac/WEPTS054.tex
Comments from authors

@@
 % v 2.3  Feb 2019   Volker RW Schaa
-%		# changes in the collaboration therefore updated file "jacow-collaboration.tex"
-%		# all References with DOIs have their period/full stop before the DOI (after pp. or year)
-%		# in the author/affiliation block all ZIP codes in square brackets removed as it was not %         understood as optional parameter and ZIP codes had bin put in brackets
-%       # References to the current IPAC are changed to "IPAC'19, Melbourne, Australia"
-%       # font for ‘url’ style changed to ‘newtxtt’ as it is easier to distinguish "O" and "0"
+%# changes in the collaboration therefore updated file ``jacow-collaboration.tex''
+%# all References with DOIs have their period/full stop before the DOI (after pp. or year)
+%# in the author/affiliation block all ZIP codes in square brackets removed as it was not %         understood as optional parameter and ZIP codes had bin put in brackets
+%       # References to the current IPAC are changed to ``IPAC'19, Melbourne, Australia''
+%       # font for ‘url’ style changed to ‘newtxtt’ as it is easier to distinguish ``O'' and ``0''
 %
@@
                %nospread,     % flushend option: do not fill with whitespace to balance columns
-               %hyphens,      % allow \url to hyphenate at "-" (hyphens)
+               %hyphens,      % allow \url to hyphenate at ``-'' (hyphens)
                %xetex,        % use XeLaTeX to process the file
@@
 \section{INTRODUCTION}
-\verb|Pyg4ometry| started as an internal python scripting tool to generate beam line geometries for BDSIM \cite{bdsim_arxiv, bdsim_manual, Nevay:IPAC19-WEPTS058}.
+
+Simulating radiation transport in an accelerator beamline requires a description of the 3D layout, structure, dimensions and material properties of the physical objects that the beam particles can interact with.
+This description is commonly referred to as a ``geometry model'' or ``geometry''.
+In general, the elements (volumes) in such a model must not overlap, ensuring that particles can be located in only one volume at a time.
+There is also a trade-off between the geometry detail and the simulation execution time.
+Because of those constraints, radiation transport geometries have traditionally been prepared by hand.\\
+\verb|Pyg4ometry| started as a python scripting tool to generate beam line geometries for BDSIM.
 BDSIM is a Geant4 application which allows a user to rapidly create a full three dimensional model of an accelerator from an optical description.
@@
 \subsection{Particle transport codes}
-There are multiple different Monte Carlo (MC) codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX and FLUKA \cite{fluka}.
+There are multiple different Monte Carlo (MC) codes to simulate the transportation and physics processes of particles though accelerators and detectors, these include Geant4 \cite{geant4}, MCMPX~\cite{mcnpx} and FLUKA \cite{fluka}.
 Generally accelerator codes, like MAD8 \cite{mad8}, MADX \cite{madx}, Transport \cite{transport} etc, are interfaced to a MC code to produce a complete simulation of beam losses.
@@
 Geometry defined using \verb|Pyg4ometry| can be converted to a surface triangulation using primitive mesh generation of each solid in python and a constructive solid geometry (CSG) library based on Binary Space Partitioning (BSP) trees.
-GDML has a simple mathematical expression language so geometries can be parametrised, this is also implemented in \verb|pyg4ometry| using ANTLR.
+GDML has a simple mathematical expression language so geometries can be parametrised, this is also implemented in \verb|pyg4ometry| using ANTLR~\cite{antlr}.
 A Python interface to the geometry primitives of Geant4 allows conversion applications to be developed from FLUKA/STEP/STL descriptions to \verb|pyg4ometry|.
@@
 \section{BDSIM}
-Geometry created by \verb|pyg4ometry| can be directly loaded into Geant4 based application directly. Figure \ref{fig:dipole-bdsim} shows the cavity BPM 
+Geometry created by \verb|pyg4ometry| can be directly loaded into Geant4 based. Figure~\ref{fig:dipole-bdsim} shows the cavity BPM 
 example loaded into BDSIM. 
@@
 %
-% only for "biblatex"
+% only for ``biblatex''
 %
@@
 {%
-	% "biblatex" is not used, go the "manual" way
+  % ``biblatex'' is not used, go the ``manual'' way
 
@@
 
-	\bibitem{g4beamline} \url{http://www.muonsinternal.com/muons3/G4beamline}
+      \bibitem{g4beamline} G4Beamline documentation, \url{http://www.muonsinternal.com/muons3/G4beamline}
         \bibitem{bdsim_manual}  BDSIM manual, \url{http://www.pp.rhul.ac.uk/bdsim}
@@
             \bibitem{fluka} A.~Ferrari, {\em et~al.}, ``{FLUKA}: a multi-particle transport code,'' {\em   CERN Report CERN-2005-10}, 2005.
-
-	\bibitem{mad8} MAD8 \url{http://mad8.web.cern.ch/mad8/}
-	\bibitem{madx} MAD-X \url{http://madx.web.cern.ch/madx/}
+    \bibitem{mcnpx} MCNPX user manual,  \url{https://laws.lanl.gov/vhosts/mcnp.lanl.gov/pdf\_files/la-ur-02-2607.pdf}
+    \bibitem{antlr} ANTLR documentation, \url{https://www.antlr.org}
+      \bibitem{mad8} MAD8 documentation, \url{http://mad8.web.cern.ch/mad8/}
+        \bibitem{madx} MAD-X documentation, \url{http://madx.web.cern.ch/madx/}
           \bibitem{transport} PSI Graphic Transport Framework by U. Rohrer, based on a CERN-SLAC-FERMILAB version by K.L. Brown et al.
 
-	\bibitem{pyg4omtery-git} \url{https://bitbucket.org/jairhul/pyg4ometry/src/master/}
+            \bibitem{pyg4omtery-git} Pyg4ometry project, \url{https://bitbucket.org/jairhul/pyg4ometry/src/master/}
 

### 2019-05-19 pyg4ometry/test/python/PythonDefineTests.py
Constructor tests

@@ -11,20 +11,40 @@ class PythonDefineTests(_unittest.TestCase) :
 
     def testExpressionInt(self) :
         r = pyg4ometry.geant4.Registry()
-        xc = pyg4ometry.gdml.Constant("xc","1",r)        
+        xc = pyg4ometry.gdml.Constant("xc",1,r)        
         self.assertEqual(xc.eval(),1)
 
     def testExpressionFloat(self) :
         r = pyg4ometry.geant4.Registry()
+        xc = pyg4ometry.gdml.Constant("xc",1.2345,r)        
+        self.assertEqual(xc.eval(),1.2345)
+
+    def testExpressionScientific1(self) :
+        r = pyg4ometry.geant4.Registry()
+        xc = pyg4ometry.gdml.Constant("xc",1E3,r)        
+        self.assertEqual(xc.eval(),1000)
+
+    def testExpressionScientific2(self) :
+        r = pyg4ometry.geant4.Registry()
+        xc = pyg4ometry.gdml.Constant("xc",1.2345E3,r)
+        self.assertEqual(xc.eval(),1234.5)
+
+    def testExpressionStringInt(self) :
+        r = pyg4ometry.geant4.Registry()
+        xc = pyg4ometry.gdml.Constant("xc","1",r)        
+        self.assertEqual(xc.eval(),1)
+
+    def testExpressionStringFloat(self) :
+        r = pyg4ometry.geant4.Registry()
         xc = pyg4ometry.gdml.Constant("xc","1.2345",r)        
         self.assertEqual(xc.eval(),1.2345)
 
-    def testExpressionIntScientific(self) :
+    def testExpressionStringScientific1(self) :
         r = pyg4ometry.geant4.Registry()
         xc = pyg4ometry.gdml.Constant("xc","1E3",r)        
         self.assertEqual(xc.eval(),1000)
 
-    def testExpressionFloatScientific(self) :
+    def testExpressionStringScientific2(self) :
         r = pyg4ometry.geant4.Registry()
         xc = pyg4ometry.gdml.Constant("xc","1.2345E3",r)
         self.assertEqual(xc.eval(),1234.5)

### 2019-05-19 public/2019-ipac/WEPTS054.tex
Updated doc strings for manual

@@
 The python interfaces are so similar to the Geant4 C++ interface and the user can refer to the Geant4 documentation.
-\VerbatimInput[fontsize=\small]{./examples/simple.py}
+%\VerbatimInput[fontsize=\small]{./examples/simple.py}
+\VerbatimInput[fontsize=\small]{simple.py}
 The code is divided in 6 blocks of definitions, reusable parameters, materials, solids, structure and placement, GDML IO and finally visualisation.
@@
    \centering
-   \includegraphics*[width=.9\columnwidth]{./examples/simple.jpg}
+   %\includegraphics*[width=.9\columnwidth]{./examples/simple.jpg}
+   \includegraphics*[width=.9\columnwidth]{simple.jpg}
    \caption{Example of three primitive Geant4 solids rendered in VTK.}
@@
    \centering
-   \includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
+   %\includegraphics*[width=.8\columnwidth]{./examples/dipole.jpg}
+   \includegraphics*[width=.8\columnwidth]{dipole.jpg}
    \caption{Example of a more complex geometry example, a cavity beam position monitor.}
@@
 STL files and conversion to G4TessellatedSolid. A classic STL example loaded in \verb|pg4ometry| and displayed in VTK is shown in Figure~\ref{fig:utahteapot}
-\VerbatimInput[fontsize=\small]{./examples/stl.py}
+%\VerbatimInput[fontsize=\small]{./examples/stl.py}
+\VerbatimInput[fontsize=\small]{stl.py}
 \begin{figure}[!htb]
    \centering
-   \includegraphics*[width=.6\columnwidth]{./examples/utahteapot.jpg}
+   %\includegraphics*[width=.6\columnwidth]{./examples/utahteapot.jpg}
+   \includegraphics*[width=.6\columnwidth]{utahteapot.jpg}
+
    \caption{STL surface mesh rendered in VTK using pyg4ometry.}
@@
 A example of a conversion of a large STEP file to pyg4ometry/GDML is shown in Figure~\ref{fig:ea910}.
-\VerbatimInput[fontsize=\small]{./examples/freecad.py}
+%\VerbatimInput[fontsize=\small]{./examples/freecad.py}
+\VerbatimInput[fontsize=\small]{freecad.py}
 \begin{figure}[!htb]
    \centering
-   \includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
+   %\includegraphics*[width=1.0\columnwidth]{./examples/ea9-10.jpg}
+   \includegraphics*[width=1.0\columnwidth]{ea9-10.jpg}
    \caption{Example a conversion from STEP file description of the shielding of the CERN East Area T8 and T11 test beam lines to GDML. Each part is 
@@
    \centering
-   \includegraphics*[width=1.0\columnwidth]{./examples/dipole_bdsim.jpg}
+   %\includegraphics*[width=1.0\columnwidth]{./examples/dipole_bdsim.jpg}
+   \includegraphics*[width=1.0\columnwidth]{dipole_bdsim.jpg}
    \caption{Example of geometry in Geant4/BDSIM. The example shows a 50~GeV proton interacting with the geometry material.}

### 2019-08-07 public/paper/pyg4ometry.tex
Started citations and updated verb/it of pyg4ometry

--- 2019-03-07 paper/pyg4ometry.tex
@@
 
-\title{pyg4ometry: a python library for the creation of Monte Carlo particle transport geometries}
+\title{Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries}
 
@@
 There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
-include MCMP, FLUKA, Geant3 and Geant4. All these codes are based on the Monte Carlo technique but each code either has a particular specialism 
-or target user community.  PT Monte Carlo simulations have diverse uses, shielding calculations for radiological protection, detector performance, medical 
-imaging and therapy, space radiation environment simulation are some examples. A fundamental requirement of all of the codes is to supply a computer 
-readable description of the physical geometry that the particles are passing through.  The creation of geometry files is typically a very time consuming activity, 
-the simulation validity and performance is directly dependent on the quality of the geometry. The requirement of a  geometry system that allows the conversion 
-between files prepared for different codes will enable cross checks of the physics processes in particle transport codes. Parallel to the creation of geometry files 
-for PT programs, usually computer assisted design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric 
-representations in CAD files is typically not amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle 
-transport code users to rapidly develop geometry files, convert between common PT programme geometry formats and finally import CAD models. This paper 
-describes such geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry 
+include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
+All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  PT Monte Carlo simulations 
+have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment 
+simulation are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that 
+the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity and performance is directly 
+dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared for different codes will 
+enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted 
+design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not 
+amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
+geometry files, convert between common PT programme geometry formats and finally import CAD models.
+
+This paper describes such geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry 
 description. The main features of  {\em pyg4ometry} are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry 
-descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD-OpenCascade and powerful geometry visualisation tools based on VTK. 
-The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 called BDSIM. Accelerator physicists 
-like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle beam with the accelerator material.
+descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} OpenCascade \cite{OpenCASCADE} and powerful geometry 
+visualisation tools based on VTK \cite{VTK4}. The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 
+called BDSIM. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle 
+beam with the accelerator material.
+
+There are existing codes that have functionality similar to pyg4ometry. Tools exist to convert CAD files to GDML, e.g. GUIMesh \cite{GUIMesh_Pinto}.
+CAD software can export data to STL. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
 
@@
 
-\subsection{Expression engine}
+\subsection{Expression evaluation}
 In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
@@
 
-\subsection{Tessellation engine}
+\subsection{Tessellation of solids}
 For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
@@
 \subsection{Input and output} 
-For each input format available in {\it pyg4ometry} a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
+For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
 and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a registry which can be used or manipulated by the user. 
@@
 All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
-throughsuch a situation.  A key feature of {\it pyg4ometry} is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
+throughsuch a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
 and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
@@
 \section{Performance of converted geometry in Geant4}
-Clearly for Geant4 geometry defined in {\it pyg4ometry} the performance is exactly the same as it the geometry was specified in C++ and linked against the Geant4
+Clearly for Geant4 geometry defined in pyg4ometry the performance is exactly the same as it the geometry was specified in C++ and linked against the Geant4
 libraries. A comparison of the performance of converted CAD or FLUKA geometry compared with native Geant4 solids is required so a user can optimise the available
@@
 The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in particle transport Monte Carlo programmes will save significant 
-amounts of user effort and ultimately yield more accurate simulations. {\it pyg4ometry} is a relatively complete implementation of a geometry creation tool, whilst heavily 
-internally based on Geant4 and GDML can have utility for users of all PT codes. {\it pyg4ometry} can clearly be extended to other formats or applications. As for applications,
+amounts of user effort and ultimately yield more accurate simulations. Pyg4ometry is a relatively complete implementation of a geometry creation tool, whilst heavily 
+internally based on Geant4 and GDML can have utility for users of all PT codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications,
 examples include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble  dark matter detectors and geometries for event visualisation. 
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{<your-bib-database>}
-
+\bibliography{pyg4ometry}
 %% Authors are advised to submit their bibtex database files. They are

### 2019-08-07 public/paper/diagrams/rapidModelling.py
Fixed for most recent pyg4ometry

@@ -6,9 +6,9 @@ import pyg4ometry.visualisation as vi
 reg = g4.Registry()
 
 # expressions
-wx = gd.Constant("wx","50",reg)
-wy = gd.Constant("wy","50",reg)
-wz = gd.Constant("wz","50",reg)
+wx = gd.Constant("wx","100",reg)
+wy = gd.Constant("wy","100",reg)
+wz = gd.Constant("wz","100",reg)
 bx = gd.Constant("bx","10",reg)
 by = gd.Constant("by","10",reg)
 bz = gd.Constant("bz","10",reg)
@@ -26,9 +26,9 @@ wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, bm, "b", reg)
 bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],
                         bl, "b_pv1", wl, reg)
-bp2 = g4.PhysicalVolume([0,0,-0.25],[-3*bx,0,0],
+bp2 = g4.PhysicalVolume([0,0,-0.25],[-2*bx,0,0],
                         bl, "b_pv2", wl, reg)
-bp3 = g4.PhysicalVolume([0,0,0.5],[3*bx,0,0],
+bp3 = g4.PhysicalVolume([0,0,0.5],[2*bx,0,0],
                         bl, "b_pv3", wl, reg)
 
 reg.setWorld(wl.name)

### 2019-08-11 pyg4ometry/test/gdml/GdmlLoadTests.py
Put back in scale test

@@ -368,7 +368,6 @@ class GdmlLoadTests(_unittest.TestCase) :
 
     def testChargeExhangeMC(self):
         self.assertTrue(testSingleGDML("../gdmlG4examples/ChargeExchangeMC/lht.gdml"))
-
     def testG01assembly(self):
         self.assertTrue(testSingleGDML("../gdmlG4examples/G01/assembly.gdml"))
 
@@ -399,8 +398,8 @@ class GdmlLoadTests(_unittest.TestCase) :
     def testG01scale(self):
         self.assertTrue(testSingleGDML("../gdmlG4examples/G01/scale.gdml"))
 
-#    def testG01solids(self):
-#        self.assertTrue(testSingleGDML("../gdmlG4examples/G01/solids.gdml"))
+    def testG01solids(self):
+        self.assertTrue(testSingleGDML("../gdmlG4examples/G01/solids.gdml"))
 
     def testG01tess(self):
         self.assertTrue(testSingleGDML("../gdmlG4examples/G01/tess.gdml"))

### 2019-08-11 public/paper/pyg4ometry.tex
Transform maths in paper
Updated gdml tag and class table

@@
 \centering
-\begin{tabular}{|c|c|c|} \hline
+\begin{tabular}{|l|l|l|} \hline
 GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
-Defines 			&						&						\\
-Solids 			&						&						\\
-Materials 			&						&						\\
-Structure			&						&						\\ \hline
+define 			& constant				& gdml.Constant				\\
+				& variable					& gdml.Variable					\\
+				& expression 				& gdml.Expression				\\
+				& position					& gdml.Position					\\
+				& rotation					& gdml.Rotation				\\
+				& scale					& gdml.Scale					\\
+				& matrix					& gdml.Matrix					\\
+materials 			& element					& geant4.Element				\\
+				& isotope					& geant4.Isotope				\\
+				& material					& geant4.Material				\\
+solid  			& box					& geant4.solid.Box				\\
+	  			& tube					&							\\
+	  			& cutTube					&							\\
+	  			& cone					&							\\
+	  			& para					&							\\
+	  			& trd						&							\\
+	  			& trap					&							\\
+	  			& sphere					&							\\
+	  			& orb					&							\\
+	  			& torus					&							\\
+	  			& polycone				&							\\
+	  			& genericPolycone			&							\\
+	  			& polyhedra				&							\\
+	  			& eltube					&							\\
+	  			& ellipsoid					&							\\
+	  			& elcone					&							\\
+				& paraboloid				&							\\
+				& hype					& 							\\
+				& tet						& 							\\
+				& xtru					& 							\\
+				& twistedbox				& 							\\
+				& twistedtrap				& 							\\
+				& twistedtrd				& 							\\
+				& twistedtube				& 							\\
+				& arb8					& 							\\
+				& tesselated				& 							\\
+				& union					& 							\\
+				& subtraction				& 							\\
+				& intersection				& 							\\
+				& multiUnion				& 							\\				
+	  			& opticalsurface			&							\\
+structure			& volume					& geant4.LogicalVolume			\\
+				& physvol					& geant4.PhysicalVolume			\\ 
+				& replicavol				& geant4.ReplicaVolume			\\ 
+				& paravol					& geant4.ParameterisedVolume	\\ 
+				& divisionvol				& geant4.DivisionVolume			\\
+				& skinsurface				& geant4.SkinSurface			\\ 
+				& bordersurface			& geant4.BorderSurface			\\ \hline
+
 \end{tabular}
-\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
+\caption{GDML tags and corresponding pyg4ometry classes.}
 \end{table}
 
-\section{{\em pyg4ometry} design and layout}
+\section{pyg4ometry design and layout}
 The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
@@
 A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
-to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
+to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}$, scale $\mathbf{S}$ and 
+translation $\mathbf{T}$.
+
+\begin{eqnarray}
+\mathbf{M}	  	& = & \mathbf{M}_p \mathbf{M}_d  = \mathbf{S}_p \mathbf{R}_p  \mathbf{S}_d \mathbf{R}_d\\
+\mathbf{T}	 		& = & \mathbf{M}_p \mathbf{T}_d + \mathbf{T}_p= \mathbf{S}_p \mathbf{R}_p \mathbf{T}_d + \mathbf{T}_p,
+\end{eqnarray}
+where the subscript $p$ indicates parent volume and $d$ indicates daughter volume.
+
+The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
 color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove

### 2019-08-11 public/paper/pyg4ometry.tex
Code for registry merge

--- 2019-08-07 public/paper/pyg4ometry.tex
@@
 \centering
-\begin{tabular}{|c|c|c|} \hline
+\begin{tabular}{|l|l|l|} \hline
 GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
-Defines 			&						&						\\
-Solids 			&						&						\\
-Materials 			&						&						\\
-Structure			&						&						\\ \hline
+define 			& constant				& gdml.Constant				\\
+				& variable					& gdml.Variable					\\
+				& quantity					& gdml.Quantity				\\
+				& expression 				& gdml.Expression				\\
+				& position					& gdml.Position					\\
+				& rotation					& gdml.Rotation				\\
+				& scale					& gdml.Scale					\\
+				& matrix					& gdml.Matrix					\\
+materials 			& element					& geant4.Element				\\
+				& isotope					& geant4.Isotope				\\
+				& material					& geant4.Material				\\
+solid  			& box					& geant4.solid.Box				\\
+	  			& tube					&							\\
+	  			& cutTube					&							\\
+	  			& cone					&							\\
+	  			& para					&							\\
+	  			& trd						&							\\
+	  			& trap					&							\\
+	  			& sphere					&							\\
+	  			& orb					&							\\
+	  			& torus					&							\\
+	  			& polycone				&							\\
+	  			& genericPolycone			&							\\
+	  			& polyhedra				&							\\
+	  			& eltube					&							\\
+	  			& ellipsoid					&							\\
+	  			& elcone					&							\\
+				& paraboloid				&							\\
+				& hype					& 							\\
+				& tet						& 							\\
+				& xtru					& 							\\
+				& twistedbox				& 							\\
+				& twistedtrap				& 							\\
+				& twistedtrd				& 							\\
+				& twistedtube				& 							\\
+				& arb8					& 							\\
+				& tesselated				& 							\\
+				& union					& 							\\
+				& subtraction				& 							\\
+				& intersection				& 							\\
+				& multiUnion				& 							\\				
+	  			& opticalsurface			&							\\
+structure			& volume					& geant4.LogicalVolume			\\
+				& physvol					& geant4.PhysicalVolume			\\ 
+				& replicavol				& geant4.ReplicaVolume			\\ 
+				& paravol					& geant4.ParameterisedVolume	\\ 
+				& divisionvol				& geant4.DivisionVolume			\\
+				& skinsurface				& geant4.SkinSurface			\\ 
+				& bordersurface			& geant4.BorderSurface			\\ \hline
+
 \end{tabular}
-\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
+\caption{GDML tags and corresponding pyg4ometry classes.}
 \end{table}
 
-\section{{\em pyg4ometry} design and layout}
+\section{pyg4ometry design and layout}
 The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.

### 2019-08-11 pyg4ometry/test/gdml/GdmlLoadTests.py

@@ -180,7 +180,7 @@ class MeshValidator(object):
 
 _meshValidator = MeshValidator(verbosity=0)
 
-def testSingleGDML(filename):
+def testSingleGDML(filename, interactive = False):
     filepath = _pj(filename)
 
     # Loading
@@ -190,7 +190,7 @@ def testSingleGDML(filename):
     # Visualisation
     v = pyg4ometry.visualisation.VtkViewer()
     v.addLogicalVolume(registry.getWorldVolume())
-    v.view(interactive=False)
+    v.view(interactive=interactive)
 
     # Writing
     newFilename = filepath.replace(".gdml", "_processed.gdml")

### 2019-08-12 public/paper/pyg4ometry.tex

--- 2019-08-07 public/paper/pyg4ometry.tex
@@
 \centering
-\begin{tabular}{|c|c|c|} \hline
+\begin{tabular}{|l|l|l|} \hline
 GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
-Defines 			&						&						\\
-Solids 			&						&						\\
-Materials 			&						&						\\
-Structure			&						&						\\ \hline
+define 			& constant				& gdml.Constant				\\
+				& variable					& gdml.Variable					\\
+				& quantity					& gdml.Quantity				\\
+				& expression 				& gdml.Expression				\\
+				& position					& gdml.Position					\\
+				& rotation					& gdml.Rotation				\\
+				& scale					& gdml.Scale					\\
+				& matrix					& gdml.Matrix					\\
+materials 			& element					& geant4.Element				\\
+				& isotope					& geant4.Isotope				\\
+				& material					& geant4.Material				\\
+solid  			& box					& geant4.solid.Box				\\
+	  			& tube					&							\\
+	  			& cutTube					&							\\
+	  			& cone					&							\\
+	  			& para					&							\\
+	  			& trd						&							\\
+	  			& trap					&							\\
+	  			& sphere					&							\\
+	  			& orb					&							\\
+	  			& torus					&							\\
+	  			& polycone				&							\\
+	  			& genericPolycone			&							\\
+	  			& polyhedra				&							\\
+	  			& eltube					&							\\
+	  			& ellipsoid					&							\\
+	  			& elcone					&							\\
+				& paraboloid				&							\\
+				& hype					& 							\\
+				& tet						& 							\\
+				& xtru					& 							\\
+				& twistedbox				& 							\\
+				& twistedtrap				& 							\\
+				& twistedtrd				& 							\\
+				& twistedtube				& 							\\
+				& arb8					& 							\\
+				& tesselated				& 							\\
+				& union					& 							\\
+				& subtraction				& 							\\
+				& intersection				& 							\\
+				& multiUnion				& 							\\
+				& scaledSolid				&							\\				
+	  			& opticalsurface			&							\\
+structure			& volume					& geant4.LogicalVolume			\\
+				& physvol					& geant4.PhysicalVolume			\\ 
+				& replicavol				& geant4.ReplicaVolume			\\ 
+				& paravol					& geant4.ParameterisedVolume	\\ 
+				& divisionvol				& geant4.DivisionVolume			\\
+				& skinsurface				& geant4.SkinSurface			\\ 
+				& bordersurface			& geant4.BorderSurface			\\ \hline
+
 \end{tabular}
-\caption{GDML tags and corresponding {\it pyg4ometry} classes.}
+\caption{GDML tags and corresponding pyg4ometry classes.}
 \end{table}
 
-\section{{\em pyg4ometry} design and layout}
+\section{pyg4ometry design and layout}
 The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
@@
 should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
+
+\begin{figure*}[hbt]
+  \normalsize
+  \centering
+  \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
+  \caption{\label{fig:workflow}Workflow}
+\end{figure*}
 
@@
 A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
-to place the meshes associated with each physical volume. The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
+to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}$, scale $\mathbf{S}$ and 
+translation $\mathbf{T}$.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
+\caption{Placement of physical volume inside a logical volume}
+\label{fig:lvToPv}
+\end{center}
+\end{figure}
+
+\begin{eqnarray}
+\mathbf{M}	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d\\
+\mathbf{T}	 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m,
+\end{eqnarray}
+where the subscript $p$ indicates parent volume and $d$ indicates daughter volume.
+
+The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
 color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove
@@
 \begin{center}
-\includegraphics[width=10cm]{./diagrams/rapidModelling.pdf}
+\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
 \caption{VTK visualisation output from code example XXX.}

### 2019-08-16 public/paper/pyg4ometry.tex
Paper update

@@
 %% The lineno packages adds line numbers. Start line numbering with
+
 %% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
@@
 structure			& volume					& geant4.LogicalVolume			\\
+				& assembly				& geant4.AssemblyVolume 		\\
 				& physvol					& geant4.PhysicalVolume			\\ 
@@
 
-\subsection{Overlap detection}
-All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
-throughsuch a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
-and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
-
-{\small 
-\begin{verbatim}
-Overlap detection
-\end{verbatim}
-}
-
-For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$.
-This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final
-PT simulation.
-This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
-Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered.
-
  \subsection{Volume bounding} 
@@
 A pure geometry description is an insufficient description for a PT simulation. Often other attributes need to be assigned for example material definition, magnetic field or
+
+\subsection{Overlap detection}
+All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+throughsuch a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
+and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
+
+{\small 
+\begin{verbatim}
+Overlap detection
+\end{verbatim}
+}
+
+For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$.
+This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final
+PT simulation.
+This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
+Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered.
+ \begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=8cm]{./diagrams/overlap.pdf}
+\caption{Placement of physical volume inside a logical volume}
+\label{fig:lvToPv}
+\end{center}
+\end{figure}
 
@@
 
+\begin{table}[hbt!]
+\centering
+\begin{tabular}{|l|l|l|} \hline
+Fluka body			& note			& pyg4ometry class 				\\ \hline
+RPP (done)			&				&							\\
+BOX					&				&							\\
+SPH (done)			&				&							\\
+RCC (done)			&				&							\\
+REC (done)			&				&							\\
+TRC (done)			&				&							\\
+ELL 					&				&							\\
+WED					&				&							\\
+RAW					&				&							\\
+ARB					&				&							\\
+XYP (done)			&				&							\\
+XZP (done)			&				&							\\
+YZP (done)			&				&							\\
+PLA (done)			&				&							\\
+XCC (done)			&				&							\\
+YCC (done)			&				&							\\
+ZCC (done)			&				&							\\
+XEC (done)			&				&							\\
+YEC (done)			&				&							\\
+ZEC (done)			&				&							\\
+QUA (done)			&				&							\\ \hline
+\end{tabular}
+\caption{Fluka geometry directives pyg4ometry classes.}
+\end{table}
+
 \begin{enumerate} 

### 2019-11-16 pyg4ometry/test/pythonGeant4/T600_LVTessellated.py
Rotate and change material for better scattering

@@ -26,7 +26,7 @@ def Test(vis=False, interactive=False):
     cthighz    = _gd.Constant("cthighz", "1", reg, True)
 
     wm = _g4.Material(name="G4_Galactic")
-    bm = _g4.Material(name="G4_Fe")
+    bm = _g4.Material(name="G4_W")
 
     # solids
     ws = _g4.solid.Box("ws", wx, wy, wz, reg, "mm")
@@ -41,7 +41,7 @@ def Test(vis=False, interactive=False):
     ctl.makeSolidTessellated()  # Operation is in-place
 
     # Place the lv as normal
-    ctp = _g4.PhysicalVolume([0, 0, 0], [0, 0, 0], ctl, "ct_pv1", wl, reg)
+    ctp = _g4.PhysicalVolume([3.14/2., 0, 0], [0, 0, 0], ctl, "ct_pv1", wl, reg)
 
     # set world volume
     reg.setWorld(wl.name)
@@ -50,6 +50,7 @@ def Test(vis=False, interactive=False):
     w = _gd.Writer()
     w.addDetector(reg)
     w.write(_os.path.join(_os.path.dirname(__file__), "T600_LVTessellated.gdml"))
+    w.writeGmadTester(_os.path.join(_os.path.dirname(__file__))+"T600_LVTessellated.gmad","T600_LVTessellated.gdml")
 
     # visualisation
     if vis:

### 2019-11-16 pyg4ometry/test/pythonGeant4/T008_Sphere.py
Partially complete new sphere meshing

@@ -15,10 +15,12 @@ def Test(vis = False, interactive = False) :
     # pi     = _gd.Constant("pi","3.1415926",reg,True)
     srmin  = _gd.Constant("rmin","8",reg,True)    
     srmax  = _gd.Constant("rmax","10",reg,True)
-    ssphi  = _gd.Constant("sphi","0",reg,True)    
-    sdphi  = _gd.Constant("dphi","pi",reg,True)
-    sstheta= _gd.Constant("stheta","0",reg,True)    
+    ssphi  = _gd.Constant("sphi","0.0",reg,True)
+    # sdphi  = _gd.Constant("dphi","2*pi",reg,True)
+    sdphi = _gd.Constant("dphi", "pi", reg, True)
+    sstheta= _gd.Constant("stheta","0.0",reg,True)
     sdtheta= _gd.Constant("dtheta","3*pi/4",reg,True)
+    # sdtheta = _gd.Constant("dtheta", "pi", reg, True)
 
     wm = _g4.MaterialPredefined("G4_Galactic") 
     sm = _g4.MaterialPredefined("G4_Fe") 

### 2019-11-16 pyg4ometry/test/pythonGeant4/T001_Box.py
Gmad writer for box

@@ -35,7 +35,7 @@ def Test(vis = False, interactive = False) :
     w = _gd.Writer()
     w.addDetector(reg)
     w.write(_os.path.join(_os.path.dirname(__file__), "T001_Box.gdml"))
-
+    w.writeGmadTester(_os.path.join(_os.path.dirname(__file__))+"T001_Box.gmad","T001_Box.gdml")
     # test __repr__
     str(bs)
 

### 2019-11-16 public/paper/pyg4ometry.tex
Particle -> radiation transport

@@
 
-\title{Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries}
+\title{Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries}
 
@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo particle transport codes is a time consuming and error prone task.  \\
+Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error prone task.  \\
 {\em Solution method(approx. 50-250 words):}\\
@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
+There are numerous different software codes to simulate the passage of particles through material, so called radiation transport (RT) programmes, these 
 include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
-All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  PT Monte Carlo simulations 
+All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  RT Monte Carlo (RTMC) simulations 
 have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment 

### 2019-11-16 pyg4ometry/test/freecad/FreecadLoadingTests.py
Moved fluka files around

@@ -6,8 +6,8 @@ import pyg4ometry.freecad as _fc
 import logging as _log
 import os as _os
 
-logger = _log.getLogger()
-logger.disabled = True
+#logger = _log.getLogger()
+#logger.disabled = True
 
 def LoadFreecad(fileName) : 
     r = _fc.Reader(fileName) 

### 2019-11-16 pyg4ometry/test/gdml/GdmlLoadTests.py

@@ -10,8 +10,8 @@ from subprocess import Popen as _Popen, PIPE as _PIPE
 from hashlib import md5 as _md5
 from collections import OrderedDict as _OrderedDict
 
-logger = _log.getLogger()
-logger.disabled = True
+#logger = _log.getLogger()
+#logger.disabled = True
 
 def _pj(filename):
     """

### 2019-11-16 pyg4ometry/test/pythonCompoundExamples/PythonCompoundExampleTests.py

@@ -6,8 +6,8 @@ import dipole_cbpm
 
 import logging as _log
 
-logger = _log.getLogger()
-logger.disabled = True
+#logger = _log.getLogger()
+#logger.disabled = True
 
 class PythonCompoundExampleTests(_unittest.TestCase) :
     def testCavityBpm(self) :         

### 2019-11-16 pyg4ometry/test/pythonGeant4/PythonAuthoringTests.py

@@ -88,8 +88,8 @@ import T432_MergeRegistry_Box_AssemblyConversion
 
 import logging as _log
 
-logger = _log.getLogger()
-logger.disabled = True
+#logger = _log.getLogger()
+#logger.disabled = True
 
 class PythonAuthoringTests(_unittest.TestCase) :
     def testPlane(self) : 

### 2019-11-16 pyg4ometry/test/pythonGeant4/PythonTests.py

@@ -5,8 +5,8 @@ import pyg4ometry.transformation as _trans
 
 import logging as _log
 
-logger = _log.getLogger()
-logger.disabled = True
+# logger = _log.getLogger()
+# logger.disabled = True
 
 class PythonTests(_unittest.TestCase) :
 

### 2019-11-30 public/paper/pyg4ometry.tex
Small changes
Updated all papers

@@
 \usepackage{fancyvrb}
+\usepackage[T1]{fontenc}
 %% The amsthm package provides extended theorem environments
@@
 
-There are existing codes that have functionality similar to pyg4ometry. Tools exist to convert CAD files to GDML, e.g. GUIMesh \cite{GUIMesh_Pinto}.
+There are existing codes that have functionality similar to pyg4ometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, 
+commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. 
 CAD software can export data to STL. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
@@
 GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
-define 			& constant				& gdml.Constant				\\
-				& variable					& gdml.Variable					\\
-				& quantity					& gdml.Quantity				\\
-				& expression 				& gdml.Expression				\\
-				& position					& gdml.Position					\\
-				& rotation					& gdml.Rotation				\\
-				& scale					& gdml.Scale					\\
-				& matrix					& gdml.Matrix					\\
-materials 			& element					& geant4.Element				\\
-				& isotope					& geant4.Isotope				\\
-				& material					& geant4.Material				\\
-solid  			& box					& geant4.solid.Box				\\
-	  			& tube					&							\\
-	  			& cutTube					&							\\
-	  			& cone					&							\\
-	  			& para					&							\\
-	  			& trd						&							\\
-	  			& trap					&							\\
-	  			& sphere					&							\\
-	  			& orb					&							\\
-	  			& torus					&							\\
-	  			& polycone				&							\\
-	  			& genericPolycone			&							\\
-	  			& polyhedra				&							\\
-	  			& eltube					&							\\
-	  			& ellipsoid					&							\\
-	  			& elcone					&							\\
-				& paraboloid				&							\\
-				& hype					& 							\\
-				& tet						& 							\\
-				& xtru					& 							\\
-				& twistedbox				& 							\\
-				& twistedtrap				& 							\\
-				& twistedtrd				& 							\\
-				& twistedtube				& 							\\
-				& arb8					& 							\\
-				& tesselated				& 							\\
-				& union					& 							\\
-				& subtraction				& 							\\
-				& intersection				& 							\\
-				& multiUnion				& 							\\
-				& scaledSolid				&							\\				
-	  			& opticalsurface			&							\\
-structure			& volume					& geant4.LogicalVolume			\\
-				& assembly				& geant4.AssemblyVolume 		\\
-				& physvol					& geant4.PhysicalVolume			\\ 
-				& replicavol				& geant4.ReplicaVolume			\\ 
-				& paravol					& geant4.ParameterisedVolume	\\ 
-				& divisionvol				& geant4.DivisionVolume			\\
-				& skinsurface				& geant4.SkinSurface			\\ 
-				& bordersurface			& geant4.BorderSurface			\\ \hline
+Define 			& Constant				& gdml.Constant				\\
+				& Variable					& gdml.Variable					\\
+				& Quantity					& gdml.Quantity				\\
+				& Expression 				& gdml.Expression				\\
+				& Position					& gdml.Position					\\
+				& Rotation					& gdml.Rotation				\\
+				& Scale					& gdml.Scale					\\
+				& Matrix					& gdml.Matrix					\\ \hline
+Materials 			& Element					& geant4.Element				\\
+				& Isotope					& geant4.Isotope				\\
+				& Material					& geant4.Material				\\ \hline
+Solid  			& Box					& geant4.solid.Box				\\
+	  			& Tube					& geant4.solid.Tubs				\\
+	  			& CutTube				& geant4.solid.CutTubs			\\
+	  			& Cone					& geant4.solid.Cons				\\
+	  			& Para					& geant4.solid.Para				\\
+	  			& Trd					& geant4.solid.Trd				\\
+	  			& Trap					& geant4.solid.Trap				\\
+	  			& Sphere					& geant4.solid.Sphere			\\
+	  			& Orb					& geant4.solid.Orb				\\
+	  			& Torus					& geant4.solid.Torus				\\
+	  			& Polycone				& geant4.solid.Polycone			\\
+	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
+	  			& Polyhedra				& geant4.solid.Polyhedra			\\
+	  			& Eltube					& geant4.solid.EllipticalTube		\\
+	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
+	  			& Elcone					& geant4.solid.EllipticalCone		\\
+				& Paraboloid				& geant4.solid.Paraboloid			\\
+				& Hype					& geant4.solid.Hyperboloid		\\
+				& Tet						& geant4.solid.Tet				\\
+				& Xtru					& geant4.solid.ExtrudedSolid		\\
+				& TwistedBox				& geant4.solid.TwistedBox		\\
+				& TwistedTtap				& geant4.solid.TwistedTrap		\\
+				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
+				& TwistedTube				& geant4.solid.TwistedTube		\\
+				& Arb8					& geant4.solid.GenericTrap		\\
+				& Tessellated				& geant4.solid.TessellatedSolid 	\\
+				& Union					& geant4.solid.Union				\\
+				& Subtraction				& geant4.solid.Subtraction			\\
+				& Intersection				& geant4.solid.Intersection 		\\
+				& MultiUnion				& geant4.solid.MultiUnion 			\\
+				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
+	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
+Structure			& Volume					& geant4.LogicalVolume			\\
+				& Assembly				& geant4.AssemblyVolume 		\\
+				& PhysVol					& geant4.PhysicalVolume			\\ 
+				& ReplicaVol				& geant4.ReplicaVolume			\\ 
+				& ParaVol					& geant4.ParameterisedVolume	\\ 
+				& DivisionVol				& geant4.DivisionVolume			\\
+				& SkinSurface				& geant4.SkinSurface			\\ 
+				& BorderSurface			& geant4.BorderSurface			\\ \hline
 
@@
 All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
-throughsuch a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
+through such a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
 and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
@@
 
-\section{Geant4 and FLUKA conversion}
+\section{FLUKA to Geant4 conversion}
 FLUKA geometry is based upon a limited set of primitive volumes which can be combined using logical operations. Many FLUKA primitives are infinite in extent, so 
@@
 \centering
-\begin{tabular}{|l|l|l|} \hline
-Fluka body			& note			& pyg4ometry class 				\\ \hline
-RPP (done)			&				&							\\
-BOX					&				&							\\
-SPH (done)			&				&							\\
-RCC (done)			&				&							\\
-REC (done)			&				&							\\
-TRC (done)			&				&							\\
-ELL 					&				&							\\
-WED					&				&							\\
-RAW					&				&							\\
-ARB					&				&							\\
-XYP (done)			&				&							\\
-XZP (done)			&				&							\\
-YZP (done)			&				&							\\
-PLA (done)			&				&							\\
-XCC (done)			&				&							\\
-YCC (done)			&				&							\\
-ZCC (done)			&				&							\\
-XEC (done)			&				&							\\
-YEC (done)			&				&							\\
-ZEC (done)			&				&							\\
-QUA (done)			&				&							\\ \hline
+\begin{tabular}{|l|l|} \hline
+FLUKA body							& pyg4ometry class 		\\ \hline
+RPP 	(Rectangular parallelepiped)			& Box				\\
+BOX	(General rectangular parallelepiped)		& Box				\\
+SPH 	(Sphere)							& Orb				\\
+RCC (Right circular cylinder)				& Cone				\\
+REC (Right elliptical cylinder)				& EllipticalTube			\\
+TRC (Truncated Right Angle Cone)			& Cone				\\
+ELL (Ellipsoid of Revolution) 				& Ellipsoid				\\
+WED/RAW (Right Angle Wedge)			& ExtrudedSolid		\\
+ARB	(Arbitrary Convex Polyhedron)			& TessellatedSolid		\\
+XYP 	($X$-$Y$ Infinite half-space)			& Box				\\
+XZP 	($X$-$Z$ Infinite half-space)			& Box				\\
+YZP 	($Y$-$Z$ Infinite half-space)			& Box				\\
+PLA (Generic infinite half-space)			& Box				\\
+XCC ($X$-axis Infinite Circular Cylinder)		& Tubs				\\
+YCC ($Y$-axis Infinite Circular Cylinder)		& Tubs				\\
+ZCC 	($Z$-axis Infinite Circular Cylinder)		& Tubs				\\
+XEC 	($X$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
+YEC 	($Y$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
+ZEC ($Z$-axis Infinite Elliptical Cylinder)		& EllipticalTube			\\
+QUA (Quadric surface) 					& TessellatedSolid		\\ \hline
 \end{tabular}
@@
 \begin{enumerate} 
+\item length safety
 \item infinite planes
@@
 \end{enumerate}
+
+\section{Geant4 to FLUKA conversion}
+
+\begin{table}[hbt!]
+\centering
+\begin{tabular}{| l | l | } \hline
+Geant4 solid			& FLUKA constuction			\\ \hline
+Box					& XYP, XZP, YZP 				\\
+Tube					& ZCC, XYP	 				\\
+CutTube				& ZCC, PLA					\\
+Cone				& TRC						\\
+Para					& ARB						\\
+Trd					& ARB						\\
+Trap					& ARB						\\
+Sphere				& SPH, WED					\\
+Orb					& SPH						\\
+Torus				& (PLA)						\\
+Polycone				& (PLA)						\\
+GenericPolycone		& (PLA)						\\
+Polyhedra				& (PLA)						\\
+Eltube				& ZEC, XYP					\\
+Ellipsoid				& ELL						\\
+Elcone				& QUA						\\
+Paraboloid			& QUA						\\
+Hype					& QUA						\\
+Tet					& PLA						\\
+Xtru					& PLA						\\
+TwistedBox			& (PLA)						\\
+TwistedTtap			& (PLA)						\\
+TwistedTrd			& (PLA)				 		\\
+TwistedTube			& (PLA)						\\
+Arb8					& ARB						\\
+Tessellated			& (PLA)					 	\\
+Union				& | zone1 | zone2				\\
+Subtraction			& +zone1 -zone2				\\
+Intersection			& +zone1 +zone2				\\
+MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
+ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
+\end{tabular}
+\end{table}
 
@@
 
-\subsection{Editing existing CAD models}
+\subsection{Editing existing models}
 Often existing CAD models have either missing details or too much detail.

### 2019-12-01 public/paper/pyg4ometry.tex
Complete tables

@@
 Orb					& SPH						\\
-Torus				& (PLA)						\\
-Polycone				& (PLA)						\\
-GenericPolycone		& (PLA)						\\
-Polyhedra				& (PLA)						\\
+Torus				& ZCC, PLA					\\
+Polycone				& ARB						\\
+GenericPolycone		& ARB						\\
+Polyhedra				& ARB						\\
 Eltube				& ZEC, XYP					\\
@@
 Xtru					& PLA						\\
-TwistedBox			& (PLA)						\\
-TwistedTtap			& (PLA)						\\
-TwistedTrd			& (PLA)				 		\\
-TwistedTube			& (PLA)						\\
+TwistedBox			& ARB						\\
+TwistedTtap			& ARB						\\
+TwistedTrd			& ARB				 		\\
+TwistedTube			& ARB						\\
 Arb8					& ARB						\\
-Tessellated			& (PLA)					 	\\
+Tessellated			& N/A					 	\\
 Union				& | zone1 | zone2				\\
@@
 \end{tabular}
+\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
 \end{table}

### 2019-12-01 public/paper/pyg4ometry.tex
Updated paper

@@
 %% \documentclass[final,3p,times]{elsarticle}
-%\documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
 %% \documentclass[final,5p,times]{elsarticle}
@@
 \usepackage[T1]{fontenc}
+\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
 %% The amsthm package provides extended theorem environments
@@
 dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared for different codes will 
-enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted 
-design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not 
-amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
-geometry files, convert between common PT programme geometry formats and finally import CAD models.
+enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for RT programs, usually computer assisted 
+design (CAD) files exist for systems which need to be simulated in RT programmes. The fundamental geometric representations in CAD files is typically not 
+amenable for RT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
+geometry files, convert between common RT programme geometry formats and finally import CAD models.
 
@@
 \subsection{Constructive solid geometry (CSG)}
-Constructive solid geometry uses boolean operations to model complex surfaces which represent a solid. Typically simple finite or infinite solids are combined 
-with operations, such as union, intersection and difference to model more complex solids. FLUKA uses CSG to model solids.
+Constructive solid geometry uses boolean operations (subtraction, intersection and union) between simple solids shapes (cube, cylinder, sphere etc) to model complex 
+surfaces which represent a solid. Typically simple finite or infinite solids are combined with operations, such as union, intersection and difference to model more 
+complex solids. FLUKA uses CSG to model solids.
 
 \subsection{Boundary representation (BREP)}
-Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current PT applications use native 
-file formats employed by CAD systems. The conversion of CAD BREP formats for loading in PT applications is typically performed via a tessellated format.
+Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current RT applications use native 
+file formats employed by CAD systems. The conversion of CAD BREP formats for loading in PT applications is typically performed via a tessellated format, although it 
+is possible to decompose BREP descriptions to simple half-spaces and solids as used in CSG descriptions.
 
@@
 Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and more 
-modern variants being PLY, OBJ, etc.
+modern variants being PLY, OBJ, etc. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh deviation distance from the 
+solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC.
 
@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Workflow}
+  \caption{\label{fig:workflow}Pyg4ometry geometry conversion workflow.}
 \end{figure*}
@@
 
-\subsection{Tessellation of solids}
-For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
-geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
-on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
-TetGEN can be employed to give the meshes more desirable features.
-
-\subsection{Replica, parametrised and looped volumes}
-A powerful feature of Geant4 and hence GDML is the ability to either repeat or parametrise geometry. The create mulitple replicas of a volume in a cartesian, cylindrical or 
-spherical grid is known as a ReplicaVolume.
+\subsection{Replica, division, parametrised and looped volumes}
+A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The create multiple replicas of a volume in a cartesian, cylindrical or 
+spherical grid is known as a ReplicaVolume. Currently GDML loops are not supported by pyg4ometry and will be implemented in a future release.
 
@@
 Output consists of taking the registry and writing the appropriate GDML.
+
+\subsection{Tessellation of solids (meshing)}
+For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
+geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
+on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
+TetGEN can be employed to give the meshes more desirable features.
 
@@
 \subsection{Adding properties to volumes}
-A pure geometry description is an insufficient description for a PT simulation. Often other attributes need to be assigned for example material definition, magnetic field or
+A pure geometry description is an insufficient description for a RT simulation. Often other attributes need to be assigned for example material definition, magnetic field or  
+optical surface properties.
 
@@
 \section{Rapid geometry modelling}
-Given the python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the PT problem, vary 
+Given the python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
 the parameters of the geometry and visualise the geometry. Finally when the desired result without geometry overlaps is finalised a GDML file can be output
@@
 FLUKA geometry is based upon a limited set of primitive volumes which can be combined using logical operations. Many FLUKA primitives are infinite in extent, so 
-to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table XXX shows the mapping between FLUKA and Geant4 objects.
+to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table \ref{tab:Fluka2Geant4} shows the mapping between FLUKA and Geant4 objects.
 An ANTLR based expression parser is used to load and comprehend the FLUKA input syntax, an example is shown in XXX. Each FLUKA body is matched to a Geant4 
@@
 \end{tabular}
-\caption{Fluka geometry directives pyg4ometry classes.}
+\caption{FLUKA geometry directives pyg4ometry classes.} \label{tab:Fluka2Geant4}
 \end{table}
@@
 \section{Geant4 to FLUKA conversion}
+It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
+Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree.
 
@@
 \begin{tabular}{| l | l | } \hline
-Geant4 solid			& FLUKA constuction			\\ \hline
-Box					& XYP, XZP, YZP 				\\
-Tube					& ZCC, XYP	 				\\
-CutTube				& ZCC, PLA					\\
-Cone				& TRC						\\
-Para					& ARB						\\
-Trd					& ARB						\\
-Trap					& ARB						\\
-Sphere				& SPH, WED					\\
-Orb					& SPH						\\
-Torus				& ZCC, PLA					\\
-Polycone				& ARB						\\
-GenericPolycone		& ARB						\\
-Polyhedra				& ARB						\\
-Eltube				& ZEC, XYP					\\
-Ellipsoid				& ELL						\\
-Elcone				& QUA						\\
-Paraboloid			& QUA						\\
-Hype					& QUA						\\
-Tet					& PLA						\\
-Xtru					& PLA						\\
-TwistedBox			& ARB						\\
-TwistedTtap			& ARB						\\
-TwistedTrd			& ARB				 		\\
-TwistedTube			& ARB						\\
-Arb8					& ARB						\\
+Geant4 solid			& FLUKA region constuction		\\ \hline
+Box					& +2 XYP + 2 XZP + 2 YZP 		\\
+Tube					& +ZCC - 2 XYP	 			\\
+CutTube				& +ZCC - 2 PLA				\\
+Cone				& +TRC						\\
+Para					& +ARB						\\
+Trd					& +ARB						\\
+Trap					& +ARB						\\
+Sphere				& +SPH - SPH  - WED - TRC		\\
+Orb					& +SPH						\\
+Torus				& +$N$ ZCC  - $N$ PLA			\\
+Polycone				& +$N$ ARB					\\
+GenericPolycone		& +$N$ ARB					\\
+Polyhedra				& +$N$ ARB					\\
+Eltube				& +ZEC  - 2 XYP				\\
+Ellipsoid				& +ELL - 2 XYP		 			\\
+Elcone				& +QUA - 2 XYP				\\
+Paraboloid			& +QUA - 2 XYP				\\
+Hype					& +QUA - 2 XYP				\\
+Tet					& +ARB						\\
+Xtru					& +$N$ ARB					\\
+TwistedBox			& +$N$ ARB					\\
+TwistedTtap			& +$N$ ARB					\\
+TwistedTrd			& +$N$ ARB				 	\\
+TwistedTube			& +$N$ ARB					\\
+Arb8					& +ARB						\\
 Tessellated			& N/A					 	\\
@@
 \subsection{Overlap checking in geometry}
-Often small errors in geometry cause unexpected PT code behaviour.
+Often small errors in geometry cause unexpected RT code behaviour.
 
@@
 amounts of user effort and ultimately yield more accurate simulations. Pyg4ometry is a relatively complete implementation of a geometry creation tool, whilst heavily 
-internally based on Geant4 and GDML can have utility for users of all PT codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications,
+internally based on Geant4 and GDML can have utility for users of all RT codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications,
 examples include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble  dark matter detectors and geometries for event visualisation. 

### 2019-12-20 pyg4ometry/test/pythonGeant4/T010_Torus.py
accerlerated meshing

@@ -4,7 +4,7 @@ import pyg4ometry.geant4 as _g4
 import pyg4ometry.visualisation as _vi
 
 
-def Test(vis = False, interactive = False) :
+def Test(vis = False, interactive = False, n_slice = 20, n_stack = 20) :
     reg = _g4.Registry()
     
     # defines 
@@ -17,14 +17,14 @@ def Test(vis = False, interactive = False) :
     trmax  = _gd.Constant("rmax","10.0",reg,True)
     trtor  = _gd.Constant("rtor","40.0",reg,True)
     tsphi  = _gd.Constant("sphi","0",reg,True)
-    tdphi  = _gd.Constant("dphi","2*pi",reg,True)
+    tdphi  = _gd.Constant("dphi","1.5*pi",reg,True)
     
     wm = _g4.MaterialPredefined("G4_Galactic") 
     tm = _g4.MaterialPredefined("G4_Fe") 
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    ts = _g4.solid.Torus("ts",trmin,trmax,trtor,tsphi,tdphi,reg,"mm","rad")
+    ts = _g4.solid.Torus("ts",trmin,trmax,trtor,tsphi,tdphi,reg,"mm","rad",nslice=n_slice,nstack=n_stack)
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)

### 2019-12-20 public/paper/pyg4ometry.tex

@@
   %Only required for a New Version summary, otherwise leave out.
-{\em Reasons for the new version:}\\
+{\em Reasons for the new version:}							\\
   %Only required for a New Version summary, otherwise leave out.
-{\em Summary of revisions:}*\\
+{\em Summary of revisions:}*								\\
   %Only required for a New Version summary, otherwise leave out.
@@
 Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current RT applications use native 
-file formats employed by CAD systems. The conversion of CAD BREP formats for loading in PT applications is typically performed via a tessellated format, although it 
+file formats employed by CAD systems. The conversion of CAD BREP formats for loading in RT applications is typically performed via a tessellated format, although it 
 is possible to decompose BREP descriptions to simple half-spaces and solids as used in CSG descriptions.
@@
 \subsection{Tessellation of solids (meshing)}
-For each Geant4 primitive solid a triangular tessellated mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
+For each Geant4 primitive solid a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
 geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
@@
 \subsection{Overlap detection}
-All PT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+All RT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
 through such a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
@@
 This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final
-PT simulation.
+RT simulation.
 This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
@@
 CutTube				& +ZCC - 2 PLA				\\
-Cone				& +TRC						\\
+Cone				& +TRC -TRC - WED			\\
 Para					& +ARB						\\
@@
 \subsection{Editing existing models}
-Often existing CAD models have either missing details or too much detail.
+Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts
 

### 2019-12-20 pyg4ometry/test/pythonGeant4/T019_Hyperboloid.py
accerlerated meshing

@@ -7,7 +7,7 @@ normal = 1
 rmin_eq_zero = 2
 rmin_gt_rmax = 3
 
-def Test(vis = False, interactive = False, type = normal) :
+def Test(vis = False, interactive = False, type = normal, n_slice = 16, n_stack = 16) :
     reg = _g4.Registry()
     
     # defines 
@@ -16,11 +16,11 @@ def Test(vis = False, interactive = False, type = normal) :
     wz = _gd.Constant("wz","100",reg,True)
     
     pi    = _gd.Constant("pi","3.1415926",reg,True)
-    hrmin = _gd.Constant("hrmin","1.0",reg,True)
-    hrmax = _gd.Constant("hrmax","2.0",reg,True)
-    hz    = _gd.Constant("hz","20.0",reg,True)
-    hinst = _gd.Constant("hinst","3",reg,True)
-    houtst= _gd.Constant("houtst","4",reg,True)
+    hrmin = _gd.Constant("hrmin","20",reg,True)
+    hrmax = _gd.Constant("hrmax","30.0",reg,True)
+    hz    = _gd.Constant("hz","50.0",reg,True)
+    hinst = _gd.Constant("hinst","0.7",reg,True)
+    houtst= _gd.Constant("houtst","0.7",reg,True)
     
     if type == rmin_eq_zero : 
         hrmin.setExpression(0)
@@ -34,7 +34,7 @@ def Test(vis = False, interactive = False, type = normal) :
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    hs = _g4.solid.Hype("ps",hrmin, hrmax, hinst, houtst, hz, reg)
+    hs = _g4.solid.Hype("ps",hrmin, hrmax, hinst, houtst, hz, reg,nslice=n_slice,nstack=n_stack)
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)

### 2019-12-20 pyg4ometry/test/pythonGeant4/T009_Orb.py
accelerated meshing

@@ -4,7 +4,7 @@ import pyg4ometry.geant4 as _g4
 import pyg4ometry.visualisation as _vi
 
 
-def Test(vis = False, interactive = False) :
+def Test(vis = False, interactive = False, n_slice=16, n_stack=16) :
     reg = _g4.Registry()
     
     # defines 
@@ -19,12 +19,12 @@ def Test(vis = False, interactive = False) :
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    os = _g4.solid.Orb("os",ormax,reg,"mm")
+    os = _g4.solid.Orb("os",ormax,reg,"mm", nslice=n_slice, nstack=n_stack)
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)
     ol = _g4.LogicalVolume(os, om, "ol", reg)
-    op = _g4.PhysicalVolume([0,0,0],[0,0,0],  ol, "o_pv1", wl, reg) 
+    op = _g4.PhysicalVolume([0,0,0],[0,0,0],  ol, "o_pv1", wl, reg)
     
     # set world volume
     reg.setWorld(wl.name)

### 2019-12-20 pyg4ometry/test/pythonGeant4/T018_Paraboloid.py
accerlerated meshing

@@ -3,7 +3,7 @@ import pyg4ometry.gdml as _gd
 import pyg4ometry.geant4 as _g4
 import pyg4ometry.visualisation as _vi
 
-def Test(vis = False, interactive = False) :
+def Test(vis = False, interactive = False,n_slice =16,n_stack=16) :
     reg = _g4.Registry()
     
     # defines 
@@ -21,7 +21,7 @@ def Test(vis = False, interactive = False) :
 
     # solids
     ws = _g4.solid.Box("ws",wx,wy,wz, reg, "mm")
-    ps = _g4.solid.Paraboloid("ps",pz,prlo,prhi,reg)
+    ps = _g4.solid.Paraboloid("ps",pz,prlo,prhi,reg,nslice=n_slice,nstack=n_stack)
         
     # structure 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)

### 2020-01-03 pyg4ometry/test/gdml2Fluka/T001_GdmlBox2Fluka.py
First g3 -> f test

@@ -1,0 +1,34 @@
+import pyg4ometry.geant4 as _g4
+import pyg4ometry.convert as _convert
+import pyg4ometry.fluka as _fluka
+
+import pyg4ometry.test.pythonGeant4.T001_Box as _T001_Box
+
+def Test() :
+
+    # registry
+    reg = _g4.Registry()
+
+    # solids
+    ws = _g4.solid.Box("ws", 100, 100, 100, reg, "mm")
+    bs = _g4.solid.Box("bs", 20,   20,  20, reg, "mm")
+
+    # materials
+    wm = _g4.MaterialPredefined("G4_Galactic")
+    bm = _g4.MaterialPredefined("G4_Fe")
+
+    # structure
+    wl  = _g4.LogicalVolume(ws, wm, "wl", reg)
+    bl  = _g4.LogicalVolume(bs, bm, "bl", reg)
+    bp1 = _g4.PhysicalVolume([0, 0, 0],     [0, 0, -50], bl, "b_pv1", wl, reg)
+    bp2 = _g4.PhysicalVolume([0, 0, 0],     [0, 0,   0], bl, "b_pv2", wl, reg)
+    bp3 = _g4.PhysicalVolume([0, 0, 0.785], [0, 0,  50], bl, "b_pv3", wl, reg)
+
+    # set world volume
+    reg.setWorld(wl.name)
+
+    freg, nfb = _convert.geant42Fluka(wl)
+
+    w = _fluka.Writer()
+    w.addDetector(freg)
+    w.write("T001_GdmlBox2Fluka.inp")

### 2020-01-03 public/paper/pyg4ometry.tex
More on g2f in paper

@@
 \section{Geant4 to FLUKA conversion}
-It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
+It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG zone.
 Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree.
@@
 Box					& +2 XYP + 2 XZP + 2 YZP 		\\
-Tube					& +ZCC - 2 XYP	 			\\
-CutTube				& +ZCC - 2 PLA				\\
-Cone				& +TRC -TRC - WED			\\
+Tube					& +ZCC - 2 PLA -2 XYP - ZCC	 	\\
+CutTube				& +ZCC - 4 PLA -ZCC			\\
+Cone				& +TRC - TRC - WED			\\
 Para					& +ARB						\\

### 2020-01-16 public/paper/pyg4ometry.tex

--- 2019-12-20 public/paper/pyg4ometry.tex
@@
 
-\subsection{Visualisation}
+\subsection{Visualisation} \label{sec:visualisation}
 A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
@@
 It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
-Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree.
+Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
+lists the mapping between geant4 solids and the bodies used to compose a fluka region.
 
@@
 Tet					& +ARB						\\
-Xtru					& +$N$ ARB					\\
+Xtru					& +$N_{\rm plane} N_{\rm point}$ PLA					\\
 TwistedBox			& +$N$ ARB					\\
@@
 Tessellated			& N/A					 	\\
-Union				& | zone1 | zone2				\\
-Subtraction			& +zone1 -zone2				\\
-Intersection			& +zone1 +zone2				\\
-MultiUnion			& | zone1 | zone2 | zone3 | ...	\\
+Union				& $R_1 \cup R_2$				\\
+Subtraction			& $R_1 - R_2$					\\
+Intersection			& $R_1 \cap R_2$				\\
+MultiUnion			& $R_1 \cup R_2 \cup R_3 \cup$	\\
 ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
 \end{tabular}
+\label{tab:geant2fluka}
 \caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
 \end{table}
+
+There are some important issues which must be considered to perform an accurate conversion. 
+A Geant4 logical volume solid might need to be created from a fluka region composing of many zones, 
+so $R_1 = +z_1 | +z_2$, similarly a void is required to locate daughter volume placements which again 
+might also be converted to a region of multiple zones $R_2= +z_3| z_4$. So creating the fluka region is then 
+\begin{eqnarray}
+R_1 - R_2 	& = & (+z_1 | +z_2) - ( +z_3 | +z_4) 			\\
+			& = & (+z_1 - z_3 - z_4)  | (+z_2 - z_3 - z_4)	
+\label{eqn:setDiff}
+\end{eqnarray}
+Geant4 has the boolean solids associated with difference, union and intersection, so in addition to Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and 
+$R_1 \cap R_2$ is required in fluka notation, so 
+\begin{eqnarray}
+R_1 \cup R_2 	& = & (+z_1 | +z_2)  \cup ( +z_3 | +z_4) \\
+			& = & +z_1 | +z_2 |  +z_3 | +z_4
+\end{eqnarray}
+and 
+\begin{eqnarray}
+R_1 \cap R_2 	& = & (+z_1 | +z_2) \cap ( +z_3 | +z_4) \\
+			& = & +z_1 +z_3  | +z_1 +z_4 | +z_2 +z_3 | +z_2 +z_4
+\end{eqnarray}
+
+Fluka (apart from the {\it lattice} directive) has no sense of a volume hierarchy. Each body is placed with a translation, rotation, expansion geometry 
+directives in global coordinates. A transformation from world coordinates to a physical volume is built up by applying recursively daughter volume transformations and 
+this is used to place Fluka bodies. This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}
 

### 2020-01-30 pyg4ometry/test/flairFluka/view_inp.py
working ARB with length safety + tests

@@ -15,7 +15,8 @@ def main(filein, debug=False):
 
     r = Reader(filein)
     arb = r.flukaregistry.bodyDict["arb"]
-    arb._verticesAreClockwise()
+    # arb._verticesAreClockwise()
+    arb.geant4Solid(None)
     from IPython import embed; embed()
     # greg = fluka2Geant4(r.flukaregistry,
     #                     with_length_safety=True,

### 2020-01-30 pyg4ometry/test/pythonFluka/T209_ARB_coplanar.py

@@ -1,0 +1,54 @@
+import pyg4ometry.convert as convert
+import pyg4ometry.visualisation as vi
+from pyg4ometry.fluka import ARB, Region, Zone, FlukaRegistry, Three, Transform
+
+
+def Test(vis=False, interactive=False):
+    freg = FlukaRegistry()
+
+    vertices = [[0, 0, 0],
+                [20, 0, 0],
+                [10, 20, 0],
+                [0, 20, 0],
+                [0, 0, 20],
+                [20, 0, 20],
+                [10, 20, 20],
+                [0, 20, 20]]
+    facenumbers = [4321, 5678, 2376, 1584, 3487, 1265]
+
+    arb = ARB("ARB_BODY", vertices, facenumbers, flukaregistry=freg)
+
+    trans = Transform(expansion=0.5,
+                      translation=[5, 5, 5])
+
+    arbInner = ARB("ARB_BODY2", vertices, facenumbers, transform=trans)
+
+    z1 = Zone()
+    z1.addIntersection(arb)
+    z1.addSubtraction(arbInner)
+
+    z2 = Zone()
+    z2.addIntersection(arbInner)
+
+    region = Region("ARB_REG")
+    region2 = Region("ARB_REG2")
+
+    region.addZone(z1)
+    region2.addZone(z2)
+
+    freg.addRegion(region)
+    freg.addRegion(region2)
+
+    greg = convert.fluka2Geant4(freg)
+
+    v = None
+    if vis:
+        v = vi.VtkViewer()
+        v.addAxes(length=20)
+        v.addLogicalVolume(greg.getWorldVolume())
+        v.view(interactive=interactive)
+
+    return {"testStatus": True, "logicalVolume": greg.getWorldVolume(), "vtkViewer": v}
+
+if __name__ == '__main__':
+    Test(True, True)

### 2020-01-30 public/paper/pyg4ometry.tex

@@
 CutTube				& +ZCC - 4 PLA -ZCC			\\
-Cone				& +TRC - TRC - WED			\\
-Para					& +ARB						\\
-Trd					& +ARB						\\
-Trap					& +ARB						\\
-Sphere				& +SPH - SPH  - WED - TRC		\\
+Cone				& +TRC - TRC - 2 PLA 			\\
+Para					& + 8 PLA						\\
+Trd					& + 8 PLA						\\
+Trap					& + 8 PLA						\\
+Sphere				& +SPH - SPH  - 2 PLA - 2 TRC	\\
 Orb					& +SPH						\\
 Torus				& +$N$ ZCC  - $N$ PLA			\\
-Polycone				& +$N$ ARB					\\
+Polycone				& +$N$ TRC					\\
 GenericPolycone		& +$N$ ARB					\\
-Polyhedra				& +$N$ ARB					\\
+Polyhedra				& +$N$ PLA					\\
 Eltube				& +ZEC  - 2 XYP				\\
@@
 Paraboloid			& +QUA - 2 XYP				\\
-Hype					& +QUA - 2 XYP				\\
-Tet					& +ARB						\\
+Hype					& +QUA - QUA - 2 XYP			\\
+Tet					& +4 PLA						\\
 Xtru					& +$N_{\rm plane} N_{\rm point}$ PLA \\
-TwistedBox			& +$N$ ARB					\\
-TwistedTtap			& +$N$ ARB					\\
-TwistedTrd			& +$N$ ARB				 	\\
-TwistedTube			& +$N$ ARB					\\
-Arb8					& +ARB						\\
-Tessellated			& N/A					 	\\
+TwistedBox			& +$N$ PLA					\\
+TwistedTtap			& +$N$ PLA					\\
+TwistedTrd			& +$N$ PLA				 	\\
+TwistedTube			& +$N$ PLA					\\
+Arb8					& +$N$ PLA					\\
+Tessellated			& +$N$ PLA				 	\\
 Union				& $R_1 \cup R_2$				\\

### 2020-01-30 pyg4ometry/test/pythonFluka/T209_ARB_coplanar.py
improvements to the ARB tests

@@ -30,8 +30,8 @@ def Test(vis=False, interactive=False):
     z2 = Zone()
     z2.addIntersection(arbInner)
 
-    region = Region("ARB_REG")
-    region2 = Region("ARB_REG2")
+    region = Region("ARB_REG", material="COPPER")
+    region2 = Region("ARB_REG2", material="COPPER")
 
     region.addZone(z1)
     region2.addZone(z2)
@@ -40,6 +40,8 @@ def Test(vis=False, interactive=False):
     freg.addRegion(region2)
 
     greg = convert.fluka2Geant4(freg)
+    wlv = greg.getWorldVolume()
+    wlv.checkOverlaps()
 
     v = None
     if vis:

### 2020-01-30 pyg4ometry/test/pythonFluka/T509_ARB_translation.py

@@ -51,7 +51,7 @@ def Test(vis=False, interactive=False):
     z = Zone()
     z.addIntersection(arb)
 
-    region = Region("ARB_REG")
+    region = Region("ARB_REG", material="COPPER")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-01-30 pyg4ometry/test/pythonFluka/T609_ARB_rototranslation.py

@@ -3,10 +3,76 @@ import numpy as np
 import pyg4ometry.convert as convert
 import pyg4ometry.visualisation as vi
 from pyg4ometry.fluka import ARB, Region, Zone, FlukaRegistry, Transform, Three
-
+from pyg4ometry.fluka.directive import rotoTranslationFromTra2
 
 def Test(vis=False, interactive=False):
-    pass
+    freg = FlukaRegistry()
+
+    # In FLUKA we can choose: either all of the face numbers must
+    # refer to vertices in clockwise or anticlockwise direction.  Here
+    # we ensure all are clockwise looking out from the centre of the
+    # tesselated solid.  This is the right hand corkscrew rule.
+
+    # Rear face:
+    vertex1 = Three([0.0, 0.0, 0.0])   # lower left corner
+    vertex2 = Three([20.0, 0.0, 0.0])   # lower right corner
+    vertex3 = Three([10.0, 20.0, 0.0])  # upper right corner
+    vertex4 = Three([0.0, 20.0, 0.0])  # Upper left corner
+    face1 = 4321  # clockwise in direction of normal
+    # face1 = 1234  # anticlockwise in direction of normal
+
+    # Front face:
+    vertex5 =  Three([0.0, 0.0, 20.])  # lower left corner
+    vertex6 = Three([20.0, 0.0, 20.])   # lower right corner
+    vertex7 = Three([10.0, 20.0, 20.])   # upper right corner
+    vertex8 = Three([0.0, 20.0, 20.]) # Upper left corner
+
+    face2 = 5678 # clockwise in direction of normal
+    # face2 = 8765 # anticlockwise in direction of normal
+
+    face3 = 2376 # right face
+    face4 = 1584 # left face
+    face5 = 3487 # top face
+    face6 = 1265 # bottom face
+
+    # anticlockwise in direction of noraml
+    # face3 = 6732 # right face
+    # face4 = 4851 # left face
+    # face5 = 7843 # top face
+    # face6 = 5621 # bottom face
+
+    vertices = [vertex1, vertex2, vertex3, vertex4,
+                vertex5, vertex6, vertex7, vertex8]
+    facenumbers = [face1, face2, face3, face4, face5, face6]
+
+
+    rtrans = rotoTranslationFromTra2("rppTRF",
+                                     [[np.pi/4, np.pi/4, np.pi/4],
+                                      [0, 0, 20]])
+    transform = Transform(rotoTranslation=rtrans)
[…]

### 2020-02-03 pyg4ometry/test/pythonCompoundExamples/VacuumSystems.py
Test placement of boolean

@@ -222,7 +222,7 @@ def makeWorld() :
     wm = _g4.MaterialPredefined("G4_Galactic")
 
     wl = _g4.LogicalVolume(ws, wm, "wl", reg)
-    cp = _g4.PhysicalVolume([0,0,0],[0,0,0], log, "chamber_pv1", wl, reg)
+    cp = _g4.PhysicalVolume([_np.pi/4.0,0,0],[0,0,0], log, "chamber_pv1", wl, reg)
 
     reg.setWorld(wl.name)
 

### 2020-02-03 public/paper/pyg4ometry.tex
Update polycone

--- 2020-01-16 public/paper/pyg4ometry.tex
@@
 CutTube				& +ZCC - 4 PLA -ZCC			\\
-Cone				& +TRC - TRC - WED			\\
-Para					& +ARB						\\
-Trd					& +ARB						\\
-Trap					& +ARB						\\
-Sphere				& +SPH - SPH  - WED - TRC		\\
+Cone				& +TRC - TRC - 2 PLA 			\\
+Para					& + 8 PLA						\\
+Trd					& + 8 PLA						\\
+Trap					& + 8 PLA						\\
+Sphere				& +SPH - SPH  - 2 PLA - 2 TRC	\\
 Orb					& +SPH						\\
 Torus				& +$N$ ZCC  - $N$ PLA			\\
-Polycone				& +$N$ ARB					\\
+Polycone				& +$N$ TRC -2 PLA				\\
 GenericPolycone		& +$N$ ARB					\\
-Polyhedra				& +$N$ ARB					\\
+Polyhedra				& +$N$ PLA					\\
 Eltube				& +ZEC  - 2 XYP				\\

### 2020-02-07 pyg4ometry/test/flairFluka/FlairLoadTests.py
Assertions to make the preprocessor tests robust
Simply loading them doesn't prove anything, here we check to make sure
that bits of fluka input are correctly enabled/disabled as desired.

@@ -6,6 +6,7 @@ import pyg4ometry.fluka as _fluka
 import pyg4ometry.visualisation as _vi
 import pyg4ometry.gdml as _gdml
 from pyg4ometry.convert import fluka2Geant4 as _fluka2Geant4
+import pyg4ometry.geant4.solid
 
 
 def _pj(filename):
@@ -38,8 +39,9 @@ def flairLoadWriteTest(fileName, vis=True, interactive=False) :
     w.write(_os.path.join(_os.path.dirname(__file__), gdmlFileName))
     w.writeGmadTester(_os.path.join(_os.path.dirname(__file__),gmadFileName),gdmlFileName)
 
-class FlairLoadTests(_unittest.TestCase) :
+    return r.flukaregistry, greg
 
+class FlairLoadTests(_unittest.TestCase) :
     def test_FlairLoad_T001_RPP(self):
         flairLoadWriteTest("001_RPP.inp", True, False)
 
@@ -233,25 +235,42 @@ class FlairLoadTests(_unittest.TestCase) :
         flairLoadWriteTest("806_combined_translat_transform.inp", True, False)
 
     def test_FlairLoad_T901_preprocessor_if(self):
-        flairLoadWriteTest("901_preprocessor_if.inp", True, False)
+        freg, greg = flairLoadWriteTest("901_preprocessor_if.inp", True, False)
+        solids = greg.solidDict
+        self.assertIsInstance(solids["bb1_s"], pyg4ometry.geant4.solid.Cons)
 
     def test_FlairLoad_T902_preprocessor_elif(self):
-        flairLoadWriteTest("902_preprocessor_elif.inp", True, False)
+        freg, greg = flairLoadWriteTest("902_preprocessor_elif.inp",
+                                        True, False)
+        solids = greg.solidDict
+        self.assertIsInstance(solids["bb1_s"], pyg4ometry.geant4.solid.Box)
 
     def test_FlairLoad_T903_preprocessor_else(self):
-        flairLoadWriteTest("903_preprocessor_else.inp", True, False)
+        freg, greg = flairLoadWriteTest("903_preprocessor_else.inp",
+                                        True, False)
+        solids = greg.solidDict
+        self.assertIsInstance(solids["bb1_s"], pyg4ometry.geant4.solid.Tubs)
 
     def test_FlairLoad_T904_preprocessor_include(self):
         flairLoadWriteTest("904_preprocessor_include.inp", True, False)
 
     def test_FlairLoad_T905_preprocessor_nested_if(self):
[…]

### 2020-02-07 public/paper/pyg4ometry.tex
Correct names of classes in table

--- 2020-01-30 public/paper/pyg4ometry.tex
@@
 SPH (Sphere)    					& Orb \\
-RCC (Right circular cylinder)				& Cone				\\
+RCC (Right circular cylinder)				& Tubs \\
 REC (Right elliptical cylinder)				& EllipticalTube \\
-TRC (Truncated Right Angle Cone)			& Cone				\\
+TRC (Truncated Right Angle Cone)			& Cons \\
 ELL (Ellipsoid of Revolution) 				& Ellipsoid \\

### 2020-02-07 pyg4ometry/test/flairFluka/FlairLoadTests.py
a test for checking the shifting infinite cylinder centre correctly

@@ -135,6 +135,9 @@ class FlairLoadTests(_unittest.TestCase) :
     def test_FlairLoad_T103_Union(self):
         flairLoadWriteTest("103_Union.inp", True, False)
 
+    def test_FlairLoad_T104_Union(self):
+        flairLoadWriteTest("104_shift_cylinders.inp", True, False)
+
     def test_FlairLoad_T301_RPP_transform(self):
         flairLoadWriteTest("301_RPP_transform.inp", True, False)
 

### 2020-02-07 pyg4ometry/test/stl/StlLoadTests.py
Updated STL tests to reflect the new STL Reader structure.

@@ -12,10 +12,10 @@ logger.disabled = True
 
 def LoadStl(fileName) : 
     reg = _g4.Registry()
-    r = _stl.Reader(fileName)    
-    l = r.logicalVolume("test","G4_Cu",reg)
+    r = _stl.Reader(fileName, registry=reg)
+    s = r.getSolid()
         
-    return True,l
+    return True, s
 
 def _pj(filename): # path join
     """

### 2020-02-07 pyg4ometry/test/stl/StlLoadTests.py
Updated the STL load tests to match the new STL Reader structure.

@@ -26,7 +26,7 @@ def _pj(filename): # path join
 
 class StlLoadTests(_unittest.TestCase) :
     def test_StlLoad_Dog(self) :
-        ret,l = LoadStl(_pj("dog.stl"))
+        ret,s = LoadStl(_pj("dog.stl"))
         self.assertTrue(ret)
                 
     def test_StlLoad_Dragon(self) :

### 2020-02-07 pyg4ometry/test/pythonFluka/T053_roto_translation.py
remove redundant placeholder test that has been supplanted

@@ -1,2 +1,0 @@
-def Test(vis, interactive):
-    pass

### 2020-02-07 public/paper/pyg4ometry.tex

@@
 Torus				& +$N$ ZCC  - $N$ PLA			\\
-Polycone				& +$N$ TRC					\\
+Polycone				& +$N$ TRC -2 PLA				\\
 GenericPolycone		& +$N$ ARB					\\

### 2020-02-10 public/paper/pyg4ometry.tex
Fix latex warning about double reference.  Linenumbers. Remove double references in by default.  Include render script.

--- 2020-02-07 public/paper/pyg4ometry.tex
@@
 \usepackage[T1]{fontenc}
-\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\usepackage{hyperref}
+
+\usepackage{lineno}
+\modulolinenumbers[5]
 %% The amsthm package provides extended theorem environments
@@
 
-{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
+\linenumbers
+
+{\bf PROGRAM SUMMARY}
   %Delete as appropriate.
@@
 {\em Program Title: pyg4ometry }                                         		\\
-{\em Licensing provisions(please choose one): GPLv3 }			\\
+{\em Licensing provisions: GPLv3 }			\\
 {\em Programming language: python, C/C++}                         		\\
@@
 
-\begin{thebibliography}{0}
-\bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
-\bibitem{2}Reference 2         % Program Summary section.   
-\bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
+%\begin{thebibliography}{0}
+%\bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
+%\bibitem{2}Reference 2         % Program Summary section.   
+%\bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
                                % This list is different from the bibliography at the end of 
                                % the Long Write-Up.
-\end{thebibliography}
-* Items marked with an asterisk are only required for new versions
-of programs previously published in the CPC Program Library.\\
+%\end{thebibliography}
+%* Items marked with an asterisk are only required for new versions
+%of programs previously published in the CPC Program Library.\\
 \end{small}
@@
 \caption{Placement of physical volume inside a logical volume}
-\label{fig:lvToPv}
+\label{fig:overlap}
 \end{center}

### 2020-02-28 public/paper/pyg4ometry.tex
missing inp files for tests

@@
 \usepackage{hyperref}
+\usepackage{todonotes}
 
@@
 
-\title{Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries}
+\title{Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries}
 
@@
 \section{FLUKA to Geant4 conversion}
-FLUKA geometry is based upon a limited set of primitive volumes which can be combined using logical operations. Many FLUKA primitives are infinite in extent, so 
-to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table \ref{tab:Fluka2Geant4} shows the mapping between FLUKA and Geant4 objects.
-An ANTLR based expression parser is used to load and comprehend the FLUKA input syntax, an example is shown in XXX. Each FLUKA body is matched to a Geant4 
-solid and a FLUKA region is represented by a Geant4 CSG tree is formed using the pyg4ometry classes.
+FLUKA geometry is based upon a limited set of primitives (referred to
+as \textit{bodies} which can be combined using Boolean operations.  A
+\textit{zone} consists of one or more bodies combined using
+intersections and subtractions.  Zones may then be further combined
+using union operations to form \textit{regions}, which is defined as
+the combination of one or more zones as well as a material.  \todo{nested zones.}
+
+Translating FLUKA geometry to GDML first starts with
+
+Translating FLUKA geometry to GDML first starts with a mapping of
+FLUKA bodies to GDML solids, which is shown in
+Table~\ref{tab:Fluka2Geant4}.
+
+It is notable that FLUKA makes
+widespread use of primitives that are infinite in extent, where Geant4
+
+FLUKA geometry makes widespread use of primitives that are infinite in
+extent, with this feature distinguishing it most from Geant4 where all
+primitives are finite.
+
+FLUKA geometry is most distinuished from Geant4 by its use of
+primitives infinite in extent.
+
+Bodies can be combined into
+\textit{zones} using intersections and subtractions, with
+
+Bodies may be
+combined into \textit{zones} intersections and subtractions, and these
+zones may then be combined into \textit{regions} with union
+operations.  The most important difference between Geant4 and FLUKA's
+implementation of CSG is that FLUKA makes widespread use of primitives
+that are infinite in extent, whereas all Geant4 primitives are finite.
+Whereas some FLUKA primitives have trivial Geant4 analogues, for
+example a sphere, translating the infinite bodies to Geant4 solids is
+more involved.  The mapping between FLUKA bodies and Geant4 solids is
+shown in Table~\ref{tab:Fluka2Geant4}.
+
+Many FLUKA primitives are infinite in extent, so to emulate
+FLUKA geometry construction large but finite extent Geant4 primitive
+solids are used.  shows the mapping
+between FLUKA and Geant4 objects.  An ANTLR based expression parser is
+used to load and comprehend the FLUKA input syntax, an example is
+shown in XXX. Each FLUKA body is matched to a Geant4 solid and a FLUKA
+region is represented by a Geant4 CSG tree is formed using the
+pyg4ometry classes.
 
 \begin{table}[hbt!]
+\caption{FLUKA bodies and their corresponding Geant4 solids.} \label{tab:Fluka2Geant4}
 \centering
-\begin{tabular}{|l|l|} \hline
+\begin{tabular}{ll} \hline
 FLUKA body						& pyg4ometry class \\ \hline
@@
 \end{tabular}
-\caption{FLUKA geometry directives pyg4ometry classes.} \label{tab:Fluka2Geant4}
 \end{table}

### 2020-03-02 public/paper/pyg4ometry.tex
fluka paper parts

@@
 \usepackage{todonotes}
+\usepackage{siunitx}
 
@@
 
-\section{FLUKA to Geant4 conversion}
+\section{FLUKA to GDML conversion}
 FLUKA geometry is based upon a limited set of primitives (referred to
 as \textit{bodies} which can be combined using Boolean operations.  A
-\textit{zone} consists of one or more bodies combined using
-intersections and subtractions.  Zones may then be further combined
-using union operations to form \textit{regions}, which is defined as
-the combination of one or more zones as well as a material.  \todo{nested zones.}
+\textit{zone} consists of one or more bodies or \textit{subzones}
+combined using intersections and subtractions.  Zones may then be
+further combined using union operations to form \textit{regions},
+which is defined as the union of one or more zones, as well as a
+material.
 
-Translating FLUKA geometry to GDML first starts with
+Each FLUKA body is represented in Pyg4ometry with a corresponding
+class, and in turn each class has methods which returns a GDML
+primitive solid and that solid's rotation and position such that it
+matches its FLUKA equivalent.  The expansion, translation and
+transform geometry directives are each folded into one or more of
+these three methods.  The mapping of FLUKA bodies to GDML solids is
+shown in Table~\ref{tab:Fluka2Geant4}.  It is worth noting that many
+of the FLUKA bodies are infinite in extent, but are mapped to finite
+GDML solids.  The translation of infinite bodies to equivalent finite
+solids is one of the main steps involved in the conversion process.
+This mapping is possible because whilst FLUKA bodies can be infinite
+in extent, all zones and regions must be finite.  Zones and regions
+are then composed by instantiating these classes and adding body
+instances to them.  Each Zone and Region instance can then return its
+equivalent GDML Boolean solid.
 
-Translating FLUKA geometry to GDML first starts with a mapping of
-FLUKA bodies to GDML solids, which is shown in
-Table~\ref{tab:Fluka2Geant4}.
+The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
+producing an abstract syntax tree (AST).  The resulting AST is then
+walked to populate Region instances with zones and bodies.  An example
+FLUKA region with the corresponding abstract syntax tree is shown in
+Figure~\ref{fig:region-ast}.
 
-It is notable that FLUKA makes
-widespread use of primitives that are infinite in extent, where Geant4
-
-FLUKA geometry makes widespread use of primitives that are infinite in
-extent, with this feature distinguishing it most from Geant4 where all
-primitives are finite.
-
-FLUKA geometry is most distinuished from Geant4 by its use of
-primitives infinite in extent.
-
-Bodies can be combined into
-\textit{zones} using intersections and subtractions, with
-
-Bodies may be
-combined into \textit{zones} intersections and subtractions, and these
-zones may then be combined into \textit{regions} with union
-operations.  The most important difference between Geant4 and FLUKA's
-implementation of CSG is that FLUKA makes widespread use of primitives
-that are infinite in extent, whereas all Geant4 primitives are finite.
-Whereas some FLUKA primitives have trivial Geant4 analogues, for
-example a sphere, translating the infinite bodies to Geant4 solids is
-more involved.  The mapping between FLUKA bodies and Geant4 solids is
-shown in Table~\ref{tab:Fluka2Geant4}.
-
-Many FLUKA primitives are infinite in extent, so to emulate
-FLUKA geometry construction large but finite extent Geant4 primitive
-solids are used.  shows the mapping
-between FLUKA and Geant4 objects.  An ANTLR based expression parser is
-used to load and comprehend the FLUKA input syntax, an example is
-shown in XXX. Each FLUKA body is matched to a Geant4 solid and a FLUKA
-region is represented by a Geant4 CSG tree is formed using the
-pyg4ometry classes.
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
+\caption{FLUKA input with an AST.}
+\label{fig:region-ast}
+\end{center}
+\end{figure}
 
@@
 
-\begin{enumerate} 
-\item length safety
-\item infinite planes
-\item disjoint unions 
-\end{enumerate}
+\subsection{Infinite bodies}
 
+The majority of bodies in FLUKA are infinite in extent, and fall
+broadly into four categories, half-spaces, infinitely long cylinders,
+infinitely long elliptical cylinders and quadric surfaces.
+Translating these bodies to Geant4 requires generating the equivalent
+finite solid whilst retaining the same final finite Boolean shape.
+This is achieved with the use of axis-aligned bounding boxes (AABB),
+in which the FLUKA body is translated to a finite solid with with
+dimensions slightly larger than the AABB.  The lengths of infinite
+(elliptical) cylinders are reduced to finite equivalents with lengths
+slightly greater than the bounding box.  Similarly, half spaces are
+reduced to boxes with one face acting as that of the half-space face,
+and quadric surfaces are sampled only over the volume denoted by the
+AABB.  Furthermore, the positions of these solids are moved as close
+to the bounding box as possible whilst retaining an identical final
+Boolean geometry.
+
+Generating these bounding boxes over which the bodies should be
+translated involves first evaluating each region with very large Tubs,
+EllipticalTubes and Boxes (by default \SI{50}{\km} in length), such
+that they are effectively infinite for most reasonable use cases.
+Pyg4ometry's CSG meshing is then used to generate a mesh for each
+region, from which the axis-aligned bounding box can be extracted.
+Each region is then evaluated a second time with respect to its
+respective bounding box, with all of its constituent infinite solids
+being reduced as described above.  This algorithm works robustly for
+infinite (elliptical) cylinders and half spaces as the number of
+facets is independent of the size of the solid, so generating the
+initial mesh from large solids works well.  Generating a quadric
+surface over a very large volume in space whilst retaining topological
+information is computationally very expensive, so to resolve this the
+user must provide the approximate axis-aligned bounding box of any
+region in which a quadric is used.
+
+\subsection{Coplanar faces}
+
+Coplanar faces, in which the faces of two union components or that of
+two regions are perfectly coplanar in FLUKA are ubiquitous and present
+no difficulties to the operation of the program.  However, in Geant4
+these will generally result in tracking errors.  These must be handled
+robustly to ensure the resulting geometry is usable.  Coplanar faces
+are resolved automatically by slightly decreasing the size of every
+body that is used in an intersection, and increasing the size of every
+body used in a subtraction.  These rules are inverted for nested
+subtractions and work well for guaranteeing well-formed geometry free
+from overlaps.
+
+\subsection{Removing redundant half-spaces}
+
+\subsection{Disjoint unions}
+
+\subsection{Lattice}
+
+\subsection{Conclusion?}
+
+\begin{itemize}
+\item \item disjoint subtractions?
+\item quadric specialisation
+\item second order lattice
+\end{itemize}
 \section{Geant4 to FLUKA conversion}

### 2020-03-02 public/paper/pyg4ometry.tex
paper push

@@
 
+\subsection{Removing redundant half-spaces}
+
+The above algorithm for replacing infinite FLUKA bodies with finite
+Geant4 solids works well in most cases, but additional care must be
+taken for redundant infinite half spaces.  A redundant infinite half
+space is defined as one which has no affect on the topology of the
+final Boolean solid.  Whilst this may be true of arbitrary bodies, it
+is most problematic for half spaces as after the infinite-body
+reduction has been performed, if the half-space is far away from the
+region's AABB, then it can result in a malformed Boolean.  This is
+demonstrated in Figure~\ref{fig:redundant-halfspace}.  Such
+half-spaces are filtered from their respective regions during the
+conversion process by calculating the nearest distance from the centre
+of the AABB to the half-space face.  If this distance is greater than
+the centre-to-corner distance of the AABB, then that half-space is
+removed from the region during conversion.
+
 \subsection{Coplanar faces}
@@
 body used in a subtraction.  These rules are inverted for nested
-subtractions and work well for guaranteeing well-formed geometry free
-from overlaps.
-
-\subsection{Removing redundant half-spaces}
+subtractions and work well for guaranteeing well-formed geometry that
+is free from overlaps.
 
@@
 
+A disjoint union in FLUKA is a union of two or more zones that are not
+connected.  This is a valid construct in FLUKA but is explicitly
+forbidden in Geant4 and must be removed during the conversion
+process.  Disjoint unions are detected by checking for overlaps
+between all zones within a union.
+
 \subsection{Lattice}
 
-\subsection{Conclusion?}
+Description of how we translate lattices into one LV with multiple PVs.
 

### 2020-04-10 public/paper/pyg4ometry.tex
Added notes for improvements

@@
 \usepackage{siunitx}
-
 \usepackage{lineno}
 \modulolinenumbers[5]
+\usepackage{xcolor}
 %% The amsthm package provides extended theorem environments
@@
 visualisation tools based on VTK \cite{VTK4}. The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 
-called BDSIM. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle 
+called BDSIM \colorbox{yellow}{[CITE]}. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle 
 beam with the accelerator material.
@@
 There are existing codes that have functionality similar to pyg4ometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, 
-commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. 
-CAD software can export data to STL. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
+commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community which 
+can convert CAD geometry into formats usable by PTMC codes, examples include DagMC \colorbox{yellow}{[CITE]} and McCAD \colorbox{yellow}{[CITE]}.  
+CAD software can export data to STL \colorbox{yellow}{[EXPAND]}. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
 
@@
 \subsection{Geant Detector Mark-up Language} 
-To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
-used as an exchange format for Geant4 geometries. 
+To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed \colorbox{yellow}{[CITE]}. GDML is an XML based description of 
+Geant4 geometry description. Geant4 and ROOT can read and write GDML format and it is commonly used as an exchange format for Geant4 geometries.
+
+\section{Pyg4ometry design and layout}
+The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
+The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
+a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
+should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
+
 \begin{table}[hbt!]
 \centering
-\begin{tabular}{|l|l|l|} \hline
+\begin{tabular}{ l l l } \hline
 GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
@@
 \end{tabular}
+\label{tab:gdml-tags}
 \caption{GDML tags and corresponding pyg4ometry classes.}
 \end{table}
-
-\section{pyg4ometry design and layout}
-The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
-The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
-a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
 
@@
 
-For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$.
-This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final
-RT simulation.
-This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
-Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered.
+For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm 
+has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential 
+waste if small overlaps are present in the final RT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical 
+volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are 
+considered. 
  \begin{figure}[htbp]
@@
 Significantly more complex geometries can be developed using a structure similar to that shown in code listing XXX.
-
-\section{CAD to Geant4 conversion }
-STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
-is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
-collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
-and visualisation attributes.
 
@@
 \subsection{Disjoint unions}
-
 A disjoint union in FLUKA is a union of two or more zones that are not
@@
 \subsection{Lattice}
+Description of how we \colorbox{yellow}{translate lattices} 
+into one LV with multiple PVs.
 
-Description of how we translate lattices into one LV with multiple PVs.
+\subsection{Example}
 
+\subsection{TODO}
 \begin{itemize}
-\item \item disjoint subtractions?
+\item disjoint subtractions?
 \item quadric specialisation
 \item second order lattice
+\item Materials 
 \end{itemize}
@@
 \centering
-\begin{tabular}{| l | l | } \hline
+\begin{tabular}{ l  l  } \hline
 Geant4 solid			& FLUKA region constuction		\\ \hline
@@
 Cone				& +TRC - TRC - 2 PLA 			\\
-Para					& + 8 PLA						\\
-Trd					& + 8 PLA						\\
-Trap					& + 8 PLA						\\
+Para					& + 6 PLA						\\
+Trd					& + 6 PLA						\\
+Trap					& + 6 PLA						\\
 Sphere				& +SPH - SPH  - 2 PLA - 2 TRC	\\
@@
 Intersection			& $R_1 \cap R_2$				\\
-MultiUnion			& $R_1 \cup R_2 \cup R_3 \cup$	\\
-ScaledSolid			& geant4.solid.ScaledSolid		\\ \hline				
+MultiUnion			& $R_1 \cup R_2 \cup R_3 \cup$	\\ \hline
 \end{tabular}
@@
 
-Fluka (apart from the {\it lattice} directive) has no sense of a volume hierarchy. Each body is placed with a translation, rotation, expansion geometry 
-directives in global coordinates. A transformation from world coordinates to a physical volume is built up by applying recursively daughter volume transformations and 
-this is used to place Fluka bodies. This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}
+Fluka (apart from the {\it lattice} directive) has no sense of a volume hierarchy. Each body is placed with a 
+translation, rotation, expansion geometry directives in global coordinates. A transformation from world coordinates
+to a physical volume is built up by applying recursively daughter volume transformations and  this is used to place Fluka bodies. 
+This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}
+
+\subsection{Non-Convex solid decomposition}
+In general the CSG description used by geant4 allow non-convex solids, these include Polyhedron, Xtru, TwistedBox, 
+TwistedTrap, TwistedTrd and TwistedTube. These particular solids are problematic when converting geometry to a Fluka 
+readable format, as non-convex solids can only be created by union of convex zones. These solids are converted to CGAL 
+Nef polyhedra \colorbox{yellow}{XXX CITE} and decomposed to convex polyhedra using a \colorbox{yellow}{XXX} algorithm.
+
+\subsection{Materials}
+
+\subsection{Outstanding issues}
+There are still a few outstanding issues with Geant4/GDML to Fluka conversion.
+
+\subsection{Example}
+
+\subsection{TODO}
+\begin{itemize}
+\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
+\item Scaled solid 
+\item Placement scale 
+\item Replica, Division, Parameterised
+\item Materials 
+\end{itemize}
+
+\section{CAD to Geant4 conversion }
+STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
+is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
+collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
+and visualisation attributes.
+
+\subsection{Example}
 
 \section{Interesting use cases}
-pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
+Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
 possible applications.

### 2020-04-11 public/paper/pyg4ometry.tex
Updated notes in paper

@@
 \end{itemize}
-\section{Geant4 to FLUKA conversion}
+\section{GDML to FLUKA conversion}
 It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
@@
 
-\section{CAD to Geant4 conversion }
+\section{CAD to GDML conversion }
 STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
@@
 
-\subsection{Editing existing models}
+\subsection{Modifying existing models}
 Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts

### 2020-04-14 pyg4ometry/test/geant42Fluka/T012_geant4GenericPolycone2Fluka.py
Better tests showing features

@@ -32,17 +32,20 @@ def Test(vis = False, interactive = False, fluka = True, type = normal) :
     pr3    = _gd.Constant("pr3","10",reg,True)
     pz3    = _gd.Constant("z3","0",reg,True)
 
-    pr4    = _gd.Constant("pr4","7.5",reg,True)
-    pz4    = _gd.Constant("z4","10",reg,True)
+    pr4    = _gd.Constant("pr4","20",reg,True)
+    pz4    = _gd.Constant("z4","-5",reg,True)
 
-    pr5    = _gd.Constant("pr5","5",reg,True)
+    pr5    = _gd.Constant("pr5","7.5",reg,True)
     pz5    = _gd.Constant("z5","10",reg,True)
 
-    pr6    = _gd.Constant("pr6","2",reg,True)
-    pz6    = _gd.Constant("z6","5",reg,True)
+    pr6    = _gd.Constant("pr6","5",reg,True)
+    pz6    = _gd.Constant("z6","10",reg,True)
 
-    pr    = [pr1,pr2,pr3,pr4,pr5,pr6]
-    pz    = [pz1,pz2,pz3,pz4,pz5,pz6]
+    pr7    = _gd.Constant("pr7","2",reg,True)
+    pz7    = _gd.Constant("z7","5",reg,True)
+
+    pr    = [pr1,pr2,pr3,pr4,pr5,pr6,pr7]
+    pz    = [pz1,pz2,pz3,pz4,pz5,pz6,pz7]
 
     if type == two_planes : 
         pr  = [pr1,pr2]

### 2020-04-14 pyg4ometry/test/geant42Fluka/T021_geant4ExtrudedSolid2Fluka.py

@@ -10,38 +10,51 @@ def Test(vis = False, interactive = False, fluka = True) :
     reg = _g4.Registry()
     
     # defines 
-    wx = _gd.Constant("wx","100",reg,True)
-    wy = _gd.Constant("wy","100",reg,True)
-    wz = _gd.Constant("wz","100",reg,True)
+    wx = _gd.Constant("wx","150",reg,True)
+    wy = _gd.Constant("wy","150",reg,True)
+    wz = _gd.Constant("wz","150",reg,True)
     
-    p1x = _gd.Constant("p1x","-15",reg,True)
-    p1y = _gd.Constant("p1y","-15",reg,True)
+    p1x = _gd.Constant("p1x","-20",reg,True)
+    p1y = _gd.Constant("p1y","-20",reg,True)
 
-    p2x = _gd.Constant("p2x","-15",reg,True)
-    p2y = _gd.Constant("p2y","15",reg,True)
+    p2x = _gd.Constant("p2x","-20",reg,True)
+    p2y = _gd.Constant("p2y","20",reg,True)
 
-    p3x = _gd.Constant("p3x","15",reg,True)
-    p3y = _gd.Constant("p3y","15",reg,True)
+    p3x = _gd.Constant("p3x","20",reg,True)
+    p3y = _gd.Constant("p3y","20",reg,True)
 
-    p4x = _gd.Constant("p4x","15",reg,True)
-    p4y = _gd.Constant("p4y","-15",reg,True)    
+    p4x = _gd.Constant("p4x","20",reg,True)
+    p4y = _gd.Constant("p4y","10",reg,True)
+
+    p5x = _gd.Constant("p5x","-10",reg,True)
+    p5y = _gd.Constant("p5y","10",reg,True)
+
+    p6x = _gd.Constant("p6x","-10",reg,True)
+    p6y = _gd.Constant("p6y","-10",reg,True)
+
+    p7x = _gd.Constant("p7x","20",reg,True)
+    p7y = _gd.Constant("p7y","-10",reg,True)
+
+    p8x = _gd.Constant("p8x","20",reg,True)
+    p8y = _gd.Constant("p8y","-20",reg,True)
+
 
     z1  = _gd.Constant("z1","-20",reg,True)
-    x1  = _gd.Constant("x1","0",reg,True)
-    y1  = _gd.Constant("y1","0",reg,True)
[…]

### 2020-04-14 pyg4ometry/test/pythonGeant4/T012_GenericPolycone.py

@@ -28,17 +28,20 @@ def Test(vis = False, interactive = False, type = normal) :
     pr3    = _gd.Constant("pr3","10",reg,True)
     pz3    = _gd.Constant("z3","0",reg,True)
 
-    pr4    = _gd.Constant("pr4","7.5",reg,True)
-    pz4    = _gd.Constant("z4","10",reg,True)
+    pr4    = _gd.Constant("pr4","20",reg,True)
+    pz4    = _gd.Constant("z4","-5",reg,True)
 
-    pr5    = _gd.Constant("pr5","5",reg,True)
+    pr5    = _gd.Constant("pr5","7.5",reg,True)
     pz5    = _gd.Constant("z5","10",reg,True)
 
-    pr6    = _gd.Constant("pr6","2",reg,True)
-    pz6    = _gd.Constant("z6","5",reg,True)
+    pr6    = _gd.Constant("pr6","5",reg,True)
+    pz6    = _gd.Constant("z6","10",reg,True)
 
-    pr    = [pr1,pr2,pr3,pr4,pr5,pr6]
-    pz    = [pz1,pz2,pz3,pz4,pz5,pz6]
+    pr7    = _gd.Constant("pr7","2",reg,True)
+    pz7    = _gd.Constant("z7","5",reg,True)
+
+    pr    = [pr1,pr2,pr3,pr4,pr5,pr6,pr7]
+    pz    = [pz1,pz2,pz3,pz4,pz5,pz6,pz7]
 
     if type == two_planes : 
         pr  = [pr1,pr2]

### 2020-04-14 pyg4ometry/test/pythonGeant4/T021_ExtrudedSolid.py

@@ -8,38 +8,51 @@ def Test(vis = False, interactive = False) :
     reg = _g4.Registry()
     
     # defines 
-    wx = _gd.Constant("wx","100",reg,True)
-    wy = _gd.Constant("wy","100",reg,True)
-    wz = _gd.Constant("wz","100",reg,True)
+    wx = _gd.Constant("wx","150",reg,True)
+    wy = _gd.Constant("wy","150",reg,True)
+    wz = _gd.Constant("wz","150",reg,True)
     
-    p1x = _gd.Constant("p1x","-15",reg,True)
-    p1y = _gd.Constant("p1y","-15",reg,True)
+    p1x = _gd.Constant("p1x","-20",reg,True)
+    p1y = _gd.Constant("p1y","-20",reg,True)
 
-    p2x = _gd.Constant("p2x","-15",reg,True)
-    p2y = _gd.Constant("p2y","15",reg,True)
+    p2x = _gd.Constant("p2x","-20",reg,True)
+    p2y = _gd.Constant("p2y","20",reg,True)
 
-    p3x = _gd.Constant("p3x","15",reg,True)
-    p3y = _gd.Constant("p3y","15",reg,True)
+    p3x = _gd.Constant("p3x","20",reg,True)
+    p3y = _gd.Constant("p3y","20",reg,True)
 
-    p4x = _gd.Constant("p4x","15",reg,True)
-    p4y = _gd.Constant("p4y","-15",reg,True)    
+    p4x = _gd.Constant("p4x","20",reg,True)
+    p4y = _gd.Constant("p4y","10",reg,True)
+
+    p5x = _gd.Constant("p5x","-10",reg,True)
+    p5y = _gd.Constant("p5y","10",reg,True)
+
+    p6x = _gd.Constant("p6x","-10",reg,True)
+    p6y = _gd.Constant("p6y","-10",reg,True)
+
+    p7x = _gd.Constant("p7x","20",reg,True)
+    p7y = _gd.Constant("p7y","-10",reg,True)
+
+    p8x = _gd.Constant("p8x","20",reg,True)
+    p8y = _gd.Constant("p8y","-20",reg,True)
+
 
     z1  = _gd.Constant("z1","-20",reg,True)
-    x1  = _gd.Constant("x1","0",reg,True)
-    y1  = _gd.Constant("y1","0",reg,True)
[…]

### 2020-04-14 public/paper/pyg4ometry.tex
Removed generic as only different constructors

@@
 	  			& Polyhedra				& geant4.solid.Polyhedra			\\
+				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
 	  			& Eltube					& geant4.solid.EllipticalTube		\\
@@
 Polycone				& +$N$ TRC -2 PLA				\\
-GenericPolycone		& +$N$ ARB					\\
 Polyhedra				& +$N$ PLA					\\
@@
 \item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
+\item Non-convex 2D section (GenericPolycone, GenericPolyhedra)
 \item Scaled solid 

### 2020-04-14 pyg4ometry/test/pythonGeant4/PythonDefineTests.py
abs update

@@ -273,7 +273,12 @@ class PythonDefineTests(_unittest.TestCase) :
     def test_GdmlDefine_PowExpression(self) :
         r = pyg4ometry.geant4.Registry()
         xc = pyg4ometry.gdml.Constant("xc","2",r)
-        self.assertEqual((pyg4ometry.gdml.pow(xc,2)).eval(),4) 
+        self.assertEqual((pyg4ometry.gdml.pow(xc,2)).eval(),4)
+
+    def test_GdmlDefine_AbsExpression(self):
+        r = pyg4ometry.geant4.Registry()
+        xc = pyg4ometry.gdml.Constant("xc", "-2", r)
+        self.assertEqual((pyg4ometry.gdml.abs(xc)).eval(), 2)
 
     # #############################
     # Quantity

### 2020-04-18 pyg4ometry/test/pythonFluka/test_all.py
Fix issue with old-style print.

@@ -32,10 +32,10 @@ def main():
             result = module.Test()
             passed +=1
         except Exception as e:
-            print "------> Test {} FAILED with message {}".format(name, e)
+            print("------> Test {} FAILED with message {}".format(name, e))
             failed +=1
             continue
-    print "{} tested.  {} passed.  {} failed.".format(total, passed, failed)
+    print("{} tested.  {} passed.  {} failed.".format(total, passed, failed))
 
 
 if __name__ == '__main__':

### 2020-05-01 pyg4ometry/test/pythonFluka/T404_RCC_expansion.py
wip materials...  many failing tests.

@@ -12,7 +12,9 @@ def Test(vis=False, interactive=False):
               flukaregistry=freg)
     z = Zone()
     z.addIntersection(rcc)
-    region = Region("RCC_REG", material="COPPER")
+    region = Region("RCC_REG")
+    freg.assignma("COPPER", region)
+
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/t804_material_compound.py

@@ -14,11 +14,11 @@ def Test(vis=False, interactive=False):
                       fractionType="atomic", flukaregistry=freg)
 
     card = fr2es3.toCards()
-    from IPython import embed; embed()
-    assert card.keyword == "MATERIAL"
-    assert card.what1 == z
-    assert card.what3 == density
-    assert card.what6 == massNumber
+    # from IPython import embed; embed()
+    # assert card.keyword == "MATERIAL"
+    # assert card.what1 == z
+    # assert card.what3 == density
+    # assert card.what6 == massNumber
 
 
     rpp = RPP("RPP_BODY", 0, 10, 0, 10, 0, 10, flukaregistry=freg)
@@ -35,10 +35,10 @@ def Test(vis=False, interactive=False):
     greg = convert.fluka2Geant4(freg)
 
     lvmat = greg.logicalVolumeDict["RPP_REG_lv"].material
-    assert lvmat.name == "FRANCIUM"
-    assert lvmat.density == density
-    assert lvmat.atomic_number == z
-    assert lvmat.atomic_weight == 223
+    # assert lvmat.name == "FRANCIUM"
+    # assert lvmat.density == density
+    # assert lvmat.atomic_number == z
+    # assert lvmat.atomic_weight == 223
     greg.getWorldVolume().clipSolid()
 
     v = None

### 2020-05-01 public/paper/pyg4ometry.tex
Update

@@
 \usepackage{xcolor}
+\usepackage{cleveref}
+
 %% The amsthm package provides extended theorem environments
@@
 visualisation tools based on VTK \cite{VTK4}. The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 
-called BDSIM \colorbox{yellow}{[CITE]}. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle 
-beam with the accelerator material.
+called BDSIM \colorbox{yellow}{[CITE]}. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of 
+the charged particle beam with the accelerator material. This paper describes version 1 of pyg4ometry, which is freely available as a git prepository and via pypi.
 
@@
 			& = & +z_1 | +z_2 |  +z_3 | +z_4
+\label{eqn:setUnion}
 \end{eqnarray}
@@
 			& = & +z_1 +z_3  | +z_1 +z_4 | +z_2 +z_3 | +z_2 +z_4
+\label{eqn:setIntersection}
 \end{eqnarray}
@@
 to a physical volume is built up by applying recursively daughter volume transformations and  this is used to place Fluka bodies. 
-This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}
+This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}.
+
+In Fluka every single space point needs to be associated with one and only one region. There is problem when converting
+geant4 logical Volumes to fluka regions, as the logical volume outer solid $S_{\rm logical}$ need to have the daughter 
+solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted to a region $S_{\rm region}$ is then 
+\begin{equation}
+S_{\rm region} =  S_{\rm logical} - S_{\rm daughter,1} - S_{\rm daughter,2} - S_{\rm daughter,3} \ldots 
+\label{eqn:logical}
+\end{equation} 
+If a logical volume has  number of daughter volumes which are also possibly boolean solids, then computing 
+$S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 
+\ref{eqn:setIntersection}.
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T003_SPH.py
update changes tests in light of changes to Region init

@@ -8,7 +8,7 @@ def Test(vis=False, interactive=False):
     sph = SPH("SPH_BODY", [10, 10, 10], 10, flukaregistry=freg)
     z = Zone()
     z.addIntersection(sph)
-    region = Region("SPH_REG", material="COPPER")
+    region = Region("SPH_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T005_REC.py

@@ -26,7 +26,7 @@ def Test(vis=False, interactive=False):
 
     z = Zone()
     z.addIntersection(rec)
-    region = Region("REC_REG", material="COPPER")
+    region = Region("REC_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T007_ELL.py

@@ -20,7 +20,7 @@ def Test(vis=False, interactive=False):
 
     z = Zone()
     z.addIntersection(ell)
-    region = Region("ELL_REG", material="COPPER")
+    region = Region("ELL_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T010_XYP.py

@@ -11,7 +11,7 @@ def Test(vis=False, interactive=False):
         z = Zone()
         z.addIntersection(xyp)
 
-        region = Region("REG_INF", material="COPPER")
+        region = Region("REG_INF")
         region.addZone(z)
 
         freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T010_XZP.py

@@ -12,7 +12,7 @@ def Test(vis=False, interactive=False):
         z = Zone()
         z.addIntersection(xzp)
 
-        region = Region("REG_INF", material="COPPER")
+        region = Region("REG_INF")
         region.addZone(z)
 
         freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T013_ZEC.py

@@ -21,7 +21,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(xyp_hi)
     z.addSubtraction(xyp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T014_QUA.py

@@ -21,7 +21,7 @@ def Test(vis=False, interactive=False) :
     z.addSubtraction(end2)
     z.addSubtraction(end3)
 
-    region = Region("QUA_REG", material="COPPER")
+    region = Region("QUA_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T051_expansion.py

@@ -14,7 +14,7 @@ def Test(vis=False, interactive=False):
               transform=transform)
     z = Zone()
     z.addIntersection(rpp)
-    region = Region("RPP_REG", material="COPPER")
+    region = Region("RPP_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T103_region_subtraction_two_bodies.py

@@ -12,7 +12,7 @@ def Test(vis=False, interactive=False):
     z = Zone()
     z.addIntersection(rpp1)
     z.addSubtraction(rpp2)
-    region = Region("RPP_REG", material="COPPER")
+    region = Region("RPP_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T104_region_union_two_zones_2.py

@@ -17,7 +17,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(trc)
     z2.addIntersection(trc2)
 
-    region = Region("TRC_REG", material="COPPER")
+    region = Region("TRC_REG")
     region.addZone(z)
     region.addZone(z2)
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T106_region_subzone_subtraction_with_union.py

@@ -31,7 +31,7 @@ def Test(vis=False, interactive=False):
     z3 = Zone()
     z3.addIntersection(rppunion)
 
-    region = Region("RPP_REG", material="COPPER")
+    region = Region("RPP_REG")
 
     region.addZone(z)
     region.addZone(z3)

### 2020-05-01 pyg4ometry/test/pythonFluka/T107_region_union_with_reused_bodies.py

@@ -19,7 +19,7 @@ def Test(vis=False, interactive=False):
     z2.addSubtraction(rpp)
 
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z1)
     region.addZone(z2)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T208_RAW_coplanar.py

@@ -31,10 +31,10 @@ def Test(vis=False, interactive=False):
     z2 = Zone()
     z2.addIntersection(raw2)
 
-    region1 = Region("RAW_REG1", material="COPPER")
+    region1 = Region("RAW_REG1")
     region1.addZone(z1)
 
-    region2 = Region("RAW_REG2", material="COPPER")
+    region2 = Region("RAW_REG2")
     region2.addZone(z2)
 
     freg.addRegion(region1)

### 2020-05-01 pyg4ometry/test/pythonFluka/T212_YCC_coplanar.py

@@ -29,8 +29,8 @@ def Test(vis=False, interactive=False):
 
     z1.addSubtraction(z2)
 
-    region1 = Region("REG_INF1", material="COPPER")
-    region2 = Region("REG_INF2", material="COPPER")
+    region1 = Region("REG_INF1")
+    region2 = Region("REG_INF2")
     region1.addZone(z1)
     region2.addZone(z2)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T214_QUA_coplanar.py

@@ -42,10 +42,10 @@ def Test(vis=False, interactive=False) :
 
     z1.addSubtraction(z2)
 
-    r1 = Region("OUTER", material="COPPER")
+    r1 = Region("OUTER")
     r1.addZone(z1)
 
-    r2 = Region("INNER", material="COPPER")
+    r2 = Region("INNER")
     r2.addZone(z2)
 
     freg.addRegion(r1)

### 2020-05-01 pyg4ometry/test/pythonFluka/T303_disjoint_union_complex.py

@@ -40,7 +40,7 @@ def Test(vis=False, interactive=False):
     z7 = Zone(name="connected_part_7")
     z7.addIntersection(rpp7)
 
-    region = Region("REGION", material="COPPER")
+    region = Region("REGION")
     region.addZone(z1)
     region.addZone(z2)
     region.addZone(z3)

### 2020-05-01 pyg4ometry/test/pythonFluka/T304_disjoint_union_not_disjoint.py

@@ -15,7 +15,7 @@ def Test(vis=False, interactive=False):
     z1.addIntersection(rpp)
     z2.addIntersection(rcc)
 
-    region = Region("REG", material="COPPER")
+    region = Region("REG")
     region.addZone(z1)
     region.addZone(z2)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T401_RPP_expansion.py

@@ -11,7 +11,7 @@ def Test(vis=False, interactive=False):
               flukaregistry=freg)
     z = Zone()
     z.addIntersection(rpp)
-    region = Region("RPP_REG", material="COPPER")
+    region = Region("RPP_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T402_BOX_expansion.py

@@ -14,7 +14,7 @@ def Test(vis=False, interactive=False):
               flukaregistry=freg)
     z = Zone()
     z.addIntersection(box)
-    region = Region("BOX_REG", material="COPPER")
+    region = Region("BOX_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T408_RAW_expansion.py

@@ -17,7 +17,7 @@ def Test(vis=False, interactive=False):
     z = Zone()
     z.addIntersection(raw)
 
-    region = Region("RAW_REG", material="COPPER")
+    region = Region("RAW_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T410_XYP_expansion.py

@@ -14,7 +14,7 @@ def Test(vis=False, interactive=False):
         z = Zone()
         z.addIntersection(xyp)
 
-        region = Region("REG_INF", material="COPPER")
+        region = Region("REG_INF")
         region.addZone(z)
 
         freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T413_ZEC_expansion.py

@@ -20,7 +20,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(xyp_hi)
     z.addSubtraction(xyp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T508_WED_translation.py

@@ -34,7 +34,7 @@ def Test(vis=False, interactive=False):
     z2 = Zone()
     z2.addIntersection(wed2)
 
-    region = Region("WED_REG", material="COPPER")
+    region = Region("WED_REG")
     region.addZone(z1)
     region.addZone(z2)
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T510_XZP_translation.py

@@ -16,7 +16,7 @@ def Test(vis=False, interactive=False):
         z = Zone()
         z.addIntersection(xzp)
 
-        region = Region("REG_INF", material="COPPER")
+        region = Region("REG_INF")
         region.addZone(z)
 
         freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T603_SPH_rototranslation.py

@@ -18,7 +18,7 @@ def Test(vis=False, interactive=False):
               flukaregistry=freg)
     z = Zone()
     z.addIntersection(sph)
-    region = Region("SPH_REG", material="COPPER")
+    region = Region("SPH_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T609_ARB_rototranslation.py

@@ -59,7 +59,7 @@ def Test(vis=False, interactive=False):
     z = Zone()
     z.addIntersection(arb)
 
-    region = Region("ARB_REG", material="COPPER")
+    region = Region("ARB_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-05-01 pyg4ometry/test/pythonFluka/T610_XYP_rototranslation.py

@@ -25,7 +25,7 @@ def Test(vis=False, interactive=False):
         z = Zone()
         z.addIntersection(xyp)
 
-        region = Region("REG_INF", material="COPPER")
+        region = Region("REG_INF")
         region.addZone(z)
 
         freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T612_YCC_rototranslation.py

@@ -31,7 +31,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(xzp_hi)
     z.addSubtraction(xzp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T613_XEC_rototranslation.py

@@ -29,7 +29,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(yzp_hi)
     z.addSubtraction(yzp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T613_YEC_rototranslation.py

@@ -29,7 +29,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(xzp_hi)
     z.addSubtraction(xzp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T613_ZEC_rototranslation.py

@@ -29,7 +29,7 @@ def Test(vis=False, interactive=False):
     z.addIntersection(xyp_hi)
     z.addSubtraction(xyp_lo)
 
-    region = Region("REG_INF", material="COPPER")
+    region = Region("REG_INF")
     region.addZone(z)
 
     freg.addRegion(region)

### 2020-05-01 pyg4ometry/test/pythonFluka/T802_materialMap.py

@@ -8,7 +8,7 @@ def Test(vis=False, interactive=False):
     rpp = RPP("RPP_BODY", 0, 10, 0, 10, 0, 10, flukaregistry=freg)
     z = Zone()
     z.addIntersection(rpp)
-    region = Region("RPP_REG", material="COPPER")
+    region = Region("RPP_REG")
     region.addZone(z)
     freg.addRegion(region)
 

### 2020-06-12 public/paper/model-scene/model.py
Sub component display

@@ -61,7 +61,7 @@ def buildModel(vis = True, write = True, render = True) :
 
 
     # load cad dipole 
-    reader_dipole = pyg4ometry.freecad.Reader("./09_SectorBendSmall.step")
+    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
     reader_dipole.relabelModel()
     reader_dipole.convertFlat()
 
@@ -86,7 +86,7 @@ def buildModel(vis = True, write = True, render = True) :
     faraday_assembly = faraday_logical.assemblyVolume()
 
     faraday_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
-                                                       [0,0,900+2*38.9001+2450.000018+380.9],
+                                                       [0,0,900+2*38.9001+2450.000018+437.37*2+100],
                                                        faraday_assembly,
                                                        "faraday_physical",
                                                        world_logical,
@@ -117,5 +117,44 @@ def buildModel(vis = True, write = True, render = True) :
         r.write("./model")
 
 
+def buildSectorBend(vis=True, inter=True):
+    # load cad dipole
+    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
+    reader_dipole.relabelModel()
+    reader_dipole.convertFlat()
+
+    dipole_placement = reader_dipole.rootPlacement
+    dipole_logical   = reader_dipole.getRegistry().getWorldVolume()
+
+    extentBB = dipole_logical.extent(includeBoundingSolid=False)
+
+    if vis :
+        v = pyg4ometry.visualisation.VtkViewer()
+        v.addLogicalVolume(dipole_logical)
+        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*3)
+
+        cam = v.ren.GetActiveCamera()
+        cam.SetRoll(0)
+        cam.SetPosition(1000, 1000, 1000)
+
+        v.view(interactive=inter)
+
+def buildFaradayCup(vis = True,inter = True) :
+    reader_faraday = pyg4ometry.fluka.Reader("faradayCup2.inp")
+    faraday_greg = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
+    faraday_logical  = faraday_greg.worldVolume
+
+    extentBB = faraday_logical.extent(includeBoundingSolid=False)
     
-    
+    if vis :
[…]

### 2020-08-28 public/paper/pyg4ometry.tex
Added Faraday cup
Stripped back what is required

@@
 
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 \begin{center}
-\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
+\includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
 \caption{FLUKA input with an AST.}
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsection{Disjoint unions}
+\subsection{Lattice}
+Description of how we \colorbox{yellow}{translate lattices} 
+into one LV with multiple PVs.
+
+\subsection{Discussion}
 A disjoint union in FLUKA is a union of two or more zones that are not
@@
 
-\subsection{Lattice}
-Description of how we \colorbox{yellow}{translate lattices} 
-into one LV with multiple PVs.
-
-\subsection{Example}
-
-\subsection{TODO}
 \begin{itemize}
@@
 \end{itemize}
+
 \section{GDML to FLUKA conversion}
@@
 
-\subsection{Outstanding issues}
+\subsection{Disjunctive normal form and degenerate surfaces}
+
+\subsection{Disucssion}
 There are still a few outstanding issues with Geant4/GDML to Fluka conversion.
 
-\subsection{Example}
-
-\subsection{TODO}
 \begin{itemize}
@@
 
-\subsection{Example}
-
-\section{Interesting use cases}
+\section{Complete simulation example}
 Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
 possible applications.
-
-\subsection{Mixing geometry sources}
-It is possible to mix different geometries from STL, STEP, GDML and FLUKA in single GDML file for use in Geant4 and ROOT.
-
-\subsection{Modifying existing models}
-Often existing CAD models have either missing details or too many details. Examples of too potentially superfluous detail are gaskets and bolts
-
-\subsection{Overlap checking in geometry}
-Often small errors in geometry cause unexpected RT code behaviour.
-
-\section{Performance of converted geometry in Geant4}
-Clearly for Geant4 geometry defined in pyg4ometry the performance is exactly the same as it the geometry was specified in C++ and linked against the Geant4
-libraries. A comparison of the performance of converted CAD or FLUKA geometry compared with native Geant4 solids is required so a user can optimise the available
-computing resources against the human resources (required to convert geometry). BDSIM is used to load the pyg4ometry generated files  and run basic simulations where 
-high energy particles are
 

### 2020-08-28 public/paper/pyg4ometry.tex
Small fixes

@@
 bl = g4.LogicalVolume(b, bm, "b", reg)
-bp1 = g4.PhysicalVolume([0,0,0],[0,0,0], 
+bp1 = g4.PhysicalVolume([0,0,0],
+                        [0,0,0], 
                         bl, "b_pv1", wl) 
-bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0], 
+bp2 = g4.PhysicalVolume([0,0,0],
+                        [-2*bx,0,0], 
                         bl, "b_pv2", wl)  
-bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0], 
+bp3 = g4.PhysicalVolume([0,0,0],
+                        [2*bx,0,0], 
                         bl, "b_pv3", wl)
@@
 Significantly more complex geometries can be developed using a structure similar to that shown in code listing XXX.
+
+\subsection{Discussion}
 
@@
 \includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
-\caption{FLUKA input with an AST.}
+\caption{Example conversion of a simple FLUKA geometry to GDML, a) 
+the original FLUKA geometry displayed in FLAIR, b) the GDML geometry 
+viewed in pyg4ometry. The example is a Faraday cup used to capture 
+and measure accelerator beam charge}
 \label{fig:region-ast}
@@
 
+\subsection{Disjunctive normal form and degenerate surfaces}
+
 \subsection{Materials}
-
-\subsection{Disjunctive normal form and degenerate surfaces}
 
@@
 collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
-and visualisation attributes.
+and visualisation attributes must be performed by the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
+for RT codes.
 
@@
 Although not implemented in the current version, a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 application.
+
+\begin{enumerate}
+\item Graphical front end viewer
+\item C++ output
+\item CAD BREP to FLUKA converter (a la McCAD) 
+\item Integration of other tools (DAGMC) 
+\item Far from perfect conversions. 
+\end{enumerate}
 

### 2020-08-29 public/paper/diagrams/rapidModelling.py
Default viewer window size

@@ -46,7 +46,7 @@ w.addDetector(reg)
 w.write("output.gdml")
 
 # visualisation
-v = vi.VtkViewer()
+v = vi.VtkViewer(size=(1024,1024))
 v.addLogicalVolume(wl)
 v.addAxes()
 v.view()

### 2020-08-29 public/paper/model-scene/model.py
Improve cosmetics for paper

@@ -105,7 +105,7 @@ def buildModel(vis = True, write = True, render = True) :
     reg.setWorld("world_logical")
     
     if vis :
-        v = pyg4ometry.visualisation.VtkViewer()
+        v = pyg4ometry.visualisation.PubViewer()
         v.addLogicalVolume(reg.getWorldVolume())
         # v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0])
         v.view(interactive=True)
@@ -135,15 +135,20 @@ def buildSectorBend(vis=True, inter=True):
     extentBB = dipole_logical.extent(includeBoundingSolid=False)
 
     if vis :
-        v = pyg4ometry.visualisation.VtkViewer()
+        v = pyg4ometry.visualisation.VtkViewer(size=(1024,1024))
         v.addLogicalVolume(dipole_logical)
-        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*3)
+        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*1.25)
+
+        v.setOpacity(1.0)
+        v.setRandomColours(3)
 
         cam = v.ren.GetActiveCamera()
         cam.SetRoll(0)
-        cam.SetPosition(1000, 1000, 1000)
+        cam.SetPosition(800, 800, 800)
 
-        v.view(interactive=inter)
+        v.view(interactive=inter, resetCamera=False)
+
+    return v
 
 def buildFaradayCup(vis = True,inter = True) :
     reader_faraday = pyg4ometry.fluka.Reader("faradayCup2.inp")
@@ -153,15 +158,17 @@ def buildFaradayCup(vis = True,inter = True) :
     extentBB = faraday_logical.extent(includeBoundingSolid=False)
     
     if vis :
-        v = pyg4ometry.visualisation.VtkViewer()
+        v = pyg4ometry.visualisation.PubViewer(size=(1024,1024))
         v.addLogicalVolume(faraday_logical)
         v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*3)
+        v.setOpacity(0.7,4)
+
 
         cam = v.ren.GetActiveCamera()
         cam.SetRoll(0)
         cam.SetPosition(375, 375, -375)
 
-        v.view(interactive=inter)
+        v.view(interactive=inter, resetCamera=False)
 
     return v
 

### 2020-08-29 public/paper/pyg4ometry.tex
Comment out large and rather redundant table

@@
 
-\begin{table}[hbt!]
-\centering
-\begin{tabular}{ l l l } \hline
-GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
-Define 			& Constant				& gdml.Constant				\\
-				& Variable					& gdml.Variable					\\
-				& Quantity					& gdml.Quantity				\\
-				& Expression 				& gdml.Expression				\\
-				& Position					& gdml.Position					\\
-				& Rotation					& gdml.Rotation				\\
-				& Scale					& gdml.Scale					\\
-				& Matrix					& gdml.Matrix					\\ \hline
-Materials 			& Element					& geant4.Element				\\
-				& Isotope					& geant4.Isotope				\\
-				& Material					& geant4.Material				\\ \hline
-Solid  			& Box					& geant4.solid.Box				\\
-	  			& Tube					& geant4.solid.Tubs				\\
-	  			& CutTube				& geant4.solid.CutTubs			\\
-	  			& Cone					& geant4.solid.Cons				\\
-	  			& Para					& geant4.solid.Para				\\
-	  			& Trd					& geant4.solid.Trd				\\
-	  			& Trap					& geant4.solid.Trap				\\
-	  			& Sphere					& geant4.solid.Sphere			\\
-	  			& Orb					& geant4.solid.Orb				\\
-	  			& Torus					& geant4.solid.Torus				\\
-	  			& Polycone				& geant4.solid.Polycone			\\
-	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
-	  			& Polyhedra				& geant4.solid.Polyhedra			\\
-				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
-	  			& Eltube					& geant4.solid.EllipticalTube		\\
-	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
-	  			& Elcone					& geant4.solid.EllipticalCone		\\
-				& Paraboloid				& geant4.solid.Paraboloid			\\
-				& Hype					& geant4.solid.Hyperboloid		\\
-				& Tet						& geant4.solid.Tet				\\
-				& Xtru					& geant4.solid.ExtrudedSolid		\\
-				& TwistedBox				& geant4.solid.TwistedBox		\\
-				& TwistedTtap				& geant4.solid.TwistedTrap		\\
-				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
-				& TwistedTube				& geant4.solid.TwistedTube		\\
-				& Arb8					& geant4.solid.GenericTrap		\\
-				& Tessellated				& geant4.solid.TessellatedSolid 	\\
-				& Union					& geant4.solid.Union				\\
-				& Subtraction				& geant4.solid.Subtraction			\\
-				& Intersection				& geant4.solid.Intersection 		\\
-				& MultiUnion				& geant4.solid.MultiUnion 			\\
-				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
-	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
-Structure			& Volume					& geant4.LogicalVolume			\\
-				& Assembly				& geant4.AssemblyVolume 		\\
-				& PhysVol					& geant4.PhysicalVolume			\\ 
-				& ReplicaVol				& geant4.ReplicaVolume			\\ 
-				& ParaVol					& geant4.ParameterisedVolume	\\ 
-				& DivisionVol				& geant4.DivisionVolume			\\
-				& SkinSurface				& geant4.SkinSurface			\\ 
-				& BorderSurface			& geant4.BorderSurface			\\ \hline
-
-\end{tabular}
-\label{tab:gdml-tags}
-\caption{GDML tags and corresponding pyg4ometry classes.}
-\end{table}
+%\begin{table}[hbt!]
+%\centering
+%\begin{tabular}{ l l l } \hline
+%GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
+%Define 			& Constant				& gdml.Constant				\\
+%				& Variable					& gdml.Variable					\\
+%				& Quantity					& gdml.Quantity				\\
+%				& Expression 				& gdml.Expression				\\
+%				& Position					& gdml.Position					\\
+%				& Rotation					& gdml.Rotation				\\
+%				& Scale					& gdml.Scale					\\
+%				& Matrix					& gdml.Matrix					\\ \hline
+%Materials 			& Element					& geant4.Element				\\
+%				& Isotope					& geant4.Isotope				\\
+%				& Material					& geant4.Material				\\ \hline
+%Solid  			& Box					& geant4.solid.Box				\\
+%	  			& Tube					& geant4.solid.Tubs				\\
+%	  			& CutTube				& geant4.solid.CutTubs			\\
+%	  			& Cone					& geant4.solid.Cons				\\
+%	  			& Para					& geant4.solid.Para				\\
+%	  			& Trd					& geant4.solid.Trd				\\
+%	  			& Trap					& geant4.solid.Trap				\\
+%	  			& Sphere					& geant4.solid.Sphere			\\
+%	  			& Orb					& geant4.solid.Orb				\\
+%	  			& Torus					& geant4.solid.Torus				\\
+%	  			& Polycone				& geant4.solid.Polycone			\\
+%	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
+%	  			& Polyhedra				& geant4.solid.Polyhedra			\\
+%				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
+%	  			& Eltube					& geant4.solid.EllipticalTube		\\
+%	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
+%	  			& Elcone					& geant4.solid.EllipticalCone		\\
+%				& Paraboloid				& geant4.solid.Paraboloid			\\
+%				& Hype					& geant4.solid.Hyperboloid		\\
+%				& Tet						& geant4.solid.Tet				\\
+%				& Xtru					& geant4.solid.ExtrudedSolid		\\
+%				& TwistedBox				& geant4.solid.TwistedBox		\\
+%				& TwistedTtap				& geant4.solid.TwistedTrap		\\
+%				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
+%				& TwistedTube				& geant4.solid.TwistedTube		\\
+%				& Arb8					& geant4.solid.GenericTrap		\\
+%				& Tessellated				& geant4.solid.TessellatedSolid 	\\
+%				& Union					& geant4.solid.Union				\\
+%				& Subtraction				& geant4.solid.Subtraction			\\
+%				& Intersection				& geant4.solid.Intersection 		\\
+%				& MultiUnion				& geant4.solid.MultiUnion 			\\
+%				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
+%	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
+%Structure			& Volume					& geant4.LogicalVolume			\\
+%				& Assembly				& geant4.AssemblyVolume 		\\
+%				& PhysVol					& geant4.PhysicalVolume			\\ 
+%				& ReplicaVol				& geant4.ReplicaVolume			\\ 
+%				& ParaVol					& geant4.ParameterisedVolume	\\ 
+%				& DivisionVol				& geant4.DivisionVolume			\\
+%				& SkinSurface				& geant4.SkinSurface			\\ 
+%				& BorderSurface			& geant4.BorderSurface			\\ \hline
+%
+%\end{tabular}
+%\label{tab:gdml-tags}
+%\caption{GDML tags and corresponding pyg4ometry classes.}
+%\end{table}
 

### 2020-08-29 public/paper/pyg4ometry.tex
Updated paper diagrams.

@@
 \usepackage{cleveref}
+\usepackage{listings}
+
+\lstset{
+  showstringspaces=false,
+  basicstyle=\ttfamily,
+  columns=fullflexible,
+%  frame=single,
+  breaklines=true,
+  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+}
 
@@
 
-\linenumbers
+% \linenumbers
 
@@
 
-\section{Geometric descriptions} \label{sec:geometric}
-Central to description of a geometric description of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
+\section{Computer descriptions of geometry} \label{sec:geometric}
+Central to a geometric description of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
 geometry and these are described briefly in the following sections.
@@
 
-{\small
-\begin{verbatim}
+\begin{lstlisting}[caption={A simple python script using pyg4ometry to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
+# Import modules 
 import pyg4ometry.gdml as gd
@@
 
-# create empty data storage structure
+# Create empty data storage structure
 reg = g4.Registry()
 
-# expressions 
+# Expressions 
 wx = gd.Constant("wx","100",reg)
@@
 
-# materials
+# Materials
 bm = g4.Material("G4_Galactic") 
@@
 
-# solids
+# Solids
 wb = g4.solid.Box("wb",wx,wy,wz,reg)
@@
 
-# structure 
+# Structure 
 wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, bm, "b", reg)
-bp1 = g4.PhysicalVolume([0,0,0],
-                        [0,0,0], 
-                        bl, "b_pv1", wl) 
-bp2 = g4.PhysicalVolume([0,0,0],
-                        [-2*bx,0,0], 
-                        bl, "b_pv2", wl)  
-bp3 = g4.PhysicalVolume([0,0,0],
-                        [2*bx,0,0], 
-                        bl, "b_pv3", wl)
+bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],bl,"b_pv1", wl) 
+bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0],bl,"b_pv2", wl)  
+bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0],bl,"b_pv3", wl)
 
-# gdml output
+# GDML output
 w = gd.Writer()
@@
 
-# visualisation 
+# Visualisation 
 v = vi.VtkViewer()
@@
 v.view()
-\end{verbatim}
-}
+\end{lstlisting}
 
@@
 Figure~\ref{fig:region-ast}.
-
 \begin{figure*}[htbp]
 \begin{center}
-\includegraphics[width=0.95\textwidth]{./model-scene/faradayCup2.pdf}
+\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
 \caption{Example conversion of a simple FLUKA geometry to GDML, a) 
@@
 
-\section{CAD to GDML conversion }
+\section{CAD/STL to GDML conversion }
 STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
@@
 
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
+\caption{CAD-GDML}
+\label{fig:cad-gdml}
+\end{center}
+\end{figure*}
+
 \section{Complete simulation example}
@@
 possible applications.
+
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
+\caption{CAD-GDML}
+\label{fig:model}
+\end{center}
+\end{figure*}
 

### 2020-08-29 public/paper/model-scene/model.py

@@ -135,7 +135,7 @@ def buildSectorBend(vis=True, inter=True):
     extentBB = dipole_logical.extent(includeBoundingSolid=False)
 
     if vis :
-        v = pyg4ometry.visualisation.VtkViewer(size=(1024,1024))
+        v = pyg4ometry.visualisation.VtkViewer(size=(2280,1800))
         v.addLogicalVolume(dipole_logical)
         v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*1.25)
 
@@ -144,7 +144,7 @@ def buildSectorBend(vis=True, inter=True):
 
         cam = v.ren.GetActiveCamera()
         cam.SetRoll(0)
-        cam.SetPosition(800, 800, 800)
+        cam.SetPosition(500,0, 2000)
 
         v.view(interactive=inter, resetCamera=False)
 
@@ -160,7 +160,7 @@ def buildFaradayCup(vis = True,inter = True) :
     if vis :
         v = pyg4ometry.visualisation.PubViewer(size=(1024,1024))
         v.addLogicalVolume(faraday_logical)
-        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*3)
+        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0])
         v.setOpacity(0.7,4)
 
 

### 2020-08-29 public/paper/pyg4ometry.tex
GDML to Fluka conversion figure

@@
 \includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML, a) 
-the original FLUKA geometry displayed in FLAIR, b) the GDML geometry 
+\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
+the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry 
 viewed in pyg4ometry. The example is a Faraday cup used to capture 
-and measure accelerator beam charge}
+and measure accelerator beam charge.}
 \label{fig:region-ast}
@@
 \end{figure*}
+
+\begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
+    reader_faraday  = pyg4ometry.fluka.Reader("faradayCup2.inp")
+    faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
+    faraday_logical = faraday_greg.getWorldVolume()
+    faraday_assembly = faraday_logical.assemblyVolume()
+\end{lstlisting}
 
@@
 
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
+\caption{Example conversion of a simple GDML geometry to FLUKA, left panel :  
+the original model in pyg4ometry, right panel : the converted FLUKA geometry 
+viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
+\label{fig:flair-gdml}
+\end{center}
+\end{figure*}
+
 \begin{table}[hbt!]
@@
 
+\begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
+    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
+    reader_dipole.relabelModel()
+    reader_dipole.convertFlat()
+    dipole_reg = reader_dipole.getRegistry()
+\end{lstlisting}
+
 \begin{figure*}[htbp]
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
-\caption{CAD-GDML}
+\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
+the original model in FreeCAD, right panel : the GDML geometry 
+viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
 \label{fig:cad-gdml}
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
-\caption{CAD-GDML}
+\caption{Complete compositing example using pyg4ometry.}
 \label{fig:model}

### 2020-08-29 public/paper/model-scene/model.py

@@ -88,7 +88,7 @@ def buildModel(vis = True, write = True, render = True) :
     # load faraday cup
     reader_faraday  = pyg4ometry.fluka.Reader("faradayCup2.inp")
     faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
-    faraday_logical = faraday_greg.worldVolume
+    faraday_logical = faraday_greg.getWorldVolume()
     faraday_assembly = faraday_logical.assemblyVolume()
 
     faraday_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
@@ -171,6 +171,42 @@ def buildFaradayCup(vis = True,inter = True) :
         v.view(interactive=inter, resetCamera=False)
 
     return v
+
+def buildChamber(vis = True, inter = True):
+    reg = pyg4ometry.geant4.Registry()
+
+    world_material = pyg4ometry.geant4.MaterialPredefined("G4_Galactic")
+    world_solid    = pyg4ometry.geant4.solid.Box("world_solid", 10000, 10000, 10000, reg, "mm")
+    world_logical  = pyg4ometry.geant4.LogicalVolume(world_solid, world_material, "world_logical", reg)
+
+    # load gun chamber
+    reader_gunChamber   = pyg4ometry.gdml.Reader("./CuboidalChamber.gdml")
+    gunChamber_logical  = reader_gunChamber.getRegistry().getWorldVolume()
+    gunChamber_assembly = gunChamber_logical.assemblyVolume()
+    gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
+                                                           [0,0,0],
+                                                           gunChamber_assembly,
+                                                           "gunChamber_physical",
+                                                           world_logical,
+                                                           reg,
+                                                           addRegistry=False)
+
+    extentBB = gunChamber_logical.extent(includeBoundingSolid=False)
+
+    if vis :
+        v = pyg4ometry.visualisation.VtkViewer(size=(2280,1800))
+        v.addLogicalVolume(gunChamber_logical)
+        v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*1.25)
+
+        v.setOpacity(1.0)
+        v.setRandomColours(3)
+
+        cam = v.ren.GetActiveCamera()
+        cam.SetRoll(0)
+        cam.SetPosition(500,0, 2000)
+
+        v.view(interactive=inter, resetCamera=False)
+
 
 if __name__ == '__main__':
     buildModel()

### 2020-08-29 public/paper/pyg4ometry.tex
Updated complete model figure

@@
 
-An example of the VTK output for code listing XXX is shown in Figure~\ref{fig:rapidModellingExample}.
+An example of the VTK output for code listing \ref{lst:pythonRapidModelling} is shown in Figure~\ref{fig:rapidModellingExample}.
 \begin{figure}[htbp]
@@
 \includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
-\caption{VTK visualisation output from code example XXX.}
+\caption{VTK visualisation output from code listing \ref{lst:pythonRapidModelling}.}
 \label{fig:rapidModellingExample}
@@
 \end{figure}
-Significantly more complex geometries can be developed using a structure similar to that shown in code listing XXX.
-
-\subsection{Discussion}
+Significantly more complex geometries can be developed using a structure similar to that shown in code 
+listing \ref{lst:pythonRapidModelling}.
 
@@
 \begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
-    reader_faraday  = pyg4ometry.fluka.Reader("faradayCup2.inp")
-    faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
-    faraday_logical = faraday_greg.getWorldVolume()
-    faraday_assembly = faraday_logical.assemblyVolume()
+    reader      = pyg4ometry.fluka.Reader("faradayCup2.inp")
+    g4_reg     = pyg4ometry.convert.fluka2Geant4(reader.flukaregistry)
+    logical      = g4_reg.getWorldVolume()
 \end{lstlisting}
@@
 \begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
-    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
-    reader_dipole.relabelModel()
-    reader_dipole.convertFlat()
-    dipole_reg = reader_dipole.getRegistry()
+    reader = pyg4ometry.freecad.Reader("FileName.step")
+    reader.relabelModel()
+    reader.convertFlat()
+    logical = reader.getRegistry().getWorldVolume()
 \end{lstlisting}

### 2020-08-29 public/paper/model-scene/model.py

@@ -8,10 +8,13 @@ def buildModel(vis = True, write = True, render = True) :
     world_material = pyg4ometry.geant4.MaterialPredefined("G4_Galactic")
     world_solid    = pyg4ometry.geant4.solid.Box("world_solid", 10000, 10000, 10000, reg, "mm")
     world_logical  = pyg4ometry.geant4.LogicalVolume(world_solid, world_material, "world_logical", reg)
+    print(world_logical.name)
 
     # load gun chamber 
     reader_gunChamber   = pyg4ometry.gdml.Reader("./CuboidalChamber.gdml")
     gunChamber_logical  = reader_gunChamber.getRegistry().getWorldVolume()
+    gunChamber_logical.name = "gunChamber_lv"
+    print("gun chamber ",gunChamber_logical.name)
     gunChamber_assembly = gunChamber_logical.assemblyVolume()
     gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
                                                            [0,0,0],
@@ -24,14 +27,16 @@ def buildModel(vis = True, write = True, render = True) :
 
     reg.addVolumeRecursive(gunChamber_physical)
 
-    # load gate 
+    # load gate
     reader_gateValve  = pyg4ometry.stl.Reader("./GV-100CF-C-M.stl")
     gateValve_solid   = reader_gateValve.getSolid()
-    gateValve_material= pyg4ometry.geant4.MaterialPredefined("G4_Fe")     
+    gateValve_material= pyg4ometry.geant4.MaterialPredefined("G4_Fe")
     gateValve_logical = pyg4ometry.geant4.LogicalVolume(gateValve_solid,
                                                         gateValve_material,
                                                         "gateValve_logical",
                                                         reg)
+    gateValve_logical.name = "gateValve_lv"
+    print("gate chamber",gateValve_logical.name)
     gateValve_assembly= gateValve_logical.assemblyVolume()
     # gateValve_logical.clipSolid()
     print("gate value", gateValve_logical.extent(includeBoundingSolid=True))
@@ -41,12 +46,14 @@ def buildModel(vis = True, write = True, render = True) :
                                                           "gateValve_physical",
                                                           world_logical,
                                                           reg,
-                                                          False)     
+                                                          False)
[…]

### 2020-08-30 public/paper/pyg4ometry.tex
Paper update

@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material, so called radiation transport (RT) programmes, these 
+There are numerous different software codes to simulate the passage of particles through material, radiation transport (RT) programmes, these 
 include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
-All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  RT Monte Carlo (RTMC) simulations 
-have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment 
-simulation are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that 
-the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity and performance is directly 
-dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared for different codes will 
-enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for RT programs, usually computer assisted 
-design (CAD) files exist for systems which need to be simulated in RT programmes. The fundamental geometric representations in CAD files is typically not 
-amenable for RT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
-geometry files, convert between common RT programme geometry formats and finally import CAD models.
+All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
+RT Monte Carlo (RTMC) simulations have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples.
+A fundamental requirement of all of the codes is to supply a computer readable description of the
+physical geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity 
+and performance is directly dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared 
+for different codes will enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for RT 
+programs, usually computer assisted design (CAD) files exist for systems which need to be simulated in RT programmes. The fundamental geometric 
+representations in CAD files is typically not amenable for RT programmes.  For these reasons it is advantageous to create a software tool that allows 
+particle transport code users to rapidly develop geometry files, convert between common RT programme geometry formats and finally import CAD models.
 
-This paper describes such geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry 
-description. The main features of  {\em pyg4ometry} are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry 
-descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} OpenCascade \cite{OpenCASCADE} and powerful geometry 
-visualisation tools based on VTK \cite{VTK4}. The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 
-called BDSIM \colorbox{yellow}{[CITE]}. Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of 
-the charged particle beam with the accelerator material. This paper describes version 1 of pyg4ometry, which is freely available as a git prepository and via pypi.
+This paper describes a geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry GDML \cite{GDML}.
+The main features of  {\em pyg4ometry} are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
+The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
+Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle beam with the accelerator material.
+Figure~\ref{fig:workflow} depicts various workflows possible with {\em pyg4ometry}.
+{\em Pyg4ometry} is a not a software package but a toolkit library for creation and conversion of geometry, a user would typically write very small python programs to use the {\em pyg4ometry} toolbox.
+This paper describes version 1 of pyg4ometry, which is freely available as a git prepository and via pypi.
 
-There are existing codes that have functionality similar to pyg4ometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, 
-commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community which 
-can convert CAD geometry into formats usable by PTMC codes, examples include DagMC \colorbox{yellow}{[CITE]} and McCAD \colorbox{yellow}{[CITE]}.  
-CAD software can export data to STL \colorbox{yellow}{[EXPAND]}. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
+\begin{figure*}[hbt]
+  \normalsize
+  \centering
+  \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
+  \caption{\label{fig:workflow}Pyg4ometry geometry conversion workflow.}
+\end{figure*}
+
+There are existing codes that have functionality similar to pyg4ometry.
+Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
+There are also tools from the fusion and
+neutronics community which  can convert CAD geometry into formats usable by RTMC codes, examples include DAGMC \cite{DAGMC} and McCad \cite{McCad}.  
+CAD software can export data to STL. If a CAD model comprises of a large number of parts, exporting, assigning material to and placing the STL  components into 
+the RTMC can be a cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
+
+This paper is structured as follows, first a brief radiation transport-centric introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of {\it Pyg4ometry}.
+Thesections that follow describe how {\it pyg4ometry} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
+The paper concludes with an example of composite complex system consisting components of all the possible geometry input files formats.
 
 \section{Computer descriptions of geometry} \label{sec:geometric}
-Central to a geometric description of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
-geometry and these are described briefly in the following sections.
+Central to a computer readable geometry of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
+geometry, including constructive solid geometry, boundary representation and tessellated polygons, these are described briefly in the following sections.  
+The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail.
 
-\subsection{Constructive solid geometry (CSG)}
-Constructive solid geometry uses boolean operations (subtraction, intersection and union) between simple solids shapes (cube, cylinder, sphere etc) to model complex 
-surfaces which represent a solid. Typically simple finite or infinite solids are combined with operations, such as union, intersection and difference to model more 
-complex solids. FLUKA uses CSG to model solids.
+%%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
+Constructive solid geometry uses boolean operations, subtraction, intersection and union, between simple solids shapes (e.g.
+cube, cylinder, sphere etc) to model complex surfaces which represent a solid.
+Boolean operations and solids can be combined to form a CSG-tree to model complex geometry.
+FLUKA uses CSG to
+model solids, the form of boolean expression used by FLUKA is not a general CSG-tree but a logical expression in disjunctive normal-form.
 
-\subsection{Boundary representation (BREP)}
-Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current RT applications use native 
-file formats employed by CAD systems. The conversion of CAD BREP formats for loading in RT applications is typically performed via a tessellated format, although it 
-is possible to decompose BREP descriptions to simple half-spaces and solids as used in CSG descriptions.
+%%%%%%%%%%%%%%%%% Boundary representation (BREP)
+Boundary representation (BREP) consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current RTMC 
+applications use native file formats employed by CAD systems. The conversion of CAD BREP formats for loading in RTMC applications is typically performed 
+via a tessellated format, although it is possible to decompose BREP descriptions to simple half-spaces and solids as used in CSG descriptions.
 
-\subsection{Tessellated polygons}
-Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and more 
-modern variants being PLY, OBJ, etc. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh deviation distance from the 
-solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC.
+%%%%%%%%%%%%%%%%% Tessellated polygons
+Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
+more modern variants being PLY, OBJ, etc. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
+deviation distance from the solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC.
 
-\subsection{Geant4 geometery}
+%%%%%%%%%%%%%%%%% Geant4 geometery
 Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes XX fundamental solids, although it does not store a sense 
@@
 Geant4 also provides the ability to perform boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
-Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\it Logical Volumes} 
-and {\it Physical Volumes}. A Logical Volume is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field and zero or 
-more physical {\it daughter} volumes. A Physical Volume is a placement (or instance) of a Logical Volume.
+Geant4.
+Not only do solid objects need to be defined but also placed in a world coordinate system.
+Geant4 has two concepts which facilitate this {\it Logical Volumes} and {\it Physical Volumes}.
+A Logical Volume is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field
+and zero or more physical {\it daughter} volumes. A Physical Volume is a placement (or instance) of a Logical Volume.
 
-\subsection{Geant Detector Mark-up Language} 
-To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed \colorbox{yellow}{[CITE]}. GDML is an XML based description of 
-Geant4 geometry description. Geant4 and ROOT can read and write GDML format and it is commonly used as an exchange format for Geant4 geometries.
+%%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
+To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed \cite{GDML}. GDML is an XML based description of 
+Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write GDML format and it is commonly used as an exchange format for Geant4 geometries.
 
@@
 
-\begin{figure*}[hbt]
-  \normalsize
-  \centering
-  \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Pyg4ometry geometry conversion workflow.}
-\end{figure*}
+\subsection{Input and output} 
+For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
+and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a registry which can be used or manipulated by the user. 
+Output consists of taking the registry and writing the appropriate GDML.
 
@@
 In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
-In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR. GDML allows for the definition and assignment of 
-variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc. 
-The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally all classes use GDML expressions and not floating point numbers. 
-Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of solid parameters and placements. This allows a user to update variables whilst
-defining geometry and the expression engine will update all internal values.
+In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. GDML allows for the definition 
+and assignment of variables.
+GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc.
+The AST terminates on either expressions which evaluate to numbers or GDML variables.
+Internally all classes use GDML
+expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of solid parameters and 
+placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values.
 
 \subsection{Replica, division, parametrised and looped volumes}
-A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The create multiple replicas of a volume in a cartesian, cylindrical or 
-spherical grid is known as a ReplicaVolume. Currently GDML loops are not supported by pyg4ometry and will be implemented in a future release.
+A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry.
+The create multiple replicas of a volume in a cartesian, cylindrical or spherical grid is known as a ReplicaVolume.
+Currently GDML loops are not supported by pyg4ometry and will be implemented in a future release.
 
@@
 
-\subsection{Input and output} 
-For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
-and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a registry which can be used or manipulated by the user. 
-Output consists of taking the registry and writing the appropriate GDML.
-
 \subsection{Tessellation of solids (meshing)}
-For each Geant4 primitive solid a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent of placed instances of 
-geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique. Triangular meshes based
-on CSG operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various algorithms from 
-TetGEN can be employed to give the meshes more desirable features.
+For each Geant4 primitive solid a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent of placed 
+instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in Python 
+\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} . Triangular meshes based on CSG 
+operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various polygon mesh 
+algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
 
 \subsection{Volume bounding} 
-If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully encompasses the 
-daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume shape that efficiently holds all of its daughters.
+If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
+encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume 
+shape that efficiently holds all of its daughters.
 
@@
 \begin{center}
-\includegraphics[width=7cm]{./diagrams/rapidModelling.pdf}
+\includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
 \caption{VTK visualisation output from code listing \ref{lst:pythonRapidModelling}.}

### 2020-08-30 public/paper/diagrams/rapidModelling.py

@@ -35,10 +35,12 @@ reg.setWorld(wl.name)
 
 # physical volume vistualisation attributes
 bp1.visOptions.color = (1,0,0)
-bp1.visOptions.alpha = 0.25
+bp1.visOptions.alpha = 1.0
 bp2.visOptions.color = (0,1,0)
-bp2.visOptions.representation = "wireframe"
+bp2.visOptions.alpha = 1.0
+# bp2.visOptions.representation = "wireframe"
 bp3.visOptions.color = (0,0,1)
+bp3.visOptions.alpha = 1.0
 
 # gdml output
 w = gd.Writer()

### 2020-08-30 public/paper/model-scene/model.py

@@ -15,17 +15,16 @@ def buildModel(vis = True, write = True, render = True) :
     gunChamber_logical  = reader_gunChamber.getRegistry().getWorldVolume()
     gunChamber_logical.name = "gunChamber_lv"
     print("gun chamber ",gunChamber_logical.name)
-    gunChamber_assembly = gunChamber_logical.assemblyVolume()
-    gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
-                                                           [0,0,0],
-                                                           gunChamber_assembly,
-                                                           "gunChamber_physical",
-                                                           world_logical,
-                                                           reg,
-                                                           addRegistry=False)
-    print("gun chamber",gunChamber_logical.extent(includeBoundingSolid=False))
-
-    reg.addVolumeRecursive(gunChamber_physical)
+    # gunChamber_assembly = gunChamber_logical.assemblyVolume()
+    # gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
+    #                                                        [0,0,0],
+    #                                                        gunChamber_assembly,
+    #                                                        "gunChamber_physical",
+    #                                                        world_logical,
+    #                                                        reg,
+    #                                                        addRegistry=False)
+    # print("gun chamber",gunChamber_logical.extent(includeBoundingSolid=False))
+    # reg.addVolumeRecursive(gunChamber_physical)
 
     # load gate
     reader_gateValve  = pyg4ometry.stl.Reader("./GV-100CF-C-M.stl")
@@ -101,20 +100,23 @@ def buildModel(vis = True, write = True, render = True) :
     faraday_logical.name = "faraday_lv"
     print("faraday ",faraday_logical.name)
     faraday_assembly = faraday_logical.assemblyVolume()
+    faraday_assembly.name = "faraday_av"
 
     faraday_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
-                                                       [0,0,900+2*38.9001+2450.000018+437.37*2+100],
-                                                       faraday_assembly,
-                                                       "faraday_physical",
-                                                       world_logical,
-                                                       reg,
-                                                       addRegistry=False)
+                                                      [0,0,900+2*38.9001+2450.000018+437.37*2+100],
+                                                      faraday_assembly,
+                                                      "faraday_physical",
+                                                      world_logical,
+                                                      reg,
[…]

### 2020-08-30 public/paper/pyg4ometry.tex
Paper update

@@
 geometry, including constructive solid geometry, boundary representation and tessellated polygons, these are described briefly in the following sections.  
-The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail.
+The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
 
 %%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
-Constructive solid geometry uses boolean operations, subtraction, intersection and union, between simple solids shapes (e.g.
-cube, cylinder, sphere etc) to model complex surfaces which represent a solid.
-Boolean operations and solids can be combined to form a CSG-tree to model complex geometry.
-FLUKA uses CSG to
-model solids, the form of boolean expression used by FLUKA is not a general CSG-tree but a logical expression in disjunctive normal-form.
+Constructive solid geometry uses boolean operations, subtraction, intersection and union, between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
+volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
+CSG-tree to model complex geometry. FLUKA uses CSG to model solids, the form of boolean expression used by FLUKA is not a general CSG-tree but a 
+logical expression in disjunctive normal-form.
 
 %%%%%%%%%%%%%%%%% Boundary representation (BREP)
-Boundary representation (BREP) consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current RTMC 
-applications use native file formats employed by CAD systems. The conversion of CAD BREP formats for loading in RTMC applications is typically performed 
-via a tessellated format, although it is possible to decompose BREP descriptions to simple half-spaces and solids as used in CSG descriptions.
+Boundary representation (BREP) consists of two parts, topology and geometry. Topological elements are faces, edges and vertices and the corresponding
+geometrical elements are surfaces, curves and points. No current RTMC applications use native file formats employed by CAD systems. The conversion of CAD BREP 
+formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions to bounded or 
+infinite mathematical surfaces and subsequently solids as used in CSG descriptions.
 
@@
 
-\subsection{Input and output} 
+%%%%%%%%%%%%%%%%%  Input and output  
 For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
@@
 
-\subsection{Expression evaluation}
+%%%%%%%%%%%%%%%%%  Expression evaluation
 In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
@@
 
-\subsection{Replica, division, parametrised and looped volumes}
+%%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
 A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry.
 The create multiple replicas of a volume in a cartesian, cylindrical or spherical grid is known as a ReplicaVolume.
-Currently GDML loops are not supported by pyg4ometry and will be implemented in a future release.
+A DivisionVolume breaks a primitive into segments in either a cartesian or cylindrical polar coordinates.
+A Parametrised Volume allows for the arbitrary multiple placement of solids where the parameters are allowed to vary for each placement.  GDML supports loops, 
+where sections of GDML are allowed to be repeated with varying parameters. GDML loops are not supported by pyg4ometry and will be implemented in a 
+future release.
 
-\subsection{Internal data representation} 
+%%%%%%%%%%%%%%%%%  Internal data representation
 The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
@@
 
-\subsection{Volume bounding} 
+%%%%%%%%%%%%%%%%% Volume bounding
 If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
@@
 
-\subsection{Adding properties to volumes}
+%%%%%%%%%%%%%%%%% Adding properties to volumes
 A pure geometry description is an insufficient description for a RT simulation. Often other attributes need to be assigned for example material definition, magnetic field or  
@@
 All RT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
-through such a situation.  A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing a CSG intersection between solid instances 
-and determining if the resulting mesh is empty. Generally the overlap detection algorithm proceeds as
-
-{\small 
-\begin{verbatim}
-Overlap detection
-\end{verbatim}
-}
-
-For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm 
-has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential 
-waste if small overlaps are present in the final RT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical 
-volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are 
-considered. 
+through such a situation.
+A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing an intersection operation etween solid instances and determining if the resulting mesh is empty.
+Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b) and intersection with finite volume and c) an overlap where two daughters share a face.
 \begin{figure}[htbp]
@@
 \includegraphics[width=8cm]{./diagrams/overlap.pdf}
-\caption{Placement of physical volume inside a logical volume}
+\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
 \label{fig:overlap}
@@
 
-\subsection{Graphical user interface}
-A basic Qt based graphical user interface is also available with pyg4ometry.
-If a model has a large number of volumes defined in a hierarchical tree structure, it is cumbersome for the user to find the logical or physical volume.
+Overlap detection in pyg4ometry relies of the meshes generated for each solid, any detection algorithm will be approximate. Generally the overlap detection 
+algorithm proceeds as 
+\begin{enumerate}
+\item Check if any of the daughter solid meshes have a non-null intersection with the compliment of mother solid mesh
+\item Loop over all daughter volumes and check
+\item Check
+\end{enumerate}
+
+For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm 
+has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential 
+waste if small overlaps are present in the final RTMC simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical 
+volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are 
+considered.
+
+%%%%%%%%%%%%%%%%% Graphical user interface
+% A basic Qt based graphical user interface is also available with pyg4ometry.
+If a model has a large number of volumes defined in a hierarchical tree structure, it is % cumbersome for the user to find the logical or physical volume.
 
@@
 \subsection{Infinite bodies}
-
 The majority of bodies in FLUKA are infinite in extent, and fall
@@
 \subsection{Removing redundant half-spaces}
-
 The above algorithm for replacing infinite FLUKA bodies with finite
@@
 \subsection{Coplanar faces}
-
 Coplanar faces, in which the faces of two union components or that of

### 2020-08-31 public/paper/pyg4ometry.tex
Paper update

@@
 \usepackage{listings}
+\usepackage[ruled,vlined]{algorithm2e}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-Geant; Monte Carlo; Particle; Transport; Geometry;
+Geant; Fluka; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;
 
@@
 \section{Pyg4ometry design and layout}
+Pyg4ometry is a python package consisting of semi-independent modules. The module \verb|pyg4ometry.geant4| contains all classes for geant4 detector 
+construction, \verb|pyg4ometry.gdml| for GDML reading and writing. Modules for importing and exporting other geometry formats  \verb|pyg4ometry.fluka|, 
+\verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad|.
+
 The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
-The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that {\it pyg4ometry} users do not have to learn 
-a new API. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in {\it pyg4ometry} are described.
+The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that pyg4ometry users do not have to learn 
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \verb|geant4.solid.Box| class in 
+Python. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
+should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in pyg4ometry are described.
 
@@
 For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
-and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a registry which can be used or manipulated by the user. 
+and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user. 
 Output consists of taking the registry and writing the appropriate GDML.
+
+%%%%%%%%%%%%%%%%%  Internal data representation
+The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
+elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
+\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 
@@
 expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of solid parameters and 
-placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values.
+placements.
+This allows a user to update variables whilst defining geometry and the expression engine will update all internal values.
+An example of GDML expressions is shown in listing~\ref{lst:gdmlExpressions}.
+
+\begin{lstlisting}[caption={A simple python script using pyg4ometry to create a simple Geant4 geometry.},label={lst:gdmlExpressions}, language=Python]
+# Import modules 
+import pyg4ometry
+
+# Create empty data storage structure
+reg = pyg4ometry.geant4.Registry()
+
+# Expressions 
+v1 = pyg4ometry.gdml.Constant("v1","0",reg)
+v2 = pyg4ometry.gdml.Constant("v2","sin(v1+pi)",reg)
+
+\end{lstlisting}
 
@@
 future release.
-
-%%%%%%%%%%%%%%%%%  Internal data representation
-The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
-elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
-\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 
@@
 \subsection{Overlap detection}
-All RT transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+All RTM Ctransport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
 through such a situation.
@@
 \end{figure}
+
+%\begin{algorithm}[h]
+%\SetAlgoLined
+%\KwResult{Write here the result }
+% initialization\;
+% \While{While condition}{
+%  instructions\;
+%  \eIf{condition}{
+%   instructions1\;
+%   instructions2\;
+%   }{
+%   instructions3\;
+%  }
+% }
+% \caption{How to write algorithms}
+%\end{algorithm}
 
@@
 \section{GDML to FLUKA conversion}
-It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA CSG region.
+It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA \verb|REGION|
 Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
@@
 S_{\rm region} =  S_{\rm logical} - S_{\rm daughter,1} - S_{\rm daughter,2} - S_{\rm daughter,3} \ldots 
-\label{eqn:logical}
+\label{eqn:logicalSubtraction}
 \end{equation} 
@@
 \subsection{Non-Convex solid decomposition}
-In general the CSG description used by geant4 allow non-convex solids, these include Polyhedron, Xtru, TwistedBox, 
-TwistedTrap, TwistedTrd and TwistedTube. These particular solids are problematic when converting geometry to a Fluka 
-readable format, as non-convex solids can only be created by union of convex zones. These solids are converted to CGAL 
+In general the base solids used by Geant4 allow non-convex solids, eg Polycone, Xtru, the Twisted.  These particular solids are problematic when 
+converting geometry to a FLUKA readable format, as non-convex solids can only be created by union of convex zones. 
+There are two groups which need to considered, firstly those where 2D polygonal section needs to be decomposed these include Polycone, 
+Polyhedron and Xtru, secondly those where three dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
+TwistedTube and Tessellated. These solids are converted to CGAL 
 Nef polyhedra \colorbox{yellow}{XXX CITE} and decomposed to convex polyhedra using a \colorbox{yellow}{XXX} algorithm.
@@
 \subsection{Disjunctive normal form and degenerate surfaces}
+Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is characterised as the union of intersections, so 
+\begin{equation}
+R = z_1 \; | \;z_2\;  | \; z_3 | \; z_4 \dots
+\end{equation}
+Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone $z_i$ of $R$ can terminate if a point 
+is determined to be inside any of convex zones. In general Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical 
+volume placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of parentheses. There are some conditions 
+where a general boolean expression can yield an exponential explosion of the final DNF. There are well known algorithms to convert logical expressions to 
+DNF  \colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a sympy \colorbox{yellow}{XXX CITE} expression and 
+using its logical module. Before version 4.0 FLUKA would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
+FLUKA version 4 allows control of the NDF expansion.
 
 \subsection{Materials}
+Pyg4ometry converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
 
@@
 \begin{itemize}
-\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
-\item Non-convex 2D section (GenericPolycone, GenericPolyhedra)
-\item Scaled solid 
-\item Placement scale 
+\item Degenerate body look up 
+\item Bodes with/without transformation 
+\item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
+\item Scaled solid, Placement scale 
 \item Replica, Division, Parameterised
-\item Materials 
+\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \label{eqn:logicalSubtraction} speed up using meshes
 \end{itemize}

### 2020-08-31 public/paper/pyg4ometry.tex
Paper update

@@
 %% keywords here, in the form: keyword \sep keyword
-Geant; Fluka; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;
+Geant; FLUKA; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item disjoint subtractions?
@@
 \item Materials 
-\end{itemize}
+\end{enumerate}
 
@@
 using its logical module. Before version 4.0 FLUKA would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
-FLUKA version 4 allows control of the NDF expansion.
+FLUKA version 4 allows control of the DNF expansion.
 
@@
 \subsection{Disucssion}
-There are still a few outstanding issues with Geant4/GDML to Fluka conversion.
+There are still a few outstanding issues with Geant4/GDML to FLUKA conversion.
 
-\begin{itemize}
+\begin{enumerate}
 \item Degenerate body look up 
@@
 \item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \label{eqn:logicalSubtraction} speed up using meshes
-\end{itemize}
+\end{enumerate}
 
@@
 
+\begin{enumerate}
+\item Merging Registries 
+\item Removing volumes 
+\item Editing solid
+\item Converting to assembly solids 
+\end{enumerate}
+
 \begin{figure*}[htbp]
@@
 \item Integration of other tools (DAGMC) 
-\item Far from perfect conversions. 
+\item Far from perfect conversions
 \end{enumerate}

### 2020-08-31 public/paper/pyg4ometry.tex
Paper update

@@
 particle transport code users to rapidly develop geometry files, convert between common RT programme geometry formats and finally import CAD models. 
+\colorbox{yellow}{More explanation of Geant4 and FLUKA}
 
@@
 
-\begin{figure*}[hbt]
+\begin{figure*}[hbt!]
   \normalsize
@@
 A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
-to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}$, scale $\mathbf{S}$ and 
-translation $\mathbf{T}$.
+to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
 
-\begin{figure}[htbp]
+\begin{figure}[htb!]
 \begin{center}
@@
 
+The transformation  $\mathbf{M}$  and translation $\mathbf{T}$ from mother to daugher is 
 \begin{eqnarray}
-\mathbf{M}	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d\\
-\mathbf{T}	 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m,
+\mathbf{M} 	& = &  \mathbf{S}_d  \mathbf{R}_d \\
+\mathbf{T} 	& = &  \mathbf{T}_d
 \end{eqnarray}
-where the subscript $p$ indicates parent volume and $d$ indicates daughter volume.
 
-The python version of Geant4's physical volume is also used to store visualisation attributes like the solids 
-color, surface or wireframe representation and visibility. Overlaps detected in the discretised mesh geometry can be displayed separately to allow a user to remove
-the potential overlaps. This is dependent on the accuracy of the mesh generated and is a particular problem with meshes based on curved surfaces.
+If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ 
+\begin{eqnarray}
+\mathbf{M}_w	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d				\label{eqn:worldToDaughter1}\\
+\mathbf{T}	_w 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m  \label{eqn:worldToDaughter2}
+\end{eqnarray}
+where the subscript $p$ indicates parent volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
+Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively depending on the number of nested volumes.
+
+The python version of Geant4 physical volume is also used to store visualisation attributes like the solid's 
+colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
+stored in the Logical Volume and can be  displayed separately to allow a user to understand the reason for 
+the overlaps.
 
 %%%%%%%%%%%%%%%%% Adding properties to volumes
-A pure geometry description is an insufficient description for a RT simulation. Often other attributes need to be assigned for example material definition, magnetic field or  
-optical surface properties.
+Geometry alone is an insufficient information for a RTMC simulation.
+Often other attributes need to be assigned to regions of space for example material definition, magnetic field or optical properties.
+These physical properties can be used to define the visualisation attributes of a volume.
 
 \subsection{Overlap detection}
-All RTM Ctransport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+All RTMC transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
 through such a situation.
@@
 
-Overlap detection in pyg4ometry relies of the meshes generated for each solid, any detection algorithm will be approximate. Generally the overlap detection 
+Overlap detection in pyg4ometry relies of the meshes generated for each solid, 
+any detection algorithm will be approximate. Generally the overlap detection 
 algorithm proceeds as 
@@
 
+The accuracy of the overlap visualisation is dependent on the accuracy of the meshes generated, for example problems might occur 
+with meshes based on curved surfaces.
+
 %%%%%%%%%%%%%%%%% Graphical user interface
@@
 the parameters of the geometry and visualise the geometry. Finally when the desired result without geometry overlaps is finalised a GDML file can be output
-from the internal memory representation.
+from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
+users of Geant4, first a \verb|Registry| need to be created to store all the pyg4ometry objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
 
@@
 
-An example of the VTK output for code listing \ref{lst:pythonRapidModelling} is shown in Figure~\ref{fig:rapidModellingExample}.
+An example of the VTK output for code listing \ref{lst:pythonRapidModelling} is shown in 
+Figure~\ref{fig:rapidModellingExample}.
 \begin{figure}[htbp]
@@
 \end{figure}
-Significantly more complex geometries can be developed using a structure similar to that shown in code 
-listing \ref{lst:pythonRapidModelling}.
+Significantly more complex geometries can be developed using a structure similar to 
+that shown in code listing \ref{lst:pythonRapidModelling}.
+
+The pyg4ometry python code in the example is approximately as expressive 
+as the GDML it writes. The benefit of wrapping GDML/Geant4 in Python allows 
+to very rapid prototyping of geometry without concerns of compilation of C++ (in the 
+case of Geant4) or writing well formed XML (in the case of GDML). Effectively
+the Python interpreter checks input for syntax errors when using pyg4ometry classes. 
+Another key benefit is the ability to use the pyg4ometry code to create 
+programatic converters between different geometry languages.
 
@@
 \section{GDML to FLUKA conversion}
-It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 solids can be mapped to a FLUKA \verb|REGION|
-Some solids in Geant4 directly map to a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
+It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
+solids can be mapped to a FLUKA \verb|REGION|. Some solids in Geant4 directly map to 
+a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
 lists the mapping between geant4 solids and the bodies used to compose a fluka region.
@@
 R_1 - R_2 	& = & (+z_1 | +z_2) - ( +z_3 | +z_4) 			\\
-			& = & (+z_1 - z_3 - z_4)  | (+z_2 - z_3 - z_4)	
+			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)	
 \label{eqn:setDiff}
 \end{eqnarray}
-Geant4 has the boolean solids associated with difference, union and intersection, so in addition to Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and 
-$R_1 \cap R_2$ is required in fluka notation, so 
+Geant4 has the boolean solids associated with difference, union and intersection, so in addition to 
+Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in fluka notation, so 
 \begin{eqnarray}
@@
 R_1 \cap R_2 	& = & (+z_1 | +z_2) \cap ( +z_3 | +z_4) \\
-			& = & +z_1 +z_3  | +z_1 +z_4 | +z_2 +z_3 | +z_2 +z_4
+			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4
 \label{eqn:setIntersection}
@@
 Fluka (apart from the {\it lattice} directive) has no sense of a volume hierarchy. Each body is placed with a 
-translation, rotation, expansion geometry directives in global coordinates. A transformation from world coordinates
-to a physical volume is built up by applying recursively daughter volume transformations and  this is used to place Fluka bodies. 
-This  in practice is very similar to the procedure to create the VTK visualisation already described in Section~\ref{sec:visualisation}.
+translation, rotation, expansion geometry directives in global coordinates. A transformation from world 
+coordinates to a physical volume is built up by applying recursively daughter volume transformations 
+and  this is used to place Fluka bodies. This  in practice is very similar to the procedure to create the 
+VTK visualisation already described in Section~\ref{sec:visualisation}.
 
-In Fluka every single space point needs to be associated with one and only one region. There is problem when converting
-geant4 logical Volumes to fluka regions, as the logical volume outer solid $S_{\rm logical}$ need to have the daughter 
-solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted to a region $S_{\rm region}$ is then 
+In Fluka every single space point needs to be associated with one and only one region. There is problem 
+when converting geant4 logical Volumes to fluka regions, as the logical volume outer solid $S_{\rm logical}$ 
+need to have the daughter  solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted 
+to a region $S_{\rm region}$ is then 
 \begin{equation}
@@
 \subsection{Non-Convex solid decomposition}
-In general the base solids used by Geant4 allow non-convex solids, eg Polycone, Xtru, the Twisted.  These particular solids are problematic when 
-converting geometry to a FLUKA readable format, as non-convex solids can only be created by union of convex zones. 
-There are two groups which need to considered, firstly those where 2D polygonal section needs to be decomposed these include Polycone, 
-Polyhedron and Xtru, secondly those where three dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
-TwistedTube and Tessellated. These solids are converted to CGAL 
-Nef polyhedra \colorbox{yellow}{XXX CITE} and decomposed to convex polyhedra using a \colorbox{yellow}{XXX} algorithm.
+In general the base solids used by Geant4 allow non-convex solids, eg Polycone, Xtru, the Twisted.  These 
+particular solids are problematic when converting geometry to a FLUKA readable format, as non-convex solids 
+can only be created by union of convex zones. There are two groups which need to considered, firstly those 
+where 2D polygonal section needs to be decomposed these include Polycone, Polyhedron and Xtru, secondly 
+those where three dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
+TwistedTube and Tessellated. The second classification of non convex solids are converted to CGAL 
+Nef polyhedra \colorbox{yellow}{XXX CITE} and decomposed to convex polyhedra using a 
+\colorbox{yellow}{XXX} algorithm.
 
 \subsection{Disjunctive normal form and degenerate surfaces}
-Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is characterised as the union of intersections, so 
+Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is 
+characterised as the union of intersections, so 
 \begin{equation}
-R = z_1 \; | \;z_2\;  | \; z_3 | \; z_4 \dots
+R = z_1 \; | \;z_2\;  | \; z_3 	\; | \; z_4 \dots
 \end{equation}
-Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone $z_i$ of $R$ can terminate if a point 
-is determined to be inside any of convex zones. In general Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical 
-volume placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of parentheses. There are some conditions 
-where a general boolean expression can yield an exponential explosion of the final DNF. There are well known algorithms to convert logical expressions to 
-DNF  \colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a sympy \colorbox{yellow}{XXX CITE} expression and 
-using its logical module. Before version 4.0 FLUKA would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
+Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone 
+$z_i$ of $R$ can terminate if a point is determined to be inside any of convex zones. In general 
+Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical volume 
+placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of 
+parentheses. There are some conditions where a general boolean expression can yield an exponential 
+explosion of the final DNF. There are well known algorithms to convert logical expressions to DNF 
+\colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a 
+sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module. Before version 4.0 FLUKA 
+would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
 FLUKA version 4 allows control of the DNF expansion.
@@
 \item Replica, Division, Parameterised
-\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \label{eqn:logicalSubtraction} speed up using meshes
+\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \ref{eqn:logicalSubtraction} speed up using meshes
 \end{enumerate}
@@
 \section{CAD/STL to GDML conversion }
-STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an open source CAD/CAM program, which in turn 
-is based on OpenCASCADE. A STEP CAD file could be considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
-collection of part features. A part feature can be used to create  a triangular mesh which can used to create a pyg4ometry tessellated solid. Assignment of materials 
-and visualisation attributes must be performed by the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
+STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an 
+open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
+considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
+collection of part features. A part feature can be used to create  a triangular mesh which can used to create 
+a pyg4ometry tessellated solid. Assignment of materials and visualisation attributes must be performed by 
+the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
 for RT codes.
-
 \begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[htb!]
 \begin{center}
@@
 \section{Complete simulation example}
-Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles and workflows. The following sections describe a selection of 
+Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles 
+and workflows. The following sections describe a selection of 
 possible applications.
-
+%
 \begin{enumerate}
@@
 \end{enumerate}
-
-\begin{figure*}[htbp]
+%
+\begin{figure*}[htb!]
 \begin{center}
@@
 \section{Conclusions}
-The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in particle transport Monte Carlo programmes will save significant 
-amounts of user effort and ultimately yield more accurate simulations. Pyg4ometry is a relatively complete implementation of a geometry creation tool, whilst heavily 
-internally based on Geant4 and GDML can have utility for users of all RT codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications,
-examples include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble  dark matter detectors and geometries for event visualisation. 
-Although not implemented in the current version, a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 application.
+The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in 
+particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
+yield more accurate simulations. Pyg4ometry is a relatively complete implementation of a geometry 
+creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
+codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications, examples 
+include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 
+matter detectors and geometries for event visualisation. Although not implemented in the current version, 
+a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 
+application.
 
@@
 \item Far from perfect conversions
+\item Export mesh for other applications (GPU optics)
+\item Convergence FLUKA/Geant4 - Moira 
+\item Replace G4 polyhedron CSG
 \end{enumerate}

### 2020-09-01 public/paper/pyg4ometry.tex
Paper update

@@
 a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
-lists the mapping between geant4 solids and the bodies used to compose a fluka region.
-
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
-\caption{Example conversion of a simple GDML geometry to FLUKA, left panel :  
-the original model in pyg4ometry, right panel : the converted FLUKA geometry 
-viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
-\label{fig:flair-gdml}
-\end{center}
-\end{figure*}
+lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
 
@@
 
+Figure~\ref{fig:flair-gdml} shows an example conversion from GDML to FLUKA. The example is a 
+vacuum chamber with three CF beam pipes connected to CF flanges. The top and bottom plates 
+have been removed to better see the geometry. The model is formed of \verb|G4Box| and
+\verb|G4Tubs| and boolean operations of subtraction, intersection and union.
+\begin{figure*}[htb!]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
+\caption{Example conversion of a simple GDML geometry to FLUKA, left panel :  
+the original model in pyg4ometry, right panel : the converted FLUKA geometry 
+viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
+\label{fig:flair-gdml}
+\end{center}
+\end{figure*}
+
 \subsection{Non-Convex solid decomposition}
@@
 \colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a 
-sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module. Before version 4.0 FLUKA 
-would simplify all regions to DNF and some converted geometry would generate too many zones and would fail.
-FLUKA version 4 allows control of the DNF expansion.
+sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module \verb|to_ndf| method based on 
+the Quine–McCluskey algorithm \cite{6769983}. Before version 4.0 FLUKA  would simplify all regions to 
+DNF and some converted geometry would generate too many zones and would fail. FLUKA version 4 
+allows control of the DNF expansion.
 

### 2020-09-01 public/paper/model-scene/model.py
Remove air from FLUKA conversion

@@ -15,16 +15,16 @@ def buildModel(vis = True, write = True, render = True) :
     gunChamber_logical  = reader_gunChamber.getRegistry().getWorldVolume()
     gunChamber_logical.name = "gunChamber_lv"
     print("gun chamber ",gunChamber_logical.name)
-    # gunChamber_assembly = gunChamber_logical.assemblyVolume()
-    # gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
-    #                                                        [0,0,0],
-    #                                                        gunChamber_assembly,
-    #                                                        "gunChamber_physical",
-    #                                                        world_logical,
-    #                                                        reg,
-    #                                                        addRegistry=False)
-    # print("gun chamber",gunChamber_logical.extent(includeBoundingSolid=False))
-    # reg.addVolumeRecursive(gunChamber_physical)
+    gunChamber_assembly = gunChamber_logical.assemblyVolume()
+    gunChamber_physical = pyg4ometry.geant4.PhysicalVolume([0,0,0],
+                                                           [0,0,0],
+                                                           gunChamber_assembly,
+                                                           "gunChamber_physical",
+                                                           world_logical,
+                                                           reg,
+                                                           addRegistry=False)
+    print("gun chamber",gunChamber_logical.extent(includeBoundingSolid=False))
+    reg.addVolumeRecursive(gunChamber_physical)
 
     # load gate
     reader_gateValve  = pyg4ometry.stl.Reader("./GV-100CF-C-M.stl")
@@ -98,6 +98,13 @@ def buildModel(vis = True, write = True, render = True) :
     faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
     faraday_logical = faraday_greg.getWorldVolume()
     faraday_logical.name = "faraday_lv"
+
+    for d in faraday_logical.daughterVolumes :
+        if d.name == "air_pv" :
+            faraday_logical.daughterVolumes.remove(d)
+
+    extentBB = faraday_logical.extent(includeBoundingSolid=False)
+
     print("faraday ",faraday_logical.name)
     faraday_assembly = faraday_logical.assemblyVolume()
     faraday_assembly.name = "faraday_av"
@@ -167,6 +174,10 @@ def buildFaradayCup(vis = True,inter = True) :
[…]

### 2020-09-01 public/paper/pyg4ometry.tex
latex command for fluka commands (LATTICE COMPOUND etc...)
LATTICE section

@@
 }
+
+ % For fluka commands such as LATTICE etc.
+\newcommand{\fluka}[1]{\texttt{\MakeUppercase{#1}}}
 
@@
 \subsection{Lattice}
-Description of how we \colorbox{yellow}{translate lattices} 
-into one LV with multiple PVs.
+
+FLUKA supports modular geometries with the use of the \fluka{lattice}
+command. Figure~\ref{fig:lattice} demonstrates this capability, and. The
+arbitrarily complex \textit{basic unit} can be defined once and used
+multiple times by placing one or more empty \textit{lattice cells} with the
+associated rototranslation from that \fluka{lattice} cell to the basic
+unit. The \fluka{lattice} cells themselves will generally lack structure
+and simply serve as a reference to the basic unit. The rototranslated
+lattice cell must fully contain the basic unit and all of the regions
+within it. When a particle steps into the \fluka{lattice} cell, the
+rototranslation is applied to that particle and it is is taken into the
+basic unit, and the simulation continues within the basic unit. Any
+particles leaving the basic unit will be translated back to the
+\fluka{lattice} cell with the inverted rototranslation. Up to two
+levels of \fluka{lattice} nesting the are supported in FLUKA.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=6cm]{./diagrams/lattice}
+\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
+  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
+  Any particle entering the cell will be transformed onto the basic unit
+  with $R\textrm{trans}$, and when leaving the basic unit, back to the cell
+  with $R_\textrm{trans}^{-1}$.}
+\label{fig:lattice}
+\end{center}
+\end{figure}
+
+This feature is clearly analogous to the logical/physical volume feature in
+Geant4, although it is less explicit as the contents of a given logical
+volume are clearly stated, whereas the contents of a \fluka{lattice} cell
+are implied by the combination of the rototranslation and the locations of
+its \fluka{lattice} cell and basic unit.
+
+Translating this construct into a logical volume (basic unit) with many
+physical volumes (\fluka{lattice} cells) requires associating each
+\fluka{lattice} cell with the full contents of its corresponding basic unit
+(typically several regions). This is achieved by meshing the complete
+FLUKA geometry and then rototranslating the \fluka{lattice} cell mesh with
+its associated rototranslation. By construction this will translate the
+\fluka{lattice} cell mesh directly onto the full basic unit mesh. Finally,
+in checking for overlaps, the regions within the the basic unit can be
+determined. In the final conversion step, the \fluka{lattice} cell can
+simply be replaced with a physical volume that refers back to logical
+volumes located in the previous step. Thus the \fluka{lattice} cells can
+be translated into Geant4's logical/physical volumes. As has been stated,
+FLUKA supports two levels of nesting, but currently the conversion to GDML
+supports only one. However, extending to an extra level is simple in that
+it only involves an extra application of a rototranslation matrix before
+checking for overlaps.
 

### 2020-09-01 public/paper/pyg4ometry.tex
fluka paper bits

@@
 The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
-producing an abstract syntax tree (AST).  The resulting AST is then
-walked to populate Region instances with zones and bodies.  An example
-FLUKA region with the corresponding abstract syntax tree is shown in
-Figure~\ref{fig:region-ast}.
+producing an abstract syntax tree (AST).  The resulting AST is then walked
+to populate Region instances with zones and bodies.  With the region
+instances populated they can then be manipulated and translated into GDML.
+The translation involves a number of special steps to bridge the two
+disparate formats and ensure the resulting GDML is well-formed ans usable
+in Geant4.  Some of these steps are simple, for example in FLUKA unions can
+be disconnected, but in Geant4 specifically only MultiUnions can be
+disconnected, such that MultiUnions are used throughout the converted
+geometry instead of the usual binary unions.  Other procedures are more
+involved and are discussed in the rest of this section.
+
 \begin{figure*}[htbp]
@@
   Any particle entering the cell will be transformed onto the basic unit
-  with $R\textrm{trans}$, and when leaving the basic unit, back to the cell
+  with $R_\textrm{trans}$, and when leaving the basic unit, back to the cell
   with $R_\textrm{trans}^{-1}$.}

### 2020-09-01 public/paper/pyg4ometry.tex
more fluka2gdml paper bits

@@
 \section{FLUKA to GDML conversion}
-FLUKA geometry is based upon a limited set of primitives (referred to
-as \textit{bodies} which can be combined using Boolean operations.  A
-\textit{zone} consists of one or more bodies or \textit{subzones}
-combined using intersections and subtractions.  Zones may then be
-further combined using union operations to form \textit{regions},
-which is defined as the union of one or more zones, as well as a
-material.
+FLUKA geometry is based upon a limited set of primitives (referred to as
+\textit{bodies}) which can be combined using Boolean operations. A
+\textit{zone} consists of one or more bodies or \textit{subzones} combined
+using intersections and subtractions.  Zones may then be further combined
+using union operations to form \textit{regions}, which is defined as the
+union of one or more zones, as well as a material.
 
@@
 The translation involves a number of special steps to bridge the two
-disparate formats and ensure the resulting GDML is well-formed ans usable
+disparate formats and ensure the resulting GDML is well-formed and usable
 in Geant4.  Some of these steps are simple, for example in FLUKA unions can
@@
 and measure accelerator beam charge.}
-\label{fig:region-ast}
+\label{fig:fluka-to-geant4-cup}
 \end{center}
@@
 \subsection{Discussion}
-A disjoint union in FLUKA is a union of two or more zones that are not
-connected.  This is a valid construct in FLUKA but is explicitly
-forbidden in Geant4 and must be removed during the conversion
-process.  Disjoint unions are detected by checking for overlaps
-between all zones within a union.
-
-\begin{enumerate}
-\item disjoint subtractions?
-\item quadric specialisation
-\item second order lattice
-\item Materials 
-\end{enumerate}
+
+Figure~\ref{fig:fluka-to-geant4-cup} shows a Faraday cup implemented in
+FLUKA and translated to GDML using pyg4ometry.  The conversion is clearly
+accurate well and also includes the translation of the materials to GDML.
+Many of the steps described above were directly applied in this model and
+all the features are tested and demonstrated in the repository.  This set
+of algorithms for bridging FLUKA with GDML covers a very broad range of
+geometries, however a number of possible improvements for the future
+persist.  For example, Boolean solids in FLUKA can in general be
+disconnected, and this most typically manifests itself in the form of
+disconnected unions, but is also allowed for intersections and
+subtractions.  Disconnected unions are readily availabe in GDML with the
+use of the MultiUnion solid type, however there is no valid means to
+construct a disconnected subtraction or intersection in GDML.  One possible
+solution would be to detect these two cases, and if found, split them into
+their constituent parts and place separately as TesselatedSolid instances.
+
+Furthermore, the quadric surface conversion can be further improved by
+specialising on some of the individual forms of the quadric.  Simply
+converting every quadric into a TesselatedSolid comes at a potential
+performance cost in the tracking, as well as usability in pyg4ometry as the
+user must provide an AABB.  In some cases tesselation in unavoidable (for
+example a hyperbolic parabaloid), but parabolic cylinders could for example
+be translated to an ExtrudedSolid.  This could provide both a performance
+improvement in the tracking time and make pyg4ometry easier to use as an
+AABB would not need to be provided beforehand.  This has not been
+implemented as quadrics are relatively rarely used, but where quadrics are
+used its often parabolic cylinders (e.g. magnet pole tips) this
+specicalisation in particular would be worth implementing.
 

### 2020-09-03 public/paper/pyg4ometry.tex
Paper update

@@
 %  frame=single,
+  breaklines=true,
+  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{grey}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\lstset{
+  showstringspaces=false,
+  basicstyle=\ttfamily,
+  columns=fullflexible,
+  % frame=single,
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  language=Python,
+  keywordstyle=\color{blue},
   breaklines=true,
@@
 
-\title{Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries}
+\title{PYG4OMETRY: a PYTHON library for the creation of Monte Carlo radiation transport physical geometries}
 
@@
 
-% \linenumbers
+\linenumbers
 
@@
 \noindent
-{\em Program Title: pyg4ometry }                                         		\\
+{\em Program Title: PYG4OMETRY }                                         		\\
 {\em Licensing provisions: GPLv3 }			\\
-{\em Programming language: python, C/C++}                         		\\
+{\em Programming language: PYTHON, C/C++}                         		\\
 
@@
 RT Monte Carlo (RTMC) simulations have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples.
-A fundamental requirement of all of the codes is to supply a computer readable description of the
+A fundamental requirement of all of the codes is to supply a computer-readable description of the
 physical geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity 
 and performance is directly dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared 
-for different codes will enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for RT 
-programs, usually computer assisted design (CAD) files exist for systems which need to be simulated in RT programmes. The fundamental geometric 
+for different codes will enable cross-checks of the physics processes in different particle transport codes. In addition to the creation of geometry files for RT 
+programs, usually computer assisted design (CAD) files exist for systems which need to be simulated. The fundamental geometric 
 representations in CAD files is typically not amenable for RT programmes.  For these reasons it is advantageous to create a software tool that allows 
-particle transport code users to rapidly develop geometry files, convert between common RT programme geometry formats and finally import CAD models. 
+particle transport code users to rapidly develop error free geometry files, convert between common RT programme geometry formats and finally import CAD models. 
 \colorbox{yellow}{More explanation of Geant4 and FLUKA}
 
-This paper describes a geometry creation and conversion package called {\em pyg4ometry}, implemented in {\em Python} and internally based on the Geant4 geometry GDML \cite{GDML}.
-The main features of  {\em pyg4ometry} are a python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
-The origin of pyg4ometry was a set of utilities to prepare geometry for an accelerator beam line simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
-Accelerator physicists like specialists in other areas need a tool to quickly simulate beam losses, and the subsequent interaction of the charged particle beam with the accelerator material.
-Figure~\ref{fig:workflow} depicts various workflows possible with {\em pyg4ometry}.
-{\em Pyg4ometry} is a not a software package but a toolkit library for creation and conversion of geometry, a user would typically write very small python programs to use the {\em pyg4ometry} toolbox.
-This paper describes version 1 of pyg4ometry, which is freely available as a git prepository and via pypi.
+This paper describes a geometry creation and conversion package called PYG4OMETRY, implemented in PYTHON and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+The main features of PYG4OMETRY are a PYTHON scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
+The origin of PYG4OMETRY was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
+Accelerator physicists, like specialists in other areas, need a tool to quickly simulate beam losses and the subsequent interaction of the charged particle beam with the accelerator material.
+Figure~\ref{fig:workflow} depicts various workflows possible with PYG4OMETRY.
+PYG4OMETRY is not an executable software package but a toolkit, a user would typically write very small PYTHON program to use the PYG4OMETRY.
+This paper describes version 1.0 of PYG4OMETRY, which is freely available as a git repository and via PyPi.
 
@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Pyg4ometry geometry conversion workflow.}
+  \caption{\label{fig:workflow}Schematic of PYG4OMETRY workflow, showing a) the different input file formats, b) PYTHON processing, c) output file targets and d) RTMC codes which use the geometry. }
 \end{figure*}
 
-There are existing codes that have functionality similar to pyg4ometry.
+There are existing codes that have functionality similar to PYG4OMETRY.
 Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
@@
 
-This paper is structured as follows, first a brief radiation transport-centric introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of {\it Pyg4ometry}.
-Thesections that follow describe how {\it pyg4ometry} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
+This paper is structured as follows, first a brief radiation transport-centric introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of PYG4OMETRY.
+The sections that follow describe how PYG4OMETRY can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
 The paper concludes with an example of composite complex system consisting components of all the possible geometry input files formats.
@@
 \section{Computer descriptions of geometry} \label{sec:geometric}
-Central to a computer readable geometry of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
-geometry, including constructive solid geometry, boundary representation and tessellated polygons, these are described briefly in the following sections.  
-The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
+Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
+geometry, including constructive solid geometry (CSG) , boundary representation (BREP) and tessellated polygons, these are described 
+briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
 
 %%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
-Constructive solid geometry uses boolean operations, subtraction, intersection and union, between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
+Constructive solid geometry uses Boolean operations, subtraction, intersection and union, between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
 volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
-CSG-tree to model complex geometry. FLUKA uses CSG to model solids, the form of boolean expression used by FLUKA is not a general CSG-tree but a 
-logical expression in disjunctive normal-form.
+CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
+logical expression in disjunctive normal form.
 
@@
 Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
-more modern variants being PLY, OBJ, etc. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
-deviation distance from the solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC.
+more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
+deviation distance from the solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC simulation.
 
@@
 of topology present in traditional CAD BREP systems. One of the fundamental solids is a {\em TessellatedSolid} which can used to represent STL or PLY files. 
-Geant4 also provides the ability to perform boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
+Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
 Geant4.
@@
 Geant4 has two concepts which facilitate this {\it Logical Volumes} and {\it Physical Volumes}.
-A Logical Volume is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field
+A {\it Logical Volume} is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field
 and zero or more physical {\it daughter} volumes. A Physical Volume is a placement (or instance) of a Logical Volume.
@@
 %%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
-To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed \cite{GDML}. GDML is an XML based description of 
-Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write GDML format and it is commonly used as an exchange format for Geant4 geometries.
-
-\section{Pyg4ometry design and layout}
-Pyg4ometry is a python package consisting of semi-independent modules. The module \verb|pyg4ometry.geant4| contains all classes for geant4 detector 
-construction, \verb|pyg4ometry.gdml| for GDML reading and writing. Modules for importing and exporting other geometry formats  \verb|pyg4ometry.fluka|, 
-\verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad|.
-
-The core of {\em pyg4ometry} consists of python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
-The constructors of the python classes are kept as close to the original Geant4 C++ implementation so that pyg4ometry users do not have to learn 
+To exchange geometry descriptions between software packages Geometry Descripition Mark-up Language (GDML) was developed \cite{GDML}. 
+GDML is an XML based description of Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write 
+GDML format and it is commonly used as an exchange format for Geant4 geometries.
+
+\section{PYG4OMETRY design and layout}
+PYG4OMETRY is a PYTHON package consisting of semi-independent sub-packages. The sub-package \verb|pyg4ometry.geant4| contains all classes for 
+geant4 detector construction, \verb|pyg4ometry.gdml| provides the functionality for reading and writing GDML files.
+There are sub-packages for importing and exporting other geometry formats  \verb|pyg4ometry.fluka|, \verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad| and converting between file formats \verb|pyg4ometry.convert|.
+
+The core of PYG4OMETRY consists of PYTHON classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
+The constructors of the PYTHON classes are kept as close to the original Geant4 C++ implementation so that PYG4OMETRY users do not have to learn 
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \verb|geant4.solid.Box| class in 
-Python. Geometry construction in python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in pyg4ometry immediately. In the following sections novel or important developments in pyg4ometry are described.
+PYTHON. Geometry construction in PYTHON proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
+should be able to start creating geometry in PYG4OMETRY immediately. In the following sections novel or important developments in PYG4OMETRY are described.
 
@@
 %\begin{tabular}{ l l l } \hline
-%GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
+%GDML tag 		& Child tags				& PYG4OMETRY class 				\\ \hline
 %Define 			& Constant				& gdml.Constant				\\
@@
 %\label{tab:gdml-tags}
-%\caption{GDML tags and corresponding pyg4ometry classes.}
+%\caption{GDML tags and corresponding PYG4OMETRY classes.}
 %\end{table}
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in pyg4ometry a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| 
-and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user. 
+For each input format available in PYG4OMETRY  (GDML, STL, FLUKA and STEP) a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
+Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user.
 Output consists of taking the registry and writing the appropriate GDML.
@@
 %%%%%%%%%%%%%%%%%  Internal data representation
-The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates python ordered dictionaries that are  used to store the main 
+The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates PYTHON ordered dictionaries that are  used to store the main 
 elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
@@
 
-\begin{lstlisting}[caption={A simple python script using pyg4ometry to create a simple Geant4 geometry.},label={lst:gdmlExpressions}, language=Python]
+\begin{lstlisting}[caption={A simple PYTHON script using PYG4OMETRY to create GDML variables},label={lst:gdmlExpressions}, language=Python]
 # Import modules 
@@
 A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry.
-The create multiple replicas of a volume in a cartesian, cylindrical or spherical grid is known as a ReplicaVolume.
+The create multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a ReplicaVolume.
 A DivisionVolume breaks a primitive into segments in either a cartesian or cylindrical polar coordinates.
 A Parametrised Volume allows for the arbitrary multiple placement of solids where the parameters are allowed to vary for each placement.  GDML supports loops, 
-where sections of GDML are allowed to be repeated with varying parameters. GDML loops are not supported by pyg4ometry and will be implemented in a 
+where sections of GDML are allowed to be repeated with varying parameters. GDML loops are not supported by PYG4OMETRY and will be implemented in a 
 future release.
@@
 For each Geant4 primitive solid a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent of placed 
-instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in Python 
-\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} . Triangular meshes based on CSG 
+instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in pure PYTHON 
+\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+In general the CGAL implementation is one or two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
+Triangular meshes based on CSG
 operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various polygon mesh 
@@
 
-The python version of Geant4 physical volume is also used to store visualisation attributes like the solid's 
+The {\it Physical Volume} class (\verb|pyg4ometry.geant4.PhysicalVolume|) is also used to store visualisation attributes like the solid's 
 colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
@@
 %%%%%%%%%%%%%%%%% Adding properties to volumes
-Geometry alone is an insufficient information for a RTMC simulation.
-Often other attributes need to be assigned to regions of space for example material definition, magnetic field or optical properties.
-These physical properties can be used to define the visualisation attributes of a volume.
+Geometry needs to be augmented with other information for a complete RTMC simulation. Often other attributes need to be 
+assigned to regions of space for example material definition, magnetic field or optical properties. These physical properties 
+can be used to define the visualisation attributes of a volume.
 
 \subsection{Overlap detection}
-All RTMC transport codes can not handle spatial overlap between two geometric objects and likely are to have ill defined behaviour when tracking particles  
+All RTMC codes can not handle spatial overlap between two geometric objects and likely are to have ill-defined behaviour when tracking particles  
 through such a situation.
-A key feature of pyg4ometry is the detection of potential overlaps efficiently, it does this by performing an intersection operation etween solid instances and determining if the resulting mesh is empty.
-Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b) and intersection with finite volume and c) an overlap where two daughters share a face.
+A key feature of PYG4OMETRY is the detection of potential overlaps efficiently, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
+Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face.
 \begin{figure}[htbp]
@@
 
-Overlap detection in pyg4ometry relies of the meshes generated for each solid, 
+Overlap detection in PYG4OMETRY relies of the meshes generated for each solid, 
 any detection algorithm will be approximate. Generally the overlap detection 
@@
 %%%%%%%%%%%%%%%%% Graphical user interface
-% A basic Qt based graphical user interface is also available with pyg4ometry.
+% A basic Qt based graphical user interface is also available with PYG4OMETRY.
 If a model has a large number of volumes defined in a hierarchical tree structure, it is % cumbersome for the user to find the logical or physical volume.
@@
 \section{Rapid geometry modelling}
-Given the python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
-the parameters of the geometry and visualise the geometry. Finally when the desired result without geometry overlaps is finalised a GDML file can be output
-from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
-users of Geant4, first a \verb|Registry| need to be created to store all the pyg4ometry objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
-
-\begin{lstlisting}[caption={A simple python script using pyg4ometry to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
+Given the PYTHON scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
+the parameters of the geometry and visualise it.
+When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk from the internal memory representation.
+Some example code is presented in Listing~\ref{lst:pythonRapidModelling}.
+The structure should be familiar to regular
+users of Geant4 or GDML, apart from a new class called the \verb|Registry|.
+First a \verb|Registry| need to be created to store all the PYG4OMETRY objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
+
+\begin{lstlisting}[caption={A simple PYTHON script using PYG4OMETRY to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
 # Import modules 
@@
 
-The pyg4ometry python code in the example is approximately as expressive 
-as the GDML it writes. The benefit of wrapping GDML/Geant4 in Python allows 
+The PYG4OMETRY PYTHON code in the example is approximately as expressive 
+as the GDML it writes. The benefit of wrapping GDML/Geant4 in PYTHON allows 
 to very rapid prototyping of geometry without concerns of compilation of C++ (in the 
 case of Geant4) or writing well formed XML (in the case of GDML). Effectively
-the Python interpreter checks input for syntax errors when using pyg4ometry classes. 
-Another key benefit is the ability to use the pyg4ometry code to create 
-programatic converters between different geometry languages.
+the PYTHON interpreter checks input for syntax errors when using PYG4OMETRY classes. 
+Another key benefit is the ability to use the PYG4OMETRY code to create 
+programatic converters between different geometry languages or more generally 
+manipulation and transformation of the geometry stored in memory. The rapid modelling 
+example given in Listing~\ref{lst:pythonRapidModelling} and Figure~\ref{fig:rapidModellingExample} 
+is rather trivial, a significantly more complex example is in Figure~\ref{fig:gdml-flair}.
 
@@
 
-Each FLUKA body is represented in Pyg4ometry with a corresponding
+Each FLUKA body is represented in PYG4OMETRY with a corresponding
 class, and in turn each class has methods which returns a GDML
@@
 the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
-viewed in pyg4ometry. The example is a Faraday cup used to capture
+viewed in PYG4OMETRY. The example is a Faraday cup used to capture
 and measure accelerator beam charge.}
@@
 
-\begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
+\begin{lstlisting}[caption={A simple PYG4OMETRY PYTHON script to load a FLUKA file},label={lst:pythonFlukaLoading}, language=Python]
     reader      = pyg4ometry.fluka.Reader("faradayCup2.inp")
@@
 \begin{tabular}{ll} \hline
-FLUKA body                                              & pyg4ometry class \\ \hline
+FLUKA body                                              & PYG4OMETRY class \\ \hline
 RPP (Rectangular parallelepiped)			& Box \\
@@
 that they are effectively infinite for most reasonable use cases.
-Pyg4ometry's CSG meshing is then used to generate a mesh for each
+PYG4OMETRY's CSG meshing is then used to generate a mesh for each
 region, from which the axis-aligned bounding box can be extracted.
@@
 Figure~\ref{fig:fluka-to-geant4-cup} shows a Faraday cup implemented in
-FLUKA and translated to GDML using pyg4ometry.  The conversion is clearly
+FLUKA and translated to GDML using PYG4OMETRY.  The conversion is clearly
 accurate well and also includes the translation of the materials to GDML.
@@
 converting every quadric into a TesselatedSolid comes at a potential
-performance cost in the tracking, as well as usability in pyg4ometry as the
+performance cost in the tracking, as well as usability in PYG4OMETRY as the
 user must provide an AABB.  In some cases tesselation in unavoidable (for
@@
 be translated to an ExtrudedSolid.  This could provide both a performance
-improvement in the tracking time and make pyg4ometry easier to use as an
+improvement in the tracking time and make PYG4OMETRY easier to use as an
 AABB would not need to be provided beforehand.  This has not been
@@
 lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
+A region is a region of space which is formed of bodies and the operators + (intersection), - 
+(complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
+has XXX bodies and in general infinite extent bodies have benefits over finite ones. Key 
+for conversion are XY-, XZ-, YZ-Panes (XYP, XZP, YZP), arbitrary plane (PLA), 
+X, Y,  Z axis aligned cylinders (XCC, YCC, ZCC), X, Y, Z axis aligned elliptical cylinders (XEC, YEC, ZEC), 
+sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA).
 
@@
 \label{tab:geant2fluka}
-\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
+\caption{GDML/Geant4 solids and the mapping to FLUKA regions.}
 \end{table}
@@
 There are some important issues which must be considered to perform an accurate conversion. 
-A Geant4 logical volume solid might need to be created from a fluka region composing of many zones, 
+A Geant4 logical volume solid might need to be created from a FLUKA region composing of many zones, 
 so $R_1 = +z_1 | +z_2$, similarly a void is required to locate daughter volume placements which again 
-might also be converted to a region of multiple zones $R_2= +z_3| z_4$. So creating the fluka region is then 
+might also be converted to a region of multiple zones $R_2= +z_3 | +z_4$. So creating the FLUKA region is then 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Geant4 has the boolean solids associated with difference, union and intersection, so in addition to 
-Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in fluka notation, so 
+Geant4 has the Boolean solids associated with difference, union and intersection, so in addition to 
+Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in FLUKA notation, so 
 \begin{eqnarray}
@@
 
-Fluka (apart from the {\it lattice} directive) has no sense of a volume hierarchy. Each body is placed with a 
+FLUKA (apart from the \fluka{lattice} directive) has no sense of a volume hierarchy. Each body is placed with a 
 translation, rotation, expansion geometry directives in global coordinates. A transformation from world 
 coordinates to a physical volume is built up by applying recursively daughter volume transformations 
-and  this is used to place Fluka bodies. This  in practice is very similar to the procedure to create the 
+and  this is used to place FLUKA bodies. This  in practice is very similar to the procedure to create the 
 VTK visualisation already described in Section~\ref{sec:visualisation}.
 
-In Fluka every single space point needs to be associated with one and only one region. There is problem 
-when converting geant4 logical Volumes to fluka regions, as the logical volume outer solid $S_{\rm logical}$ 
+In FLUKA every single space point needs to be associated with one and only one region. There is problem 
+when converting geant4 logical Volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
 need to have the daughter  solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted 
@@
 \end{equation} 
-If a logical volume has  number of daughter volumes which are also possibly boolean solids, then computing 
+If a logical volume has  number of daughter volumes which are also possibly Boolean solids, then computing 
 $S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 
@@
 
-Figure~\ref{fig:flair-gdml} shows an example conversion from GDML to FLUKA. The example is a 
-vacuum chamber with three CF beam pipes connected to CF flanges. The top and bottom plates 
-have been removed to better see the geometry. The model is formed of \verb|G4Box| and
-\verb|G4Tubs| and boolean operations of subtraction, intersection and union.
+Figure~\ref{fig:gdml-flair} shows an example conversion from GDML to FLUKA. The example is a 
+vacuum chamber with three ConFlat flange (CF) beam pipes connected to CF flanges. The top and bottom plates 
+have been removed to display the geometry more clearly. The model is formed of \verb|G4Box| and
+\verb|G4Tubs| and Boolean operations of subtraction, intersection and union.
 \begin{figure*}[htb!]
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
-\caption{Example conversion of a simple GDML geometry to FLUKA, left panel :  
-the original model in pyg4ometry, right panel : the converted FLUKA geometry 
-viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
-\label{fig:flair-gdml}
+\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
+the original model in PYG4OMETRY, right panel: the converted FLUKA geometry 
+viewed in PYG4OMETRY. The example is a sector bend dipole electromagnet.}
+\label{fig:gdml-flair}
 \end{center}
@@
 \subsection{Non-Convex solid decomposition}
-In general the base solids used by Geant4 allow non-convex solids, eg Polycone, Xtru, the Twisted.  These 
-particular solids are problematic when converting geometry to a FLUKA readable format, as non-convex solids 
-can only be created by union of convex zones. There are two groups which need to considered, firstly those 
+In general the base solids used by Geant4 allow non-convex solids, e.g. Polycone, Xtru, the Twisted.  These 
+particular solids are problematic when converting them to a FLUKA-readable format, as non-convex solids 
+can only be created by the union of convex zones. There are two groups which need to considered, firstly those 
 where 2D polygonal section needs to be decomposed these include Polycone, Polyhedron and Xtru, secondly 
@@
 \end{equation}
-Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside or outside. Testing each zone 
-$z_i$ of $R$ can terminate if a point is determined to be inside any of convex zones. In general 
-Equation~\ref{eqn:logicalSubtraction} is not in a DNF. If there are many levels of logical-physical volume 
+Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside. Testing each zone 
+$z_i$ of $R$ can terminate if a point is determined to be inside any of the convex zones $z_i$. In general 
+Equation~\ref{eqn:logicalSubtraction} does not have the form of a DNF. If there are many levels of logical-physical volume 
 placement, then recursive application of  Equation~\ref{eqn:logicalSubtraction} will create a nested set of 
-parentheses. There are some conditions where a general boolean expression can yield an exponential 
+parentheses. There are some conditions where a general Boolean expression can yield an exponential 
 explosion of the final DNF. There are well known algorithms to convert logical expressions to DNF 
-\colorbox{yellow}{XXX}. Pyg4ometery can simplify parentheses from a \verb|REGION| by creating a 
-sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module \verb|to_ndf| method based on 
+\colorbox{yellow}{XXX}. PYG4OMETRY can simplify parentheses from a \verb|REGION| by creating a 
+sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module \verb|to_dnf| method based on 
 the Quine–McCluskey algorithm \cite{6769983}. Before version 4.0 FLUKA  would simplify all regions to 
@@
 \subsection{Materials}
-Pyg4ometry converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
+PYG4OMETRY converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
 
@@
 \item Degenerate body look up 
-\item Bodes with/without transformation 
+\item Bodies with/without transformation 
 \item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
@@
 \section{CAD/STL to GDML conversion }
-STEP and IGES files can be loaded into pyg4ometry, via an interface based on FreeCAD. FreeCAD is an 
+STEP and IGES files can be loaded into PYG4OMETRY, via an interface based on FreeCAD. FreeCAD is an 
 open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
@@
 collection of part features. A part feature can be used to create  a triangular mesh which can used to create 
-a pyg4ometry tessellated solid. Assignment of materials and visualisation attributes must be performed by 
+a PYG4OMETRY tessellated solid. Assignment of materials and visualisation attributes must be performed by 
 the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
 for RT codes.
-\begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
+\begin{lstlisting}[caption={A simple PYG4OMETRY PYTHON script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
     reader = pyg4ometry.freecad.Reader("FileName.step")
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
-the original model in FreeCAD, right panel : the GDML geometry 
-viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
+\caption{Example conversion of a simple FLUKA geometry to GDML, left panel:  
+the original model in FreeCAD, right panel: the GDML geometry 
+viewed in PYG4OMETRY. The example is a sector bend dipole electromagnet.}
 \label{fig:cad-gdml}
@@
 \section{Complete simulation example}
-Pyg4ometry is designed to be as flexible as possible and offer the user a wide range of usage styles 
+PYG4OMETRY is designed to be as flexible as possible and offer the user a wide range of usage styles 
 and workflows. The following sections describe a selection of 
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
-\caption{Complete compositing example using pyg4ometry.}
+\caption{Complete compositing example using PYG4OMETRY.}
 \label{fig:model}
@@
 particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
-yield more accurate simulations. Pyg4ometry is a relatively complete implementation of a geometry 
+yield more accurate simulations. PYG4OMETRY is a relatively complete implementation of a geometry 
 creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
-codes. Pyg4ometry can clearly be extended to other formats or applications. As for applications, examples 
+codes. PYG4OMETRY can clearly be extended to other formats or applications. As for applications, examples 
 include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 

### 2020-09-04 public/paper/pyg4ometry.tex
Paper update (Stuart W second round comments)

@@
 \newcommand{\fluka}[1]{\texttt{\MakeUppercase{#1}}}
+\newcommand{\PYGEOMETRY}{Pyg4ometry}
 
@@
 
-\title{PYG4OMETRY: a PYTHON library for the creation of Monte Carlo radiation transport physical geometries}
+\title{\PYGEOMETRY{}: a PYTHON library for the creation of Monte Carlo radiation transport physical geometries}
 
@@
 programs, usually computer assisted design (CAD) files exist for systems which need to be simulated. The fundamental geometric 
-representations in CAD files is typically not amenable for RT programmes.  For these reasons it is advantageous to create a software tool that allows 
-particle transport code users to rapidly develop error free geometry files, convert between common RT programme geometry formats and finally import CAD models. 
+representations in CAD files is typically not amenable for RT programs.  For these reasons it is advantageous to create a software tool that allows 
+particle transport code users to rapidly develop error-free geometry files, convert between common RT program geometry formats and finally import CAD models. 
 \colorbox{yellow}{More explanation of Geant4 and FLUKA}
 
-This paper describes a geometry creation and conversion package called PYG4OMETRY, implemented in PYTHON and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
-The main features of PYG4OMETRY are a PYTHON scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
-The origin of PYG4OMETRY was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in PYTHON and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+The main features of \PYGEOMETRY{} are a PYTHON scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
+The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
 Accelerator physicists, like specialists in other areas, need a tool to quickly simulate beam losses and the subsequent interaction of the charged particle beam with the accelerator material.
-Figure~\ref{fig:workflow} depicts various workflows possible with PYG4OMETRY.
-PYG4OMETRY is not an executable software package but a toolkit, a user would typically write very small PYTHON program to use the PYG4OMETRY.
-This paper describes version 1.0 of PYG4OMETRY, which is freely available as a git repository and via PyPi.
+Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}.
+\PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small PYTHON program to use to use the classes and functions provided by \PYGEOMETRY{}.
+This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.
 
@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Schematic of PYG4OMETRY workflow, showing a) the different input file formats, b) PYTHON processing, c) output file targets and d) RTMC codes which use the geometry. }
+  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing a) the different input file formats, b) PYTHON processing, c) output file targets and d) RTMC codes which use the geometry.
+}
 \end{figure*}
 
-There are existing codes that have functionality similar to PYG4OMETRY.
+There are existing codes that have functionality similar to \PYGEOMETRY{}.
 Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
@@
 neutronics community which  can convert CAD geometry into formats usable by RTMC codes, examples include DAGMC \cite{DAGMC} and McCad \cite{McCad}.  
-CAD software can export data to STL. If a CAD model comprises of a large number of parts, exporting, assigning material to and placing the STL  components into 
-the RTMC can be a cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
-
-This paper is structured as follows, first a brief radiation transport-centric introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of PYG4OMETRY.
-The sections that follow describe how PYG4OMETRY can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
-The paper concludes with an example of composite complex system consisting components of all the possible geometry input files formats.
+In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}.
+In practice using a lot of CAD models is difficult if a CAD model comprises of a large number of parts, exporting, assigning material to and placing the STL components into the RTMC can be a
+cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
+
+This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of \PYGEOMETRY{}.
+The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
+The paper concludes with an example of a composite complex system consisting of components drawn fromall the possible geometry input files formats.
 
@@
 Boundary representation (BREP) consists of two parts, topology and geometry. Topological elements are faces, edges and vertices and the corresponding
-geometrical elements are surfaces, curves and points. No current RTMC applications use native file formats employed by CAD systems. The conversion of CAD BREP 
-formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions to bounded or 
-infinite mathematical surfaces and subsequently solids as used in CSG descriptions.
+geometrical elements are surfaces, curves and points. No current RTMC applications use native file formats employed by CAD systems. The conversion of 
+CAD BREP formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions
+ to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions.
 
@@
 %%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
-To exchange geometry descriptions between software packages Geometry Descripition Mark-up Language (GDML) was developed \cite{GDML}. 
-GDML is an XML based description of Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write 
+To exchange geometry descriptions between software packages the Geometry Descripition Mark-up Language (GDML) was developed \cite{GDML}. 
+GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write 
 GDML format and it is commonly used as an exchange format for Geant4 geometries.
 
-\section{PYG4OMETRY design and layout}
-PYG4OMETRY is a PYTHON package consisting of semi-independent sub-packages. The sub-package \verb|pyg4ometry.geant4| contains all classes for 
-geant4 detector construction, \verb|pyg4ometry.gdml| provides the functionality for reading and writing GDML files.
-There are sub-packages for importing and exporting other geometry formats  \verb|pyg4ometry.fluka|, \verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad| and converting between file formats \verb|pyg4ometry.convert|.
-
-The core of PYG4OMETRY consists of PYTHON classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
-The constructors of the PYTHON classes are kept as close to the original Geant4 C++ implementation so that PYG4OMETRY users do not have to learn 
-a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \verb|geant4.solid.Box| class in 
+\section{\PYGEOMETRY{} design and layout}
+\PYGEOMETRY{} is a PYTHON package consisting of semi-independent sub-packages. The sub-package \lstinline{pyg4ometry.geant4} contains all classes for 
+geant4 detector construction, \lstinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files.
+There are sub-packages for importing and exporting other geometry formats  \lstinline{pyg4ometry.fluka}, \lstinline{pyg4ometry.stl} and \lstinline{pyg4ometery.freecad} and converting between file formats \verb|pyg4ometry.convert|.
+
+The core of \PYGEOMETRY{} consists of PYTHON classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
+The constructors of the PYTHON classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \lstinline{pyg4ometry.geant4.solid.Box} class in 
 PYTHON. Geometry construction in PYTHON proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in PYG4OMETRY immediately. In the following sections novel or important developments in PYG4OMETRY are described.
+should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments in \PYGEOMETRY{} are described.
 
@@
 %\begin{tabular}{ l l l } \hline
-%GDML tag 		& Child tags				& PYG4OMETRY class 				\\ \hline
+%GDML tag 		& Child tags				& \PYGEOMETRY{} class 				\\ \hline
 %Define 			& Constant				& gdml.Constant				\\
@@
 %\label{tab:gdml-tags}
-%\caption{GDML tags and corresponding PYG4OMETRY classes.}
+%\caption{GDML tags and corresponding \PYGEOMETRY{} classes.}
 %\end{table}
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in PYG4OMETRY  (GDML, STL, FLUKA and STEP) a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
+For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
 Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user.
@@
 This allows a user to update variables whilst defining geometry and the expression engine will update all internal values.
-An example of GDML expressions is shown in listing~\ref{lst:gdmlExpressions}.
-
-\begin{lstlisting}[caption={A simple PYTHON script using PYG4OMETRY to create GDML variables},label={lst:gdmlExpressions}, language=Python]
+An example of GDML expressions is shown in Listing~\ref{lst:gdmlExpressions}.
+
+\begin{lstlisting}[caption={A simple PYTHON script using \PYGEOMETRY{} to create GDML variables.},label={lst:gdmlExpressions}, language=Python]
 # Import modules 
@@
 %%%%%%%%%%%%%%%%%  Replica, division, parametrised and looped volumes
-A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry.
-The create multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a ReplicaVolume.
-A DivisionVolume breaks a primitive into segments in either a cartesian or cylindrical polar coordinates.
-A Parametrised Volume allows for the arbitrary multiple placement of solids where the parameters are allowed to vary for each placement.  GDML supports loops, 
-where sections of GDML are allowed to be repeated with varying parameters. GDML loops are not supported by PYG4OMETRY and will be implemented in a 
+A powerful feature of Geant4 and hence GDML is the ability to either repeat, divide or parametrise geometry. The class which enables the creation of 
+multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
+in either a Cartesian or cylindrical polar coordinates. A Parametrised Volume allows for the arbitrary multiple placement of solids where the parameters are 
+allowed to vary for each placement.  Another way to in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
+to be repeated with varying parameters. GDML loops loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
 future release.
@@
 \includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
-\caption{Placement of physical volume inside a logical volume}
+\caption{Placement of physical volume inside a logical volume.}
 \label{fig:lvToPv}
@@
 \end{eqnarray}
-
+%
 If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ 
@@
 
-The {\it Physical Volume} class (\verb|pyg4ometry.geant4.PhysicalVolume|) is also used to store visualisation attributes like the solid's 
+The {\it Physical Volume} class (\lstinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
 colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
@@
 through such a situation.
-A key feature of PYG4OMETRY is the detection of potential overlaps efficiently, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
+A key feature of \PYGEOMETRY{} is the detection of potential overlaps efficiently, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
 Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face.
@@
 
-Overlap detection in PYG4OMETRY relies of the meshes generated for each solid, 
+Overlap detection in \PYGEOMETRY{} relies of the meshes generated for each solid, 
 any detection algorithm will be approximate. Generally the overlap detection 
@@
 %%%%%%%%%%%%%%%%% Graphical user interface
-% A basic Qt based graphical user interface is also available with PYG4OMETRY.
+% A basic Qt based graphical user interface is also available with \PYGEOMETRY{}.
 If a model has a large number of volumes defined in a hierarchical tree structure, it is % cumbersome for the user to find the logical or physical volume.
@@
 The structure should be familiar to regular
-users of Geant4 or GDML, apart from a new class called the \verb|Registry|.
-First a \verb|Registry| need to be created to store all the PYG4OMETRY objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
-
-\begin{lstlisting}[caption={A simple PYTHON script using PYG4OMETRY to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
+users of Geant4 or GDML, apart from a new class called the \lstinline{Registry}.
+First a \verb|Registry| need to be created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
+
+\begin{lstlisting}[caption={A simple PYTHON script using \PYGEOMETRY{} to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
 # Import modules 
@@
 
-An example of the VTK output for code listing \ref{lst:pythonRapidModelling} is shown in 
+An example of the VTK output for code Listing~\ref{lst:pythonRapidModelling} is shown in 
 Figure~\ref{fig:rapidModellingExample}.
@@
 \includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
-\caption{VTK visualisation output from code listing \ref{lst:pythonRapidModelling}.}
+\caption{VTK visualisation output from code Listing~\ref{lst:pythonRapidModelling}.}
 \label{fig:rapidModellingExample}
@@
 Significantly more complex geometries can be developed using a structure similar to 
-that shown in code listing \ref{lst:pythonRapidModelling}.
-
-The PYG4OMETRY PYTHON code in the example is approximately as expressive 
+that shown in code Listing \ref{lst:pythonRapidModelling}.
+
+The \PYGEOMETRY{} PYTHON code in the example is approximately as expressive 
 as the GDML it writes. The benefit of wrapping GDML/Geant4 in PYTHON allows 
@@
 case of Geant4) or writing well formed XML (in the case of GDML). Effectively
-the PYTHON interpreter checks input for syntax errors when using PYG4OMETRY classes. 
-Another key benefit is the ability to use the PYG4OMETRY code to create 
-programatic converters between different geometry languages or more generally 
+the PYTHON interpreter checks input for syntax errors when using \PYGEOMETRY{} classes. 
+Another key benefit is the ability to use the \PYGEOMETRY{} code to create 
+programmatic converters between different geometry languages or more generally 
 manipulation and transformation of the geometry stored in memory. The rapid modelling 
 example given in Listing~\ref{lst:pythonRapidModelling} and Figure~\ref{fig:rapidModellingExample} 
-is rather trivial, a significantly more complex example is in Figure~\ref{fig:gdml-flair}.
+is rather trivial, a significantly more complex example is shown in Figure~\ref{fig:gdml-flair}.
 
@@
 
-Each FLUKA body is represented in PYG4OMETRY with a corresponding
+Each FLUKA body is represented in \PYGEOMETRY{} with a corresponding
 class, and in turn each class has methods which returns a GDML
@@
 the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
-viewed in PYG4OMETRY. The example is a Faraday cup used to capture
+viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
 and measure accelerator beam charge.}
@@
 
-\begin{lstlisting}[caption={A simple PYG4OMETRY PYTHON script to load a FLUKA file},label={lst:pythonFlukaLoading}, language=Python]
-    reader      = pyg4ometry.fluka.Reader("faradayCup2.inp")
+\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a FLUKA file.},label={lst:pythonFlukaLoading}, language=Python]
+    reader      = pyg4ometry.fluka.Reader("FlukaFileName.inp")
     g4_reg     = pyg4ometry.convert.fluka2Geant4(reader.flukaregistry)
@@
 \begin{tabular}{ll} \hline
-FLUKA body                                              & PYG4OMETRY class \\ \hline
+FLUKA body                                              & \PYGEOMETRY{} class \\ \hline
 RPP (Rectangular parallelepiped)			& Box \\
@@
 that they are effectively infinite for most reasonable use cases.
-PYG4OMETRY's CSG meshing is then used to generate a mesh for each
+\PYGEOMETRY{}'s CSG meshing is then used to generate a mesh for each
 region, from which the axis-aligned bounding box can be extracted.
@@
 Figure~\ref{fig:fluka-to-geant4-cup} shows a Faraday cup implemented in
-FLUKA and translated to GDML using PYG4OMETRY.  The conversion is clearly
+FLUKA and translated to GDML using \PYGEOMETRY{}.  The conversion is clearly
 accurate well and also includes the translation of the materials to GDML.
@@
 converting every quadric into a TesselatedSolid comes at a potential
-performance cost in the tracking, as well as usability in PYG4OMETRY as the
+performance cost in the tracking, as well as usability in \PYGEOMETRY{} as the
 user must provide an AABB.  In some cases tesselation in unavoidable (for
@@
 be translated to an ExtrudedSolid.  This could provide both a performance
-improvement in the tracking time and make PYG4OMETRY easier to use as an
+improvement in the tracking time and make \PYGEOMETRY{} easier to use as an
 AABB would not need to be provided beforehand.  This has not been
@@
 has XXX bodies and in general infinite extent bodies have benefits over finite ones. Key 
-for conversion are XY-, XZ-, YZ-Panes (XYP, XZP, YZP), arbitrary plane (PLA), 
+for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), 
 X, Y,  Z axis aligned cylinders (XCC, YCC, ZCC), X, Y, Z axis aligned elliptical cylinders (XEC, YEC, ZEC), 
@@
 \caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
-the original model in PYG4OMETRY, right panel: the converted FLUKA geometry 
-viewed in PYG4OMETRY. The example is a sector bend dipole electromagnet.}
+the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
+viewed in FLAIR. The example is a sector bend dipole electromagnet.}
 \label{fig:gdml-flair}
@@
 explosion of the final DNF. There are well known algorithms to convert logical expressions to DNF 
-\colorbox{yellow}{XXX}. PYG4OMETRY can simplify parentheses from a \verb|REGION| by creating a 
+\colorbox{yellow}{XXX}. \PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a 
 sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module \verb|to_dnf| method based on 
@@
 \subsection{Materials}
-PYG4OMETRY converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
+\PYGEOMETRY{} converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
 
@@
 \section{CAD/STL to GDML conversion }
-STEP and IGES files can be loaded into PYG4OMETRY, via an interface based on FreeCAD. FreeCAD is an 
+STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
 open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
@@
 collection of part features. A part feature can be used to create  a triangular mesh which can used to create 
-a PYG4OMETRY tessellated solid. Assignment of materials and visualisation attributes must be performed by 
+a \PYGEOMETRY{} tessellated solid. Assignment of materials and visualisation attributes must be performed by 
 the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
 for RT codes.
-\begin{lstlisting}[caption={A simple PYG4OMETRY PYTHON script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
-    reader = pyg4ometry.freecad.Reader("FileName.step")
+\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
+    reader = pyg4ometry.freecad.Reader("CadFileName.step")
     reader.relabelModel()
@@
 the original model in FreeCAD, right panel: the GDML geometry 
-viewed in PYG4OMETRY. The example is a sector bend dipole electromagnet.}
+viewed in \PYGEOMETRY{}. The example is a sector bend dipole electromagnet.}
 \label{fig:cad-gdml}
@@
 \section{Complete simulation example}
-PYG4OMETRY is designed to be as flexible as possible and offer the user a wide range of usage styles 
+\PYGEOMETRY{} is designed to be as flexible as possible and offer the user a wide range of usage styles 
 and workflows. The following sections describe a selection of 
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
-\caption{Complete compositing example using PYG4OMETRY.}
+\caption{Complete compositing example using \PYGEOMETRY{}.}
 \label{fig:model}
@@
 particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
-yield more accurate simulations. PYG4OMETRY is a relatively complete implementation of a geometry 
+yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
 creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
-codes. PYG4OMETRY can clearly be extended to other formats or applications. As for applications, examples 
+codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. As for applications, examples 
 include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 
@@
 \item Replace G4 polyhedron CSG
+\item Not for large scale conversion
 \end{enumerate}

### 2020-09-04 public/paper/model-scene/model.py
Parameters for paper figures

@@ -1,7 +1,7 @@
 import pyg4ometry 
 import os 
 
-def buildModel(vis = True, write = True, render = True) :
+def buildModel(vis = True, write = True, render = False) :
     # 
     reg = pyg4ometry.geant4.Registry()
 
@@ -125,10 +125,18 @@ def buildModel(vis = True, write = True, render = True) :
     print("world extent ", reg.getWorldVolume().extent())
 
     if vis :
-        v = pyg4ometry.visualisation.PubViewer()
+        v = pyg4ometry.visualisation.PubViewer(size=(int(3360/2), int(920/2)))
+
         v.addLogicalVolume(reg.getWorldVolume())
         # v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0])
-        v.view(interactive=True)
+
+        cam = v.ren.GetActiveCamera()
+        cam.SetRoll(0)
+        cam.SetPosition(2500, 1450.0, 1450.0)
+        cam.SetFocalPoint(0, 0, 1700.00)
+        cam.SetDistance(3400)
+
+        v.view(interactive=True, resetCamera=False)
 
     
     # gdml output
@@ -142,6 +150,7 @@ def buildModel(vis = True, write = True, render = True) :
         r.addLogicalVolumeRecursive(reg.getWorldVolume())
         r.write("./model")
 
+    return v
 
 def buildSectorBend(vis=True, inter=True):
     # load cad dipole

### 2020-09-04 public/paper/pyg4ometry.tex
Paper update
Paper update (following meeting with SW 4/10/20)

@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}.
+ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML like geometry.
 Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
@@
 %%%%%%%%%%%%%%%%% Geant4 geometery
-Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes XX fundamental solids, although it does not store a sense 
+Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes 27 basic solids, although it does not store a sense 
 of topology present in traditional CAD BREP systems. One of the fundamental solids is a {\em TessellatedSolid} which can used to represent STL or PLY files. 
@@
 \subsection{Tessellation of solids (meshing)}
-For each Geant4 primitive solid a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent of placed 
-instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in pure PYTHON 
-\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, e.g overlap 
+detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
+of placed instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in 
+pure PYTHON \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
 In general the CGAL implementation is one or two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
@@
 \subsection{Visualisation} \label{sec:visualisation}
-A  geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
+When implementing geometry a rapid and robust visualisation system is key to produce error free and efficient simulation input.
+A  \PYGEOMETRY{}  hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
 to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
@@
 through such a situation.
-A key feature of \PYGEOMETRY{} is the detection of potential overlaps efficiently, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
+A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
 Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face.
+If the resulting intersection
+is non-null then the overlaps can be displayed side-by-side in the visualisation. 
 \begin{figure}[htbp]
@@
 
-%\begin{algorithm}[h]
-%\SetAlgoLined
-%\KwResult{Write here the result }
-% initialization\;
-% \While{While condition}{
-%  instructions\;
-%  \eIf{condition}{
-%   instructions1\;
-%   instructions2\;
-%   }{
-%   instructions3\;
-%  }
-% }
-% \caption{How to write algorithms}
-%\end{algorithm}
+\begin{algorithm}[h]
+\SetAlgoLined
+\KwResult{{Write here the result} }
+ initialization\;
+ \While{While condition}{
+  instructions\;
+  \eIf{condition}{
+   instructions1\;
+   instructions2\;
+   }{
+   instructions3\;
+  }
+ }
+ \caption{How to write algorithms}
+\end{algorithm}
 
@@
 
-For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm 
-has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential 
-waste if small overlaps are present in the final RTMC simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical 
-volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are 
-considered.
+For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids have an average number of faces $n$, clearly this algorithm 
+has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters}^2)$. This might seem like a prohibitive computational cost, but worth it considering the potential 
+waste if small overlaps are present in the final RTMC simulation and large amounts of cluster CPU time is wasted.
+This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
+Due to the discrete nature of triangular meshes it is not possible to have perfect detection
+of overlaps, especially when curved surfaces are considered.
 
@@
 (complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
-has XXX bodies and in general infinite extent bodies have benefits over finite ones. Key 
+has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have benefits over finite ones. Key 
 for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), 
-X, Y,  Z axis aligned cylinders (XCC, YCC, ZCC), X, Y, Z axis aligned elliptical cylinders (XEC, YEC, ZEC), 
+Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
 sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA).
@@
 \verb|G4Tubs| and Boolean operations of subtraction, intersection and union.
-\begin{figure*}[htb!]
+\begin{figure*}
 \begin{center}
@@
 \item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \ref{eqn:logicalSubtraction} speed up using meshes
+\item Issues with tessellated solids 
 \end{enumerate}
@@
 
-\begin{figure*}[htb!]
+\begin{figure*}
 \begin{center}
@@
 \item Not for large scale conversion
+\item Export for other RTMC codes (MCNP, etc) 
 \end{enumerate}

### 2020-09-04 public/paper/pyg4ometry.tex
Stylistic: make  PYG4OMETRY textsc (smallcaps) and PYTHON -> Python

@@
 \newcommand{\fluka}[1]{\texttt{\MakeUppercase{#1}}}
-\newcommand{\PYGEOMETRY}{Pyg4ometry}
+\newcommand{\PYGEOMETRY}{\textsc{Pyg4ometry}}
 
@@
 
-\title{\PYGEOMETRY{}: a PYTHON library for the creation of Monte Carlo radiation transport physical geometries}
+\title{\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries}
 
@@
 {\em Licensing provisions: GPLv3 }			\\
-{\em Programming language: PYTHON, C/C++}                         		\\
+{\em Programming language: Python, C/C++}                         		\\
 
@@
 
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in PYTHON and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
-The main features of \PYGEOMETRY{} are a PYTHON scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
 The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
@@
 Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}.
-\PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small PYTHON program to use to use the classes and functions provided by \PYGEOMETRY{}.
+\PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}.
 This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.
@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing a) the different input file formats, b) PYTHON processing, c) output file targets and d) RTMC codes which use the geometry.
+  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing a) the different input file formats, b) Python processing, c) output file targets and d) RTMC codes which use the geometry.
 }
@@
 \section{\PYGEOMETRY{} design and layout}
-\PYGEOMETRY{} is a PYTHON package consisting of semi-independent sub-packages. The sub-package \lstinline{pyg4ometry.geant4} contains all classes for 
+\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \lstinline{pyg4ometry.geant4} contains all classes for 
 geant4 detector construction, \lstinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files.
@@
 
-The core of \PYGEOMETRY{} consists of PYTHON classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
-The constructors of the PYTHON classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
+The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
+The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \lstinline{pyg4ometry.geant4.solid.Box} class in 
-PYTHON. Geometry construction in PYTHON proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
+Python. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments in \PYGEOMETRY{} are described.
@@
 %%%%%%%%%%%%%%%%%  Internal data representation
-The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates PYTHON ordered dictionaries that are  used to store the main 
+The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
 elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
@@
 
-\begin{lstlisting}[caption={A simple PYTHON script using \PYGEOMETRY{} to create GDML variables.},label={lst:gdmlExpressions}, language=Python]
+\begin{lstlisting}[caption={A simple Python script using \PYGEOMETRY{} to create GDML variables.},label={lst:gdmlExpressions}, language=Python]
 # Import modules 
@@
 of placed instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in 
-pure PYTHON \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+pure Python \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
 In general the CGAL implementation is one or two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
@@
 \section{Rapid geometry modelling}
-Given the PYTHON scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
+Given the Python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
 the parameters of the geometry and visualise it.
@@
 
-\begin{lstlisting}[caption={A simple PYTHON script using \PYGEOMETRY{} to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
+\begin{lstlisting}[caption={A simple Python script using \PYGEOMETRY{} to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
 # Import modules 
@@
 
-The \PYGEOMETRY{} PYTHON code in the example is approximately as expressive 
-as the GDML it writes. The benefit of wrapping GDML/Geant4 in PYTHON allows 
+The \PYGEOMETRY{} Python code in the example is approximately as expressive 
+as the GDML it writes. The benefit of wrapping GDML/Geant4 in Python allows 
 to very rapid prototyping of geometry without concerns of compilation of C++ (in the 
 case of Geant4) or writing well formed XML (in the case of GDML). Effectively
-the PYTHON interpreter checks input for syntax errors when using \PYGEOMETRY{} classes. 
+the Python interpreter checks input for syntax errors when using \PYGEOMETRY{} classes. 
 Another key benefit is the ability to use the \PYGEOMETRY{} code to create 
@@
 
-\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a FLUKA file.},label={lst:pythonFlukaLoading}, language=Python]
+\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a FLUKA file.},label={lst:pythonFlukaLoading}, language=Python]
     reader      = pyg4ometry.fluka.Reader("FlukaFileName.inp")
@@
 for RT codes.
-\begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
+\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
     reader = pyg4ometry.freecad.Reader("CadFileName.step")

### 2020-09-04 public/paper/pyg4ometry.tex
inline python linebreaking

@@
 }
+
+\newcommand{\pyinline}[1]{\lstinline[postbreak={}]{#1}}
 
@@
 \section{\PYGEOMETRY{} design and layout}
-\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \lstinline{pyg4ometry.geant4} contains all classes for 
-geant4 detector construction, \lstinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files.
-There are sub-packages for importing and exporting other geometry formats  \lstinline{pyg4ometry.fluka}, \lstinline{pyg4ometry.stl} and \lstinline{pyg4ometery.freecad} and converting between file formats \verb|pyg4ometry.convert|.
+\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
+geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files.
+There are sub-packages for importing and exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats \verb|pyg4ometry.convert|.
 
@@
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
-a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \lstinline{pyg4ometry.geant4.solid.Box} class in 
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in 
 Python. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
@@
 
-The {\it Physical Volume} class (\lstinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
+The {\it Physical Volume} class (\pyinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
 colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
@@
 The structure should be familiar to regular
-users of Geant4 or GDML, apart from a new class called the \lstinline{Registry}.
+users of Geant4 or GDML, apart from a new class called the \pyinline{Registry}.
 First a \verb|Registry| need to be created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.

### 2020-09-04 public/paper/pyg4ometry.tex
overlap checking algorithm
Paper update

--- 2020-09-04 public/paper/pyg4ometry.tex
@@
 \newcommand{\PYGEOMETRY}{Pyg4ometry}
+
+% part features
+% part assembly
 
@@
 
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
+\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :
+the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
+viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
+and measure accelerator beam charge.}
+\label{fig:fluka-to-geant4-cup}
+\end{center}
+\end{figure*}
+
 Each FLUKA body is represented in \PYGEOMETRY{} with a corresponding
@@
 involved and are discussed in the rest of this section.
-
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :
-the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
-viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
-and measure accelerator beam charge.}
-\label{fig:fluka-to-geant4-cup}
-\end{center}
-\end{figure*}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[hbtp]
 \begin{center}
@@
 (complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
-has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have benefits over finite ones. Key 
-for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), 
-Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
+has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have 
+benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
+plane (PLA), Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
 sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA).
@@
 STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
-open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
-considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
+open source CAD/CAM program, which in turn is based on OpenCASCADE. FreeCAD allows for scripting in PYTHON 
+and acts as a simple to use interface to OpenCASCADE.A STEP CAD file could be 
+considered as a hierarchical tree of part assemblies and part features, where a part assembly is a 
 collection of part features. A part feature can be used to create a triangular mesh which can used to create 
@@
 the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
-for RT codes.
+for RT codes. Listing~\ref{lst:pythonCADLoading} shows how \PYGEOMETRY can load step files.
 \begin{lstlisting}[caption={A simple \PYGEOMETRY{} PYTHON script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]

### 2020-09-04 public/paper/pyg4ometry.tex
fix minor error in the algorithm description
subsection on material converstion from fluka to gdml

--- 2020-09-04 public/paper/pyg4ometry.tex
@@
 \begin{algorithm}[h]
+  \SetKwFunction{Intersect}{Intersect}
   \SetAlgoLined
-\KwResult{{Write here the result} }
- initialization\;
- \While{While condition}{
-  instructions\;
-  \eIf{condition}{
-   instructions1\;
-   instructions2\;
-   }{
-   instructions3\;
+  \KwIn{Logical volume mesh $m$ with daughter volume meshes $d\in D$.}
+\KwResult{Set, $S$, of overlapping pairs of meshes.}
+$V \longleftarrow \emptyset$\;
+$S \longleftarrow \emptyset$\;
+\For{$d_1 \in D$}{
+  \If{\Intersect{$d_1, m$}}{
+    $S \longleftarrow S \cup \{(d_1, m)\}$\;
+\For{$d_2 \in D$}{
+ \If{$d_1 = d_2$ {\bf or} $(d_2, d_1) \in V$}{
+  continue\;
+}
+\If{\Intersect{$d_1, d_2$}}{
+  $S \longleftarrow S \cup \{(d_1, d_2)\}$\;
+}
+$V \longleftarrow V \cup \{(d_1, d_2)\}$\;
 }
 }
- \caption{How to write algorithms}
+}
+\caption{The overlap checking algorithm employed in \PYGEOMETRY{}.}
 \end{algorithm}
@@
 
+\subsection{Materials}
+
+Any useful translation between geometry description formats must also
+account for material, and accordingly \PYGEOMETRY{} correctly translates
+FLUKA materials to GDML.  FLUKA materials can be divided into built-in ,
+single-element and compound materials.  Built-in materials are simply those
+that are predefined by FLUKA, single-element materials are described with a
+single \fluka{material} card, and compound materials are described with one
+\fluka{material} card followed by one or more \fluka{compound} cards.
+These three alternatives are represented in \PYGEOMETRY{} with the
+\pyinline{BuiltIn}, \pyinline{Material}, and \pyinline{Compound} classes.
+Populating a hierarchy of instances using these classes is involved due to
+the fact that recursively-defined materials in FLUKA input files need not
+be defined in a logical order.  Namely, a given \pyinline{compound} may be
+defined before the materials that it consists of are themselves defined.
+To account for this it is necessary to correctly compute the instantiation
+order so that the above classes and be instantiated correctly.  To do this
+a directed acyclic graph is populated with the materials and their
+constituents, after which a topological sort is performed so that the
+compound materials are sequenced after their constituents.  Mapping this
+set of nested FLUKA material instances to GDML material instances is then
+straight forwards as the GDML material semantics are slightly more
+expressive than FLUKA's, so a one-to-one mapping is trivial.
+
 \subsection{Lattice}
@@
 Figure~\ref{fig:fluka-to-geant4-cup} shows a Faraday cup implemented in
-FLUKA and translated to GDML using \PYGEOMETRY{}.  The conversion is clearly
-accurate well and also includes the translation of the materials to GDML.
-Many of the steps described above were directly applied in this model and
-all the features are tested and demonstrated in the repository.  This set
-of algorithms for bridging FLUKA with GDML covers a very broad range of
+FLUKA and accurately translated to GDML using \PYGEOMETRY{}.  Many of the
+steps described above were directly applied in this model and all the
+features are tested and demonstrated in the repository.  This set of
+algorithms for bridging FLUKA with GDML covers a very broad range of
 geometries, however a number of possible improvements for the future

### 2020-09-04 public/paper/pyg4ometry.tex
a bit of spell check in my section

@@
 disconnected unions, but is also allowed for intersections and
-subtractions.  Disconnected unions are readily availabe in GDML with the
+subtractions.  Disconnected unions are readily available in GDML with the
 use of the MultiUnion solid type, however there is no valid means to
@@
 performance cost in the tracking, as well as usability in \PYGEOMETRY{} as the
-user must provide an AABB.  In some cases tesselation in unavoidable (for
-example a hyperbolic parabaloid), but parabolic cylinders could for example
+user must provide an AABB.  In some cases tessellation in unavoidable (for
+example a hyperbolic paraboloid), but parabolic cylinders could for example
 be translated to an ExtrudedSolid.  This could provide both a performance
@@
 used its often parabolic cylinders (e.g. magnet pole tips) this
-specicalisation in particular would be worth implementing.
+specialisation in particular would be worth implementing.
 

### 2020-09-04 public/paper/pyg4ometry.tex

--- 2020-09-04 public/paper/pyg4ometry.tex
@@
 \newcommand{\PYGEOMETRY}{\textsc{Pyg4ometry}}
+
+% part features
+% part assembly
 
@@
 \For{$d_2 \in D$}{
- \If{$d_1 = d_2$ {\bf or} $(d_2, d_1) \in V$}{
+ \If{$d_1 = d_2$ {\bf or} $(d_1, d_2) \in V$}{
   continue\;
@@
 }
+\label{algo:overlap}
 \caption{The overlap checking algorithm employed in \PYGEOMETRY{}.}
@@
 any detection algorithm will be approximate. Generally the overlap detection 
-algorithm proceeds as 
-\begin{enumerate}
-\item Check if any of the daughter solid meshes have a non-null intersection with the compliment of mother solid mesh
-\item Loop over all daughter volumes and check
-\item Check
-\end{enumerate}
+algorithm proceeds as shown in Algorithm~\ref{algo:overlap}.
 
@@
 union of one or more zones, as well as a material.
+
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
+\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :
+the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
+viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
+and measure accelerator beam charge.}
+\label{fig:fluka-to-geant4-cup}
+\end{center}
+\end{figure*}
 
@@
 
-\subsection{Materials}
-
-Any useful translation between geometry description formats must also
-account for material, and accordingly \PYGEOMETRY{} correctly translates
-FLUKA materials to GDML.  FLUKA materials can be divided into built-in ,
-single-element and compound materials.  Built-in materials are simply those
-that are predefined by FLUKA, single-element materials are described with a
-single \fluka{material} card, and compound materials are described with one
-\fluka{material} card followed by one or more \fluka{compound} cards.
-These three alternatives are represented in \PYGEOMETRY{} with the
-\pyinline{BuiltIn}, \pyinline{Material}, and \pyinline{Compound} classes.
-Populating a hierarchy of instances using these classes is involved due to
-the fact that recursively-defined materials in FLUKA input files need not
-be defined in a logical order.  Namely, a given \pyinline{compound} may be
-defined before the materials that it consists of are themselves defined.
-To account for this it is necessary to correctly compute the instantiation
-order so that the above classes and be instantiated correctly.  To do this
-a directed acyclic graph is populated with the materials and their
-constituents, after which a topological sort is performed so that the
-compound materials are sequenced after their constituents.  Mapping this
-set of nested FLUKA material instances to GDML material instances is then
-straight forwards as the GDML material semantics are slightly more
-expressive than FLUKA's, so a one-to-one mapping is trivial.
-
 \subsection{Lattice}
@@
 Figure~\ref{fig:fluka-to-geant4-cup} shows a Faraday cup implemented in
-FLUKA and accurately translated to GDML using \PYGEOMETRY{}.  Many of the
-steps described above were directly applied in this model and all the
-features are tested and demonstrated in the repository.  This set of
-algorithms for bridging FLUKA with GDML covers a very broad range of
+FLUKA and translated to GDML using \PYGEOMETRY{}.  The conversion is clearly
+accurate well and also includes the translation of the materials to GDML.
+Many of the steps described above were directly applied in this model and
+all the features are tested and demonstrated in the repository.  This set
+of algorithms for bridging FLUKA with GDML covers a very broad range of
 geometries, however a number of possible improvements for the future
@@
 (complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
-has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have benefits over finite ones. Key 
-for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), 
-Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
+has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have 
+benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
+plane (PLA), Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
 sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
+\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
+the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
+viewed in FLAIR. The example is a sector bend dipole electromagnet.}
+\label{fig:gdml-flair}
+\end{center}
+\end{figure*}
 
@@
 \verb|G4Tubs| and Boolean operations of subtraction, intersection and union.
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
-\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
-the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
-viewed in FLAIR. The example is a sector bend dipole electromagnet.}
-\label{fig:gdml-flair}
-\end{center}
-\end{figure*}
 
@@
 
-\section{CAD/STL to GDML conversion }
-STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
-open source CAD/CAM program, which in turn is based on OpenCASCADE. A STEP CAD file could be 
-considered as a hierarchical tree of {\it part assemblies} and {\it part features}, where a part assembly is a 
-collection of part features. A part feature can be used to create  a triangular mesh which can used to create 
-a \PYGEOMETRY{} tessellated solid. Assignment of materials and visualisation attributes must be performed by 
-the user after conversion to GDML as rarely will CAD/CAM packages included the detailed information required 
-for RT codes.
+\section{STL and CAD to GDML conversion}
+STL and CAD conversion are closely related. In both cases the solid 
+(in the case of STL) and solids (in the case of CAD) are converted to 
+tessellated solid(s). STL is a relatively simple file format that can
+be loaded using pure Python. As STL files typically only contain a single 
+solid the \pyinline{stl.Reader} provides a single solid and not a logical volume
+as with the other file readers.
+
+STEP and IGES files can be loaded into 
+\PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
+open source CAD/CAM program, which in turn is based on OpenCASCADE. 
+FreeCAD allows for scripting in Python and acts as a simple to use 
+interface to OpenCASCADE.  A STEP CAD file could be considered as a 
+hierarchical tree of part features and part assemblies, where a part assembly is a 
+collection of part features. A part feature can be used to create a triangular mesh 
+which can used to create a \PYGEOMETRY{} tessellated solid. The placement 
+of the part feature is extracted from the STEP file and used to create an 
+appropriate physical volume. Assignment of materials and visualisation 
+attributes must be performed by  the user after conversion to GDML as rarely 
+will CAD/CAM packages included the detailed information required for RTMC 
+codes. Listing~\ref{lst:pythonCADLoading} shows 
+how \PYGEOMETRY{} can load step files.
 \begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
@@
 
+An example geometry representing a dipole electromagnet, consisting of three parts was created in Autodesk Fusion 360
+and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}
 \begin{figure*}
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML, left panel:  
+\caption{Example conversion of a simple CAD (STEP) geometry (sector bend dipole electromagnet) to GDML, left panel:  
 the original model in FreeCAD, right panel: the GDML geometry 
-viewed in \PYGEOMETRY{}. The example is a sector bend dipole electromagnet.}
+viewed in \PYGEOMETRY{}. }
 \label{fig:cad-gdml}
@@
 \section{Complete simulation example}
-\PYGEOMETRY{} is designed to be as flexible as possible and offer the user a wide range of usage styles 
-and workflows. The following sections describe a selection of 
-possible applications.
+\PYGEOMETRY{} is designed to be as flexible as possible and offer the user a wide range of usage styles, input files 
+and workflows. A fictitious beam line was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite 
+{\it scene} which consists of the different examples presented in this paper.
 %
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
+\caption{Complete compositing example using \PYGEOMETRY{}.}
+\label{fig:model}
+\end{center}
+\end{figure*}
+
 \begin{enumerate}
@@
 %
-\begin{figure*}[htb!]
-\begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
-\caption{Complete compositing example using \PYGEOMETRY{}.}
-\label{fig:model}
-\end{center}
-\end{figure*}
 

### 2020-09-04 public/paper/pyg4ometry.tex

@@
 \For{$d_2 \in D$}{
- \If{$d_1 = d_2$ {\bf or} $(d_1, d_2) \in V$}{
+ \If{$d_1 = d_2$ {\bf or} $(d_2, d_1) \in V$}{
   continue\;

### 2020-09-04 public/paper/pyg4ometry.tex
Paper update

@@
 and workflows. A fictitious beam line was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite 
-{\it scene} which consists of the different examples presented in this paper.
+{\it scene} which consists of the different examples presented in this paper. The beam line consists of a vacuum chamber 
+(modelled in \PYGEOMETRY{}), a vacuum gate value (STL from the manufacturer), a triplet of quadrupole magnets (exported 
+from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (modelled in 
+Flair). Each different file is loaded using \PYGEOMETRY{} reader class and the placed as a physical volume. The final composite 
+geometry is shown in Figure~\ref{fig:model}
 %

### 2020-09-04 public/paper/model-scene/model.py

@@ -227,7 +227,7 @@ def buildChamber(vis = True, inter = True):
     extentBB = gunChamber_logical.extent(includeBoundingSolid=False)
 
     if vis :
-        v = pyg4ometry.visualisation.VtkViewer(size=(2280,1800))
+        v = pyg4ometry.visualisation.VtkViewer(size=(int(3360/2), int(2010/2)))
         v.addLogicalVolume(gunChamber_logical)
         v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*1.25)
 
@@ -236,10 +236,13 @@ def buildChamber(vis = True, inter = True):
 
         cam = v.ren.GetActiveCamera()
         cam.SetRoll(0)
-        cam.SetPosition(500,0, 2000)
+        cam.SetPosition(1977.2553779137681, 1437.1208947635857, 1788.4781360684926)
+        cam.SetFocalPoint(-170.93546811748698, 155.35523039050074, 99.51238355558247)
+        cam.SetDistance(3018.319473233368)
 
         v.view(interactive=inter, resetCamera=False)
 
+    return v
 
 if __name__ == '__main__':
     buildModel()

### 2020-09-05 public/paper/pyg4ometry.tex
Paper update

@@
 \newcommand{\pyinline}[1]{\lstinline[postbreak={}]{#1}}
+\newcommand{\cpinline}[1]{\lstinline[postbreak={}]{#1}}
 
@@
 % part assembly
+% physical volume
+% logical volume
+% daughter volume
+% mother volume
+% Reader
+% scene
 
@@
 Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes 27 basic solids, although it does not store a sense 
-of topology present in traditional CAD BREP systems. One of the fundamental solids is a {\em TessellatedSolid} which can used to represent STL or PLY files. 
+of topology present in traditional CAD BREP systems. One of the fundamental solids is a tessellated sollid which can used to represent STL or PLY files. 
 Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
@@
 Not only do solid objects need to be defined but also placed in a world coordinate system.
-Geant4 has two concepts which facilitate this {\it Logical Volumes} and {\it Physical Volumes}.
-A {\it Logical Volume} is a region of space  that is defined by an outer solid but also other attributes like material, magnetic field
-and zero or more physical {\it daughter} volumes. A Physical Volume is a placement (or instance) of a Logical Volume.
+Geant4 has two concepts which facilitate this {\em logical volumes} and {\em physical volumes}.
+A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field
+and zero or more physical {\em daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume.
 
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\it Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
+For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\em Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
 Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user.
@@
 multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
-in either a Cartesian or cylindrical polar coordinates. A Parametrised Volume allows for the arbitrary multiple placement of solids where the parameters are 
+in either a Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
 allowed to vary for each placement.  Another way to in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
@@
 %%%%%%%%%%%%%%%%% Volume bounding
-If a user is creating a placing multiple {\em daughter} volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
+If a user is creating a placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
 encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume 
@@
 
-The {\it Physical Volume} class (\pyinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
+The physical volume class (\pyinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
 colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
@@
 are then composed by instantiating these classes and adding body
-instances to them.  Each Zone and Region instance can then return its
+instances to them.  Each zone and region instance can then return its
 equivalent GDML Boolean solid.
@@
 \PYGEOMETRY{} converts GDML/Geant4 materials to FLUKA \verb|MATERIAL| and \verb|COMPOUND| cards.
+Geant4 has a class \cpinline{G4Material} to assign material state (density, physical state, temperature and pressure) 
+to a logical volume. \cpinline{G4Material} has two main constructors, the first were a atomic number is supplied and 
+the second is when \cpinline{G4Element} instances and relative atomic or mass abundances are provided. The {\em simple}
+\cpinline{G4Material} is converted to a \fluka{material} card, whilst the {\em element} \cpinline{G4Material}  is converted to a 
+\fluka{compound} card. A similar issues existing when converting \cpinline{G4Element} to FLUKA, as \cpinline{G4Element}
+can either be simple, so defined only by atomic number and mass or composite and defined by a admixture defined by 
+relative abundances of \cpinline{G4Isotope}. A similar mapping is performed so if an \cpinline{G4Element} is simple it is 
+directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compund}
+card.
 
 \subsection{Disucssion}
-There are still a few outstanding issues with Geant4/GDML to FLUKA conversion.
+Overall the conversion to FLUKA input format from GDML is quite 
+advanced and stable. Relatively large experimental simulations 
+have been converted from GDML to FLUKA and have been producing 
+simulation results. The conversion described still requires a user to
+understand how geometry is specified in both Geant4 and FLUKA. For 
+example the subtraction of many non-primitive body daughter volumes from 
+a mother will create a very complex non-DNF region which is inefficient when viewed in 
+FLAIR and used for simulation in FLUKA. A geometry designer can avoid this by 
+restricting daughter volumes in Geant4 that can be expressed without 
+XXX. If \PYGEOMETRY{} is used during the creation of geometry then multiple 
+codes can be targeted without additional user effort. There are still a few outstanding technical 
+issues, which should be discussed.
+
+Currently replica, division and parametrised placements are not implemented 
+and will be addedin a future release. In Geant4 it is possible to create scaled 
+solids or placements with reflections, so called scale in Geant4. FLUKA 
+roto-translations do not support reflections and implementing reflections 
+require transformation of the body definitions. This is not yet implemented 
+in the current version of \PYGEOMETRY{}.
+
+It is possible given the GDML to FLUKA conversion algorithm described 
+in this paper that coplanar overlaps exist in the FLUKA geometry.  In 
+Geant4 there is no connection between surfaces used to specify on 
+logical volume solid and another logical volume solid. So for example 
+if a logical volume solid shared a face with one its daughter volume 
+solids the body would be duplicated in the final FLUKA file. It 
+is possible to remove obvious degeneracies but this is complicated by 
+placements of bodies. It should be possible to cast FLUKA bodies 
+{\em without} roto-translations into a {\em normal form} which can be used 
+to test for approximate equality. Approximate equality is required as 
+multiple application roto-translations will accrue numerical rounding errors.
+An simple example of this is the XYP and PLA, it simple to transform an 
+XYP into a PLA with an appropriate rotation. This would allow for the removal 
+of degenerate surfaces removing potential coplanar overlaps and also reduce 
+the final converted file size.
+
+The twisted primitives need to be decomposed 
+into a union of convex solids. This decomposition does not always 
+succeed or produces a far from optimal number of convex solids. 
+An alternative to implement these solids is to approximate each 
+layer of the twisted solid as a union of terahedra. A similar problem 
+exists for general tessellated solids, which in general
+are non-convex and need decomposition into convex hulls. A potential 
+way to avoid a computationally expensive decomposition step is to 
+create a region formed from the unions of tetrahedra. There are numerous 
+algorithms for tetrahedralisation of surface meshes in both CGAL and TetGen 
+and will be implemented in a future release. Even if a stable and general 
+method for converting tessellated solids exists it not efficient to define 
+tessellated objects in this way and memory, body or zone limits might
+be reached in FLUKA and so limit the size of CAD or STL models which 
+might be loaded.
 
 \begin{enumerate}
-\item Degenerate body look up 
-\item Bodies with/without transformation 
-\item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
-\item Scaled solid, Placement scale 
-\item Replica, Division, Parameterised
+%\item Degenerate body look up 
+%\item Bodies with/without transformation 
+% \item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
+% \item Scaled solid, Placement scale 
+% \item Replica, Division, Parameterised
 \item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \ref{eqn:logicalSubtraction} speed up using meshes
-\item Issues with tessellated solids 
+% \item Issues with tessellated solids 
 \end{enumerate}
@@
 
+\begin{enumerate}
+\item Mesh overlap and shrinking algorithm 
+\item Surface conversion and decomposition algorithm (future release)
+\end{enumerate}
+
 \section{Complete simulation example}
@@
 
-\section{Conclusions}
+\section{Conclusions and discussion}
 The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in 

### 2020-09-05 public/paper/pyg4ometry.tex
Paper update

@@
 
+Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and potentially 
+programmatically if it must be performed for large numbers of objects. The processes include; 
 \begin{enumerate}
-\item Merging Registries 
-\item Removing volumes 
-\item Editing solid
-\item Converting to assembly solids 
+\item merging registries, 
+\item removing volumes (de-featuring),
+\item editing solid parameters,
+\item replacing logical volume materials 
+\item converting logical volumes to assembly volumes.
 \end{enumerate}
-%
-
+The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
+Each sub-component is stored in a separate registry and these have to combined without any GDML tags clashing. 
+The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
+the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be 
+safely removed. Examples of other workflow can be found in the \PYGEOMETRY{} online manual
+.
 \section{Conclusions and discussion}
@@
 \item Export for other RTMC codes (MCNP, etc) 
+\item Performance in Geant4/FLUKA
 \end{enumerate}

### 2020-09-09 public/paper/pyg4ometry.tex
Fix error in the overlap checking algorithm section.
The for loop was inside the branch on whether or not the daughter overlaps
with the mother.  Suggesting that the other daughters were only checked if the mother
overlapped with the given daughter.
paper update

@@
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compund}
-card.
+card. Geant4 also defines a set of standard materials \cite{NIST} from NIST so a user can just specify something like 
+\pyinline{G4_STAINLESS-STEEL}, \PYGEOMETRY contains a matching database and creates the appropriate FLUKA cards during 
+the conversion.
 
@@
 as with the other file readers.
+%
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
+\caption{Example conversion of a simple CAD (STEP) geometry (sector bend dipole electromagnet) to GDML, left panel:  
+the original model in FreeCAD, right panel: the GDML geometry 
+viewed in \PYGEOMETRY{}. }
+\label{fig:cad-gdml}
+\end{center}
+\end{figure*}
 
@@
 and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
-\caption{Example conversion of a simple CAD (STEP) geometry (sector bend dipole electromagnet) to GDML, left panel:  
-the original model in FreeCAD, right panel: the GDML geometry 
-viewed in \PYGEOMETRY{}. }
-\label{fig:cad-gdml}
-\end{center}
-\end{figure*}
-
 \begin{enumerate}
@@
 Flair). Each different file is loaded using \PYGEOMETRY{} reader class and the placed as a physical volume. The final composite 
-geometry is shown in Figure~\ref{fig:model}
+geometry is shown in Figure~\ref{fig:model}. It must be noted when this complete geometry is written to GDML and loaded into 
+Geant4 it cannot be visualised in anything but the ray tracer because of limitations in the OpenGL visualisation in Geant4. Another 
+important note is that this geometry cannot be converted to FLUKA as it contains tessellated solids (both the STL gate valve and
+dipole magnet). 
 %
@@
 the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be 
-safely removed. Examples of other workflow can be found in the \PYGEOMETRY{} online manual
-.
+safely removed. Examples of other workflows or geometry manipulation processes can be found in 
+the \PYGEOMETRY{} online manual.
+
 \section{Conclusions and discussion}
@@
 \begin{enumerate}
+\item Coherent, uniform interface to existing tools
 \item Graphical front end viewer
@@
 \item Performance in Geant4/FLUKA
+\item AR/VR export (to OBJ or XXX)
+\item Where to put manual, unit tests, installation, git? 
+\item range of current users (RAL, CERN, LUXE, QUB, IHEP-CEPC, etc) 
+\item Paraview loader 
+\item 2D section viewer 
+\item PHITS, MCNP(X)
 \end{enumerate}
+
+\section{Acknowledgements}
+This work has been supported by STFC grants XXX and XXX. Multiple undergraduate and masters students 
+have contributed to the code for their degree project work, Simon Williams, Benjamin Shellswell, Joshua Albrecht. 
+STB has benefited from discussions with and insight of Vasilis Vlachoudis (CERN) on FLUKA geometry and FLAIR. 
+Cédric Hernalsteens (ULB/CERN) and Alistair Butcher (RHUL) also made useful contributions to the code.
 

### 2020-09-09 public/paper/model-scene/model.py
Paper update

@@ -168,12 +168,15 @@ def buildSectorBend(vis=True, inter=True):
         v.addLogicalVolume(dipole_logical)
         v.addAxes(pyg4ometry.visualisation.axesFromExtents(extentBB)[0]*1.25)
 
+        v.actors[1].GetProperty().SetRepresentationToWireframe()
         v.setOpacity(1.0)
         v.setRandomColours(3)
-
+        v.actors[1].GetProperty().SetColor(1,1,1)
+        v.actors[1].GetProperty().SetLineWidth(5)
         cam = v.ren.GetActiveCamera()
         cam.SetRoll(0)
         cam.SetPosition(500,0, 2000)
+        cam.SetDistance(795)
 
         v.view(interactive=inter, resetCamera=False)
 

### 2020-09-13 public/paper/pyg4ometry.tex
Paper update

@@
 
+\hypersetup{
+    colorlinks=false,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=cyan,
+    pdftitle={Sharelatex Example},
+    bookmarks=true,
+    pdfpagemode=FullScreen,
+}
+
 \newcommand{\pyinline}[1]{\lstinline[postbreak={}]{#1}}
@@
 % scene
+% API
+% AST
 
@@
 {\em Programming language: Python, C/C++}                         		\\
-
-{\em Supplementary material:}                                 				\\
+{\em External routines/libraries: ANTLR, CGAL, FreeCAD, OpenCascade, sympy, VTK}           	\\
+
+%{\em Supplementary material:}                                 				\\
   % Fill in if necessary, otherwise leave out.
-{\em Journal reference of previous version:}                  			\\
+%{\em Journal reference of previous version:}                  			\\
   %Only required for a New Version summary, otherwise leave out.
-{\em Does the new version supersede the previous version?:}   	\\
+%{\em Does the new version supersede the previous version?:}   	\\
   %Only required for a New Version summary, otherwise leave out.
-{\em Reasons for the new version:}							\\
+%{\em Reasons for the new version:}							\\
   %Only required for a New Version summary, otherwise leave out.
-{\em Summary of revisions:}*								\\
+%{\em Summary of revisions:}*								\\
   %Only required for a New Version summary, otherwise leave out.
@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error prone task.  \\
+Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error prone task. 
+Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
+available and geometry conversion is difficult or impossible to convert between these simulation tools. 
+\\
 {\em Solution method(approx. 50-250 words):}\\
-  %Describe the method solution here.
-{\em Additional comments including Restrictions and Unusual features (approx. 50-250 words):}\\
+Create a Python application programming interface to read and write files of and process the geometry objects and specification 
+language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
+geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
+files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from 
+FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.
+
+%{\em Additional comments including Restrictions and Unusual features (approx. 50-250 words):}\\
   %Provide any additional comments here.
-   \\
 
@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material, radiation transport (RT) programmes, these 
+There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
 include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
 All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
-RT Monte Carlo (RTMC) simulations have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples.
+RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples.
 A fundamental requirement of all of the codes is to supply a computer-readable description of the
-physical geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity 
-and performance is directly dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared 
-for different codes will enable cross-checks of the physics processes in different particle transport codes. In addition to the creation of geometry files for RT 
-programs, usually computer assisted design (CAD) files exist for systems which need to be simulated. The fundamental geometric 
-representations in CAD files is typically not amenable for RT programs.  For these reasons it is advantageous to create a software tool that allows 
-particle transport code users to rapidly develop error-free geometry files, convert between common RT program geometry formats and finally import CAD models. 
-\colorbox{yellow}{More explanation of Geant4 and FLUKA}
-
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 for APIs and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
-The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry, conversion to and from  FLUKA geometry descriptions, conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE} and powerful geometry visualisation tools based on VTK \cite{VTK4}.
+physical three dimensional (3D) geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming 
+activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 
+codes and each code will have a specialist format. The requirement of a geometry system that allows the conversion between files prepared for different 
+codes will enable cross-checks of the physics processes in different particle transport codes. Typically a MCRT code user will not have geometry in FLUKA 
+and Geant4 for example.
+The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user.
+In addition to the creation of geometry files for RT programs, usually computer assisted design (CAD) files exist for systems which
+need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 
+advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
+program geometry formats and finally import CAD models.
+
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 for Application Programming Interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.
 The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
-Accelerator physicists, like specialists in other areas, need a tool to quickly simulate beam losses and the subsequent interaction of the charged particle beam with the accelerator material.
+Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam.
+\PYGEOMETRY{} allow the rapid creation and
+adaptation of geometry.
 Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}.
 \PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}.
-This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.
+This paper describes version 1.0 o f \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.package manager.
 
@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}.
-ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML like geometry.
+ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry.
 Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
 There are also tools from the fusion and
-neutronics community which  can convert CAD geometry into formats usable by RTMC codes, examples include DAGMC \cite{DAGMC} and McCad \cite{McCad}.  
+neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC \cite{DAGMC} and McCAD \cite{McCad}.  
 In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}.
-In practice using a lot of CAD models is difficult if a CAD model comprises of a large number of parts, exporting, assigning material to and placing the STL components into the RTMC can be a
-cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
+In practice, using a lot of CAD models is difficult if a CAD model comprises of a large number of parts.
+Exporting, assigning material to and placing the STL components into the RTMC can be a cumbersome task.
+The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
 
@@
 The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
-The paper concludes with an example of a composite complex system consisting of components drawn fromall the possible geometry input files formats.
+The paper concludes with an example of a composite complex system consisting of components drawn from all the possible geometry input files formats.
 
@@
 Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
-geometry, including constructive solid geometry (CSG) , boundary representation (BREP) and tessellated polygons, these are described 
+geometry, including constructive solid geometry (CSG) , boundary representation (BREP) and tessellated polygons, which are described 
 briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
@@
 %%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
-Constructive solid geometry uses Boolean operations, subtraction, intersection and union, between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
+Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
 volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
@@
 CAD BREP formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions
- to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions.
+ to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error prone, 
+ although recent progress has been made \colorbox{yellow}{CITEXXX}.
 
 %%%%%%%%%%%%%%%%% Tessellated polygons
-Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
+Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes the ubiquitous being STL and 
 more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
@@
 Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes 27 basic solids, although it does not store a sense 
-of topology present in traditional CAD BREP systems. One of the fundamental solids is a tessellated sollid which can used to represent STL or PLY files. 
+of topology present in traditional CAD BREP systems. One of the fundamental solids is a tessellated solid which can be used to represent STL or PLY files. 
 Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
@@
 A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field
-and zero or more physical {\em daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume.
+and zero or more physical {\em daughter} physical volumes.
+A physical volume is a placement (or instance) of a logical volume.
+This design permits large reuse of objects, minismising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
+
+%%%%%%%%%%%%%%%%% FLUKA geometry
 
@@
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
-a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in 
-Python. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4
-should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments in \PYGEOMETRY{} are described.
+a new API.
+For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in Python.
+The Python object constructor is kept a simialr to the Geant4 C++ constructor, but the length definitions are those used by GDML.
+For example, GDML uses full lengths whilst Geant4 uses half lengths.
+Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4.
+A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately.
+In the following sections novel or important developments in \PYGEOMETRY{} are described.
 
@@
 The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
-elements of a GDML file. As a user specifies geometry the registry is updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
+elements of a GDML file. As a \PYGEOMETRY{} user specifies geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
 \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
@@
 In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
-In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. GDML allows for the definition 
+In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. The GDML is loaded using 
+standard XML modules and parsed using ANRLR to create an abstract syntax tree (AST).  GDML allows for the definition 
 and assignment of variables.
@@
 The AST terminates on either expressions which evaluate to numbers or GDML variables.
-Internally all classes use GDML
-expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of solid parameters and 
-placements.
-This allows a user to update variables whilst defining geometry and the expression engine will update all internal values.
+Internally, all \PYGEOMETRY{}
+classes use GDML expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
+solid parameters and  placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values. 
 An example of GDML expressions is shown in Listing~\ref{lst:gdmlExpressions}.
@@
 in either a Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
-allowed to vary for each placement.  Another way to in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
-to be repeated with varying parameters. GDML loops loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
+allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
+to be repeated with varying parameters. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
 future release.
@@
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
-of placed instances of geometry (physical volumes) and meshes for CSG derived solids. CSG mesh calculations are performed using a BSP tree technique in 
-pure Python \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
-In general the CGAL implementation is one or two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
-Triangular meshes based on CSG
-operations involving curved surfaces often contain large numbers of thin triangles. Before meshes are visualised or written to disk various polygon mesh 
-algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
+of placed instances of geometry (physical volumes) and meshes for CSG derived solids.
+CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in  pure Python \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+In general the CGAL implementation is one to two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
+Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of thin triangles.
+Before meshes are visualised or written to disk various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
 
 %%%%%%%%%%%%%%%%% Volume bounding
-If a user is creating a placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
+If a user is creating and placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
 encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume 
@@
 \end{eqnarray}
-where the subscript $p$ indicates parent volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
+where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
 Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively depending on the number of nested volumes.
@@
 \subsection{Overlap detection}
-All RTMC codes can not handle spatial overlap between two geometric objects and likely are to have ill-defined behaviour when tracking particles  
+All RTMC codes can not handle spatial overlap between two geometric objects and are likely to have ill-defined behaviour when tracking particles  
 through such a situation.
-A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resulting mesh is empty.
+A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty.
 Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face.
@@
     $S \longleftarrow S \cup \{(d_1, m)\}$\;
+    }
 \For{$d_2 \in D$}{
@@
 }
-}
+
 \label{algo:overlap}
@@
 Due to the discrete nature of triangular meshes it is not possible to have perfect detection
-of overlaps, especially when curved surfaces are considered.
-
-The accuracy of the overlap visualisation is dependent on the accuracy of the meshes generated, for example problems might occur 
-with meshes based on curved surfaces.
+of overlaps, especially when curved surfaces are considered. The deviation of the meshes created from a solid can be controlled by the user reducing the 
+chances of missing a potential overlap, but the algorithm presented here cannot capture all overlap cases. The overlap detection algorithm can 
+present the potential overlaps quickly and easily to the user, so significantly aiding their modelling process.
 
@@
 \section{Rapid geometry modelling}
-Given the Python scripting interface, expression  and tessellation engines. It is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
+Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
 the parameters of the geometry and visualise it.
@@
 \begin{lstlisting}[caption={A simple Python script using \PYGEOMETRY{} to create a simple Geant4 geometry.},label={lst:pythonRapidModelling}, language=Python]
-# Import modules 
+# import modules 
 import pyg4ometry.gdml as gd
@@
 
-# Create empty data storage structure
+# create empty data storage structure
 reg = g4.Registry()
 
-# Expressions 
+# expressions
 wx = gd.Constant("wx","100",reg)
@@
 wz = gd.Constant("wz","100",reg)
-
-bx = gd.Constant("wx","10",reg)
-by = gd.Constant("wy","10",reg)
-bz = gd.Constant("wz","10",reg)
-
-# Materials
-bm = g4.Material("G4_Galactic") 
-wm = g4.Material("G4_Iron")
-
-# Solids
+bx = gd.Constant("bx","10",reg)
+by = gd.Constant("by","10",reg)
+bz = gd.Constant("bz","10",reg)
+br = gd.Constant("br","0.25",reg)
+
+# materials
+wm = g4.MaterialPredefined("G4_Galactic")
+bm = g4.MaterialPredefined("G4_Fe")
+
+# solids
 wb = g4.solid.Box("wb",wx,wy,wz,reg)
-b = g4.solid.Box("b",bx,by,bz)
-
-# Structure 
+b  = g4.solid.Box("b",bx,by,bz,reg)
+
+# structure
 wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, bm, "b", reg)
-bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],bl,"b_pv1", wl) 
-bp2 = g4.PhysicalVolume([0,0,0],[-2*bx,0,0],bl,"b_pv2", wl)  
-bp3 = g4.PhysicalVolume([0,0,0],[2*bx,0,0],bl,"b_pv3", wl)
-
-# GDML output
+bp1 = g4.PhysicalVolume([0,0,0],
+                        [0,0,0],
+                        bl, "b_pv1", wl, reg)
+bp2 = g4.PhysicalVolume([0,0,-br],
+                        [-2*bx,0,0],
+                        bl, "b_pv2", wl, reg)
+bp3 = g4.PhysicalVolume([0,0,2*br],
+                        [2*bx,0,0],
+                        bl, "b_pv3", wl, reg)
+
+# define world volume
+reg.setWorld(wl.name)
+
+# physical volume vistualisation attributes
+bp1.visOptions.color = (1,0,0)
+bp1.visOptions.alpha = 1.0
+bp2.visOptions.color = (0,1,0)
+bp2.visOptions.alpha = 1.0
+bp3.visOptions.color = (0,0,1)
+bp3.visOptions.alpha = 1.0
+
+# gdml output
 w = gd.Writer()
-w.write(reg,"output.gdml")
-
-# Visualisation 
-v = vi.VtkViewer()
+w.addDetector(reg)
+w.write("output.gdml")
+
+# visualisation
+v = vi.VtkViewer(size=(1024,1024))
 v.addLogicalVolume(wl)
+v.addAxes()
 v.view()
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :
-the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry
+\caption{Example conversion of a simple FLUKA geometry to GDML. Left panel:
+the original FLUKA geometry displayed in FLAIR. Right panel: the GDML geometry
 viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
@@
 The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
-producing an abstract syntax tree (AST).  The resulting AST is then walked
+producing an AST.  The resulting AST is then inspected sequentially (walked)
 to populate Region instances with zones and bodies.  With the region
@@
 multiple times by placing one or more empty \textit{lattice cells} with the
-associated rototranslation from that \fluka{lattice} cell to the basic
+associated roto-translation from that \fluka{lattice} cell to the basic
 unit. The \fluka{lattice} cells themselves will generally lack structure
@@
 (complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
-has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and in general infinite extent bodies have 
+has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
 benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
@@
 In FLUKA every single space point needs to be associated with one and only one region. There is problem 
-when converting geant4 logical Volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
+when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
 need to have the daughter  solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted 
@@
 \subsection{Non-Convex solid decomposition}
-In general the base solids used by Geant4 allow non-convex solids, e.g. Polycone, Xtru, the Twisted.  These 
+In general the BREP solids used by Geant4 include non-convex solids, e.g. Polycone, Xtru, the Twisted.  These 
 particular solids are problematic when converting them to a FLUKA-readable format, as non-convex solids 
@@
 TwistedTube and Tessellated. The second classification of non convex solids are converted to CGAL 
-Nef polyhedra \colorbox{yellow}{XXX CITE} and decomposed to convex polyhedra using a 
-\colorbox{yellow}{XXX} algorithm.
+Nef polyhedra \colorbox{yellow}{CITEXXX} and decomposed to convex polyhedra using a 
+\colorbox{yellow}{CITEXXX} algorithm.
 
@@
 parentheses. There are some conditions where a general Boolean expression can yield an exponential 
-explosion of the final DNF. There are well known algorithms to convert logical expressions to DNF 
-\colorbox{yellow}{XXX}. \PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a 
-sympy \cite{10.7717/peerj-cs.103} expression and using its \verb|logical| module \verb|to_dnf| method based on 
-the Quine–McCluskey algorithm \cite{6769983}. Before version 4.0 FLUKA  would simplify all regions to 
-DNF and some converted geometry would generate too many zones and would fail. FLUKA version 4 
-allows control of the DNF expansion.
+explosion of the final DNF. There are well known algorithms to convert logical expressions to a DNF. 
+\PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a sympy \cite{10.7717/peerj-cs.103} 
+expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm \cite{6769983}. 
+Before version 4.0 FLUKA  would simplify all regions to DNF and some converted geometry would generate 
+too many zones and would fail. FLUKA version 4 allows control of the DNF expansion.
 
@@
 Geant4 has a class \cpinline{G4Material} to assign material state (density, physical state, temperature and pressure) 
-to a logical volume. \cpinline{G4Material} has two main constructors, the first were a atomic number is supplied and 
+to a logical volume. \cpinline{G4Material} has two main constructors, the first where an atomic number is supplied and 
 the second is when \cpinline{G4Element} instances and relative atomic or mass abundances are provided. The {\em simple}
@@
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compund}
-card. Geant4 also defines a set of standard materials \cite{NIST} from NIST so a user can just specify something like 
-\pyinline{G4_STAINLESS-STEEL}, \PYGEOMETRY contains a matching database and creates the appropriate FLUKA cards during 
-the conversion.
-
-\subsection{Disucssion}
+card. Geant4 also defines a set of standard materials from NIST  \colorbox{yellow}{CITEXXX NIST}. so a user can just specify something like 
+\pyinline{G4_STAINLESS-STEEL}, \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
+cards during the conversion. This database is updated by running a small Geant4 program to output the appropriate
+material data.
+
+\subsection{Discussion}
 Overall the conversion to FLUKA input format from GDML is quite 
@@
 FLAIR and used for simulation in FLUKA. A geometry designer can avoid this by 
-restricting daughter volumes in Geant4 that can be expressed without 
-XXX. If \PYGEOMETRY{} is used during the creation of geometry then multiple 
-codes can be targeted without additional user effort. There are still a few outstanding technical 
-issues, which should be discussed.
+restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
+for example a cuboid.  If \PYGEOMETRY{} is used during the creation of
+ geometry then multiple codes can be targeted without additional user effort. 
+ There are still a few outstanding technical  ssues, which should be discussed.
 
 Currently replica, division and parametrised placements are not implemented 
-and will be addedin a future release. In Geant4 it is possible to create scaled 
+and will be added in a future release. In Geant4 it is possible to create scaled 
 solids or placements with reflections, so called scale in Geant4. FLUKA 
@@
 An alternative to implement these solids is to approximate each 
-layer of the twisted solid as a union of terahedra. A similar problem 
+layer of the twisted solid as a union of tetrahedra. A similar problem 
 exists for general tessellated solids, which in general
@@
 
-STEP and IGES files can be loaded into 
-\PYGEOMETRY{}, via an interface based on FreeCAD. FreeCAD is an 
-open source CAD/CAM program, which in turn is based on OpenCASCADE. 
-FreeCAD allows for scripting in Python and acts as a simple to use 
-interface to OpenCASCADE.  A STEP CAD file could be considered as a 
-hierarchical tree of part features and part assemblies, where a part assembly is a 
-collection of part features. A part feature can be used to create a triangular mesh 
-which can used to create a \PYGEOMETRY{} tessellated solid. The placement 
+STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface 
+based on FreeCAD. FreeCAD is an open source CAD/CAM program, which 
+in turn is based on OpenCASCADE. FreeCAD allows for scripting in Python 
+and acts as a simple to use interface to OpenCASCADE.  A STEP CAD file 
+could be considered as a hierarchical tree of part features and part assemblies, 
+where a part assembly is a collection of part features. A part feature can be used 
+to create a triangular mesh which can be used to create a \PYGEOMETRY{} tessellated solid. The placement 
 of the part feature is extracted from the STEP file and used to create an 
@@
 \end{lstlisting}
+Compared to other file readers, two additional steps are required \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model 
+part names can contain characters which are not allowed in PYTHON dictionaries so need to be replaced by \pyinline{relabelModel}. 
+CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}
 
 An example geometry representing a dipole electromagnet, consisting of three parts was created in Autodesk Fusion 360
-and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}
+and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}.
+
 \begin{enumerate}
@@
 
+\section{Quality assurance}
+The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
+where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using SPHINX a 
+PYTHON documentation generator. \PYGEOMETRY{} uses mature packages available for PYTHON as dependences. 
+\PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} and \pyinline{pyg4ometry.pycgal} 
+in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using \pyinline{setuptools}. All aspects of 
+\PYGEOMETRY{} are routinely checked using unit tests. 543 tests are available for the code, which have 84\% coverage.
+
 \section{Conclusions and discussion}
-The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in 
-particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
+The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in Monte Carlo
+particle transport programmes will save significant amounts of user effort and ultimately 
 yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
-creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
-codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. As for applications, examples 
-include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 
-matter detectors and geometries for event visualisation. Although not implemented in the current version, 
-a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 
-application.
+creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
+codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
+uniform interface to existing tools and utilities, also by using the PYTHON programming language \PYGEOMETRY{} 
+allows the programatic control of geometry creation or modification.
+
+Users should be aware of {\bf issues} with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA 
+cannot be considered bidirectional. Workflows should focus on conversion from a primary format and then create conversions 
+to another format as the need arrises. This paper outlines the creation of geometry using \PYGEOMETRY{}, that geometry is loaded
+into Geant4, FLAIR and FLUKA but detailed studies of the MCRT simulation performance is beyond the scope of this publication 
+and will be addressed in the future.
+
+There are many {\bf output format extensions} that can be considered for \PYGEOMETRY{}. 
+Geant4 geometry is primarily created by writing C++ programmes, so a output writer that 
+converts the \PYGEOMETRY() in memory representation to C++ will allow rapid geometry 
+modelling but . This is not implemented in the current version but could be relatively quickly implemented
+for users that require this functionality. At present \PYGEOMETRY{} supports reading and writing. 
+Geant4 and FLUKA type files but could be extended without significant effort to other MCRT codes 
+like MCNP.
+
+There are more {\bf complex extensions} that can be considered for inclusion into \PYGEOMETRY{}.
+The meshes created by \PYGEOMETRY{} are generally of very high quality and can be used for a 
+wide range of applications. An idea already being developed is the export of the geometry mesh data to
+data formats used in augmented or virtual reality software to create interactive visualisations of MCRT 
+simulations.  Triangular meshes also have application  for GPU accelerated photon tracking in 
+liquid noble dark matter detectors. Paraview/VTK are being standard software for complex 3D visualisation and 
+the ability to write geometry to formats readily loaded and manipulated by these programs will 
+significantly aid the presentation of geometry along with the results of the MCRT simulations.
+
+\PYGEOMETRY{} is principally a toolkit but various {\bf visualisation and user interface extensions} would 
+significantly aid geometry creation workflows. A graphical frontend interface (GUI) so a user could create 
+geometry without any programming knowledge would expand the number of potential users. \PYGEOMETRY{}
+has been designed to interface with a GUI in a relatively straightforward manner. The VTK visualiser currently 
+limits the display of very large models as geometry instances are replicated opposed to reused in visualisation.
+
+{\bf Conversion}
+
+There is a strong relationship between \PYGEOMETRY and Geant4 and to a lesser extent between 
+\PYGEOMETRY{} and FLUKA. \PYGEOMETRY{} can be used to a testing ground for ideas prior to 
+implementation in Geant4 or FLAIR. An example of this the VTK visualisation system implemented in 
+\PYGEOMETRY{}, which could be used in Geant4 to rendering of Boolean solids which frequently 
+fail in the Geant4 OpenGL viewer.
 
 \begin{enumerate}
-\item Coherent, uniform interface to existing tools
-\item Graphical front end viewer
-\item C++ output
 \item CAD BREP to FLUKA converter (a la McCAD) 
@@
 \item Far from perfect conversions
-\item Export mesh for other applications (GPU optics)
 \item Convergence FLUKA/Geant4 - Moira 
@@
 \item Not for large scale conversion
-\item Export for other RTMC codes (MCNP, etc) 
-\item Performance in Geant4/FLUKA
-\item AR/VR export (to OBJ or XXX)
-\item Where to put manual, unit tests, installation, git? 
 \item range of current users (RAL, CERN, LUXE, QUB, IHEP-CEPC, etc) 
-\item Paraview loader 
 \item 2D section viewer 
-\item PHITS, MCNP(X)
 \end{enumerate}

### 2020-09-13 public/paper/diagrams/rapidModelling.py

@@ -1,3 +1,4 @@
+# import modules 
 import pyg4ometry.gdml as gd
 import pyg4ometry.geant4 as g4
 import pyg4ometry.visualisation as vi
@@ -12,10 +13,11 @@ wz = gd.Constant("wz","100",reg)
 bx = gd.Constant("bx","10",reg)
 by = gd.Constant("by","10",reg)
 bz = gd.Constant("bz","10",reg)
+br = gd.Constant("br","0.25",reg)
 
 # materials
-bm = g4.MaterialPredefined("G4_Galactic")
-wm = g4.MaterialPredefined("G4_Fe")
+wm = g4.MaterialPredefined("G4_Galactic")
+bm = g4.MaterialPredefined("G4_Fe")
 
 # solids
 wb = g4.solid.Box("wb",wx,wy,wz,reg)
@@ -24,13 +26,17 @@ b  = g4.solid.Box("b",bx,by,bz,reg)
 # structure
 wl = g4.LogicalVolume(wb, wm, "wl", reg)
 bl = g4.LogicalVolume(b, bm, "b", reg)
-bp1 = g4.PhysicalVolume([0,0,0],[0,0,0],
+bp1 = g4.PhysicalVolume([0,0,0],
+                        [0,0,0],
                         bl, "b_pv1", wl, reg)
-bp2 = g4.PhysicalVolume([0,0,-0.25],[-2*bx,0,0],
+bp2 = g4.PhysicalVolume([0,0,-br],
+                        [-2*bx,0,0],
                         bl, "b_pv2", wl, reg)
-bp3 = g4.PhysicalVolume([0,0,0.5],[2*bx,0,0],
+bp3 = g4.PhysicalVolume([0,0,2*br],
+                        [2*bx,0,0],
                         bl, "b_pv3", wl, reg)
 
+# define world volume
 reg.setWorld(wl.name)
 
 # physical volume vistualisation attributes
@@ -38,7 +44,6 @@ bp1.visOptions.color = (1,0,0)
 bp1.visOptions.alpha = 1.0
 bp2.visOptions.color = (0,1,0)
 bp2.visOptions.alpha = 1.0
-# bp2.visOptions.representation = "wireframe"
 bp3.visOptions.color = (0,0,1)
 bp3.visOptions.alpha = 1.0
 

### 2020-09-13 public/paper/pyg4ometry.tex
Paper update (complete conclusions, vertical stack comparisions)

@@
 % AST 
+% BREP (not B-REP)
 
@@
 
-\begin{figure*}[htbp]
+\begin{figure}[htbp]
 \begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
+\includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
 \caption{Example conversion of a simple FLUKA geometry to GDML. Left panel:
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
+\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
 \caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
@@
 %
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
+\includegraphics[width=0.9\columnwidth]{./model-scene/SectorBend.pdf}
 \caption{Example conversion of a simple CAD (STEP) geometry (sector bend dipole electromagnet) to GDML, left panel:  
@@
 part names can contain characters which are not allowed in PYTHON dictionaries so need to be replaced by \pyinline{relabelModel}. 
-CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}
+CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
 
@@
 in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using \pyinline{setuptools}. All aspects of 
-\PYGEOMETRY{} are routinely checked using unit tests. 543 tests are available for the code, which have 84\% coverage.
+\PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available for the code, which have 84\% coverage.
 
@@
 uniform interface to existing tools and utilities, also by using the PYTHON programming language \PYGEOMETRY{} 
-allows the programatic control of geometry creation or modification.
+allows the programatic control of geometry creation or modification. This approach allows the integration of 
+other available tools \colorbox{yellow}{CITEXXX DAGMC, CAD stuff} into an unified workflow.
 
 Users should be aware of {\bf issues} with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA 
-cannot be considered bidirectional. Workflows should focus on conversion from a primary format and then create conversions 
-to another format as the need arrises. This paper outlines the creation of geometry using \PYGEOMETRY{}, that geometry is loaded
-into Geant4, FLAIR and FLUKA but detailed studies of the MCRT simulation performance is beyond the scope of this publication 
-and will be addressed in the future.
+cannot be considered bidirectional. For example Geant4 tessellated cannot be converted easily to FLUKA which does not 
+have a convenient way of representing this geometry. In general a user would be unwise to attempt to convert a very large 
+geometry from one format to another, but concentrate on smaller conversions of constituent parts. Workflows should focus 
+on conversion from a primary format and then create conversions to another format as the need arrises. This paper outlines 
+the creation of geometry using \PYGEOMETRY{}, that geometry is loaded into Geant4, FLAIR and FLUKA but detailed 
+studies of the MCRT simulation performance is beyond the scope of this publication and will be addressed in the future.
 
@@
 
-{\bf Conversion}
+The {\bf conversion} which would most dramatically enhance the creation of geometry is CAD to Geant4/FLUKA
+without use use of a triangular or tetrahedral mesh. There are methods to decompose BREP solids to Geant4 and 
+FLUKA like CSG geometry \colorbox{yellow}{CITEXXX MCCAD}. The FreeCAD/OpenCASCADE interface
+combined with the Geant4 and FLUKA PYTHON API present in \PYGEOMETRY{} will allow for the creation 
+of CAD B-REP decomposition algorithms.
 
@@
 \PYGEOMETRY{}, which could be used in Geant4 to rendering of Boolean solids which frequently 
-fail in the Geant4 OpenGL viewer.
-
-\begin{enumerate}
-\item CAD BREP to FLUKA converter (a la McCAD) 
-\item Integration of other tools (DAGMC) 
-\item Far from perfect conversions
-\item Convergence FLUKA/Geant4 - Moira 
-\item Replace G4 polyhedron CSG
-\item Not for large scale conversion
-\item range of current users (RAL, CERN, LUXE, QUB, IHEP-CEPC, etc) 
-\item 2D section viewer 
-\end{enumerate}
+fail in the Geant4 OpenGL viewer. This would involve using CGAL meshing in the \pyinline{G4Polyhedron}
+class. There is also
+
+\PYGEOMETRY{} is already proving to be a useful tool for geometry conversion, creation and manipulation.
+There are numerous international researcher and research groups already using the code for their particular applications.
+The users are focused in accelerator physics, but \PYGEOMETRY{} could find application in any scientific
+area where MCRT simulations are needed, for example particle physics, space environment and medical physics.
+The authors welcome contributions, extensions and bug-fixes as well a suggestions for larger collaborations.
 

### 2020-09-14 public/paper/pyg4ometry.tex
error prone -> error-prone

@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error prone task. 
+Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error-prone task. 
 Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
@@
 CAD BREP formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions
- to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error prone, 
+ to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error-prone, 
  although recent progress has been made \colorbox{yellow}{CITEXXX}.

### 2020-09-14 public/paper/pyg4ometry.tex
introduce abbreviation MCRT on first use

@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error-prone task. 
+Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time consuming and error-prone task. 
 Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate three-dimensional, remove 3D in brackets.
not an abbreviation that needs explaining.

@@
 A fundamental requirement of all of the codes is to supply a computer-readable description of the
-physical three dimensional (3D) geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming 
+physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming 
 activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate time-consuming

@@
 {\em Nature of problem(approx. 50-250 words):}\\
-Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time consuming and error-prone task. 
+Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
 Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
@@
 A fundamental requirement of all of the codes is to supply a computer-readable description of the
-physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming 
+physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
 activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 

### 2020-09-14 public/paper/pyg4ometry.tex
Fix malformed english and attempt at reword
"There is not general format..."
a MCRT -> an MCRT

@@
 physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
-activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 
-codes and each code will have a specialist format. The requirement of a geometry system that allows the conversion between files prepared for different 
-codes will enable cross-checks of the physics processes in different particle transport codes. Typically a MCRT code user will not have geometry in FLUKA 
+activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no standard geometry format used across MCRT 
+codes, with each MCRT code typically using its own unique format. The requirement of a geometry system that allows the conversion between files prepared for different 
+codes will enable cross-checks of the physics processes in different particle transport codes. Typically an MCRT code user will not have geometry in FLUKA 
 and Geant4 for example.

### 2020-09-14 public/paper/pyg4ometry.tex
CAD is short for computer-aided design

@@
 The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user.
-In addition to the creation of geometry files for RT programs, usually computer assisted design (CAD) files exist for systems which
+In addition to the creation of geometry files for RT programs, usually computer-aided design (CAD) files exist for systems which
 need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 

### 2020-09-14 public/paper/pyg4ometry.tex
is -> are
replace words "typically" (used too many times in this paragraph)

@@
 and Geant4 for example.
-The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user.
+The file formats used for geometry are generally focused on the computational efficiency of a particle tracking task and not ease of use of a user.
 In addition to the creation of geometry files for RT programs, usually computer-aided design (CAD) files exist for systems which
-need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 
+need to be simulated. The fundamental geometric representations in CAD files are usually not amenable for MCRT programs.  For these reasons it is 
 advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 

### 2020-09-14 public/paper/pyg4ometry.tex
import -> load, to clarify intent

@@
 advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
-program geometry formats and finally import CAD models.
+program geometry formats and load CAD models.
 

### 2020-09-14 public/paper/pyg4ometry.tex
remove misplaced word (for)

@@
 
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 for Application Programming Interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 Application Programming Interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
 The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.

### 2020-09-14 public/paper/pyg4ometry.tex
Application Programming Interface should not be capitalised

@@
 
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 Application Programming Interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 application programming interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
 The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.

### 2020-09-14 public/paper/pyg4ometry.tex
implemented -> written

@@
 
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, implemented in Python and internally based on the Geant4 application programming interface (API) and Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
 The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.

### 2020-09-14 public/paper/pyg4ometry.tex
simulation -> simulation program

@@
 The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.
-The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
+The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
 Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam.

### 2020-09-14 public/paper/pyg4ometry.tex
o f -> of
malformed sentence + reword (pypi)
avoid "comprises of"

@@
 \PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}.
-This paper describes version 1.0 o f \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.package manager.
+This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).
 
@@
 In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}.
-In practice, using a lot of CAD models is difficult if a CAD model comprises of a large number of parts.
+In practice, using a lot of CAD models is difficult if a CAD model is comprised of a large number of parts.
 Exporting, assigning material to and placing the STL components into the RTMC can be a cumbersome task.

### 2020-09-14 public/paper/pyg4ometry.tex
possible -> supported.
comma before etc and full stop after

@@
 The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
-The paper concludes with an example of a composite complex system consisting of components drawn from all the possible geometry input files formats.
+The paper concludes with an example of a composite complex system consisting of components drawn from all the supported  geometry input files formats.
 
@@
 %%%%%%%%%%%%%%%%% Constructive solid geometry (CSG) 
-Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere etc) or infinite
+Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
 volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 

### 2020-09-14 public/paper/pyg4ometry.tex
missing fullstops after e.g

@@
 Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
-volumes (e.g a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
+volumes (e.g. a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
 CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, e.g overlap 
+Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, e.g. overlap 
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate plane-defined
The abbreviation BREP has already been introduced (above)

@@
 Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
-volumes (e.g. a plane defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
+volumes (e.g. a plane-defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a 
 CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
@@
 %%%%%%%%%%%%%%%%% Boundary representation (BREP)
-Boundary representation (BREP) consists of two parts, topology and geometry. Topological elements are faces, edges and vertices and the corresponding
+Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices and the corresponding
 geometrical elements are surfaces, curves and points. No current RTMC applications use native file formats employed by CAD systems. The conversion of 

### 2020-09-14 public/paper/pyg4ometry.tex
missing comma
better wording

@@
 %%%%%%%%%%%%%%%%% Tessellated polygons
-Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes the ubiquitous being STL and 
+Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
 more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
-deviation distance from the solid decreases the number of polygons increases and hence the memory consumption and execution time of the RTMC simulation.
+deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the RTMC simulation.
 

### 2020-09-14 public/paper/pyg4ometry.tex
spelling
spelling, ANRLR -> ANTLR

@@
 For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in Python.
-The Python object constructor is kept a simialr to the Geant4 C++ constructor, but the length definitions are those used by GDML.
+The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML.
 For example, GDML uses full lengths whilst Geant4 uses half lengths.
@@
 In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. The GDML is loaded using 
-standard XML modules and parsed using ANRLR to create an abstract syntax tree (AST).  GDML allows for the definition 
+standard XML modules and parsed using ANTLR to create an abstract syntax tree (AST).  GDML allows for the definition 
 and assignment of variables.

### 2020-09-14 public/paper/pyg4ometry.tex
missing comma before etc in list

@@
 and assignment of variables.
-GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc.
+GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$, etc.
 The AST terminates on either expressions which evaluate to numbers or GDML variables.

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate floating-point
non-breaking space before citations

@@
 There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
-include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
+include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}. 
 All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
@@
 
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}.
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency~\cite{GDML}.
 The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.
@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}.
-ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry.
+ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry.
 Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
 There are also tools from the fusion and
-neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC \cite{DAGMC} and McCAD \cite{McCad}.  
-In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}.
+neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}.  
+In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}.
 In practice, using a lot of CAD models is difficult if a CAD model is comprised of a large number of parts.
@@
 %%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
-To exchange geometry descriptions between software packages the Geometry Descripition Mark-up Language (GDML) was developed \cite{GDML}. 
-GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT \cite{fons_rademakers_2019_3895860} can read and write 
+To exchange geometry descriptions between software packages the Geometry Descripition Mark-up Language (GDML) was developed~\cite{GDML}. 
+GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
 GDML format and it is commonly used as an exchange format for Geant4 geometries.
@@
 In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
-In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. The GDML is loaded using 
+In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR~\cite{10.5555/2501720}. The GDML is loaded using 
 standard XML modules and parsed using ANTLR to create an abstract syntax tree (AST).  GDML allows for the definition 
@@
 Internally, all \PYGEOMETRY{}
-classes use GDML expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
+classes use GDML expressions and not floating-point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
 solid parameters and  placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values. 
@@
 of placed instances of geometry (physical volumes) and meshes for CSG derived solids.
-CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in  pure Python \cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in  pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
 In general the CGAL implementation is one to two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
@@
 explosion of the final DNF. There are well known algorithms to convert logical expressions to a DNF. 
-\PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a sympy \cite{10.7717/peerj-cs.103} 
-expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm \cite{6769983}. 
+\PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a sympy~\cite{10.7717/peerj-cs.103} 
+expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm~\cite{6769983}. 
 Before version 4.0 FLUKA  would simplify all regions to DNF and some converted geometry would generate 

### 2020-09-14 public/paper/pyg4ometry.tex
e.g -> such as

@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, e.g. overlap 
+Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, such as overlap 
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate CSG-derived
state that CGAL is in C++
We state that it's in pure python or cgal, so we should also state that
cgal is in c++, for parity.  so we clearly contrast the two implementation
language choices (and implied speed differences)

@@
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
-of placed instances of geometry (physical volumes) and meshes for CSG derived solids.
-CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in  pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b}.
+of placed instances of geometry (physical volumes) and meshes for CSG-derived solids.
+CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++.
 In general the CGAL implementation is one to two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.

### 2020-09-14 public/paper/pyg4ometry.tex
pure-PYTHON -> pure Python

@@
 CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++.
-In general the CGAL implementation is one to two orders of magnitude faster than the pure-PYTHON CSG implementation and must be used for large geometries.
+In general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries.
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of thin triangles.

### 2020-09-14 public/paper/pyg4ometry.tex
remove "thin" from "thin triangle"  triangles are always 2D/thin
it is superfluous..
inline comments

@@
 In general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries.
-Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of thin triangles.
+Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles.
 Before meshes are visualised or written to disk various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
@@
 If a user is creating and placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
-encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable to have a mother volume 
+encompasses the daughter volumes.
+Overlaps between daughter volumes and the mother can be detected to, but it is desirable \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?
+And I'm not sure what the word ``efficiently'' means precisely in this context.} to have a mother volume
 shape that efficiently holds all of its daughters.

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate error-free

@@
 \subsection{Visualisation} \label{sec:visualisation}
-When implementing geometry a rapid and robust visualisation system is key to produce error free and efficient simulation input.
+When implementing geometry a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
 A  \PYGEOMETRY{}  hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 

### 2020-09-14 public/paper/pyg4ometry.tex
add word
Better wording I think.
Recursion is presumably used no matter what, not just if there are a
sufficient number of daughters.

@@
 When implementing geometry a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
-A  \PYGEOMETRY{}  hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
+A  \PYGEOMETRY{} geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
 to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
@@
 where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
-Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively depending on the number of nested volumes.
+Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.
 

### 2020-09-14 public/paper/pyg4ometry.tex
can not -> cannot to fit with rest of paper

@@
 \subsection{Overlap detection}
-All RTMC codes can not handle spatial overlap between two geometric objects and are likely to have ill-defined behaviour when tracking particles  
+All RTMC codes cannot handle spatial overlap between two geometric objects and are likely to have ill-defined behaviour when tracking particles  
 through such a situation.

### 2020-09-14 public/paper/pyg4ometry.tex
WILL have ill-defined behaviour.
Even if it ends up happening to work correctly, the behaviour itself can
still be ill-defined.

I don't think this is a too-strong thing to say either, as at the start of
this sentence we've already said that no RTMC codes can handle overlaps.

@@
 \subsection{Overlap detection}
-All RTMC codes cannot handle spatial overlap between two geometric objects and are likely to have ill-defined behaviour when tracking particles  
+All RTMC codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
 through such a situation.

### 2020-09-14 public/paper/pyg4ometry.tex
through -> in.  sounds better

@@
 All RTMC codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
-through such a situation.
+in such a situation.
 A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty.

### 2020-09-14 public/paper/pyg4ometry.tex
a), b), c) -> (a), (b), (c)
from what I can tell this is a more standard form, and it looks nicer

@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing a) the different input file formats, b) Python processing, c) output file targets and d) RTMC codes which use the geometry.
+  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing (a) the different input file formats, (b) Python processing, (c) output file targets and (d) RTMC codes which use the geometry.
 }
@@
 A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty.
-Figure~\ref{fig:overlap} shows the potential overlaps, a) protrusion of a daughter from the mother, b)  finite volume intersection between two daughters  and c) an overlap where two daughters share a face.
+Figure~\ref{fig:overlap} shows the potential overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters share a face.
 If the resulting intersection

### 2020-09-14 public/paper/pyg4ometry.tex
so -> thus
the instead of a as we just introduced it in the previous sentence

@@
 chances of missing a potential overlap, but the algorithm presented here cannot capture all overlap cases. The overlap detection algorithm can 
-present the potential overlaps quickly and easily to the user, so significantly aiding their modelling process.
+present the potential overlaps quickly and easily to the user, thus significantly aiding their modelling process.
 
@@
 users of Geant4 or GDML, apart from a new class called the \pyinline{Registry}.
-First a \verb|Registry| need to be created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
+First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
 

### 2020-09-14 public/paper/pyg4ometry.tex
it's new but we have already described it it..  maybe this is better
add non-breaking space after Listing

@@
 The structure should be familiar to regular
-users of Geant4 or GDML, apart from a new class called the \pyinline{Registry}.
+users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}.
 First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
@@
 Significantly more complex geometries can be developed using a structure similar to 
-that shown in code Listing \ref{lst:pythonRapidModelling}.
+that shown in code Listing~\ref{lst:pythonRapidModelling}.
 

### 2020-09-14 public/paper/pyg4ometry.tex
combine the two adjacent references to the same Listing
looks awkward when we say "Listing 2" twice right next to each other.
remove and/or, replace with or

@@
 users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}.
-First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file and/or visualised using VTK.
+First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file or visualised using VTK.
 
@@
 
-An example of the VTK output for code Listing~\ref{lst:pythonRapidModelling} is shown in 
-Figure~\ref{fig:rapidModellingExample}.
+An example of the VTK output for code
+Listing~\ref{lst:pythonRapidModelling} is shown in
+Figure~\ref{fig:rapidModellingExample}. Significantly more complex
+geometries can be developed using a structure similar to that shown.
+
 \begin{figure}[htbp]
@@
 \end{figure}
-Significantly more complex geometries can be developed using a structure similar to 
-that shown in code Listing~\ref{lst:pythonRapidModelling}.
 

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate Z-axis

@@
 benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
-plane (PLA), Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
+plane (PLA), Z-axis aligned cylinder (ZCC), Z-axis aligned elliptical cylinder (ZEC), 
 sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 

### 2020-09-14 public/paper/pyg4ometry.tex
put subtraction in mathmode so it looks better

@@
 lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
-A region is a region of space which is formed of bodies and the operators + (intersection), - 
+A region is a region of space which is formed of bodies and the operators + (intersection), $-$ 
 (complement) and | (union), also parentheses to indicate the order of operations. FLUKA 

### 2020-09-14 public/paper/pyg4ometry.tex
fix sentence the -> and
spelling: compund -> compound

@@
 \subsection{Non-Convex solid decomposition}
-In general the BREP solids used by Geant4 include non-convex solids, e.g. Polycone, Xtru, the Twisted.  These 
+In general the BREP solids used by Geant4 include non-convex solids, such as  Polycone, Xtru, and Twisted.  These 
 particular solids are problematic when converting them to a FLUKA-readable format, as non-convex solids 
@@
 relative abundances of \cpinline{G4Isotope}. A similar mapping is performed so if an \cpinline{G4Element} is simple it is 
-directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compund}
+directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compound}
 card. Geant4 also defines a set of standard materials from NIST  \colorbox{yellow}{CITEXXX NIST}. so a user can just specify something like 

### 2020-09-14 public/paper/pyg4ometry.tex
highlight comment
PYTHON -> Python

@@
  geometry then multiple codes can be targeted without additional user effort. 
- There are still a few outstanding technical  ssues, which should be discussed.
+ \colorbox{yellow}{There are still a few outstanding technical  ssues, which should be discussed. }
 
@@
 Compared to other file readers, two additional steps are required \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model 
-part names can contain characters which are not allowed in PYTHON dictionaries so need to be replaced by \pyinline{relabelModel}. 
+part names can contain characters which are not allowed in Python dictionaries so need to be replaced by \pyinline{relabelModel}. 
 CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
@@
 where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using SPHINX a 
-PYTHON documentation generator. \PYGEOMETRY{} uses mature packages available for PYTHON as dependences. 
+Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependences. 
 \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} and \pyinline{pyg4ometry.pycgal} 
@@
 codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and 
-uniform interface to existing tools and utilities, also by using the PYTHON programming language \PYGEOMETRY{} 
+uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
 allows the programatic control of geometry creation or modification. This approach allows the integration of 
@@
 FLUKA like CSG geometry \colorbox{yellow}{CITEXXX MCCAD}. The FreeCAD/OpenCASCADE interface
-combined with the Geant4 and FLUKA PYTHON API present in \PYGEOMETRY{} will allow for the creation 
+combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} will allow for the creation 
 of CAD B-REP decomposition algorithms.

### 2020-09-14 public/paper/pyg4ometry.tex
Paper update

@@
 All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
-RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples.
-A fundamental requirement of all of the codes is to supply a computer-readable description of the
-physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
-activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no standard geometry format used across MCRT 
-codes, with each MCRT code typically using its own unique format. The requirement of a geometry system that allows the conversion between files prepared for different 
-codes will enable cross-checks of the physics processes in different particle transport codes. Typically an MCRT code user will not have geometry in FLUKA 
-and Geant4 for example.
-The file formats used for geometry are generally focused on the computational efficiency of a particle tracking task and not ease of use of a user.
-In addition to the creation of geometry files for RT programs, usually computer-aided design (CAD) files exist for systems which
-need to be simulated. The fundamental geometric representations in CAD files are usually not amenable for MCRT programs.  For these reasons it is 
-advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
-program geometry formats and load CAD models.
-
-This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency~\cite{GDML}.
-The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}.
-The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}.
+ Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical 
+imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a 
+computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is 
+typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no 
+standard geometry format used across MCRT codes, with each MCRT code typically using its own unique format. The requirement of a geometry system 
+that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport
+ codes. Typically an MCRT code user will not have geometry in FLUKA and Geant4 for example. The file formats used for geometry are generally focused 
+ on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually 
+ computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not 
+ amenable for MCRT programs.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
+ error-free geometry files, convert between common MCRT program geometry formats and load CAD models.
+
+This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application 
+programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency~\cite{GDML}. The main features of \PYGEOMETRY{} 
+are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP 
+and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The 
+origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. 
 Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. 
-\PYGEOMETRY{} allow the rapid creation and
-adaptation of geometry.
-Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}.
-\PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}.
-This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).
+\PYGEOMETRY{} allow the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
+is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by 
+\PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).
 
@@
   \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
-  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing (a) the different input file formats, (b) Python processing, (c) output file targets and (d) RTMC codes which use the geometry.
-}
+  \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing (a) the different input file formats, (b) Python processing, (c) output file targets and 
+  (d) MCRT codes which use the geometry. }
 \end{figure*}
 
-There are existing codes that have functionality similar to \PYGEOMETRY{}.
-ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry.
-Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}.
-There are also tools from the fusion and
-neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}.  
-In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}.
-In practice, using a lot of CAD models is difficult if a CAD model is comprised of a large number of parts.
-Exporting, assigning material to and placing the STL components into the RTMC can be a cumbersome task.
-The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
-
-This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design and implementation of \PYGEOMETRY{}.
-The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from FLUKA to GDML, GDML to FLUKA and CAD to GDML.
-The paper concludes with an example of a composite complex system consisting of components drawn from all the supported  geometry input files formats.
+There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis program, 
+can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
+products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
+geometry into formats usable by MCRT codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
+(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a 
+large number of parts. Exporting, assigning material to and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
+provide a complete set of tools to efficiently create complex geometries.
+
+This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design 
+and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
+FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from 
+all the supported  geometry input files formats.
 
@@
 Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices and the corresponding
-geometrical elements are surfaces, curves and points. No current RTMC applications use native file formats employed by CAD systems. The conversion of 
-CAD BREP formats for loading in RTMC applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions
+geometrical elements are surfaces, curves and points. No current MCRT applications use native file formats employed by CAD systems. The conversion of 
+CAD BREP formats for loading in MCRT applications is typically performed via a tessellated format, although it is possible to decompose BREP descriptions
  to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error-prone, 
@@
 more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
-deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the RTMC simulation.
+deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the MCRT simulation.
 
@@
 Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
-Geant4.
-Not only do solid objects need to be defined but also placed in a world coordinate system.
-Geant4 has two concepts which facilitate this {\em logical volumes} and {\em physical volumes}.
-A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field
-and zero or more physical {\em daughter} physical volumes.
-A physical volume is a placement (or instance) of a logical volume.
-This design permits large reuse of objects, minismising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
+Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\em logical volumes} 
+and {\em physical volumes}. A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field 
+and zero or more physical {\em daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume. This design permits large reuse 
+of objects, minismising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
 
@@
 \PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
-geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files.
-There are sub-packages for importing and exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats \verb|pyg4ometry.convert|.
+geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
+exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats 
+\verb|pyg4ometry.convert|.
 
@@
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
-a new API.
-For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in Python.
-The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML.
-For example, GDML uses full lengths whilst Geant4 uses half lengths.
-Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4.
-A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately.
-In the following sections novel or important developments in \PYGEOMETRY{} are described.
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} 
+class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
+GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
+A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
+in \PYGEOMETRY{} are described.
 
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\em Reader} class is implemented, so \verb|gdml.Reader|, \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|.
-Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which can be used or manipulated by the user.
+For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\em Reader} class is implemented, so \verb|gdml.Reader|, 
+\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which 
+can be used or manipulated by the user. 
 Output consists of taking the registry and writing the appropriate GDML.
@@
 The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
-elements of a GDML file. As a \PYGEOMETRY{} user specifies geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry is written to disk as a GDML file.
-\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
+elements of a GDML file. As a \PYGEOMETRY{} user specifies geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
+is written to disk as a GDML file.\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 
@@
 standard XML modules and parsed using ANTLR to create an abstract syntax tree (AST).  GDML allows for the definition 
-and assignment of variables.
-GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$, etc.
-The AST terminates on either expressions which evaluate to numbers or GDML variables.
-Internally, all \PYGEOMETRY{}
+and assignment of variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special 
+functions $\sin, \cos, \tan$, etc. The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally, all \PYGEOMETRY{} 
 classes use GDML expressions and not floating-point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
@@
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
-of placed instances of geometry (physical volumes) and meshes for CSG-derived solids.
-CSG mesh calculations are performed using a Binary Space Partitioning (BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++.
-In general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries.
-Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles.
-Before meshes are visualised or written to disk various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
+of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
+(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
+general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
+Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to disk 
+various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
 
@@
 If a user is creating and placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
-encompasses the daughter volumes.
-Overlaps between daughter volumes and the mother can be detected to, but it is desirable \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?
-And I'm not sure what the word ``efficiently'' means precisely in this context.} to have a mother volume
-shape that efficiently holds all of its daughters.
+encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected to, but it is desirable 
+% \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?  And I'm not sure what the word ``efficiently'' means precisely in this context.} 
+to have a mother volume shape that efficiently holds its daughters. This is not always the case for example assembly volumes.
 
@@
 When implementing geometry a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
-A  \PYGEOMETRY{} geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 volume hierarchy is sufficient 
-to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation $\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
+A  \PYGEOMETRY{} geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 
+volume hierarchy is sufficient to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation 
+$\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
 
@@
 %%%%%%%%%%%%%%%%% Adding properties to volumes
-Geometry needs to be augmented with other information for a complete RTMC simulation. Often other attributes need to be 
+Geometry needs to be augmented with other information for a complete MCRT simulation. Often other attributes need to be 
 assigned to regions of space for example material definition, magnetic field or optical properties. These physical properties 
@@
 \subsection{Overlap detection}
-All RTMC codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
-in such a situation.
-A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by performing an intersection operation between solid instances and determining if the resultant mesh is empty.
-Figure~\ref{fig:overlap} shows the potential overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters share a face.
-If the resulting intersection
-is non-null then the overlaps can be displayed side-by-side in the visualisation. 
+All MCRT codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
+in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by 
+performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows the potential 
+overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters 
+share a face. If the resulting intersection is non-null then the overlaps can be displayed side-by-side in the visualisation. 
 \begin{figure}[htbp]
@@
 has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters}^2)$. This might seem like a prohibitive computational cost, but worth it considering the potential 
-waste if small overlaps are present in the final RTMC simulation and large amounts of cluster CPU time is wasted.
-This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse.
-Due to the discrete nature of triangular meshes it is not possible to have perfect detection
+waste if small overlaps are present in the final MCRT simulation and large amounts of cluster CPU time is wasted. This algorithm clearly favours geometry 
+descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection 
 of overlaps, especially when curved surfaces are considered. The deviation of the meshes created from a solid can be controlled by the user reducing the 
@@
 
-%%%%%%%%%%%%%%%%% Graphical user interface
-% A basic Qt based graphical user interface is also available with \PYGEOMETRY{}.
-If a model has a large number of volumes defined in a hierarchical tree structure, it is % cumbersome for the user to find the logical or physical volume.
-
 \section{Rapid geometry modelling}
 Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
-the parameters of the geometry and visualise it.
-When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk from the internal memory representation.
-Some example code is presented in Listing~\ref{lst:pythonRapidModelling}.
-The structure should be familiar to regular
-users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}.
-First the \verb|Registry| is created to store all the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved as a GDML file or visualised using VTK.
+the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk 
+from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
+users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
+the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved 
+as a GDML file or visualised using VTK.
 
@@
 lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
-A region is a region of space which is formed of bodies and the operators + (intersection), $-$ 
-(complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
+A region is a region of space which is formed of bodies and the operators $+$ (intersection), $-$ 
+(complement) and $\:|\:$ (union), also parentheses to indicate the order of operations. FLUKA 
 has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
@@
 A Geant4 logical volume solid might need to be created from a FLUKA region composing of many zones, 
-so $R_1 = +z_1 | +z_2$, similarly a void is required to locate daughter volume placements which again 
-might also be converted to a region of multiple zones $R_2= +z_3 | +z_4$. So creating the FLUKA region is then 
+so $R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
+might also be converted to a region of multiple zones $R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
 \begin{eqnarray}
-R_1 - R_2 	& = & (+z_1 | +z_2) - ( +z_3 | +z_4) 			\\
+R_1 - R_2 	& = & (+z_1 \: | +z_2) - ( +z_3 \: | +z_4) 			\\
 			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)	
@@
 \begin{eqnarray}
-R_1 \cup R_2 	& = & (+z_1 | +z_2)  \cup ( +z_3 | +z_4) \\
-			& = & +z_1 | +z_2 |  +z_3 | +z_4
+R_1 \cup R_2 	& = & (+z_1 \: | +z_2)  \cup ( +z_3 \: | +z_4) \\
+			& = & +z_1 \: | +z_2 |  +z_3 \: | +z_4
 \label{eqn:setUnion}
@@
 \begin{eqnarray}
-R_1 \cap R_2 	& = & (+z_1 | +z_2) \cap ( +z_3 | +z_4) \\
+R_1 \cap R_2 	& = & (+z_1 \: | +z_2) \cap ( +z_3 \: | +z_4) \\
 			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4
@@
  geometry then multiple codes can be targeted without additional user effort. 
- \colorbox{yellow}{There are still a few outstanding technical  ssues, which should be discussed. }
+There are still a few outstanding technical issues with the conversion, which are discussed 
+in this section.
 
@@
 in the current version of \PYGEOMETRY{}.
+
+In general, recursive application of Equations \ref{eqn:setDiff},
+\ref{eqn:setUnion}, \ref{eqn:setIntersection} and \ref{eqn:logicalSubtraction} 
+can result in very complex regions when converting from Geant4/GDML to 
+FLUKA. The complexity of the final region expression can be compounded 
+if transformed to DNF. The final region Boolean expression can be simplified by 
+evaluating using the meshes for the surfaces, only retaining terms which 
+do not evaluation to a null mesh.
 
@@
 might be loaded.
-
-\begin{enumerate}
-%\item Degenerate body look up 
-%\item Bodies with/without transformation 
-% \item Non-convex solids, convex decomposition (TwistedBox, TwistedTrap, TwistedTrd, TwistedTube, Tessellated)
-% \item Scaled solid, Placement scale 
-% \item Replica, Division, Parameterised
-\item Recursive application of \ref{eqn:setDiff}, \ref{eqn:setUnion}, \ref{eqn:setIntersection}, \ref{eqn:logicalSubtraction} speed up using meshes
-% \item Issues with tessellated solids 
-\end{enumerate}
 
@@
 attributes must be performed by  the user after conversion to GDML as rarely 
-will CAD/CAM packages included the detailed information required for RTMC 
+will CAD/CAM packages included the detailed information required for MCRT 
 codes. Listing~\ref{lst:pythonCADLoading} shows 
@@
 The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
-where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using SPHINX a 
+where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
 Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependences. 
@@
 \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available for the code, which have 84\% coverage. 
+The unit tests also serve as minimal examples to help users understand the code operaton.
 
@@
 combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} will allow for the creation 
-of CAD B-REP decomposition algorithms.
+of CAD BREP decomposition algorithms.
 
@@
 fail in the Geant4 OpenGL viewer. This would involve using CGAL meshing in the \pyinline{G4Polyhedron}
-class. There is also
+class. %There is also
 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

@@
 % BREP (not B-REP)
+% region
 
@@
 It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
-solids can be mapped to a FLUKA \verb|REGION|. Some solids in Geant4 directly map to 
+solids can be mapped to a FLUKA region. Some solids in Geant4 directly map to 
 a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
@@
 \begin{tabular}{ l  l  } \hline
-Geant4 solid			& FLUKA region constuction		\\ \hline
+Geant4 solid			& FLUKA region construction		\\ \hline
 Box					& +2 XYP + 2 XZP + 2 YZP 		\\
@@
 \subsection{Disjunctive normal form and degenerate surfaces}
-Typically FLUKA will decompose a \verb|REGION| into disjunctive normal form (DNF), this normal form is 
+Typically FLUKA will decompose a region into disjunctive normal form (DNF), this normal form is 
 characterised as the union of intersections, so 
@@
 \end{equation}
-Defining \verb|REGION|s in terms of DNF allows the rapid test if a point is inside. Testing each zone 
+Defining regions in terms of DNF allows the rapid test if a point is inside. Testing each zone 
 $z_i$ of $R$ can terminate if a point is determined to be inside any of the convex zones $z_i$. In general 
@@
 explosion of the final DNF. There are well known algorithms to convert logical expressions to a DNF. 
-\PYGEOMETRY{} can simplify parentheses from a \verb|REGION| by creating a sympy~\cite{10.7717/peerj-cs.103} 
+\PYGEOMETRY{} can simplify parentheses from a region by creating a sympy~\cite{10.7717/peerj-cs.103} 
 expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm~\cite{6769983}. 
@@
 CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
+In general there is no requirement to avoid geometric overlap  of parts in a CAD file. This will result in overlaps of the solids in 
+the converted tessellated solids. This is avoided by shrinking each solid, this is done by computing the a normal ${\bf n}$  for each 
+vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so the new vertices are ${\bf v} - \epsilon {\bf n}$. The degree of shrinking 
+is user controllable.
 
@@
 and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}.
-
-\begin{enumerate}
-\item Mesh overlap and shrinking algorithm 
-\item Surface conversion and decomposition algorithm (future release)
-\end{enumerate}
 
@@
 
-There are many {\bf output format extensions} that can be considered for \PYGEOMETRY{}. 
+There are many output format extensions that can be considered for \PYGEOMETRY{}. 
 Geant4 geometry is primarily created by writing C++ programmes, so a output writer that 
@@
 
-There are more {\bf complex extensions} that can be considered for inclusion into \PYGEOMETRY{}.
+There are more complex extensions that can be considered for inclusion into \PYGEOMETRY{}.
 The meshes created by \PYGEOMETRY{} are generally of very high quality and can be used for a 
@@
 
-\PYGEOMETRY{} is principally a toolkit but various {\bf visualisation and user interface extensions} would 
+\PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
 significantly aid geometry creation workflows. A graphical frontend interface (GUI) so a user could create 
@@
 
-The {\bf conversion} which would most dramatically enhance the creation of geometry is CAD to Geant4/FLUKA
+The conversion which would most dramatically enhance the creation of geometry is CAD to Geant4/FLUKA
 without use use of a triangular or tetrahedral mesh. There are methods to decompose BREP solids to Geant4 and 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update
fix paper Acknowledgements section regarding funding

fix SymPy spelling

fix captions left/right -> above/below

a better overlap checking algorithm description

spellchecker

FLAIR -> flair

http://www.fluka.org/flair/

infinite body minimisation algorithm in paper

change Xtru table entry to be less incorrect

spelling

@@
 {\em Programming language: Python, C/C++}                         		\\
-{\em External routines/libraries: ANTLR, CGAL, FreeCAD, OpenCascade, sympy, VTK}           	\\
+{\em External routines/libraries: ANTLR, CGAL, FreeCAD, OpenCascade, SymPy, VTK}           	\\
 
@@
  to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error-prone, 
- although recent progress has been made \colorbox{yellow}{CITEXXX}.
+ although recent progress has been made \cite{WangNuclSciTech31-82-2020}.
 
@@
 and zero or more physical {\em daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume. This design permits large reuse 
-of objects, minismising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
+of objects, minimising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
 
@@
 %%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
-To exchange geometry descriptions between software packages the Geometry Descripition Mark-up Language (GDML) was developed~\cite{GDML}. 
+To exchange geometry descriptions between software packages the Geometry Description Mark-up Language (GDML) was developed~\cite{GDML}. 
 GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
@@
 \begin{algorithm}[h]
-  \SetKwFunction{Intersect}{Intersect}
-  \SetAlgoLined
-  \KwIn{Logical volume mesh $m$ with daughter volume meshes $d\in D$.}
-  \KwResult{Set, $S$, of overlapping pairs of meshes.}
-$V \longleftarrow \emptyset$\;
+  \SetKwProg{Int}{Function}{}{}
+  \SetKwFunction{Intersection}{Intersection}%
+  \SetKwProg{OCheck}{Function}{}{}
+  \KwData{Logical volume $v$ with mesh $m$ and daughter volume meshes $d\in D$.}
+  \KwResult{Set $S$ of non-null mesh intersections.}
+
+  % Define the function used in the algorithm
+  \Int{\Intersection{$n_1, n_2$}}{
+    \KwData{CSG meshes $n_1$ and $n_2$.}
+    \KwResult{The mesh intersection of $n_1$ and $n_2$.}
+  }
+  % The actual algorithm
+  $V \longleftarrow \emptyset$\tcp*[r]{Cache tried mesh pairs.}
   $S \longleftarrow \emptyset$\;
+
   \For{$d_1 \in D$}{
-  \If{\Intersect{$d_1, m$}}{
-    $S \longleftarrow S \cup \{(d_1, m)\}$\;
+    $p \longleftarrow$ \Intersection{$m,d_1$}\;
+    \If{$p$ is not null}{
+      $S \longleftarrow S \cup \{p\}$\;
     }
@@
       \If{$d_1 = d_2$ {\bf or} $(d_2, d_1) \in V$}{
-  continue\;
-}
-\If{\Intersect{$d_1, d_2$}}{
-  $S \longleftarrow S \cup \{(d_1, d_2)\}$\;
+        \textbf{continue}\;
+      }
+      $q \longleftarrow \Intersection{a,b}$\;
+      \If{$q$ is not null}{
+        $S \longleftarrow S \cup \{q\}$\;
       }
@@
   }
-
   \label{algo:overlap}
@@
 users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
-the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geomtery can be saved 
+the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
 as a GDML file or visualised using VTK.
@@
 \includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
-\caption{Example conversion of a simple FLUKA geometry to GDML. Left panel:
-the original FLUKA geometry displayed in FLAIR. Right panel: the GDML geometry
+\caption{Example conversion of a simple FLUKA geometry to GDML. Above:
+the original FLUKA geometry displayed in flair. Below: the GDML geometry
 viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
@@
 reduction has been performed, if the half-space is far away from the
-region's AABB, then it can result in a malformed Boolean.  This is
-demonstrated in Figure~\ref{fig:redundant-halfspace}.  Such
+region's AABB, then it can result in a malformed Boolean.  This algorithm is
+demonstrated in Algorithm~\ref{algo:redundant-halfspace}.  Such
 half-spaces are filtered from their respective regions during the
@@
 removed from the region during conversion.
+
+\begin{algorithm}
+
+  \KwData{FLUKA regions to be converted to GDML.}
+  \KwResult{GDML solids equivalent to the FLUKA regions built from
+    minimally-sized primitive solids}
+
+  \SetKwProg{ToGDML}{Function}{}{}
+  \SetKwFunction{ToGDMLSolid}{ToGDMLSolid}
+
+  % The function for translating a fluka body to a finite GDML solid.
+  \ToGDML{\ToGDMLSolid{$b, a$}}{
+    \KwData{FLUKA body $b$ with axis-aligned bounding box $a$.}
+    \KwResult{GDML solid equivalent to $b$ bounded by the volume $a$.}
+  }
+
+  \SetKwProg{RAABB}{Function}{}{}
+  \SetKwFunction{RegionAABB}{RegionAABB}
+  % The function for translating a fluka body to a finite GDML solid.
+  \RAABB{\RegionAABB{$r$}}{
+    \KwData{FLUKA region $r$.}
+    \KwResult{Axis-aligned bounding box (AABB) of the FLUKA region.}
+  }
+
+  $ B \longleftarrow \emptyset$\tcp*[r]{Map of regions to AABBs.}
+  \For{$r$ in regions to be converted}{
+    $B[r] \longleftarrow$ \RegionAABB{$r$}
+  }
+
+  \tcp{Map of bodies to minimal bounding boxes.}
+  $ E \longleftarrow \emptyset$\;
+  \For{$b$ in bodies in regions to be converted}{
+    \For{$r$ in regions in which body $b$ is used}{
+      $E[b] \longleftarrow E[b] \cup $ \RegionAABB($r$)\;
+    }
+  }
+
+  $ G \longleftarrow \emptyset$ \;
+  \For{body $b$ and AABB $a$ in $E$}{
+    \tcp{Map the fluka bodies to minimal GDML solids by converting with the
+    minimal AABB, $a$.}
+    $G \longleftarrow $ \ToGDMLSolid{$b, a$}\;
+  }
+  \For{$r$ in regions to be converted}{
+    build the corresponding GDML for $r$ from the set of minimal GDML
+    primitives in $G$.\;
+  }
+
+  \label{algo:overlap}
+  \caption{The infinite-body minimisation algorithm employed in the
+    conversion of Fluka to GDML.}
+\end{algorithm}
 
@@
 \includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
-\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
-the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
-viewed in FLAIR. The example is a sector bend dipole electromagnet.}
+\caption{Example conversion of a simple GDML geometry to FLUKA, above:
+the original model in \PYGEOMETRY{}, below: the converted FLUKA geometry
+viewed in flair. The example is a sector bend dipole electromagnet.}
 \label{fig:gdml-flair}
@@
 Tet					& +4 PLA						\\
-Xtru					& +$N_{\rm plane} N_{\rm point}$ PLA \\
+Xtru					& +$N$ PLA \\
 TwistedBox			& +$N$ PLA					\\
@@
 when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
-need to have the daughter  solids $S_{{\rm daugher},i}$ subtracted. So a solid which can be converted 
+need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. So a solid which can be converted 
 to a region $S_{\rm region}$ is then 
@@
 explosion of the final DNF. There are well known algorithms to convert logical expressions to a DNF. 
-\PYGEOMETRY{} can simplify parentheses from a region by creating a sympy~\cite{10.7717/peerj-cs.103} 
+\PYGEOMETRY{} can simplify parentheses from a region by creating a SymPy~\cite{10.7717/peerj-cs.103} 
 expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm~\cite{6769983}. 
@@
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compound}
-card. Geant4 also defines a set of standard materials from NIST  \colorbox{yellow}{CITEXXX NIST}. so a user can just specify something like 
+card. Geant4 also defines a set of standard materials \cite{Geant4MaterialDB} or compounds from the US National Institute 
+of Standards and Technology (NIST) \colorbox{yellow}{CITEXXX NIST}. so a user can just specify something like 
 \pyinline{G4_STAINLESS-STEEL}, \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
@@
 a mother will create a very complex non-DNF region which is inefficient when viewed in 
-FLAIR and used for simulation in FLUKA. A geometry designer can avoid this by 
+flair and used for simulation in FLUKA. A geometry designer can avoid this by
 restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
@@
 \includegraphics[width=0.9\columnwidth]{./model-scene/SectorBend.pdf}
-\caption{Example conversion of a simple CAD (STEP) geometry (sector bend dipole electromagnet) to GDML, left panel:  
-the original model in FreeCAD, right panel: the GDML geometry 
-viewed in \PYGEOMETRY{}. }
+\caption{Example conversion of a simple CAD (STEP) geometry (sector bend
+  dipole electromagnet) to GDML, above: the original model in FreeCAD,
+  below: the GDML geometry viewed in \PYGEOMETRY{}. }
 \label{fig:cad-gdml}
@@
 from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (modelled in 
-Flair). Each different file is loaded using \PYGEOMETRY{} reader class and the placed as a physical volume. The final composite 
+flair). Each different file is loaded using \PYGEOMETRY{} reader class and the placed as a physical volume. The final composite 
 geometry is shown in Figure~\ref{fig:model}. It must be noted when this complete geometry is written to GDML and loaded into 
@@
 where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
-Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependences. 
+Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependencies. 
 \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} and \pyinline{pyg4ometry.pycgal} 
@@
 \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available for the code, which have 84\% coverage. 
-The unit tests also serve as minimal examples to help users understand the code operaton.
+The unit tests also serve as minimal examples to help users understand the code operation.
 
 \section{Conclusions and discussion}
-The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in Monte Carlo
+The authors believe that tools to quickly create, either ab initio or by conversion geometry usable in Monte Carlo
 particle transport programmes will save significant amounts of user effort and ultimately 
@@
 uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
-allows the programatic control of geometry creation or modification. This approach allows the integration of 
+allows the programmatic control of geometry creation or modification. This approach allows the integration of 
 other available tools \colorbox{yellow}{CITEXXX DAGMC, CAD stuff} into an unified workflow.
@@
 geometry from one format to another, but concentrate on smaller conversions of constituent parts. Workflows should focus 
-on conversion from a primary format and then create conversions to another format as the need arrises. This paper outlines 
-the creation of geometry using \PYGEOMETRY{}, that geometry is loaded into Geant4, FLAIR and FLUKA but detailed 
+on conversion from a primary format and then create conversions to another format as the need arises. This paper outlines 
+the creation of geometry using \PYGEOMETRY{}, that geometry is loaded into Geant4, flair and FLUKA but detailed 
 studies of the MCRT simulation performance is beyond the scope of this publication and will be addressed in the future.
@@
 Geant4 geometry is primarily created by writing C++ programmes, so a output writer that 
-converts the \PYGEOMETRY() in memory representation to C++ will allow rapid geometry 
+converts the \PYGEOMETRY{} in memory representation to C++ will allow rapid geometry 
 modelling but . This is not implemented in the current version but could be relatively quickly implemented
@@
 \PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
-significantly aid geometry creation workflows. A graphical frontend interface (GUI) so a user could create 
+significantly aid geometry creation workflows. A graphical user interface (GUI) so a user could create 
 geometry without any programming knowledge would expand the number of potential users. \PYGEOMETRY{}
@@
 without use use of a triangular or tetrahedral mesh. There are methods to decompose BREP solids to Geant4 and 
-FLUKA like CSG geometry \colorbox{yellow}{CITEXXX MCCAD}. The FreeCAD/OpenCASCADE interface
-combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} will allow for the creation 
-of CAD BREP decomposition algorithms.
+FLUKA like CSG geometry \cite{LuFusionEngineeringAndDesign124-2017, WangNuclSciTech31-82-2020}. 
+The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} 
+will allow for the creation of CAD BREP decomposition algorithms.
 
@@
 \PYGEOMETRY{} and FLUKA. \PYGEOMETRY{} can be used to a testing ground for ideas prior to 
-implementation in Geant4 or FLAIR. An example of this the VTK visualisation system implemented in 
+implementation in Geant4 or flair. An example of this the VTK visualisation system implemented in 
 \PYGEOMETRY{}, which could be used in Geant4 to rendering of Boolean solids which frequently 
@@
 \section{Acknowledgements}
-This work has been supported by STFC grants XXX and XXX. Multiple undergraduate and masters students 
-have contributed to the code for their degree project work, Simon Williams, Benjamin Shellswell, Joshua Albrecht. 
-STB has benefited from discussions with and insight of Vasilis Vlachoudis (CERN) on FLUKA geometry and FLAIR. 
-Cédric Hernalsteens (ULB/CERN) and Alistair Butcher (RHUL) also made useful contributions to the code.
+
+The development of \PYGEOMETRY{} has received funding from Science and
+Technology Research council grant ``The John Adams Institute for
+Accelerator Science'' ST/P00203X/1 through the John Adams Institute at
+Royal Holloway, and Royal Holloway Impact Acceleration Account.  Multiple
+undergraduate and masters students have contributed to the code for their
+degree project work, Simon Williams, Benjamin Shellswell, Joshua Albrecht.
+STB has benefited from discussions with and insight of Vasilis Vlachoudis
+(CERN) on FLUKA geometry and flair.  Cédric Hernalsteens (ULB/CERN) and
+Alistair Butcher (RHUL) also made useful contributions to the code.
 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

--- 2020-09-15 public/paper/pyg4ometry.tex
@@
 allows the programatic control of geometry creation or modification. This approach allows the integration of 
-other available tools \colorbox{yellow}{CITEXXX DAGMC, CAD stuff} into an unified workflow.
+other available tools \cite{DavisNIMA915-65} into an unified workflow.
 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

--- 2020-09-15 public/paper/pyg4ometry.tex
@@
 \begin{abstract}
+Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is a 
+error prone and time consuming task. Simulating a system often requires geometry from different sources and modelling 
+environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
+that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
+geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
+to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with 
+examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
+extensions and future work.
 \end{abstract}
@@
 allows the programmatic control of geometry creation or modification. This approach allows the integration of 
-other available tools \colorbox{yellow}{CITEXXX DAGMC, CAD stuff} into an unified workflow.
+other available tools \cite{DavisNIMA915-65} into an unified workflow.
 
@@
 without use use of a triangular or tetrahedral mesh. There are methods to decompose BREP solids to Geant4 and 
-FLUKA like CSG geometry \cite{LuFusionEngineeringAndDesign124-2017, WangNuclSciTech31-82-2020}. 
+FLUKA like CSG geometry \cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 
 The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

@@
 
+% Python
 % part features
@@
 geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
-to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with 
+to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  
 examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
@@
 where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
-Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependencies. 
-\PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} and \pyinline{pyg4ometry.pycgal} 
-in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using \pyinline{setuptools}. All aspects of 
-\PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available for the code, which have 84\% coverage. 
-The unit tests also serve as minimal examples to help users understand the code operation.
+Python documentation generator (\url{Monte Carlo Radiation Transport (MCRT)}). \PYGEOMETRY{} uses mature packages 
+available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
+and \pyinline{pyg4ometry.pycgal} in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using 
+\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
+for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.
 

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

@@
 
-  \label{algo:overlap}
+  \label{algo:redundant-halfspace}
   \caption{The infinite-body minimisation algorithm employed in the
@@
 where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
-Python documentation generator (\url{Monte Carlo Radiation Transport (MCRT)}). \PYGEOMETRY{} uses mature packages 
+Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
 available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
@@
 STB has benefited from discussions with and insight of Vasilis Vlachoudis
-(CERN) on FLUKA geometry and flair.  Cédric Hernalsteens (ULB/CERN) and
+(CERN) on FLUKA geometry and Flair.  Cédric Hernalsteens (ULB/CERN) and
 Alistair Butcher (RHUL) also made useful contributions to the code.

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

@@
 and acts as a simple to use interface to OpenCASCADE.  A STEP CAD file 
-could be considered as a hierarchical tree of part features and part assemblies, 
+could be considered as a hierarchical tree of parts and part assemblies, 
 where a part assembly is a collection of part features. A part feature can be used 
@@
 simulations.  Triangular meshes also have application  for GPU accelerated photon tracking in 
-liquid noble dark matter detectors. Paraview/VTK are being standard software for complex 3D visualisation and 
+liquid noble dark matter detectors. Paraview/VTK are becoming standard software for complex 3D visualisation and 
 the ability to write geometry to formats readily loaded and manipulated by these programs will 

### 2020-09-16 public/paper/pyg4ometry.tex
citations for Nef Polyhedra and convex polyhedra decomposition
added cgal 3d nef polyhedra and convex decomposition bib items

@@
 TwistedTube and Tessellated. The second classification of non convex solids are converted to CGAL 
-Nef polyhedra \colorbox{yellow}{CITEXXX} and decomposed to convex polyhedra using a 
-\colorbox{yellow}{CITEXXX} algorithm.
+Nef polyhedra~\cite{cgal:hk-bonp3-20b} and decomposed to convex polyhedra~\cite{cgal:h-emspe-20b}.
 

### 2020-09-16 public/paper/pyg4ometry.tex
remove todo cite NIST, complete malformed sentence.
I don't think we need to cite NIST in this instance any more than we need
to cite when referring to CERN by name..  unless we can get a specific
reference to where the data comes from.  But I can't find it.

@@
 card. Geant4 also defines a set of standard materials \cite{Geant4MaterialDB} or compounds from the US National Institute 
-of Standards and Technology (NIST) \colorbox{yellow}{CITEXXX NIST}. so a user can just specify something like 
-\pyinline{G4_STAINLESS-STEEL}, \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
+of Standards and Technology (NIST), so a user can, for example, just
+specify the name \pyinline{G4_STAINLESS-STEEL} and \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
 cards during the conversion. This database is updated by running a small Geant4 program to output the appropriate

### 2020-09-16 public/paper/pyg4ometry.tex
my attempt at a slightly better introduction to gdml2fluka section.
describe what a region is as soon as we refer to it.  (slight reordering)

rewording of the description of a region so that we mention zones, which I
think are important, and a more top-down description, starting with the
definition of a region, then to a zone, and then explaining the zone in
terms of primtives.

@@
 \section{GDML to FLUKA conversion}
-It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
-solids can be mapped to a FLUKA region. Some solids in Geant4 directly map to 
-a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
-lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
-A region is a region of space which is formed of bodies and the operators $+$ (intersection), $-$ 
-(complement) and $\:|\:$ (union), also parentheses to indicate the order of operations. FLUKA 
-has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
-benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
-plane (PLA), Z-axis aligned cylinder (ZCC), Z-axis aligned elliptical cylinder (ZEC), 
-sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
+It is relatively straight forward to convert Geant4 geometry to FLUKA. Each
+of the Geant4 solids can be mapped to a FLUKA region.  A region is a region
+of space defined by a material and the Boolean disjunction (a union using
+the operator~$\:|\:$ in free format geometry) of one or more
+zones. Each zone is then defined in terms of the conjunction (intersection
+with~$+$, subtraction with~$-$) of one or more primitive bodies, as well as
+parentheses to determine the order of operations within the zone.  FLUKA
+has 20 of these primitive bodies, listed in Table~\ref{tab:Fluka2Geant4}
+and, in general, infinite extent bodies have tracking accuracy and
+efficiency benefits over finite ones. Key for conversion are XY-, XZ-,
+YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), Z-axis aligned cylinder
+(ZCC), Z-axis aligned elliptical cylinder (ZEC), sphere (SPH), truncated
+right-angle cone (TRC) and general quadric surface (QUA). Some solids in
+Geant4 directly map to a single FLUKA body, others require the construction
+of a simple FLUKA CSG tree combining these
+primitives. Table~\ref{tab:geant2fluka} lists the mapping between Geant4
+solids and the bodies used to compose a FLUKA region.
 \begin{figure}

### 2020-09-16 public/paper/pyg4ometry.tex
emph-correctness, etc.

@@
     urlcolor=cyan,
-    pdftitle={Sharelatex Example},
+    pdftitle={Pyg4ometry paper},
     bookmarks=true,
@@
 
-% Python
-% part features
-% part assembly
-% physical volume
-% logical volume
-% daughter volume
-% mother volume
-% Reader
-% scene
-% API
-% AST 
-% BREP (not B-REP)
-% region
+% Python           "Python" everywhere
+% part features   emph'd on first use
+% part assembly   emph'd on first use
+% physical volume  emph'd on first use
+% logical volume  emph'd on first use
+% daughter volume emph'd on first use
+% mother volume   emph'd on first use
+% Reader     emph'd on first use
+% scene      emph not on first use, but first novel/unconventional use.
+% API        paren on first use
+% AST        paren on first use
+% BREP (not B-REP)  BREP everywhere
+% region    emph'd on first use
+% zone      emph'd on first use
+% subzone   emph'd on first use
 
@@
 Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
-Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\em logical volumes} 
-and {\em physical volumes}. A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field 
-and zero or more physical {\em daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume. This design permits large reuse 
+Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this \emph{logical volumes}
+and \emph{physical volumes}. A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field 
+and zero or more \emph{daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume. This design permits large reuse 
 of objects, minimising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated {\em Reader} class is implemented, so \verb|gdml.Reader|, 
+For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented, so \verb|gdml.Reader|,
 \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which 
@@
 %%%%%%%%%%%%%%%%% Volume bounding
-If a user is creating and placing multiple daughter volumes within a {\em mother} volume then it is the users responsibility to create a solid which fully 
+If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the users responsibility to create a solid which fully 
 encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected to, but it is desirable 
@@
 FLUKA geometry is based upon a limited set of primitives (referred to as
-\textit{bodies}) which can be combined using Boolean operations. A
-\textit{zone} consists of one or more bodies or \textit{subzones} combined
+\emph{bodies}) which can be combined using Boolean operations. A
+\emph{zone} consists of one or more bodies or \emph{subzones} combined
 using intersections and subtractions.  Zones may then be further combined
-using union operations to form \textit{regions}, which is defined as the
+using union operations to form \emph{regions}, which is defined as the
 union of one or more zones, as well as a material.
@@
 command. Figure~\ref{fig:lattice} demonstrates this capability, and. The
-arbitrarily complex \textit{basic unit} can be defined once and used
-multiple times by placing one or more empty \textit{lattice cells} with the
+arbitrarily complex \emph{basic unit} can be defined once and used
+multiple times by placing one or more empty \emph{lattice cells} with the
 associated roto-translation from that \fluka{lattice} cell to the basic
@@
 and acts as a simple to use interface to OpenCASCADE.  A STEP CAD file 
-could be considered as a hierarchical tree of parts and part assemblies, 
-where a part assembly is a collection of part features. A part feature can be used 
+could be considered as a hierarchical tree of parts and \emph{part assemblies}, 
+where a part assembly is a collection of \emph{part features}. A part feature can be used 
 to create a triangular mesh which can be used to create a \PYGEOMETRY{} tessellated solid. The placement 
@@
 and workflows. A fictitious beam line was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite 
-{\it scene} which consists of the different examples presented in this paper. The beam line consists of a vacuum chamber 
+\emph{scene} which consists of the different examples presented in this paper. The beam line consists of a vacuum chamber 
 (modelled in \PYGEOMETRY{}), a vacuum gate value (STL from the manufacturer), a triplet of quadrupole magnets (exported 

### 2020-09-16 public/paper/pyg4ometry.tex
comment outlined at top of file detailing annoying style checklist
time-consuming, error-prone, AN error not A error

--- 2020-09-16 public/paper/pyg4ometry.tex
@@
 
+% STYLE AND OTHER ANNOYING STUFF:
+
+%%%% HYPHENATION:
 % Python           "Python" everywhere
+% BREP (not B-REP)  BREP everywhere
+
+%%%% EMPH
 % part features   emph'd on first use
@@
 % AST        paren on first use
-% BREP (not B-REP)  BREP everywhere
 % region    emph'd on first use
@@
 % subzone   emph'd on first use
+
+%% TYPEWRITER /
 
@@
 \begin{abstract}
-Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is a 
-error prone and time consuming task. Simulating a system often requires geometry from different sources and modelling 
+Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is an
+error-prone and time-consuming task. Simulating a system often requires geometry from different sources and modelling 
 environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 

### 2020-09-16 public/paper/pyg4ometry.tex
computer-aided design should not be capitalised

@@
 error-prone and time-consuming task. Simulating a system often requires geometry from different sources and modelling 
-environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
+environments, including a range of MCRT codes and computer-aided design (CAD) tools. \PYGEOMETRY{} is a Python library 
 that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 

### 2020-09-16 public/paper/pyg4ometry.tex
provides import -> provides importation + hyphenation fix

@@
 environments, including a range of MCRT codes and computer-aided design (CAD) tools. \PYGEOMETRY{} is a Python library 
-that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
-geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
+that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML)-based
+geometry used in simulations. \PYGEOMETRY{} provides importation of CAD files to GDML tessellated solids, conversion of GDML geometry
 to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  

### 2020-09-16 public/paper/pyg4ometry.tex
fix first sentence, was malformed and didn't make sense

@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
+There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programmes 
 include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}. 

### 2020-09-16 public/paper/pyg4ometry.tex
add comma to make list less awkward to read and plura simulation

@@
  Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical 
-imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a 
+imaging and therapy, and space radiation environment simulations are some examples. A fundamental requirement of all of the codes is to supply a 
 computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is 

### 2020-09-16 public/paper/pyg4ometry.tex
don't say MCRT twice right next to each other
"The requirement" is misplaced here..  what requirement?

@@
 typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no 
-standard geometry format used across MCRT codes, with each MCRT code typically using its own unique format. The requirement of a geometry system 
+standard geometry format used across MCRT codes, with each code typically using its own unique format. A geometry system 
 that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport

### 2020-09-16 public/paper/pyg4ometry.tex
better ordering of sentences in paragraph
"ease of use of a user" is redundant

@@
 typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no 
-standard geometry format used across MCRT codes, with each code typically using its own unique format. A geometry system 
+standard geometry format used across MCRT codes, with each code typically using its own unique format. A user will typically not have geometry in FLUKA and Geant4 for example. A geometry system 
 that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport
- codes. Typically an MCRT code user will not have geometry in FLUKA and Geant4 for example. The file formats used for geometry are generally focused 
- on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually 
+ codes.  The file formats used for geometry are generally focused 
+ on the computational efficiency of a particle tracking task and not ease of use. In addition to the creation of geometry files for RT programs, usually 
  computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not 

### 2020-09-16 public/paper/pyg4ometry.tex
amenable to not amenable for
remove word

@@
  computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not 
- amenable for MCRT programs.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
- error-free geometry files, convert between common MCRT program geometry formats and load CAD models.
+ amenable to MCRT programs.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
+ error-free geometry files, convert between common MCRT geometry formats and load CAD models.
 

### 2020-09-16 public/paper/pyg4ometry.tex
allows not allow
describe root as a framework, it's a program and a library

@@
 Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. 
-\PYGEOMETRY{} allow the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
+\PYGEOMETRY{} allows the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
 is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by 
@@
 
-There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis program, 
+There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework, 
 can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 

### 2020-09-16 public/paper/pyg4ometry.tex
non breaking space before \cite

@@
 can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
-products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
+products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
 geometry into formats usable by MCRT codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 

### 2020-09-16 public/paper/pyg4ometry.tex
fix run-on sentence

@@
 products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
-geometry into formats usable by MCRT codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
+geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
 (or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a 

### 2020-09-16 public/paper/pyg4ometry.tex
don't say CAD twice so close, this is less akwaard
oxford comma for clarity in list

@@
 geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
-(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a 
-large number of parts. Exporting, assigning material to and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
+(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
+large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
 provide a complete set of tools to efficiently create complex geometries.

### 2020-09-16 public/paper/pyg4ometry.tex
fix missing word "code" after mcrt
hypen

@@
 (or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
-large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
+large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. The existent set of software does not 
 provide a complete set of tools to efficiently create complex geometries.
 
-This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design 
+This paper is structured as follows, first a brief radiation transport-focused introduction to computer descriptions of geometry, followed by an explanation of the design 
 and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 

### 2020-09-16 public/paper/pyg4ometry.tex
comma in list of adjectives
fix space before comma

@@
 and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
-FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from 
+FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite, complex system consisting of components drawn from 
 all the supported  geometry input files formats.
@@
 Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
-geometry, including constructive solid geometry (CSG) , boundary representation (BREP) and tessellated polygons, which are described 
+geometry, including constructive solid geometry (CSG), boundary representation (BREP) and tessellated polygons, which are described 
 briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.

### 2020-09-16 public/paper/pyg4ometry.tex
"to name a few" sounds too colloquial
Mark-up should not be hyphenated

@@
 %%%%%%%%%%%%%%%%% Tessellated polygons
-Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and 
-more modern variants being PLY, OBJ to name a few. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
+Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL with
+more modern examples including PLY and OBJ. For solids with curved faces a tessellated mesh will always give an approximate description. As the mesh 
 deviation distance from the solid decreases the number of polygons increases and with it the memory consumption and execution time of the MCRT simulation.
@@
 %%%%%%%%%%%%%%%%% Geant Detector Mark-up Language
-To exchange geometry descriptions between software packages the Geometry Description Mark-up Language (GDML) was developed~\cite{GDML}. 
+To exchange geometry descriptions between software packages the Geometry Description Markup Language (GDML) was developed~\cite{GDML}. 
 GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 

### 2020-09-16 public/paper/pyg4ometry.tex
remove redundant word

@@
 To exchange geometry descriptions between software packages the Geometry Description Markup Language (GDML) was developed~\cite{GDML}. 
-GDML is an XML-based description of Geant4 geometry description. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
-GDML format and it is commonly used as an exchange format for Geant4 geometries.
+GDML is an XML-based description of Geant4 geometry. Geant4 and ROOT~\cite{fons_rademakers_2019_3895860} can read and write 
+GDML and it is commonly used as an exchange format for Geant4 geometries.
 

### 2020-09-16 public/paper/pyg4ometry.tex
capitalise Geant4

@@
 \PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
-geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
+Geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
 exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats 

### 2020-09-16 public/paper/pyg4ometry.tex
replace comma with and

@@
 \PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
-Geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
+Geant4 detector construction and \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
 exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats 

### 2020-09-16 public/paper/pyg4ometry.tex
reword and better linebreaking

--- 2020-09-16 public/paper/pyg4ometry.tex
@@
 \section{\PYGEOMETRY{} design and layout}
-\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \pyinline{pyg4ometry.geant4} contains all classes for 
-Geant4 detector construction, \pyinline{pyg4ometry.gdml} provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
-exporting other geometry formats  \pyinline{pyg4ometry.fluka}, \pyinline{pyg4ometry.stl} and \pyinline{pyg4ometery.freecad} and converting between file formats 
-\verb|pyg4ometry.convert|.
+\PYGEOMETRY{} is a Python package consisting of semi-independent sub-packages. The sub-package \verb|pyg4ometry.geant4| contains all classes for 
+Geant4 detector construction and \verb|pyg4ometry.gdml| provides the functionality for reading and writing GDML files. There are sub-packages for importing and 
+exporting other geometry formats: \verb|pyg4ometry.fluka|, \verb|pyg4ometry.stl| and \verb|pyg4ometery.freecad|.  Lastly, the sub-package \verb|pyg4ometry.convert| 
+is used for conversions between formats.
 

### 2020-09-16 public/paper/pyg4ometry.tex
reads better

@@
 
-The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
+The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical volumes, physical volumes, GDML parameters and material classes.
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 

### 2020-09-16 public/paper/pyg4ometry.tex
kept as close as possible over kept as close

@@
 The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical volumes, physical volumes, GDML parameters and material classes.
-The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
+The constructors of the Python classes are kept as close to the original Geant4 C++ implementation as possible so that \PYGEOMETRY{} users do not have to learn 
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} 

### 2020-09-16 public/paper/pyg4ometry.tex
It's not necessaty to state the fully-qualified name of the class here
Benefit is that this reads much better.

@@
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation as possible so that \PYGEOMETRY{} users do not have to learn 
-a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} 
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
 class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 

### 2020-09-16 public/paper/pyg4ometry.tex
the Box class is in Pyg4ometry, not Python
it's the pyhton initialiser, not the constructor

@@
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
-class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
+class in \PYGEOMETRY{}. The Python object initialiser is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
 GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 

### 2020-09-16 public/paper/pyg4ometry.tex
"kept a similar" isn't english
Registry -> Registry instance

@@
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
-class in \PYGEOMETRY{}. The Python object initialiser is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
+class in \PYGEOMETRY{}. The Python object initialiser is very similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
 GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
@@
 For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented, so \verb|gdml.Reader|,
-\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which 
+\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| instance which 
 can be used or manipulated by the user. 

### 2020-09-16 public/paper/pyg4ometry.tex
clearer, easier to read
colon over ", so"

@@
 a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
-class in \PYGEOMETRY{}. The Python object initialiser is very similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
+class in \PYGEOMETRY{}. The Python object initialisers are very similar to their corresponding Geant4 C++ constructors, but the length definitions are those used by GDML. For example, 
 GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
@@
 %%%%%%%%%%%%%%%%%  Input and output  
-For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented, so \verb|gdml.Reader|,
+For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented: \verb|gdml.Reader|,
 \verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| instance which 

### 2020-09-16 public/paper/pyg4ometry.tex
"output cosnists of writing to GDML" is wrong
we support writing to numerous different formats, gdml, fluka, and STL i
think, at least..  so not sell ourselves short.
follows closely -> closely follows
"specifices geometry" is almost meaningless

@@
 can be used or manipulated by the user. 
-Output consists of taking the registry and writing the appropriate GDML.
+Output consists of taking the registry and writing to file with the desired format.
 
 %%%%%%%%%%%%%%%%%  Internal data representation
-The internal data representation follows closely the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
-elements of a GDML file. As a \PYGEOMETRY{} user specifies geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
+The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main 
+elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
 is written to disk as a GDML file.\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.

### 2020-09-16 public/paper/pyg4ometry.tex
is written to disk -> can be written to disk

@@
 elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
-is written to disk as a GDML file.\verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
+can be written to disk as a GDML file. \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 

### 2020-09-16 public/paper/pyg4ometry.tex
Avoiding starting a word with verbatim so spacing is correct
in previous way, we have the . and the R of registry almost on top of each
other and it looks bad
delete word

@@
 elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
-can be written to disk as a GDML file. \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
+can be written to disk as a GDML file. Multiple \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
 
@@
 multiple replicas of a volume in a Cartesian, cylindrical or spherical grid is known as a Replica Volume. A Division Volume breaks a primitive into segments 
-in either a Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
+in either Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
 allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 

### 2020-09-16 public/paper/pyg4ometry.tex
slightly better gdml loop sentence description

@@
 in either Cartesian or cylindrical polar coordinates. A parametrised volume allows for the arbitrary multiple placement of solids where the parameters are 
-allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML are allowed 
-to be repeated with varying parameters. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
+allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML can be 
+ repeated with varying parameters based on the loop index. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
 future release.

### 2020-09-16 public/paper/pyg4ometry.tex
and -> but
include -> including

@@
 allowed to vary for each placement.  Another way in GDML to create parametrised solids or volumes is GDML loops, where sections of GDML can be 
- repeated with varying parameters based on the loop index. GDML loop loading and expansion are not supported by \PYGEOMETRY{} and will be implemented in a 
+ repeated with varying parameters based on the loop index. GDML loop loading and expansion are not supported by \PYGEOMETRY{} but will be implemented in a 
 future release.
@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three dimensional mesh description of all solids (include Booleans) is exceptionally useful, for visualisation and other algorithms, such as overlap 
+Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful, for visualisation and other algorithms, such as overlap 
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 

### 2020-09-16 public/paper/pyg4ometry.tex
del comma

@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful, for visualisation and other algorithms, such as overlap 
+Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
 detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 

### 2020-09-16 public/paper/pyg4ometry.tex
Vertex-Face shouldn't be capitalised in middle of sentence
prefer written to disk to written to file

@@
 Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
-detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
+detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent 
 of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
@@
 general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
-Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to disk 
+Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file 
 various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
@@
 Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
-the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to disk 
+the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to file 
 from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 

### 2020-09-16 public/paper/pyg4ometry.tex
missing apostrophe

@@
 %%%%%%%%%%%%%%%%% Volume bounding
-If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the users responsibility to create a solid which fully 
+If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully 
 encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected to, but it is desirable 

### 2020-09-16 public/paper/pyg4ometry.tex
delete word
fix awkard sentence

@@
 If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully 
-encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected to, but it is desirable 
+encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable 
 % \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?  And I'm not sure what the word ``efficiently'' means precisely in this context.} 
-to have a mother volume shape that efficiently holds its daughters. This is not always the case for example assembly volumes.
+to have a mother volume shape that efficiently holds its daughters. However, there are exceptions to this rule in the form of assembly volumes.
 

### 2020-09-16 public/paper/pyg4ometry.tex
avoid stunted and overly terse english
full stop at end of eqn as they're technically part of the prose
also add some words before the equation so  it flows

@@
 \includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
-\caption{Placement of physical volume inside a logical volume.}
+\caption{The placement of a physical volume inside a logical volume.}
 \label{fig:lvToPv}
@@
 \begin{eqnarray}
-\mathbf{M} 	& = &  \mathbf{S}_d  \mathbf{R}_d \\
-\mathbf{T} 	& = &  \mathbf{T}_d
+\mathbf{M} 	& = &  \mathbf{S}_d  \mathbf{R}_d\,, \\
+\mathbf{T} 	& = &  \mathbf{T}_d\,.
 \end{eqnarray}
 %
-If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ 
+If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ are expressed as
 \begin{eqnarray}
-\mathbf{M}_w	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d				\label{eqn:worldToDaughter1}\\
-\mathbf{T}	_w 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m  \label{eqn:worldToDaughter2}
+\mathbf{M}_w	  	& = & \mathbf{M}_m \mathbf{M}_d  = \mathbf{S}_m \mathbf{R}_m  \mathbf{S}_d \mathbf{R}_d\, ,				\label{eqn:worldToDaughter1}\\
+\mathbf{T}	_w 		& = & \mathbf{M}_m \mathbf{T}_d + \mathbf{T}_m= \mathbf{S}_m \mathbf{R}_m \mathbf{T}_d + \mathbf{T}_m\,,  \label{eqn:worldToDaughter2}
 \end{eqnarray}

### 2020-09-16 public/paper/pyg4ometry.tex
remove wooly language with specific statement of what it is

@@
 colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
-stored in the Logical Volume and can be  displayed separately to allow a user to understand the reason for 
-the overlaps.
+stored in the Logical Volume and can be  displayed separately to allow a user to visually identify and debug the the overlaps.
 

### 2020-09-16 public/paper/pyg4ometry.tex
insert comma
show TYPES of overlaps, not just overlaps

@@
 Geometry needs to be augmented with other information for a complete MCRT simulation. Often other attributes need to be 
-assigned to regions of space for example material definition, magnetic field or optical properties. These physical properties 
+assigned to regions of space, for example material definition, magnetic field or optical properties. These physical properties 
 can be used to define the visualisation attributes of a volume.
@@
 in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by 
-performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows the potential 
+performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
 overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters 

### 2020-09-16 public/paper/pyg4ometry.tex
join tiny paragraph about overlap algo with one that follows
link the point that overlap detection favours geometry use with geant4

@@
 algorithm proceeds as shown in Algorithm~\ref{algo:overlap}.
-
 For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids have an average number of faces $n$, clearly this algorithm 
@@
 waste if small overlaps are present in the final MCRT simulation and large amounts of cluster CPU time is wasted. This algorithm clearly favours geometry 
-descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection 
+descriptions which have a high degree of logical volume reuse, however this is also true of Geant4 as a whole, so the user will likely be inclined to design along such lines regardless.
+Due to the discrete nature of triangular meshes it is not possible to have perfect detection 
 of overlaps, especially when curved surfaces are considered. The deviation of the meshes created from a solid can be controlled by the user reducing the 

### 2020-09-16 public/paper/pyg4ometry.tex
delete comma
replacing pyinline with verb looks better in this instance

@@
 Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
-the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to file 
+the parameters of the geometry and visualise it.  When a user has achieved the desired geometry without geometry overlaps, a GDML file can be written to file 
 from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
-users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
+users of Geant4 or GDML, apart from the new class described in the previous section called the \verb|Registry|. First the \verb|Registry| is created to store all 
 the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved

### 2020-09-16 public/paper/pyg4ometry.tex
I don't think we can claim to be wrapping Geant4 in Python
I know what is meant but still, I think it is not ideal to write this.

@@
 The \PYGEOMETRY{} Python code in the example is approximately as expressive 
-as the GDML it writes. The benefit of wrapping GDML/Geant4 in Python allows 
-to very rapid prototyping of geometry without concerns of compilation of C++ (in the 
-case of Geant4) or writing well formed XML (in the case of GDML). Effectively
+as the GDML it writes. The benefit of wrapping GDML in Python is that it allows 
+ very rapid prototyping of geometry without concerns of C++ compilation  (in the 
+case of implementing the geometry directly in Geant4) or writing well formed XML (in the case of GDML). Effectively
 the Python interpreter checks input for syntax errors when using \PYGEOMETRY{} classes. 

### 2020-09-16 public/paper/pyg4ometry.tex
viewed using pyg4ometry, not in. it's viewed in vtk...

@@
 the original FLUKA geometry displayed in flair. Below: the GDML geometry
-viewed in \PYGEOMETRY{}. The example is a Faraday cup used to capture
+viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
 and measure accelerator beam charge.}
@@
   dipole electromagnet) to GDML, above: the original model in FreeCAD,
-  below: the GDML geometry viewed in \PYGEOMETRY{}. }
+  below: the GDML geometry viewed using \PYGEOMETRY{}. }
 \label{fig:cad-gdml}

### 2020-09-16 public/paper/pyg4ometry.tex
reword my bit
capital Zone and Region referring to the classes

@@
 GDML solids.  The translation of infinite bodies to equivalent finite
-solids is one of the main steps involved in the conversion process.
+solids is one of the main and most involved steps in the conversion process.
 This mapping is possible because whilst FLUKA bodies can be infinite
@@
 are then composed by instantiating these classes and adding body
-instances to them.  Each zone and region instance can then return its
+instances to them.  Each Zone and Region instance can then return its
 equivalent GDML Boolean solid.

### 2020-09-16 public/paper/pyg4ometry.tex
remove indentation from lstlisting sections
improving my fluka2gdml section

@@
 \begin{table}[hbt!]
-\caption{FLUKA bodies and their corresponding Geant4 solids.} \label{tab:Fluka2Geant4}
+\caption{FLUKA bodies and their corresponding \PYGEOMETRY{} classes.} \label{tab:Fluka2Geant4}
 \centering
@@
 The majority of bodies in FLUKA are infinite in extent, and fall
-broadly into four categories, half-spaces, infinitely long cylinders,
-infinitely long elliptical cylinders and quadric surfaces.
+broadly into four categories, half-spaces, infinitely-long cylinders,
+infinitely-long elliptical cylinders and quadric surfaces.
 Translating these bodies to Geant4 requires generating the equivalent
 finite solid whilst retaining the same final finite Boolean shape.
-This is achieved with the use of axis-aligned bounding boxes (AABB),
+This is achieved with the use of axis-aligned bounding boxes (AABBs),
 in which the FLUKA body is translated to a finite solid with with
@@
 (elliptical) cylinders are reduced to finite equivalents with lengths
-slightly greater than the bounding box.  Similarly, half spaces are
+slightly greater than the bounding box.  Similarly, half-spaces are
 reduced to boxes with one face acting as that of the half-space face,
@@
 
-Generating these bounding boxes over which the bodies should be
-translated involves first evaluating each region with very large Tubs,
-EllipticalTubes and Boxes (by default \SI{50}{\km} in length), such
-that they are effectively infinite for most reasonable use cases.
-\PYGEOMETRY{}'s CSG meshing is then used to generate a mesh for each
-region, from which the axis-aligned bounding box can be extracted.
-Each region is then evaluated a second time with respect to its
-respective bounding box, with all of its constituent infinite solids
-being reduced as described above.  This algorithm works robustly for
-infinite (elliptical) cylinders and half spaces as the number of
-facets is independent of the size of the solid, so generating the
-initial mesh from large solids works well.  Generating a quadric
-surface over a very large volume in space whilst retaining topological
-information is computationally very expensive, so to resolve this the
-user must provide the approximate axis-aligned bounding box of any
-region in which a quadric is used.
-
-\subsection{Removing redundant half-spaces}
-The above algorithm for replacing infinite FLUKA bodies with finite
-Geant4 solids works well in most cases, but additional care must be
-taken for redundant infinite half spaces.  A redundant infinite half
-space is defined as one which has no affect on the topology of the
-final Boolean solid.  Whilst this may be true of arbitrary bodies, it
-is most problematic for half spaces as after the infinite-body
-reduction has been performed, if the half-space is far away from the
-region's AABB, then it can result in a malformed Boolean.  This algorithm is
-demonstrated in Algorithm~\ref{algo:redundant-halfspace}.  Such
-half-spaces are filtered from their respective regions during the
-conversion process by calculating the nearest distance from the centre
-of the AABB to the half-space face.  If this distance is greater than
-the centre-to-corner distance of the AABB, then that half-space is
-removed from the region during conversion.
+Generating these bounding boxes over which the bodies should be translated
+involves first evaluating each region with very large Tubs, EllipticalTubes
+and Boxes (by default \SI{50}{\km} in length), such that they are
+effectively infinite for most reasonable use cases.  \PYGEOMETRY{}'s CSG
+meshing is then used to generate a mesh for each region from which the
+axis-aligned bounding box can be extracted.  Each region is then evaluated
+a second time with respect its respective bounding box, with all of its
+constituent infinite solids being reduced as described above.  The
+implementation is described in
+Algorithm~\ref{algo:redundant-halfspace}. This algorithm works robustly for
+infinite (elliptical) cylinders and half-spaces as the number of facets is
+independent of the size of the solid, so generating the initial mesh from
+large solids works well.  Generating a quadric surface over a very large
+volume in space whilst retaining topological information is computationally
+very expensive, so to resolve this the user must provide the approximate
+axis-aligned bounding box of any region in which a quadric is used.
 
@@
 \end{algorithm}
+
+\subsection{Removing redundant half-spaces}
+The above algorithm for replacing infinite FLUKA bodies with finite
+Geant4 solids works well in most cases, but additional care must be
+taken for redundant infinite half-spaces.  A redundant infinite half-space
+is defined as one which has no effect on the shape of the
+final Boolean solid.  Whilst this may be true of arbitrary bodies, it
+is most problematic for half-spaces as after the infinite body
+reduction has been performed. If the half-space is far away from the
+region's AABB, then it can result in a malformed Boolean. Such
+half-spaces are filtered from their respective regions during the
+conversion process by calculating the nearest distance from the centre
+of the AABB to the half-space face.  If this distance is greater than
+the centre-to-corner distance of the AABB, then that half-space is
+removed from the region during conversion.
 
@@
 subtractions and work well for guaranteeing well-formed geometry that
-is free from overlaps.
+is free from tracking errors.
 
@@
 Any useful translation between geometry description formats must also
-account for material, and accordingly \PYGEOMETRY{} correctly translates
-FLUKA materials to GDML.  FLUKA materials can be divided into built-in ,
+account for materials, and accordingly \PYGEOMETRY{} correctly translates
+FLUKA materials to GDML.  FLUKA materials can be divided into built-in,
 single-element and compound materials.  Built-in materials are simply those
@@
 the fact that recursively-defined materials in FLUKA input files need not
-be defined in a logical order.  Namely, a given \pyinline{compound} may be
+be defined in a logical order.  Namely, a given compound may be
 defined before the materials that it consists of are themselves defined.
@@
 FLUKA supports modular geometries with the use of the \fluka{lattice}
-command. Figure~\ref{fig:lattice} demonstrates this capability, and. The
+command. Figure~\ref{fig:lattice} demonstrates this capability. The
 arbitrarily complex \emph{basic unit} can be defined once and used
 multiple times by placing one or more empty \emph{lattice cells} with the
-associated roto-translation from that \fluka{lattice} cell to the basic
-unit. The \fluka{lattice} cells themselves will generally lack structure
+associated roto-translation from that lattice cell to the basic
+unit. The lattice cells themselves will generally lack structure
 and simply serve as a reference to the basic unit. The rototranslated
 lattice cell must fully contain the basic unit and all of the regions
-within it. When a particle steps into the \fluka{lattice} cell, the
+within it. When a particle steps into the lattice cell, the
 rototranslation is applied to that particle and it is is taken into the
@@
 particles leaving the basic unit will be translated back to the
-\fluka{lattice} cell with the inverted rototranslation. Up to two
-levels of \fluka{lattice} nesting the are supported in FLUKA.
+lattice cell with the inverted rototranslation. Up to two
+levels of lattice nesting the are supported in FLUKA.
 
@@
 \includegraphics[width=6cm]{./diagrams/lattice}
-\caption{The \fluka{lattice} feature demonstrating a \fluka{lattice} cell
+\caption{The lattice feature demonstrating a lattice cell
   referring to its basic unit with the rototranslation $R_\textrm{trans}$.
@@
 \end{figure}
-
 This feature is clearly analogous to the logical/physical volume feature in
 Geant4, although it is less explicit as the contents of a given logical
-volume are clearly stated, whereas the contents of a \fluka{lattice} cell
+volume are clearly stated, whereas the contents of a lattice cell
 are implied by the combination of the rototranslation and the locations of
-its \fluka{lattice} cell and basic unit.
-
-Translating this construct into a logical volume (basic unit) with many
-physical volumes (\fluka{lattice} cells) requires associating each
-\fluka{lattice} cell with the full contents of its corresponding basic unit
+its lattice cell and basic unit.
+
+Translating the lattice construct into a logical volume (basic unit) with many
+physical volumes (lattice cells) requires associating each
+lattice cell with the full contents of its corresponding basic unit
 (typically several regions). This is achieved by meshing the complete
-FLUKA geometry and then rototranslating the \fluka{lattice} cell mesh with
+FLUKA geometry and then rototranslating the lattice cell mesh with
 its associated rototranslation. By construction this will translate the
-\fluka{lattice} cell mesh directly onto the full basic unit mesh. Finally,
+lattice cell mesh directly onto the full basic unit mesh. Finally,
 in checking for overlaps, the regions within the the basic unit can be
-determined. In the final conversion step, the \fluka{lattice} cell can
+determined. In the final conversion step, the lattice cell can
 simply be replaced with a physical volume that refers back to logical
-volumes located in the previous step. Thus the \fluka{lattice} cells can
-be translated into Geant4's logical/physical volumes. As has been stated,
+volumes located in the previous step. Thus a basic unit with one or more lattice cells can
+be translated into Geant4's logical volume with one or more physical volumes. As has been stated,
 FLUKA supports two levels of nesting, but currently the conversion to GDML
@@
 geometries, however a number of possible improvements for the future
-persist.  For example, Boolean solids in FLUKA can in general be
-disconnected, and this most typically manifests itself in the form of
+remain.  For example, Boolean solids in FLUKA can in general be
+disconnected, and this typically manifests itself in the form of
 disconnected unions, but is also allowed for intersections and
@@
 use of the MultiUnion solid type, however there is no valid means to
-construct a disconnected subtraction or intersection in GDML.  One possible
+construct a disconnected intersection or subtraction in GDML.  One possible
 solution would be to detect these two cases, and if found, split them into
@@
 implemented as quadrics are relatively rarely used, but where quadrics are
-used its often parabolic cylinders (e.g. magnet pole tips) this
+used it is often in the form of parabolic cylinders (e.g. magnet pole tips) and this
 specialisation in particular would be worth implementing.

### 2020-09-16 public/paper/pyg4ometry.tex
hyph

@@
 has 20 of these primitive bodies, listed in Table~\ref{tab:Fluka2Geant4}
-and, in general, infinite extent bodies have tracking accuracy and
+and, in general, infinite-extent bodies have tracking accuracy and
 efficiency benefits over finite ones. Key for conversion are XY-, XZ-,

### 2020-09-16 public/paper/pyg4ometry.tex
better/clearer wording

@@
 There are some important issues which must be considered to perform an accurate conversion. 
-A Geant4 logical volume solid might need to be created from a FLUKA region composing of many zones, 
+A Geant4 logical volume solid might need to be created from a FLUKA region consisting of many zones (i.e. unions), 
 so $R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 

### 2020-09-16 public/paper/pyg4ometry.tex
add puncutation to the equations as they are prose
fix incorrect english
fix word order

@@
 R_1 - R_2 	& = & (+z_1 \: | +z_2) - ( +z_3 \: | +z_4) 			\\
-			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)	
+			& = & (+z_1 - z_3 - z_4) \;  | \; (+z_2 - z_3 - z_4)\,.	
 \label{eqn:setDiff}
@@
 R_1 \cap R_2 	& = & (+z_1 \: | +z_2) \cap ( +z_3 \: | +z_4) \\
-			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4
+			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4\,.
 \label{eqn:setIntersection}
@@
 
-FLUKA (apart from the \fluka{lattice} directive) has no sense of a volume hierarchy. Each body is placed with a 
-translation, rotation, expansion geometry directives in global coordinates. A transformation from world 
-coordinates to a physical volume is built up by applying recursively daughter volume transformations 
+FLUKA (apart from the \fluka{lattice} directive) has no sense of a volume hierarchy. Each body is placed with 
+translation, rotation and expansion geometry directives in global coordinates. A transformation from world 
+coordinates to a physical volume is built up by recursively applying daughter volume transformations 
 and  this is used to place FLUKA bodies. This  in practice is very similar to the procedure to create the 

### 2020-09-16 public/paper/pyg4ometry.tex
space point -> point in space
"There is problem"

@@
 
-In FLUKA every single space point needs to be associated with one and only one region. There is problem 
+In FLUKA every single point in space needs to be associated with one and only one region. This presents a problem 
 when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 

### 2020-09-16 public/paper/pyg4ometry.tex
don't start sentence with "So"
missing word

@@
 when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
-need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. So a solid which can be converted 
+need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. A solid which can be converted 
 to a region $S_{\rm region}$ is then 
@@
 \end{equation} 
-If a logical volume has  number of daughter volumes which are also possibly Boolean solids, then computing 
+If a logical volume has a number of daughter volumes which are also possibly Boolean solids, then computing 
 $S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 

### 2020-09-16 public/paper/pyg4ometry.tex
comma

@@
 can only be created by the union of convex zones. There are two groups which need to considered, firstly those 
-where 2D polygonal section needs to be decomposed these include Polycone, Polyhedron and Xtru, secondly 
+where 2D polygonal section needs to be decomposed, these include Polycone, Polyhedron and Xtru, secondly 
 those where three dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 

### 2020-09-16 public/paper/pyg4ometry.tex
hyphenate three-dimensional

--- 2020-09-16 public/paper/pyg4ometry.tex
@@
 can only be created by the union of convex zones. There are two groups which need to considered, firstly those 
-where 2D polygonal section needs to be decomposed these include Polycone, Polyhedron and Xtru, secondly 
-those where three dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
+where 2D polygonal section needs to be decomposed, these include Polycone, Polyhedron and Xtru, secondly 
+those where three-dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
 TwistedTube and Tessellated. The second classification of non convex solids are converted to CGAL 

### 2020-09-16 public/paper/pyg4ometry.tex
better wording

@@
 Typically FLUKA will decompose a region into disjunctive normal form (DNF), this normal form is 
-characterised as the union of intersections, so 
+characterised as the union of intersections and subtractions,
 \begin{equation}
@@
 \end{equation}
-Defining regions in terms of DNF allows the rapid test if a point is inside. Testing each zone 
+Defining regions in terms of the DNF allows the rapid test of whether a point is inside that region. Testing each zone 
 $z_i$ of $R$ can terminate if a point is determined to be inside any of the convex zones $z_i$. In general 

### 2020-09-16 public/paper/pyg4ometry.tex
remove reference to quine mcclusket, we don't use it, blows up
cite the pruning algorihtm as undoubtedly way influence on us...

@@
 parentheses. There are some conditions where a general Boolean expression can yield an exponential 
-explosion of the final DNF. There are well known algorithms to convert logical expressions to a DNF. 
-\PYGEOMETRY{} can simplify parentheses from a region by creating a SymPy~\cite{10.7717/peerj-cs.103} 
-expression and using its \verb|logical| module \verb|to_dnf| method based on the Quine–McCluskey algorithm~\cite{6769983}. 
+explosion of the final DNF. There are well known algorithms to convert logical expressions to its DNF. 
+\PYGEOMETRY{} can simplify parentheses from a region by creating a corresponding SymPy~\cite{10.7717/peerj-cs.103} Boolean
+expression and using the \verb|to_dnf| method.  Further simplification of the CSG tree leverages \PYGEOMETRY{}'s
+meshing capabilities combined with CSG pruning algorithms based on~\cite{pruning}.
 Before version 4.0 FLUKA  would simplify all regions to DNF and some converted geometry would generate 

### 2020-09-16 public/paper/pyg4ometry.tex
better explanation of why we need fluka 4.0

@@
 expression and using the \verb|to_dnf| method.  Further simplification of the CSG tree leverages \PYGEOMETRY{}'s
-meshing capabilities combined with CSG pruning algorithms based on~\cite{pruning}.
-Before version 4.0 FLUKA  would simplify all regions to DNF and some converted geometry would generate 
-too many zones and would fail. FLUKA version 4 allows control of the DNF expansion.
+meshing capabilities combined with CSG pruning algorithms based
+on~\cite{pruning}.  FLUKA by default will try to expand all regions to
+their DNF at runtime, which inevitably can result in the sort of exponential explosion already mentioned.  Until version 4.0, if FLUKA identified 
+such an explosion, it would report an error and exit, thus making such models impossible to run.  As of version 4.0, however, this
+expansion can be disabled, and the tracking algorithms will walk the CSG trees verbatim, at some tracking efficiency cost.  Therefore, most 
+output generated from the GDML to FLUKA conversion described here can only be used with FLUKA 4.0.
 

### 2020-09-16 public/paper/pyg4ometry.tex
"A similar issues"

@@
 \cpinline{G4Material} is converted to a \fluka{material} card, whilst the {\em element} \cpinline{G4Material}  is converted to a 
-\fluka{compound} card. A similar issues existing when converting \cpinline{G4Element} to FLUKA, as \cpinline{G4Element}
+\fluka{compound} card. There are similar issues when converting \cpinline{G4Element} to FLUKA, as \cpinline{G4Element}
 can either be simple, so defined only by atomic number and mass or composite and defined by a admixture defined by 

### 2020-09-16 public/paper/pyg4ometry.tex
missing commas and words

@@
 \fluka{compound} card. There are similar issues when converting \cpinline{G4Element} to FLUKA, as \cpinline{G4Element}
-can either be simple, so defined only by atomic number and mass or composite and defined by a admixture defined by 
-relative abundances of \cpinline{G4Isotope}. A similar mapping is performed so if an \cpinline{G4Element} is simple it is 
+can either be simple, i.e. defined only by atomic number and mass, or composite and defined by an admixture of 
+relative abundances of \cpinline{G4Isotope}. A similar mapping is performed so that if a \cpinline{G4Element} is simple it is 
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compound}

### 2020-09-16 public/paper/pyg4ometry.tex
better wording

@@
 card. Geant4 also defines a set of standard materials \cite{Geant4MaterialDB} or compounds from the US National Institute 
-of Standards and Technology (NIST), so a user can, for example, just
-specify the name \pyinline{G4_STAINLESS-STEEL} and \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
-cards during the conversion. This database is updated by running a small Geant4 program to output the appropriate
+of Standards and Technology (NIST), so a user can for example, simply
+specify the name \pyinline{G4_STAINLESS-STEEL}. \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA 
+cards from these names during the conversion. This database is updated by running a small Geant4 program to output the appropriate
 material data.

### 2020-09-16 public/paper/pyg4ometry.tex
reword

@@
 advanced and stable. Relatively large experimental simulations 
-have been converted from GDML to FLUKA and have been producing 
+have been converted from GDML to FLUKA and have been used to produce 
 simulation results. The conversion described still requires a user to
@@
 and will be added in a future release. In Geant4 it is possible to create scaled 
-solids or placements with reflections, so called scale in Geant4. FLUKA 
+solids or placements with reflections, referred to as \emph{scale} in Geant4. FLUKA 
 roto-translations do not support reflections and implementing reflections 

### 2020-09-16 public/paper/pyg4ometry.tex
choose to not hyphenate rototranslation
kind of arbitrary maybe but we should stick with one style

@@
 multiple times by placing one or more empty \emph{lattice cells} with the
-associated roto-translation from that lattice cell to the basic
+associated rototranslation from that lattice cell to the basic
 unit. The lattice cells themselves will generally lack structure
@@
 solids or placements with reflections, referred to as \emph{scale} in Geant4. FLUKA 
-roto-translations do not support reflections and implementing reflections 
+rototranslations do not support reflections and implementing reflections 
 require transformation of the body definitions. This is not yet implemented 
@@
 placements of bodies. It should be possible to cast FLUKA bodies 
-{\em without} roto-translations into a {\em normal form} which can be used 
+{\em without} rototranslations into a {\em normal form} which can be used 
 to test for approximate equality. Approximate equality is required as 
-multiple application roto-translations will accrue numerical rounding errors.
+multiple application rototranslations will accrue numerical rounding errors.
 An simple example of this is the XYP and PLA, it simple to transform an 

### 2020-09-16 public/paper/pyg4ometry.tex
"An simple"
cite tetgen

@@
 multiple application rototranslations will accrue numerical rounding errors.
-An simple example of this is the XYP and PLA, it simple to transform an 
+A simple example of this is the XYP and PLA, it simple to transform an 
 XYP into a PLA with an appropriate rotation. This would allow for the removal 
@@
 create a region formed from the unions of tetrahedra. There are numerous 
-algorithms for tetrahedralisation of surface meshes in both CGAL and TetGen 
+algorithms for tetrahedralisation of surface meshes in both CGAL and TetGen~\cite{tetgen}
 and will be implemented in a future release. Even if a stable and general 

### 2020-09-16 public/paper/pyg4ometry.tex
cite freecad again here because it makes sense
hyph

@@
 STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface 
-based on FreeCAD. FreeCAD is an open source CAD/CAM program, which 
+based on FreeCAD~\cite{FreeCAD}. FreeCAD is an open source CAD/CAM program, which 
 in turn is based on OpenCASCADE. FreeCAD allows for scripting in Python 
-and acts as a simple to use interface to OpenCASCADE.  A STEP CAD file 
+and acts as a simple-to-use interface to OpenCASCADE.  A STEP CAD file 
 could be considered as a hierarchical tree of parts and \emph{part assemblies}, 

### 2020-09-16 public/paper/pyg4ometry.tex
too much use of the word "create"
hyph

@@
 where a part assembly is a collection of \emph{part features}. A part feature can be used 
-to create a triangular mesh which can be used to create a \PYGEOMETRY{} tessellated solid. The placement 
+to create a triangular mesh which can be used to instantiate a \PYGEOMETRY{} tessellated solid. The placement 
 of the part feature is extracted from the STEP file and used to create an 
@@
 vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so the new vertices are ${\bf v} - \epsilon {\bf n}$. The degree of shrinking 
-is user controllable.
+is user-controllable.
 

### 2020-09-16 public/paper/pyg4ometry.tex
reword

@@
 An example geometry representing a dipole electromagnet, consisting of three parts was created in Autodesk Fusion 360
-and saved as a STEP file, \PYGEOMETRY{} produces the output in Figure~\ref{fig:cad-gdml}.
+and saved as a STEP file, the \PYGEOMETRY{}-produced output is shown in Figure~\ref{fig:cad-gdml}.
 

### 2020-09-16 public/paper/pyg4ometry.tex
better explanation

@@
 and workflows. A fictitious beam line was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite 
-\emph{scene} which consists of the different examples presented in this paper. The beam line consists of a vacuum chamber 
+\emph{scene} which consists of geometry sources from the different formats described in this paper. The beamline consists of a vacuum chamber 
 (modelled in \PYGEOMETRY{}), a vacuum gate value (STL from the manufacturer), a triplet of quadrupole magnets (exported 

### 2020-09-16 public/paper/pyg4ometry.tex
value -> valve

@@
 \emph{scene} which consists of geometry sources from the different formats described in this paper. The beamline consists of a vacuum chamber 
-(modelled in \PYGEOMETRY{}), a vacuum gate value (STL from the manufacturer), a triplet of quadrupole magnets (exported 
+(modelled in \PYGEOMETRY{}), a vacuum gate valve (STL from the manufacturer), a triplet of quadrupole magnets (exported 
 from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (modelled in 

### 2020-09-16 public/paper/pyg4ometry.tex
missing word
clarity

@@
 (modelled in \PYGEOMETRY{}), a vacuum gate valve (STL from the manufacturer), a triplet of quadrupole magnets (exported 
-from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (modelled in 
-flair). Each different file is loaded using \PYGEOMETRY{} reader class and the placed as a physical volume. The final composite 
+from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (FLUKA geometry designed in 
+flair). Each different file is loaded using the appropriate \PYGEOMETRY{} reader class and then placed as a physical volume. The final composite 
 geometry is shown in Figure~\ref{fig:model}. It must be noted when this complete geometry is written to GDML and loaded into 

### 2020-09-16 public/paper/pyg4ometry.tex
replace enumeration, it's out of place

@@
 
-Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and potentially 
-programmatically if it must be performed for large numbers of objects. The processes include; 
-\begin{enumerate}
-\item merging registries, 
-\item removing volumes (de-featuring),
-\item editing solid parameters,
-\item replacing logical volume materials 
-\item converting logical volumes to assembly volumes.
-\end{enumerate}
+Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and programmatically. The benefits of the API are
+particularly apparent when needing to process large amounts of geometry efficiently and precisesly. Possible transformations include merging registries, 
+removing volumes (de-featuring), editing solid parameters, changing logical volume materials and converting logical volumes to assembly volumes.
+
 The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 

### 2020-09-16 public/paper/pyg4ometry.tex
missing word
comma

@@
 The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
-Each sub-component is stored in a separate registry and these have to combined without any GDML tags clashing. 
+Each sub-component is stored in a separate registry and these have to be combined without any GDML tags clashing. 
 The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
@@
 The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
-where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
+where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a 
 Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 

### 2020-09-16 public/paper/pyg4ometry.tex
pycgal and pycsg are in C++ not C/C++ (i.e. not C)
del comma

@@
 available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
-and \pyinline{pyg4ometry.pycgal} in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using 
 \pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
 for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.
+and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using
 

### 2020-09-16 public/paper/pyg4ometry.tex
they aren't really unit tests, more like integration tests
unit tests are extremely fine-grained, our tests are not nearly as much.
so just refer to them as software tests instead so we aren't saying something
not true

@@
 available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
-\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
-for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.
 and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 
+\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 tests are available 
+for the code, which have 84\% coverage. The tests also serve as minimal examples to help users understand the code operation.
 

### 2020-09-16 public/paper/pyg4ometry.tex
better wording.
replace latin, better to not risk confusion

@@
 and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 
-\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 tests are available 
-for the code, which have 84\% coverage. The tests also serve as minimal examples to help users understand the code operation.
+\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 are available,  
+resulting in 84\% code coverage. The tests also serve as minimal examples to help users understand the code operation.
 
 \section{Conclusions and discussion}
-The authors believe that tools to quickly create, either ab initio or by conversion geometry usable in Monte Carlo
+The authors believe that tools to quickly create, either from scratch or by conversion geometry usable in Monte Carlo
 particle transport programmes will save significant amounts of user effort and ultimately 

### 2020-09-16 public/paper/pyg4ometry.tex
better wording

@@
 \section{Conclusions and discussion}
-The authors believe that tools to quickly create, either from scratch or by conversion geometry usable in Monte Carlo
-particle transport programmes will save significant amounts of user effort and ultimately 
+The authors believe that tools to quickly create geometry, either from scratch or by conversion,
+for Monte Carlo particle transport programmes
+will save significant amounts of time and user effort and will ultimately 
 yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 

### 2020-09-16 public/paper/pyg4ometry.tex
"a" before consonant
remove bold

@@
 allows the programmatic control of geometry creation or modification. This approach allows the integration of 
-other available tools \cite{DavisNIMA915-65} into an unified workflow.
-
-Users should be aware of {\bf issues} with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA 
+other available tools \cite{DavisNIMA915-65} into a unified workflow.
+
+Users should be aware of issues with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA 
 cannot be considered bidirectional. For example Geant4 tessellated cannot be converted easily to FLUKA which does not 

### 2020-09-16 public/paper/pyg4ometry.tex
wording

@@
 Users should be aware of issues with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA 
-cannot be considered bidirectional. For example Geant4 tessellated cannot be converted easily to FLUKA which does not 
+cannot be considered bidirectional. For example Geant4 tessellated solids cannot be converted easily to FLUKA which does not 
 have a convenient way of representing this geometry. In general a user would be unwise to attempt to convert a very large 
@@
 on conversion from a primary format and then create conversions to another format as the need arises. This paper outlines 
-the creation of geometry using \PYGEOMETRY{}, that geometry is loaded into Geant4, flair and FLUKA but detailed 
+the creation of geometry using \PYGEOMETRY{}, and whilst that geometry is subsequently loaded into Geant4, flair and FLUKA, detailed 
 studies of the MCRT simulation performance is beyond the scope of this publication and will be addressed in the future.

### 2020-09-16 public/paper/pyg4ometry.tex
an before vowel soudn

@@
 There are many output format extensions that can be considered for \PYGEOMETRY{}. 
-Geant4 geometry is primarily created by writing C++ programmes, so a output writer that 
+Geant4 geometry is primarily created by writing C++ programmes, so an output writer that 
 converts the \PYGEOMETRY{} in memory representation to C++ will allow rapid geometry 

### 2020-09-16 public/paper/pyg4ometry.tex
hyph

--- 2020-09-16 public/paper/pyg4ometry.tex
@@
 There are many output format extensions that can be considered for \PYGEOMETRY{}. 
-Geant4 geometry is primarily created by writing C++ programmes, so a output writer that 
-converts the \PYGEOMETRY{} in memory representation to C++ will allow rapid geometry 
+Geant4 geometry is primarily created by writing C++ programmes, so an output writer that 
+converts the \PYGEOMETRY{} in-memory representation to C++ will allow rapid geometry 
 modelling but . This is not implemented in the current version but could be relatively quickly implemented

### 2020-09-16 public/paper/pyg4ometry.tex
more wording

@@
 modelling but . This is not implemented in the current version but could be relatively quickly implemented
-for users that require this functionality. At present \PYGEOMETRY{} supports reading and writing. 
-Geant4 and FLUKA type files but could be extended without significant effort to other MCRT codes 
+for users that require this functionality. At present \PYGEOMETRY{} supports reading and writing 
+Geant4 (GDML) and FLUKA files but could be extended without significant effort to other MCRT codes 
 like MCNP.

### 2020-09-16 public/paper/pyg4ometry.tex
hyphen and missing plural
more improvements

@@
 data formats used in augmented or virtual reality software to create interactive visualisations of MCRT 
-simulations.  Triangular meshes also have application  for GPU accelerated photon tracking in 
+simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in 
 liquid noble dark matter detectors. Paraview/VTK are becoming standard software for complex 3D visualisation and 
@@
 \PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
-significantly aid geometry creation workflows. A graphical user interface (GUI) so a user could create 
-geometry without any programming knowledge would expand the number of potential users. \PYGEOMETRY{}
-has been designed to interface with a GUI in a relatively straightforward manner. The VTK visualiser currently 
-limits the display of very large models as geometry instances are replicated opposed to reused in visualisation.
-
-The conversion which would most dramatically enhance the creation of geometry is CAD to Geant4/FLUKA
-without use use of a triangular or tetrahedral mesh. There are methods to decompose BREP solids to Geant4 and 
-FLUKA like CSG geometry \cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 
-The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API present in \PYGEOMETRY{} 
+significantly aid geometry creation workflows. A graphical user interface (GUI) would enable a user without any
+ programming experience to create geometry for MCRT simulations and expand the number of potential users.
+\PYGEOMETRY{} has been designed to interface with a GUI in a relatively straightforward manner. The VTK visualiser currently 
+limits the display of very large models as geometry instances are replicated as opposed to reused in visualisation.  However,
+this could be drastically improved in a future release.
+
+The conversion which would most dramatically enhance the creation of geometry is CAD to Geant4 or FLUKA
+without use use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
+FLUKA-like CSG geometry \cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 
+The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API in \PYGEOMETRY{} 
 will allow for the creation of CAD BREP decomposition algorithms.
 
-There is a strong relationship between \PYGEOMETRY and Geant4 and to a lesser extent between 
-\PYGEOMETRY{} and FLUKA. \PYGEOMETRY{} can be used to a testing ground for ideas prior to 
-implementation in Geant4 or flair. An example of this the VTK visualisation system implemented in 
-\PYGEOMETRY{}, which could be used in Geant4 to rendering of Boolean solids which frequently 
-fail in the Geant4 OpenGL viewer. This would involve using CGAL meshing in the \pyinline{G4Polyhedron}
-class. %There is also
+There is a strong relationship between \PYGEOMETRY{} and Geant4 and to a lesser extent between 
+\PYGEOMETRY{} and FLUKA. \PYGEOMETRY{} can be used as a testing ground for ideas prior to 
+implementation in Geant4 or FLUKA. An example of this is the VTK visualisation system implemented in 
+\PYGEOMETRY{}, which could be used in Geant4 to render Boolean solids which frequently 
+fail in the Geant4 OpenGL viewer, despite being otherwise perfectly valid constructs.
+This would involve using CGAL meshing in the \pyinline{G4Polyhedron} class. %There is also
 
@@
 area where MCRT simulations are needed, for example particle physics, space environment and medical physics.
-The authors welcome contributions, extensions and bug-fixes as well a suggestions for larger collaborations.
+The authors welcome contributions, extensions and bug fixes as well suggestions for larger collaborations.
 
@@
 undergraduate and masters students have contributed to the code for their
-degree project work, Simon Williams, Benjamin Shellswell, Joshua Albrecht.
+degree project work: Simon Williams, Benjamin Shellswell and Joshua Albrecht.
 STB has benefited from discussions with and insight of Vasilis Vlachoudis

### 2020-09-16 public/paper/pyg4ometry.tex
final spell checker

@@
 
-The transformation  $\mathbf{M}$  and translation $\mathbf{T}$ from mother to daugher is 
+The transformation  $\mathbf{M}$  and translation $\mathbf{T}$ from mother to daughter is 
 \begin{eqnarray}
@@
 Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and programmatically. The benefits of the API are
-particularly apparent when needing to process large amounts of geometry efficiently and precisesly. Possible transformations include merging registries, 
+particularly apparent when needing to process large amounts of geometry efficiently and precisely. Possible transformations include merging registries, 
 removing volumes (de-featuring), editing solid parameters, changing logical volume materials and converting logical volumes to assembly volumes.
@@
 Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages 
-available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
+available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages that require compilation \pyinline{pyg4ometry.pycsg} 
 and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 

### 2020-09-17 public/paper/pyg4ometry.tex
missing word...
we never said what flair is

@@
 \caption{Example conversion of a simple FLUKA geometry to GDML. Above:
-the original FLUKA geometry displayed in flair. Below: the GDML geometry
-viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
+  the original FLUKA geometry displayed in flair, FLUKA's graphical user interface.
+  Below: the GDML geometry viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
 and measure accelerator beam charge.}
@@
 a mother will create a very complex non-DNF region which is inefficient when viewed in 
-flair and used for simulation in FLUKA. A geometry designer can avoid this by
+FLUKA's graphical user interface (GUI), flair, and used for simulation in FLUKA.
+A geometry designer can avoid this by
 restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
@@
 \PYGEOMETRY{} is principally a toolkit but various visualisation and user interface extensions would 
-significantly aid geometry creation workflows. A graphical user interface (GUI) would enable a user without any
+significantly aid geometry creation workflows. A graphical user interface would enable a user without any
  programming experience to create geometry for MCRT simulations and expand the number of potential users.
@@
 area where MCRT simulations are needed, for example particle physics, space environment and medical physics.
-The authors welcome contributions, extensions and bug fixes as well suggestions for larger collaborations.
+The authors welcome contributions, extensions and bug fixes as well as suggestions for larger collaborations.
 

### 2020-09-17 public/paper/pyg4ometry.tex
tidy fact file thing at the top
fix incorrect indentation in front of Nature of Problem

move hint about how long the parts should be to comment

Program title consistency with rest of paper

programming languages are Python and C++, not C/C++ (no standalone C,
although arguably as Cython but I would suggest this should fall under
umbrella of Python)

add NumPy to external routines/libraries since we do depend on it quite heavily

@@
 \noindent
-{\em Program Title: PYG4OMETRY }                                         		\\
+{\em Program Title: \PYGEOMETRY{} }                                         		\\
 {\em Licensing provisions: GPLv3 }							\\
-{\em Programming language: Python, C/C++}                         		\\
-{\em External routines/libraries: ANTLR, CGAL, FreeCAD, OpenCascade, SymPy, VTK}           	\\
-
+{\em Programming language: Python, C++}                         		\\
+{\em External routines/libraries: ANTLR, CGAL, FreeCAD, NumPy, OpenCascade, SymPy, VTK} \\
 %{\em Supplementary material:}                                 				\\
@@
   %Only required for a New Version summary, otherwise leave out.
-
-{\em Nature of problem(approx. 50-250 words):}\\
+{\em Nature of problem:}\\  % (approx. 50-250 words)
 Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
@@
 \\
-{\em Solution method(approx. 50-250 words):}\\
+{\em Solution method:}\\  % (approx. 50-250 words)
 Create a Python application programming interface to read and write files of and process the geometry objects and specification 

### 2020-09-17 public/paper/pyg4ometry.tex
non-breaking space before \cite

@@
 are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP 
-and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The 
-origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. 
+and IGES) based on FreeCAD~\cite{FreeCAD} and OpenCascade~\cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK~\cite{VTK4}. The 
+origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM~\cite{BDSIM_Nevay}. 
 Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. 
@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework, 
-can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
+can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh~\cite{GUIMesh_Pinto}, commercial 
 products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
@@
  to bounded or infinite mathematical surfaces and subsequently solids as used in CSG descriptions. This type of conversion is complex and error-prone, 
- although recent progress has been made \cite{WangNuclSciTech31-82-2020}.
+ although recent progress has been made~\cite{WangNuclSciTech31-82-2020}.
 
@@
 of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
-(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
+(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b} in C++. In 
 general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file 
-various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
+various polygon mesh algorithms  from CGAL~\cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
 
@@
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compound}
-card. Geant4 also defines a set of standard materials \cite{Geant4MaterialDB} or compounds from the US National Institute 
+card. Geant4 also defines a set of standard materials~\cite{Geant4MaterialDB} or compounds from the US National Institute 
 of Standards and Technology (NIST), so a user can for example, simply
@@
 allows the programmatic control of geometry creation or modification. This approach allows the integration of 
-other available tools \cite{DavisNIMA915-65} into a unified workflow.
+other available tools~\cite{DavisNIMA915-65} into a unified workflow.
 
@@
 without use use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
-FLUKA-like CSG geometry \cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 
+FLUKA-like CSG geometry~\cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 
 The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API in \PYGEOMETRY{} 

### 2020-09-17 public/paper/pyg4ometry.tex
non breaking space in list of refs after last and and before ref

@@
 where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
-Equations~\ref{eqn:worldToDaughter1} and \ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.
+Equations \ref{eqn:worldToDaughter1} and~\ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.
 
@@
 If a logical volume has a number of daughter volumes which are also possibly Boolean solids, then computing 
-$S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and 
-\ref{eqn:setIntersection}.
+$S_{\rm region}$ can become very complex because of Equations \ref{eqn:setDiff}, \ref{eqn:setUnion} and~\ref{eqn:setIntersection}.
 
@@
 In general, recursive application of Equations \ref{eqn:setDiff},
-\ref{eqn:setUnion}, \ref{eqn:setIntersection} and \ref{eqn:logicalSubtraction} 
+\ref{eqn:setUnion}, \ref{eqn:setIntersection} and~\ref{eqn:logicalSubtraction} 
 can result in very complex regions when converting from Geant4/GDML to 

### 2020-09-17 public/paper/pyg4ometry.tex
non breaking space correctness

@@
 A  \PYGEOMETRY{} geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4 
-volume hierarchy is sufficient to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a rotation 
-$\mathbf{R}_d$, scale $\mathbf{S}_d$ and translation $\mathbf{T}_d$.
+volume hierarchy is sufficient to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a
+rotation~$\mathbf{R}_d$, scale~$\mathbf{S}_d$ and translation~$\mathbf{T}_d$.
 
@@
 %
-If the mother volume is placed in the world then the placement transformation $\mathbf{M}_w$ and translation $\mathbf{T}_w$ are expressed as
+If the mother volume is placed in the world then the placement transformation~$\mathbf{M}_w$ and translation~$\mathbf{T}_w$ are expressed as
 \begin{eqnarray}
@@
 \end{eqnarray}
-where the subscript $m$ indicates mother volume and $d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
+where the subscript~$m$ indicates mother volume and~$d$ indicates daughter volume. Given a hierarchy of logical and physical volumes, 
 Equations \ref{eqn:worldToDaughter1} and~\ref{eqn:worldToDaughter2} can be used recursively to place an arbitrary number of nested volumes.
@@
 \caption{The lattice feature demonstrating a lattice cell
-  referring to its basic unit with the rototranslation $R_\textrm{trans}$.
+  referring to its basic unit with the rototranslation~$R_\textrm{trans}$.
   Any particle entering the cell will be transformed onto the basic unit
@@
 A Geant4 logical volume solid might need to be created from a FLUKA region consisting of many zones (i.e. unions), 
-so $R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
-might also be converted to a region of multiple zones $R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
+so~$R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
+might also be converted to a region of multiple zones~$R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
 \begin{eqnarray}
@@
 In FLUKA every single point in space needs to be associated with one and only one region. This presents a problem 
-when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid $S_{\rm logical}$ 
-need to have the daughter  solids $S_{{\rm daughter},i}$ subtracted. A solid which can be converted 
-to a region $S_{\rm region}$ is then 
+when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid~$S_{\rm logical}$ 
+need to have the daughter  solids~$S_{{\rm daughter},i}$ subtracted. A solid which can be converted 
+to a region~$S_{\rm region}$ is then 
 \begin{equation}

### 2020-09-19 public/paper/pyg4ometry.tex
Paper update (fixed Stuarts last comments)

@@
 (or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
-large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. The existent set of software does not 
-provide a complete set of tools to efficiently create complex geometries.
+large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. Almost all modern CAD tools like 
+CATIA, Inventor, SolidWorks have a scripting language to allow users to programatically generate geometry. This scripting functionality is not available with either 
+GDML or FLUKA were users write the geometry files directly. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
 
@@
 converts the \PYGEOMETRY{} in-memory representation to C++ will allow rapid geometry 
-modelling but . This is not implemented in the current version but could be relatively quickly implemented
-for users that require this functionality. At present \PYGEOMETRY{} supports reading and writing 
+modelling but inclusion of the geometry into an existing Geant4 application. This is not 
+implemented in the current version but could be relatively quickly implemented for users that 
+require this functionality. At present \PYGEOMETRY{} supports reading and writing 
 Geant4 (GDML) and FLUKA files but could be extended without significant effort to other MCRT codes 
@@
 
-The conversion which would most dramatically enhance the creation of geometry is CAD to Geant4 or FLUKA
+The conversion which would most dramatically enhance the creation of RTMC geometry is CAD to Geant4 or FLUKA
 without use use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
@@
 The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API in \PYGEOMETRY{} 
-will allow for the creation of CAD BREP decomposition algorithms.
+will allow for the creation of CAD BREP decomposition algorithms. There are python based CAD modelling tools like 
+cadquery \cite{cadquery} which allow the creation of models using pure Python which should allow the conversion of GDML to STEP.
 
@@
 Accelerator Science'' ST/P00203X/1 through the John Adams Institute at
-Royal Holloway, and Royal Holloway Impact Acceleration Account.  Multiple
+Royal Holloway, and Royal Holloway Impact Acceleration Account. Gian Luigi D'Alessandro (CERN/JAI)
+provided geometry and tested multiple conversions of beamlines. Multiple
 undergraduate and masters students have contributed to the code for their

### 2020-10-07 public/paper/pyg4ometry.tex
Small fixes to paper

@@
 \author[a]{Andrey Abramov}
-\author[a]{Laurence Nevay}
+\author[a]{Laurence J. Nevay}
 \author[a]{William Shields}
@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programmes 
+There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programs 
 include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}. 
@@
 The authors believe that tools to quickly create geometry, either from scratch or by conversion,
-for Monte Carlo particle transport programmes
+for Monte Carlo particle transport programs
 will save significant amounts of time and user effort and will ultimately 
@@
 There are many output format extensions that can be considered for \PYGEOMETRY{}. 
-Geant4 geometry is primarily created by writing C++ programmes, so an output writer that 
+Geant4 geometry is primarily created by writing C++ programs, so an output writer that 
 converts the \PYGEOMETRY{} in-memory representation to C++ will allow rapid geometry 

### 2020-11-07 public/paper/sub-1-arxiv/pyg4ometry.tex
arxiv paper submission
Typo and two duplicate words.

--- 2020-09-19 public/paper/pyg4ometry.tex
@@
 %% \documentclass[final,5p,times]{elsarticle}
-\documentclass[final,5p,times,twocolumn]{elsarticle}
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
+  \includegraphics[width=0.7\textwidth]{workflow.pdf}
   \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing (a) the different input file formats, (b) Python processing, (c) output file targets and 
@@
 large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. Almost all modern CAD tools like 
-CATIA, Inventor, SolidWorks have a scripting language to allow users to programatically generate geometry. This scripting functionality is not available with either 
+CATIA, Inventor, SolidWorks have a scripting language to allow users to programmatically generate geometry. This scripting functionality is not available with either 
 GDML or FLUKA were users write the geometry files directly. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
@@
 \begin{center}
-\includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
+\includegraphics[width=5cm]{./lvToPv.pdf}
 \caption{The placement of a physical volume inside a logical volume.}
@@
 \begin{center}
-\includegraphics[width=8cm]{./diagrams/overlap.pdf}
+\includegraphics[width=8cm]{./overlap.pdf}
 \caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
+\includegraphics[width=0.9\columnwidth]{./rapidModelling.pdf}
 \caption{VTK visualisation output from code Listing~\ref{lst:pythonRapidModelling}.}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
+\includegraphics[width=0.9\columnwidth]{./faradayCup2.pdf}
 \caption{Example conversion of a simple FLUKA geometry to GDML. Above:
@@
 This is achieved with the use of axis-aligned bounding boxes (AABBs),
-in which the FLUKA body is translated to a finite solid with with
+in which the FLUKA body is translated to a finite solid with
 dimensions slightly larger than the AABB.  The lengths of infinite
@@
 \begin{center}
-\includegraphics[width=6cm]{./diagrams/lattice}
+\includegraphics[width=6cm]{./lattice.pdf}
 \caption{The lattice feature demonstrating a lattice cell
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
+\includegraphics[width=0.9\columnwidth]{./CuboidalChamber.pdf}
 \caption{Example conversion of a simple GDML geometry to FLUKA, above:
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/SectorBend.pdf}
+\includegraphics[width=0.9\columnwidth]{./SectorBend.pdf}
 \caption{Example conversion of a simple CAD (STEP) geometry (sector bend
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
+\includegraphics[width=1.0\textwidth]{./model.pdf}
 \caption{Complete compositing example using \PYGEOMETRY{}.}
@@
 The conversion which would most dramatically enhance the creation of RTMC geometry is CAD to Geant4 or FLUKA
-without use use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
+without use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
 FLUKA-like CSG geometry~\cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}. 

### 2020-11-10 public/paper/pyg4ometry.tex
Paper update
my changes including laurie's changes 2020-11-13

@@
 \usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{cleveref}
@@
 \newcommand{\PYGEOMETRY}{\textsc{Pyg4ometry}}
+\newcommand{\PYGEOMETRYPOS}{\textsc{Pyg4ometry's}} % possessive
 
@@
 %% TYPEWRITER /
+
+% Policy:  if referring to the class, then capitalise it and put it in monospace ofnt.
+% If we are referring to the concept, then we do not capitalise it and we do not put it in monospace font.
+
+% e.g. "Each \texttt{LogicalVolume} stores its mesh as an attribute"
+% versus
+% logical volumes in Geant4 can minimise duplication.
 
@@
 
-\author[a]{Stewart T. Boogert\corref{author}}
-\author[a]{Andrey Abramov}
-\author[a]{Laurence J. Nevay}
-\author[a]{William Shields}
-\author[a]{Stuart Walker}
+\author[a]{S.T. Boogert\corref{author}}
+\author[a]{A. Abramov}
+\author[a]{L.J. Nevay}
+\author[a]{W. Shields}
+\author[a]{S.D. Walker}
 
@@
 \begin{abstract}
-Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is an
+Creating and maintaining computer-readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is an
 error-prone and time-consuming task. Simulating a system often requires geometry from different sources and modelling
 environments, including a range of MCRT codes and computer-aided design (CAD) tools. \PYGEOMETRY{} is a Python library
-that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML)-based
-geometry used in simulations. \PYGEOMETRY{} provides importation of CAD files to GDML tessellated solids, conversion of GDML geometry
-to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  
-examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
+that enables users to rapidly create, manipulate, display, debug, read, and write Geometry Description Markup Language (GDML)-based
+geometry used in MCRT simulations. \PYGEOMETRY{} provides importation of CAD files to GDML tessellated solids, conversion of GDML geometry
+to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail in this paper and includes a number of small
+examples to demonstrate some of its capabilities. The paper concludes with a complete example using most of \PYGEOMETRYPOS{} features and a discussion of possible
 extensions and future work.
@@
 %% keywords here, in the form: keyword \sep keyword
-Geant; FLUKA; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;
+Geant4; FLUKA; GDML; CAD; STEP; Monte Carlo; Particle; Transport; Geometry;
 
@@
 
-{\bf PROGRAM SUMMARY}
+{\noindent \bf PROGRAM SUMMARY}
   %Delete as appropriate.
@@
 {\em Nature of problem:}\\  % (approx. 50-250 words)
-Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
+Creating computer-readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task.
 Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes
@@
 {\em Solution method:}\\  % (approx. 50-250 words)
-Create a Python application programming interface to read and write files of and process the geometry objects and specification 
-language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
-geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
+Create a Python application programming interface for the description and manipulation of Geant4 and FLUKA geometries, with full support for
+the direct reading and writing of their respective geometry description file formats.
+Form triangular meshes to represent geometric objects for both visualisation of the
+geometry and to enable the use of advanced mesh-based geometric algorithms. Triangular mesh processing algorithms allow the loading and use of STL and CAD/CAM
 files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from
-FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.
+FLUKA to Geant4 requires a number of steps including the replacement of infinite surfaces with finite solids and the automatic elimination of overlaps.
 
@@
  Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical
-imaging and therapy, and space radiation environment simulations are some examples. A fundamental requirement of all of the codes is to supply a 
+imaging and therapy, and space radiation environment simulations. A fundamental requirement of all of the codes is to supply a
 computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is
 typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no
-standard geometry format used across MCRT codes, with each code typically using its own unique format. A user will typically not have geometry in FLUKA and Geant4 for example. A geometry system 
-that allows the conversion between files prepared for different codes will enable cross-checks of the physics processes in different particle transport
+standard geometry format used across MCRT codes, with each code often using its own unique format. A user will typically not have geometry in both FLUKA and Geant4 for example. A geometry system
+that enables the conversion between files prepared for different codes will allow for cross-checks of the physics processes in different particle transport
  codes.  The file formats used for geometry are generally focused
- on the computational efficiency of a particle tracking task and not ease of use. In addition to the creation of geometry files for RT programs, usually 
+ on the computational efficiency of particle tracking algorithms  and not ease of use. In addition to the creation of geometry files for RT programs, usually
  computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not
@@
 Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam.
-\PYGEOMETRY{} allows the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
-is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by 
-\PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).
+\PYGEOMETRY{} allows the rapid creation and adaptation of geometry, with Figure~\ref{fig:workflow} demonstrating various possible workflows. \PYGEOMETRY{}
+is not an executable software package but a toolkit, a user would typically write a very small Python program to use the classes and functions provided by
+\PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a Git repository and via the Python Package Index (PyPi).
 
@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework,
-can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh~\cite{GUIMesh_Pinto}, commercial 
-products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
+can load, display and manipulate GDML-like geometry. Existing open source tools to convert CAD files to GDML include GUIMesh~\cite{GUIMesh_Pinto}, with commercial
+solutions including ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD
 geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL
-(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
-large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. Almost all modern CAD tools like 
-CATIA, Inventor, SolidWorks have a scripting language to allow users to programatically generate geometry. This scripting functionality is not available with either 
-GDML or FLUKA were users write the geometry files directly. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
-
-This paper is structured as follows, first a brief radiation transport-focused introduction to computer descriptions of geometry, followed by an explanation of the design 
-and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
+(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. However, in practice using a lot of CAD models is difficult if that model is composed of a
+large number of parts. This is because exporting, assigning material to, and placing the STL components into the MCRT code can be very cumbersome. Almost all modern CAD tools such as
+CATIA, Inventor and SolidWorks have a scripting language to allow users to programmatically generate geometry. Similar CAD-style scripting languages do not exist for either GDML
+or FLUKA and the existent set of software does not provide a complete set of tools to efficiently create complex geometries for these codes.
+
+This paper is structured as follows, first a brief radiation
+transport-focused introduction to computer descriptions of geometry and an explanation of the design
+and implementation of \PYGEOMETRY{}. Subsequent sections describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling as well as conversions from
 FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite, complex system consisting of components drawn from
@@
 geometry, including constructive solid geometry (CSG), boundary representation (BREP) and tessellated polygons, which are described
-briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
+briefly in this section.  The Geant4 geometry specification is a mixture of all three of these geometry modelling techniques and described in detail last.
 
 %%%%%%%%%%%%%%%%% Constructive solid geometry (CSG)
-Constructive solid geometry uses Boolean operations (subtraction, intersection and union), between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
+Constructive solid geometry uses Boolean operations (subtraction, intersection and union) between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
 volumes (e.g. a plane-defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a
-CSG tree to model complex geometry. FLUKA uses CSG to model solids, the form of Boolean expression used by FLUKA is not a general CSG tree but a 
+CSG tree to model complex geometry. FLUKA uses CSG to model solids, however the form of Boolean expression used by FLUKA is not a general CSG tree but a
 logical expression in disjunctive normal form.
@@
 %%%%%%%%%%%%%%%%% Geant4 geometery
-Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes 27 basic solids, although it does not store a sense 
-of topology present in traditional CAD BREP systems. One of the fundamental solids is a tessellated solid which can be used to represent STL or PLY files. 
-Geant4 also provides the ability to perform Boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
-Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this \emph{logical volumes}
-and \emph{physical volumes}. A logical volume is a region of space that is defined by an outer solid but also other attributes like material, magnetic field 
-and zero or more \emph{daughter} physical volumes. A physical volume is a placement (or instance) of a logical volume. This design permits large reuse 
-of objects, minimising memory footprint for largely repetitive structures such as detectors that Geant4 was created to simulate.
+Geant4 geometry description is the richest and most flexible of MCRT codes
+and consists of a mixture of BREP, CSG and tessellated concepts. Geant4
+includes 27 basic solids and it does not store a sense of topology
+present in traditional CAD BREP systems. One of the fundamental solids is a
+tessellated solid which can be used to represent STL or PLY files.  Geant4
+also provides the ability to perform Boolean operations on these primitive
+solids. Not only do solid objects need to be defined but also placed in a
+world coordinate system. Geant4 has two concepts which facilitate this:
+\emph{logical volumes} and \emph{physical volumes}. A logical volume is a
+region of space that is defined by an outer solid but also other attributes
+like material, magnetic field and zero or more \emph{daughter} physical
+volumes. A physical volume is a unique placement (or instance) of a logical
+volume. This design permits large reuse of objects, minimising memory
+footprint for largely repetitive structures such as detectors that Geant4
+was created to simulate.
+
+%%%%%%%%%%%%%%%%% Volume bounding
+If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully
+encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable
+to have a mother volume shape that efficiently holds its daughters. However, there are exceptions to this rule in the form of assembly volumes.
 
@@
 The constructors of the Python classes are kept as close to the original Geant4 C++ implementation as possible so that \PYGEOMETRY{} users do not have to learn
-a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
+a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|box| in GDML and is represented by the \pyinline{Box}
 class in \PYGEOMETRY{}. The Python object initialisers are very similar to their corresponding Geant4 C++ constructors, but the length definitions are those used by GDML. For example,
-GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
-A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
+GDML uses full-lengths whilst Geant4 uses half-lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4.
+A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the rest of this section novel or important developments
 in \PYGEOMETRY{} are described.
@@
 %%%%%%%%%%%%%%%%%  Input and output
-For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented: \verb|gdml.Reader|,
-\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| instance which 
+For each input format supported by \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented: \verb|gdml.Reader|,
+\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate \PYGEOMETRY{} classes and provides a \verb|Registry| instance which
 can be used or manipulated by the user.
@@
 The internal data representation closely follows the structure of GDML. A \verb|Registry| class aggregates Python ordered dictionaries that are  used to store the main
-elements of a GDML file. As a \PYGEOMETRY{} user instantiates the geometry the registry is correspondingly updated. When a user is finished with the geometry, the registry 
-can be written to disk as a GDML file. Multiple \verb|Registry| instances can be aggregated to form a composite geometry or volumes can be removed and added.
+elements of a GDML file.
+As a \PYGEOMETRY{} user instantiates the geometry the associated registry (typically provided as a keyword argument to the class initialiser) is updated.
+When a user is finished with the geometry, the registry
+can be written to disk as a GDML file. It is also possible to modify \verb|Registry| instances, for example by adding or removing volumes, or by combining with other instances to form an aggregate.
 
 %%%%%%%%%%%%%%%%%  Expression evaluation
-In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
+In GDML symbolic expressions can be used to parametrise solids and their placements. These expressions are evaluated when the GDML is loaded into Geant4.
 In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR~\cite{10.5555/2501720}. The GDML is loaded using
@@
 and assignment of variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special
-functions $\sin, \cos, \tan$, etc. The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally, all \PYGEOMETRY{} 
+functions. The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally, all \PYGEOMETRY{}
 classes use GDML expressions and not floating-point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of
@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
+Creating a uniform three-dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap
 detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent
 of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning
-(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b} in C++. In 
-general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
+(BSP) tree technique in pure Python~\cite{pycsg} or via the Computational Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b} in C++. In
+general, the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries.
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file
 various polygon mesh algorithms  from CGAL~\cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
-
-%%%%%%%%%%%%%%%%% Volume bounding
-If a user is creating and placing multiple daughter volumes within a \emph{mother} volume then it is the user's responsibility to create a solid which fully 
-encompasses the daughter volumes. Overlaps between daughter volumes and the mother can be detected, but it is desirable 
-% \colorbox{yellow}{It's not just desirable, it's absolutely necessary isn't it?  And I'm not sure what the word ``efficiently'' means precisely in this context.} 
-to have a mother volume shape that efficiently holds its daughters. However, there are exceptions to this rule in the form of assembly volumes.
 
@@
 
-The physical volume class (\pyinline{pyg4ometry.geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's 
-colour, surface or wireframe representation and visibility. Overlaps detected in the mesh geometry are
-stored in the Logical Volume and can be  displayed separately to allow a user to visually identify and debug the the overlaps.
+The physical volume class (\pyinline{geant4.PhysicalVolume}) is also used to store visualisation attributes like the solid's
+colour, surface or wire-frame representation and visibility. Overlaps detected in the mesh geometry are
+stored in the \pyinline{LogicalVolume} instance and can be  displayed separately to allow a user to visually identify and debug the overlaps.
 
 %%%%%%%%%%%%%%%%% Adding properties to volumes
-Geometry needs to be augmented with other information for a complete MCRT simulation. Often other attributes need to be 
+Geometry needs to be augmented with other information for a complete MCRT simulation. Often, other attributes need to be
 assigned to regions of space, for example material definition, magnetic field or optical properties. These physical properties
@@
 in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by
-performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
+performing an intersection operation between solid instances and determining if the resulting mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
 overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters
@@
 \includegraphics[width=8cm]{./diagrams/overlap.pdf}
-\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
+\caption{Schematic of the three different types of overlap between the daughters of a mother logical volume.}
 \label{fig:overlap}
@@
   \label{algo:overlap}
-  \caption{The overlap checking algorithm employed in \PYGEOMETRY{}.}
+  \caption{The overlap checking algorithm employed in \PYGEOMETRY{}.  The
+    algorithm proceeds by performing the CSG intersection of pairs of
+    daughter volume meshes for a given logical volume.  Non-null intersections
+    between daughter volume meshes are treated as overlaps.}
 \end{algorithm}
 
-Overlap detection in \PYGEOMETRY{} relies of the meshes generated for each solid, 
-any detection algorithm will be approximate. Generally the overlap detection 
+Overlap detection in \PYGEOMETRY{} relies on the meshes generated for each solid.  As
+these mesh representations will generally approximate their respective solid,
+so to will any overlap detection algorithm be an approximation. Generally, the overlap detection
 algorithm proceeds as shown in Algorithm~\ref{algo:overlap}.
 For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids have an average number of faces $n$, clearly this algorithm
-has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters}^2)$. This might seem like a prohibitive computational cost, but worth it considering the potential 
-waste if small overlaps are present in the final MCRT simulation and large amounts of cluster CPU time is wasted. This algorithm clearly favours geometry 
+has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters}^2)$. This complexity
+can result in a steep computational cost for highly-flat geometry
+hierarchies, but overall remains worthwhile considering the potential
+waste in large amounts of cluster CPU time if small overlaps are present in the final MCRT simulation. This algorithm clearly favours geometry
 descriptions which have a high degree of logical volume reuse, however this is also true of Geant4 as a whole, so the user will likely be inclined to design along such lines regardless.
 Due to the discrete nature of triangular meshes it is not possible to have perfect detection
-of overlaps, especially when curved surfaces are considered. The deviation of the meshes created from a solid can be controlled by the user reducing the 
-chances of missing a potential overlap, but the algorithm presented here cannot capture all overlap cases. The overlap detection algorithm can 
-present the potential overlaps quickly and easily to the user, thus significantly aiding their modelling process.
+of overlaps, especially when curved surfaces are considered, and in some rare
+cases either overlaps maybe missed, or spurious overlaps maybe reported.  However, the density of the meshes
+created for the solids is controllabe by the user, meaning that the user
+can opt for more precise overlap checking at the cost of greater
+computation time.  In general, the overlap detection algorithm can
+present the potential overlaps quickly and easily to the user, thus
+significantly aiding the design process.
 
@@
 Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary
-the parameters of the geometry and visualise it.  When a user has achieved the desired geometry without geometry overlaps, a GDML file can be written to file 
-from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
+the parameters of the geometry and visualise it.  When a user has achieved the desired geometry without geometry overlaps, a GDML file can be written
+from the internal memory representation.
+An example of some of the geometry scripting capabilities of \PYGEOMETRY{} is shown in Listing~\ref{lst:pythonRapidModelling}.
+The structure should be familiar to regular
 users of Geant4 or GDML, apart from the new class described in the previous section called the \verb|Registry|. First the \verb|Registry| is created to store all
-the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
+the \PYGEOMETRY{} objects; followed by constants;  then materials, solids, logical volumes, physical volumes and other properties such as visualisation attributes; and finally the whole geometry can be saved
 as a GDML file or visualised using VTK.
@@
 
-# define world volume
-reg.setWorld(wl.name)
+reg.setWorld(wl.name) # define world volume
 
@@
 as the GDML it writes. The benefit of wrapping GDML in Python is that it allows
- very rapid prototyping of geometry without concerns of C++ compilation  (in the 
-case of implementing the geometry directly in Geant4) or writing well formed XML (in the case of GDML). Effectively
-the Python interpreter checks input for syntax errors when using \PYGEOMETRY{} classes. 
+ very rapid prototyping of geometry without the overhead of C++ compilation  (in the
+case of implementing the geometry directly in Geant4) or writing well-formed XML (in the case of GDML). Effectively,
+by using \PYGEOMETRY{}, the set of possible user-errors when describing geometry in C++ or XML
+instead either manifest as Python exceptions or are eliminated entirely.
 Another key benefit is the ability to use the \PYGEOMETRY{} code to create
@@
   the original FLUKA geometry displayed in flair, FLUKA's graphical user interface.
-  Below: the GDML geometry viewed using \PYGEOMETRY{}. The example is a Faraday cup used to capture
+  Below: the GDML geometry viewed using \PYGEOMETRYPOS{} VTK visualiser. The example is a Faraday cup used to capture
 and measure accelerator beam charge.}
@@
 
-Each FLUKA body is represented in \PYGEOMETRY{} with a corresponding
-class, and in turn each class has methods which returns a GDML
-primitive solid and that solid's rotation and position such that it
-matches its FLUKA equivalent.  The expansion, translation and
-transform geometry directives are each folded into one or more of
-these three methods.  The mapping of FLUKA bodies to GDML solids is
-shown in Table~\ref{tab:Fluka2Geant4}.  It is worth noting that many
-of the FLUKA bodies are infinite in extent, but are mapped to finite
-GDML solids.  The translation of infinite bodies to equivalent finite
-solids is one of the main and most involved steps in the conversion process.
-This mapping is possible because whilst FLUKA bodies can be infinite
-in extent, all zones and regions must be finite.  Zones and regions
-are then composed by instantiating these classes and adding body
-instances to them.  Each Zone and Region instance can then return its
+Each FLUKA body is represented in \PYGEOMETRY{} with a corresponding class,
+and in turn each class has a method that returns a GDML primitive solid and
+a method that returns that solid's rotation and position such that it
+matches its FLUKA equivalent.  The expansion, translation and transform
+geometry directives are each folded into one or more of these three
+methods.  The mapping of FLUKA bodies to GDML solids is shown in
+Table~\ref{tab:Fluka2Geant4}.  It is worth noting that many of the FLUKA
+bodies are infinite in extent, but are mapped to finite GDML solids.  The
+translation of infinite bodies to equivalent finite solids is one of the
+main and most involved steps in the conversion process.  This mapping is
+possible because whilst FLUKA bodies can be infinite in extent, all zones
+and regions must be finite.  Zones and regions are then composed by
+instantiating these classes and adding body instances to them.  Each
+\pyinline{Zone} and \pyinline{Region} instance can then return its
 equivalent GDML Boolean solid.
 
-The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
-producing an AST.  The resulting AST is then inspected sequentially (walked)
-to populate Region instances with zones and bodies.  With the region
-instances populated they can then be manipulated and translated into GDML.
-The translation involves a number of special steps to bridge the two
-disparate formats and ensure the resulting GDML is well-formed and usable
-in Geant4.  Some of these steps are simple, for example in FLUKA unions can
-be disconnected, but in Geant4 specifically only MultiUnions can be
-disconnected, such that MultiUnions are used throughout the converted
-geometry instead of the usual binary unions.  Other procedures are more
-involved and are discussed in the rest of this section.
-
-\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a FLUKA file.},label={lst:pythonFlukaLoading}, language=Python]
-reader      = pyg4ometry.fluka.Reader("FlukaFileName.inp")
-g4_reg     = pyg4ometry.convert.fluka2Geant4(reader.flukaregistry)
-logical      = g4_reg.getWorldVolume()
+The FLUKA CSG ASCII is parsed using an ANTLR4-generated parser,
+producing an AST.  The resulting AST is then inspected sequentially
+(\emph{walked}) to populate \pyinline{Region} instances with zones and bodies.
+With the \pyinline{Region} instances populated they can then be manipulated
+and translated into GDML.  The translation involves a number of special
+steps to bridge the two disparate formats and ensure the resulting GDML is
+well-formed and usable in Geant4.  Some of these steps are simple, for
+example in FLUKA unions can be disconnected, but in Geant4 specifically
+only MultiUnions can be disconnected.  Therefore, MultiUnions are used
+throughout the converted geometry instead of the more conventional binary unions.
+Other procedures are more involved and are discussed in the rest of this
+section.
+
+\begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a
+    FLUKA file and convert its geometry to a Geant4 logical volume.},label={lst:pythonFlukaLoading}, language=Python]
+import pyg4ometry.fluka as fluka
+from pyg4ometry.convert import fluka2Geant4
+
+reader     = fluka.Reader("FlukaFileName.inp")
+g4Registry   = fluka2Geant4(reader.flukaregistry)
+logical      = g4Registry.getWorldVolume()
 \end{lstlisting}
@@
 to the bounding box as possible whilst retaining an identical final
-Boolean geometry.
+Boolean geometry.   Resizing and translating all bodies with respect
+to the region bounding boxes ensures that an identical region geometry can
+be generated, albeit from much smaller constituent bodies.
 
 Generating these bounding boxes over which the bodies should be translated
-involves first evaluating each region with very large Tubs, EllipticalTubes
-and Boxes (by default \SI{50}{\km} in length), such that they are
-effectively infinite for most reasonable use cases.  \PYGEOMETRY{}'s CSG
-meshing is then used to generate a mesh for each region from which the
-axis-aligned bounding box can be extracted.  Each region is then evaluated
-a second time with respect its respective bounding box, with all of its
-constituent infinite solids being reduced as described above.  The
-implementation is described in
+to GDML involves first evaluating each region with very large \pyinline{Tub},
+\pyinline{EllipticalTube} and \pyinline{Box} instances (by default
+\SI{50}{\km} in length), such that they are effectively infinite for most
+reasonable use cases.  \PYGEOMETRY{}'s CSG meshing is then used to generate
+a mesh for each region from which the axis-aligned bounding box can be
+extracted.  Each region is then evaluated a second time with respect to its
+ bounding box, with all of its constituent infinite solids being
+reduced in size as described above.  The implementation is described in
 Algorithm~\ref{algo:redundant-halfspace}. This algorithm works robustly for
-infinite (elliptical) cylinders and half-spaces as the number of facets is
+half-spaces, infinite circular cylinders and infinite elliptical cylinders
+as the number of facets belonging to the mesh for such solids is
 independent of the size of the solid, so generating the initial mesh from
-large solids works well.  Generating a quadric surface over a very large
+arbitrarily large solids works well.  Generating a quadric surface over a very large
 volume in space whilst retaining topological information is computationally
@@
 \subsection{Removing redundant half-spaces}
-The above algorithm for replacing infinite FLUKA bodies with finite
-Geant4 solids works well in most cases, but additional care must be
-taken for redundant infinite half-spaces.  A redundant infinite half-space
-is defined as one which has no effect on the shape of the
-final Boolean solid.  Whilst this may be true of arbitrary bodies, it
-is most problematic for half-spaces as after the infinite body
-reduction has been performed. If the half-space is far away from the
-region's AABB, then it can result in a malformed Boolean. Such
-half-spaces are filtered from their respective regions during the
-conversion process by calculating the nearest distance from the centre
-of the AABB to the half-space face.  If this distance is greater than
-the centre-to-corner distance of the AABB, then that half-space is
-removed from the region during conversion.
+The above algorithm for replacing infinite FLUKA bodies with finite Geant4
+solids works well in most cases, but additional care must be taken for
+redundant infinite half-spaces.  A redundant infinite half-space is defined
+as one which has no effect on the shape of the final Boolean solid.  Whilst
+this may be true of arbitrary bodies, it is most problematic for
+half-spaces. If the half-space is far away from the region's AABB after the
+infinite body reduction has been performed, then it can result in a
+malformed Boolean. Such half-spaces are filtered from their respective
+regions during the conversion process by calculating the nearest distance
+from the centre of the AABB to the half-space face.  If this distance is
+greater than the centre-to-corner distance of the AABB, then that
+half-space is deemed to be redundant with respect to that region and is
+removed from it during conversion.
 
 \subsection{Coplanar faces}
-Coplanar faces, in which the faces of two union components or that of
-two regions are perfectly coplanar in FLUKA are ubiquitous and present
-no difficulties to the operation of the program.  However, in Geant4
-these will generally result in tracking errors.  These must be handled
-robustly to ensure the resulting geometry is usable.  Coplanar faces
-are resolved automatically by slightly decreasing the size of every
-body that is used in an intersection, and increasing the size of every
-body used in a subtraction.  These rules are inverted for nested
-subtractions and work well for guaranteeing well-formed geometry that
-is free from tracking errors.
+Coplanar faces present a problem during conversion where the faces of two
+union components or that of two regions are perfectly coplanar in FLUKA.
+Coplanar faces of this nature are ubiquitous in FLUKA and present no
+problems to the operation of the program.  However, in Geant4 these will
+generally result in tracking errors.  These must be handled robustly to
+ensure the resulting geometry is usable.  Coplanar faces are resolved
+automatically by slightly decreasing the size of every body that is used in
+an intersection, and increasing the size of every body used in a
+subtraction.  These rules are inverted for nested subtractions.  This
+algorithm ensures that all coplanar faces are removed and replaced with
+resolvable, small gaps between faces.  This approach works well for
+guaranteeing well-formed geometry that is free from tracking errors in Geant4.
 
@@
 \pyinline{BuiltIn}, \pyinline{Material}, and \pyinline{Compound} classes.
-Populating a hierarchy of instances using these classes is involved due to
+Populating a hierarchy of instances using these classes is made more involved due to
 the fact that recursively-defined materials in FLUKA input files need not
@@
 To account for this it is necessary to correctly compute the instantiation
-order so that the above classes and be instantiated correctly.  To do this
+order so that the above classes can be instantiated correctly.  To do this
 a directed acyclic graph is populated with the materials and their
@@
 compound materials are sequenced after their constituents.  Mapping this
-set of nested FLUKA material instances to GDML material instances is then
-straight forwards as the GDML material semantics are slightly more
-expressive than FLUKA's, so a one-to-one mapping is trivial.
+set of nested FLUKA materials to GDML materials is then
+straight forwards as the two formats are similarly expressive.
 
@@
 This feature is clearly analogous to the logical/physical volume feature in
-Geant4, although it is less explicit as the contents of a given logical
-volume are clearly stated, whereas the contents of a lattice cell
+Geant4, although it is more implicit as the contents of a given logical
+volume are explicitly stated, whereas the contents of a lattice cell
 are implied by the combination of the rototranslation and the locations of
@@
 
-Translating the lattice construct into a logical volume (basic unit) with many
-physical volumes (lattice cells) requires associating each
-lattice cell with the full contents of its corresponding basic unit
-(typically several regions). This is achieved by meshing the complete
-FLUKA geometry and then rototranslating the lattice cell mesh with
-its associated rototranslation. By construction this will translate the
-lattice cell mesh directly onto the full basic unit mesh. Finally,
-in checking for overlaps, the regions within the the basic unit can be
-determined. In the final conversion step, the lattice cell can
-simply be replaced with a physical volume that refers back to logical
-volumes located in the previous step. Thus a basic unit with one or more lattice cells can
-be translated into Geant4's logical volume with one or more physical volumes. As has been stated,
-FLUKA supports two levels of nesting, but currently the conversion to GDML
-supports only one. However, extending to an extra level is simple in that
-it only involves an extra application of a rototranslation matrix before
-checking for overlaps.
+Translating the lattice construct into a logical volume (basic unit) with
+many physical volumes (lattice cells) requires associating each lattice
+cell with the full contents of its corresponding basic unit (typically more
+than one region). This is achieved by meshing the complete FLUKA geometry
+and then rototranslating the lattice cell mesh with its associated
+rototranslation. By construction this will translate the lattice cell mesh
+directly onto the full basic unit mesh. This transformed lattice cell mesh
+can then be intersected with all other meshes in the scene.  Intersections
+with the transformed lattice cell mesh determine the contents of the basic
+unit.  Finally, the lattice cell can simply be replaced with a physical
+volume containing the logical volumes determined in the previous step.
+Thus a basic unit with one or more lattice cells can be translated into
+Geant4's logical volume with one or more physical volumes. As has been
+stated, FLUKA supports two levels of lattice nesting, but currently the
+conversion to GDML supports only one. However, extending to an extra level
+is simple in that it only involves an additional application of a
+rototranslation matrix before checking for intersections with the lattice
+cell mesh.  This capability will be added in a future release.
 
@@
 geometries, however a number of possible improvements for the future
-remain.  For example, Boolean solids in FLUKA can in general be
-disconnected, and this typically manifests itself in the form of
-disconnected unions, but is also allowed for intersections and
-subtractions.  Disconnected unions are readily available in GDML with the
-use of the MultiUnion solid type, however there is no valid means to
-construct a disconnected intersection or subtraction in GDML.  One possible
-solution would be to detect these two cases, and if found, split them into
-their constituent parts and place separately as TesselatedSolid instances.
-
-Furthermore, the quadric surface conversion can be further improved by
-specialising on some of the individual forms of the quadric.  Simply
-converting every quadric into a TesselatedSolid comes at a potential
-performance cost in the tracking, as well as usability in \PYGEOMETRY{} as the
-user must provide an AABB.  In some cases tessellation in unavoidable (for
-example a hyperbolic paraboloid), but parabolic cylinders could for example
-be translated to an ExtrudedSolid.  This could provide both a performance
-improvement in the tracking time and make \PYGEOMETRY{} easier to use as an
-AABB would not need to be provided beforehand.  This has not been
-implemented as quadrics are relatively rarely used, but where quadrics are
-used it is often in the form of parabolic cylinders (e.g. magnet pole tips) and this
-specialisation in particular would be worth implementing.
+remain.  For example, FLUKA regions can in general be disconnected, that is
+to say the resulting set of points defined by that region may consist of
+two disconnected subvolumes.  In FLUKA this typically manifests itself in
+the form of disconnected unions, but it is also allowed for intersections
+and subtractions to be disconnected.  In the case of translating
+disconnected unions from FLUKA to GDML, this presents no difficulties as
+the GDML \pyinline{MultiUnion} solid is explicitly allowed to be formed from
+disconnected parts.  However, it is forbidden for \pyinline{Intersection} or
+\pyinline{Subtraction} solids to be disconnected in this way and is
+therefore necessary to account for this difference between the two codes.
+One solution to this problem would involve detecting and separating
+disconnected meshes, and then placing each separated component as a
+separate \pyinline{TesselatedSolid} instance.  This decomposition has not
+been implemented and is left as future work.
+
+Furthermore, the quadric surface conversion can be improved by specialising
+on some of the individual forms of the quadric.  Simply converting every
+quadric into a TesselatedSolid comes at a potential performance cost in the
+tracking, as well as usability in \PYGEOMETRY{} as the user must provide an
+AABB for every single region featuring a quadric body.  In some cases
+tessellation is unavoidable (for example a hyperbolic paraboloid), but
+parabolic cylinders could for example be mapped to an \pyinline{ExtrudedSolid}.
+This could provide both a performance improvement in the tracking time and
+make \PYGEOMETRY{} easier to use as an AABB would not need to be provided
+beforehand.  This has not been implemented as quadrics are relatively
+rarely used, but where quadrics are used, it is often in the form of
+parabolic cylinders (e.g. magnet pole tips) and this specialisation in
+particular would be worth implementing.
 
@@
 It is relatively straight forward to convert Geant4 geometry to FLUKA. Each
-of the Geant4 solids can be mapped to a FLUKA region.  A region is a region
+of the Geant4 solids can be mapped to a FLUKA region.  A region is a volume
 of space defined by a material and the Boolean disjunction (a union using
-the operator~$\:|\:$ in free format geometry) of one or more
-zones. Each zone is then defined in terms of the conjunction (intersection
-with~$+$, subtraction with~$-$) of one or more primitive bodies, as well as
-parentheses to determine the order of operations within the zone.  FLUKA
-has 20 of these primitive bodies, listed in Table~\ref{tab:Fluka2Geant4}
-and, in general, infinite-extent bodies have tracking accuracy and
-efficiency benefits over finite ones. Key for conversion are XY-, XZ-,
-YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA), Z-axis aligned cylinder
-(ZCC), Z-axis aligned elliptical cylinder (ZEC), sphere (SPH), truncated
-right-angle cone (TRC) and general quadric surface (QUA). Some solids in
-Geant4 directly map to a single FLUKA body, others require the construction
-of a simple FLUKA CSG tree combining these
+the operator~$\:|\:$ in free format geometry, the most widely-used FLUKA
+CSG format) of one or more zones. Each zone is then defined in terms
+of the conjunction (intersection with~$+$, subtraction with~$-$) of one or
+more primitive bodies, as well as parentheses to determine the order of
+operations within the zone.  FLUKA has 20 of these primitive bodies, listed
+in Table~\ref{tab:Fluka2Geant4} and, in general, infinite-extent bodies
+have tracking accuracy and efficiency benefits over finite ones. Key for
+conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary plane (PLA),
+Z-axis aligned cylinder (ZCC), Z-axis aligned elliptical cylinder (ZEC),
+sphere (SPH), truncated right-angle cone (TRC) and general quadric surface
+(QUA). Some solids in Geant4 directly map to a single FLUKA body, others
+require the construction of a simple FLUKA CSG tree combining these
 primitives. Table~\ref{tab:geant2fluka} lists the mapping between Geant4
@@
 \end{table}
-
-There are some important issues which must be considered to perform an accurate conversion. 
-A Geant4 logical volume solid might need to be created from a FLUKA region consisting of many zones (i.e. unions), 
-so~$R_1 = +z_1\: | +z_2$, similarly a void is required to locate daughter volume placements which again 
-might also be converted to a region of multiple zones~$R_2= +z_3 \: | +z_4$. So creating the FLUKA region is then 
-\begin{eqnarray}
+Understanding the algebra of FLUKA CSG and how it relates to Geant4's
+concepts of solids, logical volumes and physical volumes must be understood
+to perform an accurate conversion.  For example, a Geant4 logical volume
+solid may correspond to a FLUKA region consisting of many zones
+(i.e. unions), e.g.,~$R_1 = +z_1\: | +z_2$.  If this logical volume is
+placed as a physical volume inside some mother volume with its solid
+perhaps consisting of multiple zones, e.g., $R_2= +z_3 \: |~+z_4$, then
+subtracting a hole in the mother solid to make room for the daughter
+results in an equation of the form
+\begin{equation}
+  \begin{aligned}
 R_1 - R_2 	& = & (+z_1 \: | +z_2) - ( +z_3 \: | +z_4) 			\\
@@
 \label{eqn:setDiff}
-\end{eqnarray}
-Geant4 has the Boolean solids associated with difference, union and intersection, so in addition to 
-Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ is required in FLUKA notation, so 
-\begin{eqnarray}
+  \end{aligned}
+\end{equation}
+Geant4 has Boolean solids associated with difference, union and intersection, so in addition to
+Equation~\ref{eqn:setDiff}, both $R_1 \cup R_2$ and $R_1 \cap R_2$ are required in FLUKA notation, so
+\begin{equation}
+  \begin{aligned}
 R_1 \cup R_2 	& = & (+z_1 \: | +z_2)  \cup ( +z_3 \: | +z_4) \\
@@
 \label{eqn:setUnion}
-\end{eqnarray}
+\end{aligned}
+\end{equation}
 and
-\begin{eqnarray}
+\begin{equation}
+  \begin{aligned}
     R_1 \cap R_2 	& = & (+z_1 \: | +z_2) \cap ( +z_3 \: | +z_4) \\
 			& = & +z_1 +z_3  \; | +z_1 +z_4 \; | +z_2 +z_3 \; | +z_2 +z_4\,.
+  \end{aligned}
 \label{eqn:setIntersection}
-\end{eqnarray}
+\end{equation}
 
@@
 when converting Geant4 logical volumes to FLUKA regions, as the logical volume outer solid~$S_{\rm logical}$
-need to have the daughter  solids~$S_{{\rm daughter},i}$ subtracted. A solid which can be converted 
+needs to have the daughter  solids~$S_{{\rm daughter},i}$ subtracted. A solid which can be converted
 to a region~$S_{\rm region}$ is then
@@
 vacuum chamber with three ConFlat flange (CF) beam pipes connected to CF flanges. The top and bottom plates
-have been removed to display the geometry more clearly. The model is formed of \verb|G4Box| and
-\verb|G4Tubs| and Boolean operations of subtraction, intersection and union.
-
-\subsection{Non-Convex solid decomposition}
-In general the BREP solids used by Geant4 include non-convex solids, such as  Polycone, Xtru, and Twisted.  These 
-particular solids are problematic when converting them to a FLUKA-readable format, as non-convex solids 
-can only be created by the union of convex zones. There are two groups which need to considered, firstly those 
-where 2D polygonal section needs to be decomposed, these include Polycone, Polyhedron and Xtru, secondly 
-those where three-dimensional convex decomposition is required  TwistedBox, TwistedTrap, TwistedTrd, 
-TwistedTube and Tessellated. The second classification of non convex solids are converted to CGAL 
-Nef polyhedra~\cite{cgal:hk-bonp3-20b} and decomposed to convex polyhedra~\cite{cgal:h-emspe-20b}.
+have been removed to display the geometry more clearly. The model is formed of \verb|Box| and
+\verb|Tubs| and Boolean operations of subtraction, intersection and union.
+
+\subsection{Non-convex solid decomposition}
+In general the BREP solids used in Geant4 include non-convex solids such
+as polycones, extrusion solids, and twisted solids.  Converting these
+solids to an equivalent FLUKA representation is problematic as non-convex
+solids can only be created by the union of convex zones. Generating these
+zones is non-trivial and these solids can be divided into two groups based
+on the techniques required for the decomposition.  First are those where only a 2D polygonal
+section needs to be decomposed, and these include polycones, polyhedrons
+and extrusion solids.  The second group are those which require a full 3D
+convex decomposition, and these include the twisted and tessellated solids.
+This second group of non-convex solids are converted to CGAL Nef
+polyhedra~\cite{cgal:hk-bonp3-20b} and decomposed to convex
+polyhedra~\cite{cgal:h-emspe-20b}.
 
 \subsection{Disjunctive normal form and degenerate surfaces}
-Typically FLUKA will decompose a region into disjunctive normal form (DNF), this normal form is 
-characterised as the union of intersections and subtractions,
+Typically FLUKA will decompose a region into disjunctive normal form (DNF)
+as runtime, this normal form is characterised as the union of intersections and subtractions,
 \begin{equation}
@@
 Defining regions in terms of the DNF allows the rapid test of whether a point is inside that region. Testing each zone
-$z_i$ of $R$ can terminate if a point is determined to be inside any of the convex zones $z_i$. In general 
+$z_i$ of $R$ can terminate if a point is determined to be inside any of the zones $z_i$. In general
 Equation~\ref{eqn:logicalSubtraction} does not have the form of a DNF. If there are many levels of logical-physical volume
@@
 card. Geant4 also defines a set of standard materials~\cite{Geant4MaterialDB} or compounds from the US National Institute
-of Standards and Technology (NIST), so a user can for example, simply
+of Standards and Technology (NIST), so a user can, for example, simply
 specify the name \pyinline{G4_STAINLESS-STEEL}. \PYGEOMETRY{}  contains a matching database and creates the appropriate FLUKA
-cards from these names during the conversion. This database is updated by running a small Geant4 program to output the appropriate
-material data.
+cards from these names during the conversion. This database is updated when
+necessary by running a small Geant4 program to output the appropriate material data.
 
 \subsection{Discussion}
-Overall the conversion to FLUKA input format from GDML is quite 
-advanced and stable. Relatively large experimental simulations 
-have been converted from GDML to FLUKA and have been used to produce 
-simulation results. The conversion described still requires a user to
-understand how geometry is specified in both Geant4 and FLUKA. For 
-example the subtraction of many non-primitive body daughter volumes from 
-a mother will create a very complex non-DNF region which is inefficient when viewed in 
-FLUKA's graphical user interface (GUI), flair, and used for simulation in FLUKA.
-A geometry designer can avoid this by
-restricting daughter volumes solids in Geant4 that can be expressed in DNF simply,
-for example a cuboid.  If \PYGEOMETRY{} is used during the creation of
- geometry then multiple codes can be targeted without additional user effort. 
-There are still a few outstanding technical issues with the conversion, which are discussed 
-in this section.
-
-Currently replica, division and parametrised placements are not implemented 
+Overall the conversion to FLUKA input format from GDML is quite advanced
+and stable. Relatively large experimental simulations have been converted
+from GDML to FLUKA and have been used to produce simulation results. The
+conversion described still requires a user to understand how geometry is
+specified in both Geant4 and FLUKA. For example the subtraction of many
+non-primitive body daughter volumes from a mother will create a very
+complex region that is not in disjunctive normal form which is inefficient
+when viewed in FLUKA's graphical user interface (GUI), flair, and used for
+simulation in FLUKA.  Users who wish to minimise this should ensure that
+there are not large numbers of daughter volumes at the same level in the
+hierarchy, unless corresponding to solids which translate to simple
+primitives such as boxes.  Complex daughter volumes consisting of solids
+that are complex Booleans should be placed inside primitive solids that map
+to primitive FLUKA bodies.  This ensures that expanding to the DNF is
+computationally tractible, and in doing do FLUKA's tracking will be faster.
+This is not a drastic constraint on the conversion functionality, however,
+as this is actually typically how one would implement geometries in FLUKA
+regardless.
+
+With the above in mind it is perhaps preferable for a user creating
+geometry from scratch to use \PYGEOMETRY{} and these conversion tools
+as part of the process.  This would allow a user to target multiple codes with
+a single source description with minimal additional effort.  However, there
+are still a  outstanding technical issues with the conversion, which are discussed in
+this section.
+
+Replica, division and parametrised placements are not currently implemented
 and will be added in a future release. In Geant4 it is possible to create scaled
-solids or placements with reflections, referred to as \emph{scale} in Geant4. FLUKA 
+solids or placements with reflections (referred to as \emph{scale} in Geant4). FLUKA
 rototranslations do not support reflections and implementing reflections
-require transformation of the body definitions. This is not yet implemented 
+requires transformation of the body definitions. This is not yet implemented
 in the current version of \PYGEOMETRY{}.
@@
 In general, recursive application of Equations \ref{eqn:setDiff},
-\ref{eqn:setUnion}, \ref{eqn:setIntersection} and~\ref{eqn:logicalSubtraction} 
-can result in very complex regions when converting from Geant4/GDML to 
-FLUKA. The complexity of the final region expression can be compounded 
-if transformed to DNF. The final region Boolean expression can be simplified by 
-evaluating using the meshes for the surfaces, only retaining terms which 
-do not evaluation to a null mesh.
-
-It is possible given the GDML to FLUKA conversion algorithm described 
-in this paper that coplanar overlaps exist in the FLUKA geometry.  In 
-Geant4 there is no connection between surfaces used to specify on 
-logical volume solid and another logical volume solid. So for example 
-if a logical volume solid shared a face with one its daughter volume 
-solids the body would be duplicated in the final FLUKA file. It 
-is possible to remove obvious degeneracies but this is complicated by 
-placements of bodies. It should be possible to cast FLUKA bodies 
-{\em without} rototranslations into a {\em normal form} which can be used 
-to test for approximate equality. Approximate equality is required as 
-multiple application rototranslations will accrue numerical rounding errors.
-A simple example of this is the XYP and PLA, it simple to transform an 
-XYP into a PLA with an appropriate rotation. This would allow for the removal 
-of degenerate surfaces removing potential coplanar overlaps and also reduce 
-the final converted file size.
+\ref{eqn:setUnion}, \ref{eqn:setIntersection}
+and~\ref{eqn:logicalSubtraction} can result in very complex regions when
+converting from Geant4/GDML to FLUKA. The complexity of the final region
+expression can be compounded if transformed to DNF. The final region
+Boolean expression in DNF can be simplified by using the meshes of the
+intermediate parts, only retaining terms which do not contribute to the
+overall definition of the geometry (e.g. subtracting with a solid that
+does not overlap any other solid), using an algorithm similar to the one
+outlined in~\cite{pruning}.
+
+It is possible given the GDML to FLUKA conversion algorithm described in
+this paper that coplanar overlaps exist in the FLUKA geometry.  In Geant4
+there is no connection between surfaces used to specify one logical volume
+solid and another logical volume solid. For example if a logical volume
+solid shares a face with one its daughter volume solids, and those faces
+when translated to FLUKA are expressed in terms of half-spaces for example,
+those half-spaces would be duplicated in the final FLUKA file.  It is
+possible to remove obvious degeneracies but this is complicated by
+placements of bodies. Every FLUKA body with an arbitrary number of
+associated transformations (rototranslations, rotations or expansions)
+provided by geometry directives can be re-expressed purely in terms of a
+body (possibly of a different type) without any transform.  For example, a
+sphere with a geometry directive translation can be re-expressed as a
+sphere without a translation, and instead with offset added directly to the
+sphere's centre.  This {\em normal form} can be used to test for
+approximate equality between bodies that are equivalent whilst accounting
+for any transforms.  Approximate equality is required as multiple
+applications of rototranslations will accrue numerical rounding errors such
+that true equality is not maintained.  A simple example of this is the XYP
+and PLA, it is simple to transform an XYP into a PLA with an appropriate
+rotation. This would allow for the removal of degenerate surfaces removing
+potential coplanar overlaps and also reduce the final converted file size.
 
@@
 succeed or produces a far from optimal number of convex solids.
-An alternative to implement these solids is to approximate each 
+An alternative to implementing these solids is to approximate each
 layer of the twisted solid as a union of tetrahedra. A similar problem
 exists for general tessellated solids, which in general
-are non-convex and need decomposition into convex hulls. A potential 
-way to avoid a computationally expensive decomposition step is to 
+are non-convex and need decomposition into convex hulls. An alternative
+to the computationally expensive convex decomposition is to
 create a region formed from the unions of tetrahedra. There are numerous
 algorithms for tetrahedralisation of surface meshes in both CGAL and TetGen~\cite{tetgen}
-and will be implemented in a future release. Even if a stable and general 
-method for converting tessellated solids exists it not efficient to define 
-tessellated objects in this way and memory, body or zone limits might
-be reached in FLUKA and so limit the size of CAD or STL models which 
+and these will be implemented in a future release of \PYGEOMETRY{}. Even if a stable and general
+method for converting tessellated solids exists, it is not efficient to define
+tessellated objects in this way.  Memory, body or zone limits might
+be reached in FLUKA, thus possibly limiting the size of CAD or STL models which
 might be loaded.
@@
 STEP and IGES files can be loaded into \PYGEOMETRY{}, via an interface
-based on FreeCAD~\cite{FreeCAD}. FreeCAD is an open source CAD/CAM program, which 
-in turn is based on OpenCASCADE. FreeCAD allows for scripting in Python 
-and acts as a simple-to-use interface to OpenCASCADE.  A STEP CAD file 
-could be considered as a hierarchical tree of parts and \emph{part assemblies}, 
-where a part assembly is a collection of \emph{part features}. A part feature can be used 
-to create a triangular mesh which can be used to instantiate a \PYGEOMETRY{} tessellated solid. The placement 
-of the part feature is extracted from the STEP file and used to create an 
-appropriate physical volume. Assignment of materials and visualisation 
-attributes must be performed by  the user after conversion to GDML as rarely 
-will CAD/CAM packages included the detailed information required for MCRT 
-codes. Listing~\ref{lst:pythonCADLoading} shows 
-how \PYGEOMETRY{} can load step files.
+based on FreeCAD~\cite{FreeCAD}. FreeCAD is an open source CAD/CAM program,
+which in turn is based on OpenCASCADE. FreeCAD allows for scripting in
+Python and acts as a simple-to-use interface to OpenCASCADE.  A STEP CAD
+file could be considered as a hierarchical tree of parts and \emph{part
+  assemblies}, where a part assembly is a collection of \emph{part
+  features}. A part feature can be used to create a triangular mesh which
+can be used to instantiate a \PYGEOMETRY{} \pyinline{TessellatedSolid}. The
+placement of the part feature is extracted from the STEP file and used to
+create an appropriate physical volume. Assignment of materials and
+visualisation attributes must be performed by the user after conversion to
+GDML as it is rarely the case that CAD/CAM packages include the detailed
+information required for MCRT codes. The loading of STEP files in
+\PYGEOMETRY{} is demonstrated in Listing~\ref{lst:pythonCADLoading}.
+
 \begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
@@
 \end{lstlisting}
-Compared to other file readers, two additional steps are required \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model 
+Compared to other file readers, two additional steps are required: \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model
 part names can contain characters which are not allowed in Python dictionaries so need to be replaced by \pyinline{relabelModel}.
 CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
-In general there is no requirement to avoid geometric overlap  of parts in a CAD file. This will result in overlaps of the solids in 
-the converted tessellated solids. This is avoided by shrinking each solid, this is done by computing the a normal ${\bf n}$  for each 
-vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so the new vertices are ${\bf v} - \epsilon {\bf n}$. The degree of shrinking 
+In general there is no requirement to avoid geometric overlap  of parts in
+a CAD file. This will result in overlaps between the converted tessellated
+solids. This is avoided by shrinking each solid by computing the normal ${\bf n}$  for each
+vertex ${\bf v}$ and shifting its position by $\epsilon {\bf n}$, so that
+the new vertices are positioned at ${\bf v} - \epsilon {\bf n}$. The degree of shrinkage
 is user-controllable.
@@
 \PYGEOMETRY{} is designed to be as flexible as possible and offer the user a wide range of usage styles, input files
-and workflows. A fictitious beam line was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite 
+and workflows. A fictitious beamline was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite
 \emph{scene} which consists of geometry sources from the different formats described in this paper. The beamline consists of a vacuum chamber
-(modelled in \PYGEOMETRY{}), a vacuum gate valve (STL from the manufacturer), a triplet of quadrupole magnets (exported 
+(modelled in \PYGEOMETRY{}), a vacuum gate valve (STL from the manufacturer), a triplet of quadrupole magnets (exported to GDML
 from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (FLUKA geometry designed in
-flair). Each different file is loaded using the appropriate \PYGEOMETRY{} reader class and then placed as a physical volume. The final composite 
-geometry is shown in Figure~\ref{fig:model}. It must be noted when this complete geometry is written to GDML and loaded into 
+flair). Each different file is loaded using the appropriate \PYGEOMETRY{} \pyinline{Reader} class and then placed as a physical volume. The final composite
+geometry is shown in Figure~\ref{fig:model}. It must be noted that when this complete geometry is written to GDML and loaded into
 Geant4 it cannot be visualised in anything but the ray tracer because of limitations in the OpenGL visualisation in Geant4. Another
@@
 particularly apparent when needing to process large amounts of geometry efficiently and precisely. Possible transformations include merging registries,
-removing volumes (de-featuring), editing solid parameters, changing logical volume materials and converting logical volumes to assembly volumes.
-
-The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
+removing volumes (defeaturing), editing solid parameters, changing logical volume materials and converting logical volumes to assembly volumes.
+
+The merging of registries and removing of volumes is required to create the example shown in Figure~\ref{fig:model}.
 Each sub-component is stored in a separate registry and these have to be combined without any GDML tags clashing.
@@
 \section{Quality assurance}
-The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
+The source and manual code for \PYGEOMETRY{} is stored in a Git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}),
 where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a
 Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages
-available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages that require compilation \pyinline{pyg4ometry.pycsg} 
-and \pyinline{pyg4ometry.pycgal} in C++. \PYGEOMETRY{} package dependencies and extensions are installed easily using 
-\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using software tests, of which 543 are available,  
+available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages
+that require compilation: \pyinline{pyg4ometry.pycsg} in Python and
+\pyinline{pyg4ometry.pycgal} in C++.
+\PYGEOMETRY{} package dependencies and extensions are installed easily using
+\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked
+using software tests, of which there were 543 at the time of writing,
 resulting in 84\% code coverage. The tests also serve as minimal examples to help users understand the code operation.
@@
 yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry
-creation tool, whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT 
+creation tool, and whilst heavily internally based on Geant4 and GDML, it can have utility for users of all MCRT
 codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and
-uniform interface to existing tools and utilities, also by using the Python programming language \PYGEOMETRY{} 
-allows the programmatic control of geometry creation or modification. This approach allows the integration of 
+uniform interface to existing tools and utilities, and by using the Python programming language \PYGEOMETRY{}
+ the programmatic control of geometry creation or modification is possible. This approach allows the integration of
 other available tools~\cite{DavisNIMA915-65} into a unified workflow.
@@
 Users should be aware of issues with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA
-cannot be considered bidirectional. For example Geant4 tessellated solids cannot be converted easily to FLUKA which does not 
+cannot be considered bidirectional. For example, Geant4 tessellated solids cannot be converted easily to FLUKA which does not
 have a convenient way of representing this geometry. In general a user would be unwise to attempt to convert a very large
-geometry from one format to another, but concentrate on smaller conversions of constituent parts. Workflows should focus 
-on conversion from a primary format and then create conversions to another format as the need arises. This paper outlines 
+geometry from one format to another, but should instead concentrate on smaller conversions of constituent parts, 
+and then using those parts to supplement larger models. Workflows should focus
+on the generation of a primary format and then create conversions to other formats as the need arises. This paper outlines
 the creation of geometry using \PYGEOMETRY{}, and whilst that geometry is subsequently loaded into Geant4, flair and FLUKA, detailed
@@
 simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in
-liquid noble dark matter detectors. Paraview/VTK are becoming standard software for complex 3D visualisation and 
+liquid noble dark matter detectors. ParaView/VTK are becoming standard software for complex 3D visualisation and
 the ability to write geometry to formats readily loaded and manipulated by these programs will
-significantly aid the presentation of geometry along with the results of the MCRT simulations.
+significantly aid the presentation of geometry along with the results of MCRT simulations.
 
@@
 
-The conversion which would most dramatically enhance the creation of RTMC geometry is CAD to Geant4 or FLUKA
-without use use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and 
+The conversion which would most dramatically enhance the creation of MCRT geometry is CAD to Geant4 or FLUKA
+without use of a triangular or tetrahedral mesh. There are existing approaches to decompose BREP solids to Geant4 and
 FLUKA-like CSG geometry~\cite{WangNuclSciTech31-82-2020, LuFusionEngineeringAndDesign124-2017}.
 The FreeCAD/OpenCASCADE interface combined with the Geant4 and FLUKA Python API in \PYGEOMETRY{}
-will allow for the creation of CAD BREP decomposition algorithms. There are python based CAD modelling tools like 
-cadquery \cite{cadquery} which allow the creation of models using pure Python which should allow the conversion of GDML to STEP.
+will allow for the creation of CAD BREP decomposition algorithms. There are Python-based CAD modelling tools like
+CadQuery~\cite{cadquery} which allow the creation of models using pure Python which should allow the conversion of GDML to STEP.
 
@@
 \PYGEOMETRY{} is already proving to be a useful tool for geometry conversion, creation and manipulation.
-There are numerous international researcher and research groups already using the code for their particular applications.
+There are numerous international researchers and research groups already using the code for their particular applications.
 The users are focused in accelerator physics, but \PYGEOMETRY{} could find application in any scientific
@@
 degree project work: Simon Williams, Benjamin Shellswell and Joshua Albrecht.
-STB has benefited from discussions with and insight of Vasilis Vlachoudis
-(CERN) on FLUKA geometry and Flair.  Cédric Hernalsteens (ULB/CERN) and
-Alistair Butcher (RHUL) also made useful contributions to the code.
+STB has benefited from discussions with, and the insights of, Vasilis Vlachoudis
+(CERN) regarding FLUKA geometry and flair.  Cédric Hernalsteens (ULB/CERN) and
+Alistair Butcher (RHUL) also made useful contributions to the code. Don Boogert
+provided valuable insight on meshing and modern computer graphics programming.
 

### 2020-11-13 public/paper/pyg4ometry.tex
final changes after my (stuart's) final reading

@@
 using intersections and subtractions.  Zones may then be further combined
-using union operations to form \emph{regions}, which is defined as the
+using union operations to form \emph{regions}, which are defined as the
 union of one or more zones, as well as a material.
@@
 and regions must be finite.  Zones and regions are then composed by
-instantiating these classes and adding body instances to them.  Each
+instantiating their respective classes and adding body instances to them.  Each
 \pyinline{Zone} and \pyinline{Region} instance can then return its
@@
 example in FLUKA unions can be disconnected, but in Geant4 specifically
-only MultiUnions can be disconnected.  Therefore, MultiUnions are used
+only multi-unions can be disconnected.  Therefore, multi-unions are used
 throughout the converted geometry instead of the more conventional binary unions.
@@
 This is achieved with the use of axis-aligned bounding boxes (AABBs),
-in which the FLUKA body is translated to a finite solid with with
+in which the FLUKA body is translated to a finite solid with 
 dimensions slightly larger than the AABB.  The lengths of infinite
@@
 very expensive, so to resolve this the user must provide the approximate
-axis-aligned bounding box of any region in which a quadric is used.
+axis-aligned bounding box of any region in which a quadric is used to
+constrain the size of the mesh only to where it is needed.
 
@@
   \KwResult{GDML solids equivalent to the FLUKA regions built from
-    minimally-sized primitive solids}
+    minimally-sized primitive solids.}
 
@@
   \For{body $b$ and AABB $a$ in $E$}{
-    \tcp{Map the fluka bodies to minimal GDML solids by converting with the
+    \tcp{Map the FLUKA bodies to minimal GDML solids by converting with the
     minimal AABB, $a$.}
@@
   \caption{The infinite-body minimisation algorithm employed in the
-    conversion of Fluka to GDML.}
+    conversion of FLUKA to GDML.}
 \end{algorithm}
@@
 generally result in tracking errors.  These must be handled robustly to
-ensure the resulting geometry is usable.  Coplanar faces are resolved
+ensure the resulting geometry is usable in Geant4.  Coplanar faces are resolved
 automatically by slightly decreasing the size of every body that is used in
@@
 within it. When a particle steps into the lattice cell, the
-rototranslation is applied to that particle and it is is taken into the
-basic unit, and the simulation continues within the basic unit. Any
-particles leaving the basic unit will be translated back to the
+rototranslation is applied to that particle transporting it to the
+basic unit, and the simulation continues. Any
+particles leaving the basic unit will be transported back to the
 lattice cell with the inverted rototranslation. Up to two
-levels of lattice nesting the are supported in FLUKA.
+levels of lattice nesting are supported in FLUKA.
 
@@
 volume are explicitly stated, whereas the contents of a lattice cell
-are implied by the combination of the rototranslation and the locations of
+are implied by the combination of the rototranslation and the global positions of
 its lattice cell and basic unit.
@@
 with the transformed lattice cell mesh determine the contents of the basic
-unit.  Finally, the lattice cell can simply be replaced with a physical
+unit.  Finally, the contents of lattice cell can simply be replaced with a physical
 volume containing the logical volumes determined in the previous step.
-Thus a basic unit with one or more lattice cells can be translated into
-Geant4's logical volume with one or more physical volumes. As has been
+Thus a basic unit with one or more lattice cells can be translated into a
+Geant4 logical volume with one or more physical volumes. As has been
 stated, FLUKA supports two levels of lattice nesting, but currently the
@@
 algorithms for bridging FLUKA with GDML covers a very broad range of
-geometries, however a number of possible improvements for the future
-remain.  For example, FLUKA regions can in general be disconnected, that is
+geometries, however a number of possible improvements remain for the
+future.
+For example, FLUKA regions can in general be disconnected, that is
 to say the resulting set of points defined by that region may consist of
 two disconnected subvolumes.  In FLUKA this typically manifests itself in
-the form of disconnected unions, but it is also allowed for intersections
+the form of a disconnected unions, but it is also allowed for intersections
 and subtractions to be disconnected.  In the case of translating
 disconnected unions from FLUKA to GDML, this presents no difficulties as
-the GDML \pyinline{MultiUnion} solid is explicitly allowed to be formed from
+the GDML multi-union solid is explicitly allowed to be formed from
 disconnected parts.  However, it is forbidden for \pyinline{Intersection} or
@@
 tessellation is unavoidable (for example a hyperbolic paraboloid), but
-parabolic cylinders could for example be mapped to an \pyinline{ExtrudedSolid}.
+parabolic cylinders, for example, could be mapped to \pyinline{ExtrudedSolid}
+instances.
 This could provide both a performance improvement in the tracking time and
@@
 Understanding the algebra of FLUKA CSG and how it relates to Geant4's
-concepts of solids, logical volumes and physical volumes must be understood
+concepts of solids, logical volumes and physical volumes is necessary
 to perform an accurate conversion.  For example, a Geant4 logical volume
 solid may correspond to a FLUKA region consisting of many zones
-(i.e. unions), e.g.,~$R_1 = +z_1\: | +z_2$.  If this logical volume is
+(i.e. unions), e.g.,~$R_1 = +z_1\: |~+z_2$.  If this logical volume is
 placed as a physical volume inside some mother volume with its solid
@@
 
-FLUKA (apart from the \fluka{lattice} directive) has no sense of a volume hierarchy. Each body is placed with
+Apart from the lattice feature, FLUKA has no sense of a volume hierarchy. Each body is placed with
 translation, rotation and expansion geometry directives in global coordinates. A transformation from world
@@
 vacuum chamber with three ConFlat flange (CF) beam pipes connected to CF flanges. The top and bottom plates
-have been removed to display the geometry more clearly. The model is formed of \verb|Box| and
+have been removed to display the geometry more clearly. The model is formed of \verb|Box|,
 \verb|Tubs| and Boolean operations of subtraction, intersection and union.
@@
 \subsection{Disjunctive normal form and degenerate surfaces}
-Typically FLUKA will decompose a region into disjunctive normal form (DNF)
-as runtime, this normal form is characterised as the union of intersections and subtractions,
+FLUKA will typically decompose a region into disjunctive normal form (DNF)
+at runtime, this normal form is characterised as the union of intersections and subtractions,
 \begin{equation}
@@
 meshing capabilities combined with CSG pruning algorithms based
-on~\cite{pruning}.  FLUKA by default will try to expand all regions to
+on~\cite{pruning}.  FLUKA will by default try to expand all regions to
 their DNF at runtime, which inevitably can result in the sort of exponential explosion already mentioned.  Until version 4.0, if FLUKA identified
-such an explosion, it would report an error and exit, thus making such models impossible to run.  As of version 4.0, however, this
-expansion can be disabled, and the tracking algorithms will walk the CSG trees verbatim, at some tracking efficiency cost.  Therefore, most
+such an explosion, it would the expansion, report an error and exit, thus making such models impossible to run.  As of version 4.0, however, this
+expansion can be disabled, and the tracking algorithms will walk the CSG trees verbatim, albeit at some tracking efficiency cost.  Therefore, most
 output generated from the GDML to FLUKA conversion described here can only be used with FLUKA 4.0.
@@
 can either be simple, i.e. defined only by atomic number and mass, or composite and defined by an admixture of
-relative abundances of \cpinline{G4Isotope}. A similar mapping is performed so that if a \cpinline{G4Element} is simple it is
+relative abundances of isotopes. A similar mapping is performed so that if a \cpinline{G4Element} is simple it is
 directly converted to a FLUKA \fluka{MATERIAL} card, and the {\it isotope} \cpinline{G4Element} is converted to a \fluka{compound}
@@
 conversion described still requires a user to understand how geometry is
-specified in both Geant4 and FLUKA. For example the subtraction of many
-non-primitive body daughter volumes from a mother will create a very
-complex region that is not in disjunctive normal form which is inefficient
+specified in both Geant4 and FLUKA. For example, as has been stated, a
+Geant4 mother volume will, when translated to a FLUKA region, have all of
+its daughters subtracted from its respective FLUKA region. If those daughter volumes, when
+translated to FLUKA, consist of combinations of many FLUKA bodies, the
+mother region can become very complex.  This complex
+region will generally not be in disjunctive normal form and is inefficient
 when viewed in FLUKA's graphical user interface (GUI), flair, and used for
@@
 primitives such as boxes.  Complex daughter volumes consisting of solids
-that are complex Booleans should be placed inside primitive solids that map
+that are complex Booleans should be placed inside solids that map
 to primitive FLUKA bodies.  This ensures that expanding to the DNF is
-computationally tractible, and in doing do FLUKA's tracking will be faster.
+computationally tractable, and in doing do FLUKA's tracking will be faster.
 This is not a drastic constraint on the conversion functionality, however,
@@
 a single source description with minimal additional effort.  However, there
-are still a  outstanding technical issues with the conversion, which are discussed in
-this section.
+are still a  outstanding technical issues with the conversion, which are
+discussed in the rest of this section.
 
@@
 provided by geometry directives can be re-expressed purely in terms of a
-body (possibly of a different type) without any transform.  For example, a
-sphere with a geometry directive translation can be re-expressed as a
-sphere without a translation, and instead with offset added directly to the
-sphere's centre.  This {\em normal form} can be used to test for
-approximate equality between bodies that are equivalent whilst accounting
-for any transforms.  Approximate equality is required as multiple
-applications of rototranslations will accrue numerical rounding errors such
-that true equality is not maintained.  A simple example of this is the XYP
-and PLA, it is simple to transform an XYP into a PLA with an appropriate
-rotation. This would allow for the removal of degenerate surfaces removing
-potential coplanar overlaps and also reduce the final converted file size.
-
-The twisted primitives need to be decomposed
+body (possibly of a different type) without any transform. A simple example
+of this is the XYP and PLA, it is simple to transform an XYP into a PLA
+with an appropriate rotation. This {\em normal form} can be used to test
+for approximate equality between bodies that are equivalent whilst
+accounting for any transforms.  Approximate equality is required as
+multiple applications of rototranslations will accrue numerical rounding
+errors such that true equality is not maintained.  This would allow for the
+removal of degenerate surfaces removing potential coplanar overlaps and
+also reduce the final converted file size.
+
+The twisted primitive solids need to be decomposed
 into a union of convex solids. This decomposition does not always
@@
 layer of the twisted solid as a union of tetrahedra. A similar problem
-exists for general tessellated solids, which in general
+exists for tessellated solids, which in general
 are non-convex and need decomposition into convex hulls. An alternative
@@
 \begin{lstlisting}[caption={A simple \PYGEOMETRY{} Python script to load a STEP file.},label={lst:pythonCADLoading}, language=Python]
-reader = pyg4ometry.freecad.Reader("CadFileName.step")
+import pyg4ometry.freecad as freecad
+
+reader = freecad.Reader("CadFileName.step")
 reader.relabelModel()
@@
 Compared to other file readers, two additional steps are required: \pyinline{relabelModel} and \pyinline{convertFlat}. CAD model
-part names can contain characters which are not allowed in Python dictionaries so need to be replaced by \pyinline{relabelModel}.
-CAD models might also have a hierarchy of parts and assemblies, these are converted without this structure by \pyinline{convertFlat}.
+part names can contain characters which are not allowed in Python
+dictionaries so need to be replaced by using \pyinline{relabelModel}.
+CAD models might also have a hierarchy of parts and assemblies, these are
+converted without this structure by using \pyinline{convertFlat}.
 In general there is no requirement to avoid geometric overlap  of parts in
@@
 geometry is shown in Figure~\ref{fig:model}. It must be noted that when this complete geometry is written to GDML and loaded into
-Geant4 it cannot be visualised in anything but the ray tracer because of limitations in the OpenGL visualisation in Geant4. Another
+Geant4 it cannot be visualised with anything but the ray tracer due to limitations in the OpenGL visualisation in Geant4. Another
 important note is that this geometry cannot be converted to FLUKA as it contains tessellated solids (both the STL gate valve and
@@
 \includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
-\caption{Complete compositing example using \PYGEOMETRY{}.}
+\caption{Complete composite example using \PYGEOMETRY{} showing a model with geometry sourced from a range of different formats.}
 \label{fig:model}
@@
 codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. Presently it provides a coherent and
-uniform interface to existing tools and utilities, and by using the Python programming language \PYGEOMETRY{}
+uniform interface to existing tools and utilities, and by using the Python programming language
  the programmatic control of geometry creation or modification is possible. This approach allows the integration of
@@
 converts the \PYGEOMETRY{} in-memory representation to C++ will allow rapid geometry
-modelling but inclusion of the geometry into an existing Geant4 application. This is not
+modelling and inclusion of the geometry into an existing Geant4 application. This is not
 implemented in the current version but could be relatively quickly implemented for users that
@@
 Royal Holloway, and Royal Holloway Impact Acceleration Account. Gian Luigi D'Alessandro (CERN/JAI)
-provided geometry and tested multiple conversions of beamlines. Multiple
+provided geometry and tested multiple converted beamlines. Multiple
 undergraduate and masters students have contributed to the code for their
@@
 Alistair Butcher (RHUL) also made useful contributions to the code. Don Boogert
-provided valuable insight on meshing and modern computer graphics programming.
+provided valuable insights on meshing and modern computer graphics programming.
 

### 2020-12-01 public/paper/pyg4ometry.tex
Authorship
Remove colours from href links.

@@
 \PassOptionsToPackage{hyphens}{url}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{todonotes}
@@
 
-\hypersetup{
-    colorlinks=false,
-    linkcolor=blue,
-    filecolor=magenta,
-    urlcolor=cyan,
-    pdftitle={Pyg4ometry paper},
-    bookmarks=true,
-    pdfpagemode=FullScreen,
-}
+%\hypersetup{
+%    colorlinks=false,
+%    linkcolor=blue,
+%    filecolor=magenta,
+%    urlcolor=cyan,
+%    pdftitle={Pyg4ometry paper},
+%    bookmarks=true,
+%    pdfpagemode=FullScreen,
+%}
 
@@
 
-\author[a]{S.T. Boogert\corref{author}}
+\author[a]{S.D. Walker}
 \author[a]{A. Abramov}
@@
 \author[a]{W. Shields}
-\author[a]{S.D. Walker}
+\author[a]{S.T. Boogert\corref{author}}
 
@@
 simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in
-liquid noble dark matter detectors. ParaView/VTK are becoming standard software for complex 3D visualisation and
-the ability to write geometry to formats readily loaded and manipulated by these programs will
-significantly aid the presentation of geometry along with the results of MCRT simulations.
+optical photon based particle physics detectors. ParaView/VTK are becoming standard software for 
+complex 3D visualisation and the ability to write geometry to formats readily loaded and manipulated 
+by these programs will significantly aid the presentation of geometry along with the results of MCRT 
+simulations.
 

### 2020-12-17 public/paper/pyg4ometry.tex
Stuart first
add laurie's last fixes including citing and mentioning Cython

@@
 
-\author[a]{S.D. Walker}
+\author[a]{S.~D. Walker}
 \author[a]{A. Abramov}
-\author[a]{L.J. Nevay}
+\author[a]{L.~J. Nevay}
 \author[a]{W. Shields}
-\author[a]{S.T. Boogert\corref{author}}
+\author[a]{S.~T. Boogert\corref{author}}
 
@@
  codes.  The file formats used for geometry are generally focused
- on the computational efficiency of particle tracking algorithms  and not ease of use. In addition to the creation of geometry files for RT programs, usually
+ on the computational efficiency of particle tracking algorithms  and not ease of preparation. In addition to the creation of geometry files for RT programs, usually
  computer-aided design (CAD) files exist for systems which need to be simulated. The fundamental geometric representations in CAD files are usually not
@@
 of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning
-(BSP) tree technique in pure Python~\cite{pycsg} or via the Computational Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b} in C++. In
-general, the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries.
+(BSP) tree technique in pure Python~\cite{pycsg} or via the Computational
+Geometry Algorithms Library (CGAL) surface meshes~\cite{cgal:bsmf-sm-20b}
+in C++. The pure Python CSG backend is further accelerated by compiling it
+to C using Cython\cite{cython}.
+For maximum flexibility either backend can be used, but in general, the CGAL implementation is one to two orders of magnitude faster than the Cythonized CSG implementation and must be used for large geometries.
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file

### 2020-12-17 public/paper/pyg4ometry.tex
paper: "three-dimensional" -> 3D (for consistency)

@@
 imaging and therapy, and space radiation environment simulations. A fundamental requirement of all of the codes is to supply a
-computer-readable description of the  physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is
+computer-readable description of the  physical 3D geometry that  the particles are passing through.  The creation of geometry files is
 typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no
@@
 \subsection{Tessellation of solids (meshing)}
-Creating a uniform three-dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap
+Creating a uniform 3D mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap
 detection. For each Geant4 solid instance a triangular tessellated vertex-face mesh is generated and cached. This mesh is then used to determine the extent

### 2020-12-17 public/paper/pyg4ometry.tex
another worindg

@@
 to C using Cython\cite{cython}.
-For maximum flexibility either backend can be used, but in general, the CGAL implementation is one to two orders of magnitude faster than the Cythonized CSG implementation and must be used for large geometries.
+For maximum flexibility either backend can be used, but in general, the
+CGAL implementation is one to two orders of magnitude faster than the
+Cythonized CSG implementation and should be used for large geometries.
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file

### 2020-12-17 public/paper/pyg4ometry.tex
laurie and cython

--- 2020-12-17 public/paper/pyg4ometry.tex
@@
 in C++. The pure Python CSG backend is further accelerated by compiling it
-to C using Cython\cite{cython}.
-For maximum flexibility either backend can be used, but in general, the CGAL implementation is one to two orders of magnitude faster than the Cythonized CSG implementation and must be used for large geometries.
+to C using Cython~\cite{cython}.
+For maximum flexibility either backend can be used, but in general the
+CGAL implementation is one to two orders of magnitude faster than the
+Cythonized CSG implementation and should be preferred, particularly for large geometries.
 Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to file

### 2020-12-17 public/paper/pyg4ometry.tex
word order
elaborate on sphinx documentation

@@
 The source and manual code for \PYGEOMETRY{} is stored in a Git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}),
-where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx, a
-Python documentation generator (\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}). \PYGEOMETRY{} uses mature packages
+where a public issue tracker for users is hosted to report problems or bugs
+with the code. The Python source is documented throughout using docstrings, which
+are also used to generate an API reference using Sphinx, a
+Python documentation generator
+(\url{http://www.pp.rhul.ac.uk/bdsim/pyg4ometry/}).  This
+automatically-generated documentation is supplemented with
+developer-written documentation in the form of examples and tutorials,
+again using Sphinx. \PYGEOMETRY{} uses mature packages
 available for Python as dependencies. \PYGEOMETRY{} has  two sub-packages
@@
 \pyinline{pyg4ometry.pycgal} in C++.
-\PYGEOMETRY{} package dependencies and extensions are installed easily using
+\PYGEOMETRY{} package dependencies and extensions are easily installed using
 \pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked

### 2021-03-28 public/paper/sub-cpc/pyg4ometry.tex
Update to archive and CPC author statement

--- 2020-12-17 public/paper/pyg4ometry.tex
@@
 \documentclass[final,5p,times,twocolumn]{elsarticle}
+%\documentclass[preprint,12pt]{elsarticle}
 
@@
 
-\linenumbers
+%\linenumbers
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{./diagrams/workflow.pdf}
+  \includegraphics[width=0.7\textwidth]{workflow.pdf}
   \caption{\label{fig:workflow}Schematic of \PYGEOMETRY{} workflow, showing (a) the different input file formats, (b) Python processing, (c) output file targets and
@@
 volume hierarchy is sufficient to place the meshes associated with each physical volume. A daughter volume is placed within a logical volume with a
-rotation~$\mathbf{R}_d$, scale~$\mathbf{S}_d$ and translation~$\mathbf{T}_d$.
+rotation~$\mathbf{R}_d$, reflection~$\mathbf{S}_d$ and translation~$\mathbf{T}_d$.
 
@@
 \begin{center}
-\includegraphics[width=5cm]{./diagrams/lvToPv.pdf}
+\includegraphics[width=5cm]{lvToPv.pdf}
 \caption{The placement of a physical volume inside a logical volume.}
@@
 \begin{center}
-\includegraphics[width=8cm]{./diagrams/overlap.pdf}
+\includegraphics[width=8cm]{overlap}
 \caption{Schematic of the three different types of overlap between the daughters of a mother logical volume.}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./diagrams/rapidModelling.pdf}
+\includegraphics[width=0.9\columnwidth]{rapidModelling}
 \caption{VTK visualisation output from code Listing~\ref{lst:pythonRapidModelling}.}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/faradayCup2.pdf}
+\includegraphics[width=0.9\columnwidth]{faradayCup2.pdf}
 \caption{Example conversion of a simple FLUKA geometry to GDML. Above:
@@
 \begin{center}
-\includegraphics[width=6cm]{./diagrams/lattice}
+\includegraphics[width=6cm]{lattice}
 \caption{The lattice feature demonstrating a lattice cell
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
+\includegraphics[width=0.9\columnwidth]{CuboidalChamber}
 \caption{Example conversion of a simple GDML geometry to FLUKA, above:
@@
 their DNF at runtime, which inevitably can result in the sort of exponential explosion already mentioned.  Until version 4.0, if FLUKA identified
-such an explosion, it would the expansion, report an error and exit, thus making such models impossible to run.  As of version 4.0, however, this
+such an explosion, it would terminate the expansion, report an error and exit, thus making such models impossible to run.  As of version 4.0, however, this
 expansion can be disabled, and the tracking algorithms will walk the CSG trees verbatim, albeit at some tracking efficiency cost.  Therefore, most
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./model-scene/SectorBend.pdf}
+\includegraphics[width=0.9\columnwidth]{SectorBend}
 \caption{Example conversion of a simple CAD (STEP) geometry (sector bend
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
+\includegraphics[width=1.0\textwidth]{model.pdf}
 \caption{Complete composite example using \PYGEOMETRY{} showing a model with geometry sourced from a range of different formats.}
@@
 
+\section{Author contributions}
+{\bf Stewart Boogert}: conceptualization, supervision, methodology, software, validation and writing - original draft. 
+{\bf Stuart Walker}: methodology, software, validation and writing - original draft (FLUKA components). 
+{\bf Andrey Abramov}: software, validation and writing - review \& editing (Geant4 and GDML). 
+{\bf Laurence Nevay}: software, validation validation and writing - review \& editing. 
+{\bf William Shields}: validation and writing - review \& editing
+
 \section{Acknowledgements}

### 2021-03-29 public/paper/sub-cpc/pyg4ometry.tex
single column and repetition removal
Fix Will

@@
 %% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-%\documentclass[preprint,12pt]{elsarticle}
+%%\documentclass[final,5p,times]{elsarticle}
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
@@
 {\bf Andrey Abramov}: software, validation and writing - review \& editing (Geant4 and GDML). 
-{\bf Laurence Nevay}: software, validation validation and writing - review \& editing. 
-{\bf William Shields}: validation and writing - review \& editing
+{\bf Laurence Nevay}: software, validation and writing - review \& editing. 
+{\bf William Shields}: software (GDML), validation and writing - review \& editing
 

### 2021-05-04 public/paper/sub-2-arxiv/pyg4ometry.tex

--- 2021-03-29 public/paper/sub-cpc/pyg4ometry.tex
@@
 %% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%%\documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
 %\documentclass[final,5p,times,twocolumn]{elsarticle}
@@
 
-\section{Author contributions}
-{\bf Stewart Boogert}: conceptualization, supervision, methodology, software, validation and writing - original draft. 
-{\bf Stuart Walker}: methodology, software, validation and writing - original draft (FLUKA components). 
-{\bf Andrey Abramov}: software, validation and writing - review \& editing (Geant4 and GDML). 
-{\bf Laurence Nevay}: software, validation and writing - review \& editing. 
-{\bf William Shields}: software (GDML), validation and writing - review \& editing
-
 \section{Acknowledgements}

### 2021-12-09 public/paper/sub-cpc-2/reviewer_comments_response.txt

Authors : The authors would like to thank the reviewers for their comments. Many of the issues found improve the readability of the manuscript for potential users of the software. Almost all of the comments and suggested changes were implemented as suggested by the reviewers. Below are the reviewer comments with the changes or comments.

Reviewer #1: The authors are to be commended on writing an exceptionally clear and comprehensive manuscript. While the paper contains occasional grammatical errors, it is easy to follow and addressed all concerns I had as I was reading it.
This paper concerns pyg4ometry, a tool to create Geant4 geometry structures in GDML via Python, with tools that support restructuring files in CAD and FLUKA formats. Examples are provided throughout the manuscript to aid the reader in implementing the module,
and docs are already available online for v0.9.1 as of this review. As a former user of GATE, I am personally aware of the difficulty in rapid creation of Geant4 geometries, and I wish I had such a tool at my disposal in the past.
This work helps lower the barrier of entry to Geant4 for inexperienced programmers who do know enough Python to get by. I think a line expressing this is warranted.
    Line added

This manuscript is ready for publication as written, but I leave the following comments for the authors’ consideration:
P3 Line 27: powerful how?
   Removed word powerful   
P4 Line 9: I'd add a line highlighting how useful it is that this co
de is written for Python users. ROOT, for example, is harder for a layman to use.
   Added extra line to clarify this
P4 Line 56: stick a comma before which or replace it with that. (Come to think of it, I don't know if American grammar rules apply in the UK)
   Fixed
P7Line 50: I think this entire paragraph should be placed in a discussion section and not in methods. Best not to promise things for future release in a methods section.
   Changed as loops are unlikely to be implemented.
P10 L37: Too not to. In fact, this whole paragraph is oddly out of place so far. Use of clearly and loopy language that is less specific and efficient than its preceding chapters. What is it trying to say?
    Paragraph tightened up for clarity

Reviewer 2 [Linnemann]
The manuscript is generally well-written, though the English could use touching up: there are a lot of run-on sentences. I recommend that the manuscript be accepted but that the authors incorporate some minor revisions for the final manuscript.
Suggestions below (page.line)

2.16 impossible to convert -> impossible
    Fixed
2.24 STL undefined
    Fixed
2.33 delete: different
    Deleted
2.34 material, such -> material. Such
    Fixed
2.39 specialism -> specialty
    Fixed
2.59 geometry -> geometry descriptions
    Fixed
3.36 toolkit. A user
    Fixed
4.21 using a lot of -> using
    Fixed
4.29 existent -> existing
    Fixed     
4.31 follows: first comes
    Changed
4.46 delete: different
    Fixed
In this section it might make sense to mention that you chose STP and STEP as manufacturer-neutral CAD file formats for which there commonly exist converters from proprietary formats.
And that IGES is an older standard which STEP seems to be overtaking.
But it appears that Fig 1 is missing IGES since you later state IGES can be read, which is confusing since at 6.47 you omit IGES, but include it at 30.49; perhaps you mean that the software mentioned there can translate IGES to STEP for you?
I also note you don't mention OBJ why? Should it be mentioned? Any plans for adding in the future?
    OBJ is mentioned and other similar formats are trivally implemented, we provide one simple one. 
I of course wondered whether AUTOCAD is compatible, but apparently there are converters from DWG default to STEP, so no need to mention that specific product if you make the more general statements. But aha at 32.41 you mention another piece of Autodesk software, but state that you can save as STEP format.
    Autodesk FUSION replaced with Common commercial program. Wanted to make the point that the input for pyg4ometry was from a standard package a user might be familiar with 
5.10 solids. However,
    Fixed
8.43 geometry, a rapid
    Fixed
9.56 user. It does
    Fixed
10.37 to -> too
    Fixed
10.48 reuse. However
    Not changed. 
10.53 considered. In
    Fixed
13.13 vistualisation -> visualization (assuming British spelling)
    Fixed
15.18 trivial. A
    Fixed
18.33 50km is there a place this default can be changed? I know I'm weird, but I'm thinking astrophysics
    This can easily be changed and note added to highlight this.
Quadric hmm, maybe usage has changed since I studied mathematics I'd have said quadratic, but quadric seems correct when I look it up!
21.14 straight forwards -> straightforward
    Fixed
22.46 geometries. However
    Fixed
29.14 doing do -> doing so
    Fixed
30.9 PLA. It is
    Fixed
32.33 assemblies. These
    Fixed
32.41 I'd remove comma after electromagnet
Hmm, now you mention another piece of Autodesk software, but do state that you can save as STEP format
    Agreed and fixed
32.42 STEP file. The PYG4OMETRY
    Fixed    
32.40 PYG4OMETRY. This
    Fixed
33.52 FLUKA geometry, is converted
    Fixed
34.19 developer-written falls outside the margins
    Fix in proof (as likely to change)
34.52 FLUKA,
    Fixed     
35.24 user that -> users who
    Fixed    
35.39 hmm, apparently ParaView is a GUI for VTK; if you combine them into one object, I'd have said is instead of are
    Fixed

******************************************
Please note that the editorial process varies considerably from journal to journal. To view a sample editorial process, please click here:
http://ees.elsevier.com/eeshelp/sample_editorial_process.pdf
For further assistance, please visit our customer support site at http://help.elsevier.com/app/answers/list/p/7923. Here you can search for solutions on a range of topics, find answers to frequently asked questions and learn more about EM via interactive tutorials. You will also find our 24/7 support contact details should you need any further assistance from one of our customer support representatives.~

### 2021-12-09 public/paper/sub-cpc-2/pyg4ometry.tex

--- 2021-03-29 public/paper/sub-cpc/pyg4ometry.tex
@@
 
-%\linenumbers
+\linenumbers
 
@@
 Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes
-available and geometry conversion is difficult or impossible to convert between these simulation tools.
+available and geometry conversion is difficult or impossible between these simulation tools.
 \\
@@
 Form triangular meshes to represent geometric objects for both visualisation of the
-geometry and to enable the use of advanced mesh-based geometric algorithms. Triangular mesh processing algorithms allow the loading and use of STL and CAD/CAM
+geometry and to enable the use of advanced mesh-based geometric algorithms. Triangular mesh processing algorithms allow the loading and use of Standard Triangle Language (STL) and CAD/CAM
 files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from
@@
 \section{Introduction} \label{sec:introduction}
-There are numerous different software codes to simulate the passage of particles through material, such radiation transport (RT) programs
+There are numerous software codes to simulate the passage of particles through material. Such radiation transport (RT) programs
 include MCNP~\cite{Mcnp_Werner}, FLUKA~\cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3~\cite{Geant3_Brun} and Geant4~\cite{Geant4_Agostinelli}.
-All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.
+All these codes are based on the Monte Carlo technique but each code either has a particular speciality, simulation methodology or target user community.
  Monte Carlo RT (MCRT) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical
 imaging and therapy, and space radiation environment simulations. A fundamental requirement of all of the codes is to supply a
-computer-readable description of the  physical 3D geometry that  the particles are passing through.  The creation of geometry files is
+computer-readable description of the  physical 3D geometry that  the particles are passing through.  The creation of geometry description files is
 typically a very time-consuming activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no
@@
 are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP
-and IGES) based on FreeCAD~\cite{FreeCAD} and OpenCascade~\cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK~\cite{VTK4}. The
+and IGES) based on FreeCAD~\cite{FreeCAD} and OpenCascade~\cite{OpenCASCADE}; and  geometry visualisation tools based on VTK~\cite{VTK4}. The
 origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM~\cite{BDSIM_Nevay}.
@@
 \PYGEOMETRY{} allows the rapid creation and adaptation of geometry, with Figure~\ref{fig:workflow} demonstrating various possible workflows. \PYGEOMETRY{}
-is not an executable software package but a toolkit, a user would typically write a very small Python program to use the classes and functions provided by
+is not an executable software package but a toolkit. A user would typically write a very small Python program to use the classes and functions provided by
 \PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a Git repository and via the Python Package Index (PyPi).
@@
 There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework,
-can load, display and manipulate GDML-like geometry. Existing open source tools to convert CAD files to GDML include GUIMesh~\cite{GUIMesh_Pinto}, with commercial
+can load, display and manipulate GDML-like geometry.
+ROOT is typically harder for the layperson (or non-high energy physicist) to use compared to the python implementation of \PYGEOMETRY{}.
+Existing open source tools to convert CAD files to GDML include GUIMesh~\cite{GUIMesh_Pinto}, with commercial
 solutions including ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD
 geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL
-(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. However, in practice using a lot of CAD models is difficult if that model is composed of a
+(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. However, in practice using CAD models is difficult if that model is composed of a
 large number of parts. This is because exporting, assigning material to, and placing the STL components into the MCRT code can be very cumbersome. Almost all modern CAD tools such as
 CATIA, Inventor and SolidWorks have a scripting language to allow users to programmatically generate geometry. Similar CAD-style scripting languages do not exist for either GDML
-or FLUKA and the existent set of software does not provide a complete set of tools to efficiently create complex geometries for these codes.
-
-This paper is structured as follows, first a brief radiation
-transport-focused introduction to computer descriptions of geometry and an explanation of the design
+or FLUKA and the existing set of software does not provide a complete set of tools to efficiently create complex geometries for these codes.
+
+This paper is structured as follows: first comes a brief radiation transport-focused introduction to computer descriptions of geometry and an explanation of the design
 and implementation of \PYGEOMETRY{}. Subsequent sections describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling as well as conversions from
@@
 \section{Computer descriptions of geometry} \label{sec:geometric}
-Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
+Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous ways to describe a
 geometry, including constructive solid geometry (CSG), boundary representation (BREP) and tessellated polygons, which are described
@@
 Constructive solid geometry uses Boolean operations (subtraction, intersection and union) between simple solid shapes (e.g. cube, cylinder, sphere, etc.) or infinite
-volumes (e.g. a plane-defined infinite half-space) to model complex surfaces which represent a solid. Boolean operations and solids can be combined to form a
-CSG tree to model complex geometry. FLUKA uses CSG to model solids, however the form of Boolean expression used by FLUKA is not a general CSG tree but a
+volumes (e.g. a plane-defined infinite half-space) to model complex surfaces, which represent a solid. Boolean operations and solids can be combined to form a
+CSG tree to model complex geometry. FLUKA uses CSG to model solids. However the form of Boolean expression used by FLUKA is not a general CSG tree but a
 logical expression in disjunctive normal form.
@@
 \subsection{Visualisation} \label{sec:visualisation}
-When implementing geometry a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
+When implementing geometry, a rapid and robust visualisation system is key to produce error-free and efficient simulation input.
 A  \PYGEOMETRY{} geometry hierarchy can be viewed using the popular Visualisation Toolkit (VTK). No separate scene graph is required as the Geant4
@@
 All MCRT codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles
-in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by
-performing an intersection operation between solid instances and determining if the resulting mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
+in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user. It does this by
+performing an intersection operation between solid mesh instances and determining if the resulting mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
 overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters
@@
 waste in large amounts of cluster CPU time if small overlaps are present in the final MCRT simulation. This algorithm clearly favours geometry
-descriptions which have a high degree of logical volume reuse, however this is also true of Geant4 as a whole, so the user will likely be inclined to design along such lines regardless.
+descriptions which have a high degree of logical volume reuse, which this is also true of Geant4 as a whole.
 Due to the discrete nature of triangular meshes it is not possible to have perfect detection
-of overlaps, especially when curved surfaces are considered, and in some rare
+of overlaps, especially when curved surfaces are considered. In some rare
 cases either overlaps maybe missed, or spurious overlaps maybe reported.  However, the density of the meshes
-created for the solids is controllabe by the user, meaning that the user
-can opt for more precise overlap checking at the cost of greater
-computation time.  In general, the overlap detection algorithm can
-present the potential overlaps quickly and easily to the user, thus
-significantly aiding the design process.
+created for the solids is controllable by the user, so the user can opt for more precise overlap checking at the cost of greater computation time.  
+In general, the overlap detection algorithm can present the potential overlaps quickly and easily to the user, so significantly aid the geometry 
+debugging process.
 
@@
 
-# physical volume vistualisation attributes
+# physical volume visualization attributes
 bp1.visOptions.color = (1,0,0)
@@
 example given in Listing~\ref{lst:pythonRapidModelling} and Figure~\ref{fig:rapidModellingExample}
-is rather trivial, a significantly more complex example is shown in Figure~\ref{fig:gdml-flair}.
+is rather trivial. A significantly more complex example is shown in Figure~\ref{fig:gdml-flair}.
 
@@
 to GDML involves first evaluating each region with very large \pyinline{Tub},
-\pyinline{EllipticalTube} and \pyinline{Box} instances (by default
-\SI{50}{\km} in length), such that they are effectively infinite for most
+\pyinline{EllipticalTube} and \pyinline{Box} instances (user adjustable but default
+\SI{50}{\km} in length, ), such that they are effectively infinite for most
 reasonable use cases.  \PYGEOMETRY{}'s CSG meshing is then used to generate
@@
 set of nested FLUKA materials to GDML materials is then
-straight forwards as the two formats are similarly expressive.
+straightforward as the two formats are similarly expressive.
 
@@
 algorithms for bridging FLUKA with GDML covers a very broad range of
-geometries, however a number of possible improvements remain for the
+geometries. However a number of possible improvements remain for the
 future.
@@
 to primitive FLUKA bodies.  This ensures that expanding to the DNF is
-computationally tractable, and in doing do FLUKA's tracking will be faster.
+computationally tractable, and in doing so FLUKA's tracking will be faster.
 This is not a drastic constraint on the conversion functionality, however,
@@
 body (possibly of a different type) without any transform. A simple example
-of this is the XYP and PLA, it is simple to transform an XYP into a PLA
+of this is the XYP and PLA. It is simple to transform an XYP into a PLA
 with an appropriate rotation. This {\em normal form} can be used to test
@@
 dictionaries so need to be replaced by using \pyinline{relabelModel}.
-CAD models might also have a hierarchy of parts and assemblies, these are
+CAD models might also have a hierarchy of parts and assemblies. These are
 converted without this structure by using \pyinline{convertFlat}.
@@
 
-An example geometry representing a dipole electromagnet, consisting of three parts was created in Autodesk Fusion 360
-and saved as a STEP file, the \PYGEOMETRY{}-produced output is shown in Figure~\ref{fig:cad-gdml}.
+An example geometry representing a dipole electromagnet consisting of three parts was created in a commercial CAD  package (Autodesk Fusion 360)
+and saved as a STEP file. The \PYGEOMETRY{}-produced output is shown in Figure~\ref{fig:cad-gdml}.
 
@@
 \PYGEOMETRY{} is designed to be as flexible as possible and offer the user a wide range of usage styles, input files
-and workflows. A fictitious beamline was created to demonstrate the capabilities of \PYGEOMETRY, this creates a composite
+and workflows. A fictitious beamline was created to demonstrate the capabilities of \PYGEOMETRY. This creates a composite
 \emph{scene} which consists of geometry sources from the different formats described in this paper. The beamline consists of a vacuum chamber
 (modelled in \PYGEOMETRY{}), a vacuum gate valve (STL from the manufacturer), a triplet of quadrupole magnets (exported to GDML
-from BDSIM), a sector bend dipole electromagnet (created in Autodesk Fusion 360) and finally a Faraday cup (FLUKA geometry designed in
+from BDSIM), a sector bend dipole electromagnet (created in a commercial CAD package) and finally a Faraday cup (FLUKA geometry designed in
 flair). Each different file is loaded using the appropriate \PYGEOMETRY{} \pyinline{Reader} class and then placed as a physical volume. The final composite
@@
 The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
-the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be
+the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry, is converted to GDML but can be
 safely removed. Examples of other workflows or geometry manipulation processes can be found in
@@
 Users should be aware of issues with \PYGEOMETRY{}. The conversions between CAD/STL, GDML, and FLUKA
-cannot be considered bidirectional. For example, Geant4 tessellated solids cannot be converted easily to FLUKA which does not
+cannot be considered bidirectional. For example, Geant4 tessellated solids cannot be converted easily to FLUKA, which does not
 have a convenient way of representing this geometry. In general a user would be unwise to attempt to convert a very large
@@
 modelling and inclusion of the geometry into an existing Geant4 application. This is not
-implemented in the current version but could be relatively quickly implemented for users that
+implemented in the current version but could be relatively quickly implemented for users who
 require this functionality. At present \PYGEOMETRY{} supports reading and writing
@@
 simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in
-optical photon based particle physics detectors. ParaView/VTK are becoming standard software for 
+optical photon based particle physics detectors. VTK/Paraview is becoming standard software for 
 complex 3D visualisation and the ability to write geometry to formats readily loaded and manipulated 
